### 2020-01-09 analysis/OEDcheck.Rmd
initial analysis of new human and initial model choices

---
title: "curiobaby_drop OED"
author: "George Kachergis"
date: "1/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
require(tidyverse)
```

## Load data

```{r, load-data}
dirs = list.files("agent-data")
d = data.frame()
for(dir in dirs) {
  filenames <- list.files(paste("agent-data",dir,sep='/'), full.names=TRUE)
  for(f in filenames) {
    tmp <- read.csv(f, header=T)
    d = rbind(d, tmp)
  }
}
```

`r nrow(d)` simulations with `r length(unique(d$dropped_objects))` unique dropped objects, of which we only used a subset of 9 for our behavioral experiments. We filter the simulations with undesired objects (sphere, cylinder, and cube).

```{r, count-unique-subsets}
names(d) # collision_count

hash_cols <- function(dat, cols) {
  shapes = c("Bowl", "Cylinder", "Cone", "Cube", "Dumbbell", "Octahedron", 
             "Pentagon", "Pipe", "Pyramid", "Ring", "Sphere", "TriangularPrism")
  for(i in 1:length(cols)) {
    dat[,cols[i]] = as.numeric(factor(dat[,cols[i]], levels=shapes)) #* 10^(i-1)
  }
  for(r in 1:nrow(dat)) {
    dat[r,cols] = sort(dat[,cols])
  }
  for(i in 1:length(cols)) {
    dat[,cols[i]] = dat[,cols[i]] * 10^(i-1)
  }
  hash = rowSums(dat[,cols])
  return(hash)
}

unwanted = c("Sphere","Cylinder","Cube")

d$drop_set = hash_cols(d, 8:10)
d$ground_set = hash_cols(d, 5:7)

df <- d %>% 
  filter(
    !ground_object_1 %in% unwanted,
    !ground_object_2 %in% unwanted,
    !ground_object_3 %in% unwanted,
    !available_drop_object_1 %in% unwanted,
    !available_drop_object_2 %in% unwanted,
    !available_drop_object_3 %in% unwanted
  )

length(unique(d$drop_set)) # 285 unique drop sets...
length(unique(d$ground_set)) # 285 unique ground sets..

#d = subset(d, episode>299) # Michael says first 300 are warm-up off-policy
d = read_csv("agent/20191203-084115/agent_0.csv") # most recent = trained dynamics model

# selected drop object is in collision_object_1 or _2, so target is case where dropped_object!=collision_object
d <- d %>% mutate(
  collision_object_1 = ifelse(collision_object_1=="None", NA, collision_object_1),
  collision_object_2 = ifelse(collision_object_2=="None", NA, collision_object_2),
  target = ifelse(collision_object_1==dropped_object, collision_object_2, collision_object_1)
  )

```

## Drop Preferences

```{r}

drops = sort(table(d$dropped_object), decr=T) # 13 objects

round(drops / sum(drops), 2)

# should normalize by available_drop_objects_1 _2 and _3
```

Some changing preference in drop objects: cube, pentagon, torus, and cone > octahedron and bowl
Thirteen objects here, but we've only printed 9 (though could add a sphere easily, at least)

## Target Preferences

Are objects roughly equally available as targets?

```{r}
all_ground = c(d$ground_object_1, d$ground_object_2, d$ground_object_3)
sort(round(table(all_ground) / sum(table(all_ground)), 2), decr=T)
```

Roughly...

```{r}
# sometimes collision_object_1 == collision_object_2 == None ?
targ = sort(table(d$target), decr=T)
round(targ / sum(targ), 2)
```

Collision count:
```{r}
round(table(d$collision_count) / sum(table(d$collision_count)), 2)
```

### 2020-01-09 analysis/analysis.R

@@ -1,0 +1,92 @@
+require(here)
+require(tidyverse)
+require(tidyboot)
+
+hdp = read.csv2("human-data/curiobaby_drop-data - drop pilot.csv", sep=',', header=T)
+hd = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
+
+length(unique(hdp$SID)) # 8
+length(unique(hd$SID)) # 42
+
+cols = intersect(names(hdp), names(hd))
+
+hum = rbind(hdp[,cols], hd[,cols]) # 609
+hum = subset(hum, Exclude!="Y") # 577 trials
+
+length(unique(hum$SID)) # 49 subjects
+
+md <- hum %>% group_by(SID) %>% summarise(max=max(Trial))
+
+
+hum$DropChoice = as.character(hum$DropChoice)
+hum$DropLocation = as.character(hum$DropLocation)
+
+hum$Age = as.numeric(as.character(hum$Age))
+
+
+ch_tr <- hum %>% 
+  group_by(Trial, DropChoice) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n)) %>%
+  filter(Trial < 13) # 1 incorrectly-coded trial - fixing
+  #group_by(Trial, DropChoice) %>% 
+  #tidyboot_mean(freq) 
+
+ch_tr$DropChoice <- as.factor(ch_tr$DropChoice)
+g <- ggplot(ch_tr, aes(x=Trial, y=freq, shape=DropChoice, color=DropChoice, size=n)) + geom_point(alpha=.8) +
+  scale_shape_manual(values=10:19) +
+  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Trial") + ylab("Drop Choice") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few()
+ggsave("drop_choice_by_trial.pdf", width=4.5, height=4.5)
+
+loc_tr <- hum %>% group_by(Trial, DropLocation) %>% 
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n)) %>%
+  filter(Trial < 13)
+
+g <- ggplot(loc_tr, aes(x=Trial, y=freq, shape=DropLocation, color=DropLocation, size=n)) + geom_point(alpha=.8) + 
+  xlab("Trial") + ylab("Drop Location") +
+  scale_shape_manual(values=10:22) +
+  langcog::scale_fill_solarized() + ggthemes::theme_few()
[…]

### 2020-01-14 paper/paper.Rmd
starting outline

---
title: "Modeling children's intrinsically-motivated curiosity about object interactions"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

abstract: >
    Although the question of what inspires a child's curiosity is difficult to determine,
    it's generally agreed that curiosity indicates awareness of a knowledge gap that the 
    learner is interested in filling. A promising approach to teasing apart

keywords: >
    curiosity; novel objects; object interactions; intuitive physics

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
```

```{r, load-data}
raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
hum = subset(raw, Exclude!="Y") # 577 trials

s_tr <- hum %>% group_by(SID, Age_Group) %>% summarise(max=max(Trial)) %>% arrange(max)
age = table(s_tr$Age_Group)
```

# Introduction

Whence intrinsically-motivated curiosity?
Novelty, opportunity for learning, etc.

Intuitive physics, play..

Best way to test is to create models instantiating different curiosity policies and then compare model and human behavior.

# Experiment

## Method

### Participants
Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
Exclusions were made based on...
After exclusions, results from `r length(hum$SID)` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.

### Materials

### Procedure

## Results

# Model

## Baseline Curiosity Policy

## Antagonistic Curiosity Policy

## Results

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## Comparison with Children

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Discussion

# Acknowledgements

This work was funded by HAI seed grant #. 
We thank X and Y for helpful comments.

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2020-01-14 analysis/analysis.R

@@ -2,20 +2,20 @@ require(here)
 require(tidyverse)
 require(tidyboot)
 
-hdp = read.csv2("human-data/curiobaby_drop-data - drop pilot.csv", sep=',', header=T)
+#hdp = read.csv2("human-data/curiobaby_drop-data - drop pilot.csv", sep=',', header=T)
 hd = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
 
-length(unique(hdp$SID)) # 8
-length(unique(hd$SID)) # 42
+#length(unique(hdp$SID)) # 8 subjects
+length(unique(hd$SID)) # 53
 
-cols = intersect(names(hdp), names(hd))
+#cols = intersect(names(hdp), names(hd))
+#hum = rbind(hdp[,cols], hd[,cols]) # 609
 
-hum = rbind(hdp[,cols], hd[,cols]) # 609
-hum = subset(hum, Exclude!="Y") # 577 trials
+hum = subset(hd, Exclude!="Y") # 577 trials
 
-length(unique(hum$SID)) # 49 subjects
+length(unique(hum$SID)) # 51 subjects
 
-md <- hum %>% group_by(SID) %>% summarise(max=max(Trial))
+md <- hum %>% group_by(SID) %>% summarise(max=max(Trial)) %>% arrange(max)
 
 
 hum$DropChoice = as.character(hum$DropChoice)

### 2020-01-15 paper/paper.Rmd
some refs and basic outline

@@
 ---
-title: "Modeling children's intrinsically-motivated curiosity about object interactions"
+#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
+title: "What if you drop that? Modeling children's curiosity about physical interactions"
 bibliography: library.bib
@@
 
+the gap: major outstanding issue in the research on curiosity and exploratory play is the functional form of the intrinsic motivation
+
+gold standard would be direct comparison of human and AI agents, but human behavior is so wide-ranging
+
+we propose a new paradigm that enables
+
+paragraph
+
 Whence intrinsically-motivated curiosity?
@@
 Best way to test is to create models instantiating different curiosity policies and then compare model and human behavior.
+
+## Model subsection first
+
+- or joint paradigm section
+- developmental data collection
+- model r
+
+- simple statistical test (per drop / target set): 
+chisq.test 
+Observed vs Expected
 

### 2020-01-15 analysis/analysis.R

@@ -3,15 +3,26 @@ require(tidyverse)
 require(tidyboot)
 
 #hdp = read.csv2("human-data/curiobaby_drop-data - drop pilot.csv", sep=',', header=T)
-hd = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
+raw = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
+
+# ab = cone, octahedron, pipe
+# ac = bowl, dumbbell, pentagon
+# ba = pyramid, torus, trig prism
+# bc = bowl, dumbbell, pentagon
+# ca = pyramid, torus, trig prism
+# cb = cone, octahedron, pipe
+
+# a = pyramid, torus, trig prism
+# b = cone, octahedron, pipe
+# c = bowl, dumbbell, pentagon
 
 #length(unique(hdp$SID)) # 8 subjects
-length(unique(hd$SID)) # 53
+length(unique(raw$SID)) # 53
 
 #cols = intersect(names(hdp), names(hd))
 #hum = rbind(hdp[,cols], hd[,cols]) # 609
 
-hum = subset(hd, Exclude!="Y") # 577 trials
+hum = subset(raw, Exclude!="Y") # 577 trials
 
 length(unique(hum$SID)) # 51 subjects
 
@@ -23,6 +34,18 @@ hum$DropLocation = as.character(hum$DropLocation)
 
 hum$Age = as.numeric(as.character(hum$Age))
 
+ch_cond <- hum %>% 
+  group_by(StimSet, DropChoice) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n)) 
+
+ch_cond$DropChoice <- as.factor(ch_cond$DropChoice)
+g <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice, size=n)) + geom_point(alpha=.8) +
+  scale_shape_manual(values=10:19) +
+  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Stimulus Set") + ylab("Drop Choice") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few()
+ggsave("drop_choice_by_trial.pdf", width=4.5, height=4.5)
 
 ch_tr <- hum %>% 
   group_by(Trial, DropChoice) %>%

### 2020-01-15 paper/paper.Rmd
add header from HAI proposal

--- 2020-01-14 paper/paper.Rmd
@@
 # Introduction
+
+Within the first two years of life, human infants develop a remarkable suite of exploratory behaviors — they begin to direct their own movement through their environ- ment, they can shift their attention to events they find most interesting, and they interact with objects in complex, creative ways [2, 6, 8, 9, 23].
+This ability to playfully explore and (re)structure their environment sets infants apart from even the most advanced robots today, which must be taught what to do in every scenario.
+The goal of this proposal is to develop computationally pre- cise models of exploration and learning that mirror the trajectory of human infant development.
+Our ongoing strategy is to combine approaches from artificial intelligence, computational cognitive science, and developmental psychology.
 

### 2020-01-15 analysis/OEDcheck.Rmd

@@
   for(f in filenames) {
-    tmp <- read.csv(f, header=T)
+    #tmp <- read.csv(f, header=T)
+    tmp <- read.table(f, sep=',', header=T, stringsAsFactors = F)
     d = rbind(d, tmp)
@@
   for(r in 1:nrow(dat)) {
-    dat[r,cols] = sort(dat[,cols])
+    dat[r,cols] = sort(dat[r,cols])
   }
@@
     !available_drop_object_3 %in% unwanted
-  )
+  ) # 3200 left
 
@@
 length(unique(d$ground_set)) # 285 unique ground sets..
+
+A = c("Pyramid", "Torus", "TriangularPrism")
+B = c("Cone", "Octahedron", "Pipe")
+C = c("Bowl", "Dumbbell", "Pentagon")
+d$DropSet = NA
+for(r in 1:nrow(d)) {
+  model_drop_objs = d[r,paste0("available_drop_object_", 1:3)]
+  d[r,]$DropSet = ifelse(setequal(model_drop_objs, A), "A", 
+                    ifelse(setequal(model_drop_objs, B), "B",
+                      ifelse(setequal(model_drop_objs, C), "C", NA)))
+}
+
+xp = na.omit(d)
 

### 2020-01-15 paper/paper.Rmd
some figures

--- 2020-01-15 paper/paper.Rmd
@@
 #title: "Modeling children's intrinsically-motivated curiosity about object interactions"
+#title: "Drop it like it's hot: Modeling children's curiosity about physical interactions"
+#title: "A drop in the bucket: Modeling children's curiosity about physical interactions"
 title: "What if you drop that? Modeling children's curiosity about physical interactions"
@@
 ```{r, load-data}
-raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
-hum = subset(raw, Exclude!="Y") # 577 trials
+raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors=F)
+hum = subset(raw, Exclude!="Y")
+
+hum = hum[-which(hum$StimSet=="bc" & hum$DropChoice=="bowl and dumbbell"),] # chose two - exclude
 
@@
 Exclusions were made based on...
-After exclusions, results from `r length(hum$SID)` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.
+After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.
 
 ### Materials
+
+```{r object-sets}
+shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism")
+
+a = c("pyramid", "torus", "trig prism")
+b = c("cone", "octahedron", "pipe")
+c = c("bowl", "dumbbell", "pentagon")
+```
 
@@
 
-```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns.
-And the caption text is limited to 0.8 of the width of the document."}
-img <- png::readPNG("figs/walrus.png")
-grid::grid.raster(img)
+We first examine children's choice of drop objects and target objects to see if children had any preference for particular objects.
+
+```{r drop-choice, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
+ch_cond <- hum %>% 
+  group_by(StimSet, DropChoice) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
+ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
+  geom_point(alpha=.8) +
+  scale_shape_manual(values=10:19) +
+  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,.66) + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
+  geom_hline(yintercept=.33, lty='dashed')
+```
+
+```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
+hum$Target = hum$DropLocation
+ch_cond <- hum %>% 
+  filter(Target!="outside") %>%
+  group_by(StimSet, Target) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
+ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
+  geom_point(alpha=.8) +
+  scale_shape_manual(values=10:20) +
+  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Stimulus Set") + ylab("Rate of Target Object Choice") + ylim(0,.66) + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
+  geom_hline(yintercept=.33, lty='dashed')
+```
+
+```{r target-space, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
+
+hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)
+
+ch_cond <- hum %>% 
+  filter(is.element(TargetSpace, shapes)) %>%
+  group_by(StimSet, TargetSpace) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ch_cond$TargetSpace <- factor(ch_cond$TargetSpace, levels = shapes)
+ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
+  geom_point(alpha=.8) +
+  scale_shape_manual(values=10:19) +
+  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Stimulus Set") + ylab("Rate of Target Location Choice") + ylim(0,.66) + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
+  geom_hline(yintercept=.33, lty='dashed')
 ```
@@
 ## Comparison with Children
-
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
-
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
-
-You can use the xtable function in the xtable package.
-
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
-
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                       caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
 

### 2020-01-15 analysis/analysis.R

@@ -3,7 +3,7 @@ require(tidyverse)
 require(tidyboot)
 
 #hdp = read.csv2("human-data/curiobaby_drop-data - drop pilot.csv", sep=',', header=T)
-raw = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T)
+raw = read.csv2("human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors = F)
 
 # ab = cone, octahedron, pipe
 # ac = bowl, dumbbell, pentagon
@@ -32,7 +32,7 @@ md <- hum %>% group_by(SID) %>% summarise(max=max(Trial)) %>% arrange(max)
 hum$DropChoice = as.character(hum$DropChoice)
 hum$DropLocation = as.character(hum$DropLocation)
 
-hum$Age = as.numeric(as.character(hum$Age))
+hum$Age_Group = as.numeric(hum$Age_Group)
 
 ch_cond <- hum %>% 
   group_by(StimSet, DropChoice) %>%
@@ -45,7 +45,6 @@ g <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice, 
   #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
   xlab("Stimulus Set") + ylab("Drop Choice") +
   langcog::scale_fill_solarized() + ggthemes::theme_few()
-ggsave("drop_choice_by_trial.pdf", width=4.5, height=4.5)
 
 ch_tr <- hum %>% 
   group_by(Trial, DropChoice) %>%

### 2020-01-15 paper/paper.Rmd
intro and results drafted

--- 2020-01-15 paper/paper.Rmd
@@
 output: cogsci2016::cogsci_paper
+#    includes:
+#      in_header: preamble.tex
 #final-submission: \cogscifinalcopy
@@
 
-the gap: major outstanding issue in the research on curiosity and exploratory play is the functional form of the intrinsic motivation
+Curiosity is a fundamental part of our motivation, driving everyday behaviors that we spend a surprising amount of time pursuing, from browsing the internet to reading novels, watching the news, and many other forms of information seeking.
+Curiosity is so strongly linked to learning that William James (1899) considered it to be "the impulse towards better cognition".
+Researchers have credited curiosity for inspiring behaviors ranging from exploration and play to latent learning and neophilia.
+However, there is a major outstanding difficulty in research on curiosity: there is no integrative theory of the mechanisms and basis for curiosity.
+What pairings of stimuli and knowledge states inspire curiosity? 
+How does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
 
-gold standard would be direct comparison of human and AI agents, but human behavior is so wide-ranging
+Although several theories of curiosity (surveyed briefly below) partially address these issues, a gold standard for testing these theories would require a fully-instantiated theory of curiosity in an artificial agent whose behavior can be directly compared to that of humans.
+However, a further difficulty of this approach is selecting a task that adequately captures the general nature of curiosity: curiosity-driven human behavior is so wide-ranging that it is difficult to systematically compare to presently limited artificial agents.
+In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing a variety of forms of curiosity.
 
-we propose a new paradigm that enables
-
-paragraph
+## Theories of Curiosity
 
@@
 
-Intuitive physics, play..
+## Related Behavioral Work
 
-Best way to test is to create models instantiating different curiosity policies and then compare model and human behavior.
+Intuitive physics, play
 
-## Model subsection first
+## Model subsection first?
 
-- or joint paradigm section
-- developmental data collection
-- model r
-
-- simple statistical test (per drop / target set): 
-chisq.test 
-Observed vs Expected
+...or joint paradigm section, and then developmental data collection, model description and comparison
 
@@
 Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
-Exclusions were made based on...
+Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
 After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.
@@
 
+Stimuli included 3D-printed objects produced using Blender modeling software. 
+The 9 stimuli objects were bowl, cone, dumbbell, octahedron, pentagon, pipe, pyramid, torus, and triangular prism. 
+The printed objects were all yellow, rigid plastic material and designed to fit comfortably in the child’s hand (dimension range: 3.8-10.1 cm).
+
+The set of 9 objects were divided into 3 subsets (A = {pyramid, torus, triangular prism}, B = {cone, octahedron, pipe}, and C = {bowl, dumbbell, pentagon}). 
+These subsets served as sets (A, B, C) of target/drop objects in six successive blocks of 2 trials, for a total of 12 trials. 
+For example, in Order 1, in the first block of 2 trials, set A served as the target objects from which the child chose to drop on the target objects (set B).
+
+The target:drop block sequence for Order 1 was A:B, B:C, C:A, A:C, B:A, C:B.
+Sequence for Order 2 (reverse of Order 1) was C:B, B:A, A:C, C:A, B:C, A:B.
+Participants were assigned to condition in counterbalanced order.
+
 ### Procedure
+
+After the parent provided informed consent, children were assigned to Order 1 or Order 2. Participants were assigned to condition in counterbalanced order.
+
+We introduced children to a set of 3D-printed toy objects ("blocks"). 
+The child played a game where they could pick which of three blocks to drop in a bin containing three other blocks, to see what happens. 
+We then swapped target/drop blocks, based on assigned order sequence, and asked the child to do the same selection and dropping a dozen times. 
+Finally, we asked the child to build a "cool" tower with any of the toy blocks for about one minute.
+
+Based on piloting, we estimated the activity would would only require five minutes to complete. 
+In both conditions, a video camera was used to record the play session from an angle above the bin, to show child's block selection and drop location as well as child's completed tower. 
+After child notified the researcher that they were finished building their tower, the session was completed and camera was turned off.
+
+### Drop Coding Procedure
+
+Each session's video was manually coded for object drop choice and drop location.
+Drop choice is defined as the child's single selection of three drop objects to drop into the bin containing three different objects.
+The bin is divided into three quadrants of equal area. 
+Each target object resides in one of these three areas. 
+Drop location was defined as the site of collision of drop object at the base of the bin. 
+Drop locations include either i) direct collision with one of three target objects, ii) collision in an empty space surrounding select target object, or iii) outside the bin.
+
+If drop object collided with empty space, we recorded which target object quadrant it landed. 
+We also recorded events where drop object bounced from empty space or a target object then collided with other target object(s). 
+Number of collisions and with which target(s) was also coded.
+
+Trials were excluded if child i) dropped object outside of the bin, ii) touched target object(s) prior to a drop, iii) dropped object during set change, iv) selected more than one object to drop, or iv) dropped (or threw) object from too high (>1.5 m).
+Trials were also excluded if the experimenter made a mistake (e.g., used the wrong stimulus set or repeated a trial more than twice).
 
@@
 
-# Model
+```{r chance-comparison}
 
-## Baseline Curiosity Policy
+report_chisq <- function(X) {
+  # e.g. X^2 (2, N = 88) = 2.1, p = .35
+  pval = round(X$p.value, 3)
+  if(pval==0) { 
+    pval = ", p<.001" 
+  } else {
+    pval = paste0(", p=",pval)
+  }
+  return(paste0("($X^2$(", X$parameter, ", N=", sum(X$expected), ") = ", round(X$statistic,2), pval, ")"))
+}
 
-## Antagonistic Curiosity Policy
+# see if children's choices (per subset) are random
+drop_ch = table(hum$StimSet, hum$DropChoice)
+# chisq.test(rbind(colSums(drop_ch[,a]), rep(sum(drop_ch[,a]/3), 3)) )
 
-## Results
+Xa_drop = chisq.test( colSums(drop_ch[,a]) ) 
+Xb_drop = chisq.test( colSums(drop_ch[,b]) )
+Xc_drop = chisq.test( colSums(drop_ch[,c]) )
 
-We first examine children's choice of drop objects and target objects to see if children had any preference for particular objects.
+target_ch = table(hum$StimSet, hum$DropLocation)
+
+Xa_targ = chisq.test( colSums(target_ch[,a]) ) # n.s.
+Xb_targ = chisq.test( colSums(target_ch[,b]) ) # n.s.
+Xc_targ = chisq.test( colSums(target_ch[,c]) ) # n.s.
+
+```
+
+We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
+We used a chi-square test of independence on children's choices (drop and target) from each set of objects (A, B, C).
+Children's drop choices from set A significantly differed from chance `r report_chisq(Xa_drop)`.
+Children's drop choices from set B also significantly differed from chance `r report_chisq(Xb_drop)`.
+Children's drop choices from set C did not significantly differ from chance `r report_chisq(Xc_drop)`.
+The 
+Of all the drops, many
+Children's target choices did not significantly differ from chance for set A `r report_chisq(Xa_targ)`, B `r report_chisq(Xb_targ)`, or C `r report_chisq(Xc_targ)`.
+
+```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+get_table_string <- function(tableX, set) {
+  tt = sort(colSums(tableX[,set]))
+  tstr = paste(paste0(names(tt), " (", tt, "),"), collapse=' ')
+  tstr = gsub('.{1}$', '', tstr)
+  return(tstr)
+}
+dA = get_table_string(drop_ch, a)
+dB = get_table_string(drop_ch, b)
+dC = get_table_string(drop_ch, c)
+
+tA = get_table_string(target_ch, a)
+tB = get_table_string(target_ch, b)
+tC = get_table_string(target_ch, c)
+
+tabl <- paste0("
+| Set |  Drop Object (N) | Target Object (N) |
+|-----|:----------------:|-----------:|
+|  A  | ", dA,"   | ", tA," |
+|  B  | ", dB,"   | ", tB," |
+|  C  | ", dC,"   | ", tC," |
+")
+#cat(tabl)
+
+#tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
+#                       caption = "This table prints across one column.")
+#print(tab1, type="latex", comment = F, table.placement = "H")
+```
 
@@
 
+# Model
+
+## Baseline Curiosity Policy
+
+## Antagonistic Curiosity Policy
+
+## Results
+
 ## Comparison with Children

### 2020-01-16 paper/paper.Rmd
adding figures

@@
 #title: "Drop it like it's hot: Modeling children's curiosity about physical interactions"
-#title: "A drop in the bucket: Modeling children's curiosity about physical interactions"
+#title: "A drop in the bucket: Progress towards modeling children's curiosity about physical interactions"
 title: "What if you drop that? Modeling children's curiosity about physical interactions"
@@
 However, a further difficulty of this approach is selecting a task that adequately captures the general nature of curiosity: curiosity-driven human behavior is so wide-ranging that it is difficult to systematically compare to presently limited artificial agents.
+The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model -- an inviting playground, a surprisingly complex device, or a novel research question. 
 In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing a variety of forms of curiosity.
@@
 
-Stimuli included 3D-printed objects produced using Blender modeling software. 
-The 9 stimuli objects were bowl, cone, dumbbell, octahedron, pentagon, pipe, pyramid, torus, and triangular prism. 
+Stimuli were 3D-printed plastic objects produced using Blender 3D-modeling software. 
+The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
 The printed objects were all yellow, rigid plastic material and designed to fit comfortably in the child’s hand (dimension range: 3.8-10.1 cm).
@@
 The set of 9 objects were divided into 3 subsets (A = {pyramid, torus, triangular prism}, B = {cone, octahedron, pipe}, and C = {bowl, dumbbell, pentagon}). 
-These subsets served as sets (A, B, C) of target/drop objects in six successive blocks of 2 trials, for a total of 12 trials. 
+These subsets served as sets (A, B, C) of target or drop objects in six successive blocks of 2 trials, making a total of 12 trials per participant.
 For example, in Order 1, in the first block of 2 trials, set A served as the target objects from which the child chose to drop on the target objects (set B).
+The target:drop block sequence for Order 1 was A:B, B:C, C:A, A:C, B:A, C:B.
+The sequence for Order 2 was the reverse of Order 1: C:B, B:A, A:C, C:A, B:C, A:B.
+Participants were assigned to condition in counterbalanced order.
 
-The target:drop block sequence for Order 1 was A:B, B:C, C:A, A:C, B:A, C:B.
-Sequence for Order 2 (reverse of Order 1) was C:B, B:A, A:C, C:A, B:C, A:B.
-Participants were assigned to condition in counterbalanced order.
+Target objects were placed in a circular bin (25 in diameter x 10 in height). 
+The bin was divided with tape into sections of equal area, and one target object from the appropriate set was placed in the center of each third. 
+Drop objects were presented to participants on a table at approximately eye level.
+
+```{r fig1-sets, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Sets of 3D objects used for dropping and as targets."}
+img <- png::readPNG("figs/drop_sets.png")
+grid::grid.raster(img)
+```
 
@@
 After the parent provided informed consent, children were assigned to Order 1 or Order 2. Participants were assigned to condition in counterbalanced order.
-
 We introduced children to a set of 3D-printed toy objects ("blocks"). 
 The child played a game where they could pick which of three blocks to drop in a bin containing three other blocks, to see what happens. 
+An example trial is illustrated in Figure 2.
 We then swapped target/drop blocks, based on assigned order sequence, and asked the child to do the same selection and dropping a dozen times. 
@@
 After child notified the researcher that they were finished building their tower, the session was completed and camera was turned off.
+
+```{r fig2-task, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial."}
+img <- png::readPNG("figs/DropTaskFigure.png")
+grid::grid.raster(img)
+```
 
@@
 
-Xa_drop = chisq.test( colSums(drop_ch[,a]) ) 
-Xb_drop = chisq.test( colSums(drop_ch[,b]) )
-Xc_drop = chisq.test( colSums(drop_ch[,c]) )
+Xa_drop = chisq.test( colSums(drop_ch[,a]) ) # p<.001
+Xb_drop = chisq.test( colSums(drop_ch[,b]) ) # p=.01
+Xc_drop = chisq.test( colSums(drop_ch[,c]) ) # p=.056
 
@@
 
-```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+```{r table1-drop, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
 get_table_string <- function(tableX, set) {
@@
 
-tabl <- paste0("
-| Set |  Drop Object (N) | Target Object (N) |
-|-----|:----------------:|-----------:|
-|  A  | ", dA,"   | ", tA," |
-|  B  | ", dB,"   | ", tB," |
-|  C  | ", dC,"   | ", tC," |
-")
-#cat(tabl)
-
+tabl <- tribble(~Set, ~`Drop Object (N)`, 
+                "A", dA,
+                "B", dB,
+                "C", dC)
+t1 <- xtable::xtable(tabl, caption="Children's drop object choices by set.")
 #tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
 #                       caption = "This table prints across one column.")
-#print(tab1, type="latex", comment = F, table.placement = "H")
+print(t1, type="latex", comment = F, table.placement = "H")
+```
+
+```{r table2-target, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+tabl2 <- tribble(~Set, ~`Target Object (N)`, 
+                "A", tA,
+                "B", tB,
+                "C", tC)
+t2 <- xtable::xtable(tabl2, caption="Children's target object choices by set.")
+#tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
+#                       caption = "This table prints across one column.")
+print(t2, type="latex", comment = F, table.placement = "H")
 ```

### 2020-01-17 paper/paper.Rmd
intro almost done

@@
 abstract: >
-    Although the question of what inspires a child's curiosity is difficult to determine,
-    it's generally agreed that curiosity indicates awareness of a knowledge gap that the 
-    learner is interested in filling. A promising approach to teasing apart
+     Curiosity is a fundamental driver of human behavior, and yet because of its open-ended nature 
+     and the wide variety of behaviors it inspires in different contexts, it is remarkably difficult 
+     to study in a laboratory context. A promising approach to developing and testing theories of 
+     curiosity is to instantiate them in artificial agents that are able to act and explore in a 
+     simulated environment, and then compare the behavior of these agents to humans exploring the 
+     same stimuli. Here we propose a new paradigm for examining curiosity about physical interact
 
@@
 Curiosity is a fundamental part of our motivation, driving everyday behaviors that we spend a surprising amount of time pursuing, from browsing the internet to reading novels, watching the news, and many other forms of information seeking.
-Curiosity is so strongly linked to learning that William James (1899) considered it to be "the impulse towards better cognition".
-Researchers have credited curiosity for inspiring behaviors ranging from exploration and play to latent learning and neophilia.
-However, there is a major outstanding difficulty in research on curiosity: there is no integrative theory of the mechanisms and basis for curiosity.
-What pairings of stimuli and knowledge states inspire curiosity? 
-How does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
+Curiosity is so strongly linked to learning that William James (1899) considered it to be "the impulse towards better cognition", a description that is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
+Taking this view of children [even infants: @Gopnik2009] as "little scientists", researchers have credited curiosity for inspiring behaviors ranging from novelty-seeking to exploration and play, and yet there is a major outstanding difficulty in curiosity research: there is no integrative theory of the mechanisms and basis for curiosity [@Kidd2015].
+What combinations of stimuli and knowledge states inspire curiosity? 
+By what mechanism does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
 
@@
 However, a further difficulty of this approach is selecting a task that adequately captures the general nature of curiosity: curiosity-driven human behavior is so wide-ranging that it is difficult to systematically compare to presently limited artificial agents.
+Behavioral investigations of children's exploratory play have often offered a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], but the real world offers many more degrees of freedom.
 The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model -- an inviting playground, a surprisingly complex device, or a novel research question. 
-In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing a variety of forms of curiosity.
+In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity.
+Below, we give a brief overview of theories of curiosity, relevant developmental empirical findings, and computational models instantiating curiosity.
 
@@
 
-Whence intrinsically-motivated curiosity?
-Novelty, opportunity for learning, etc.
+@Berlyne1954's influential theory of curiosity distinguished between perceptual curiosity, a desire to seek out novel stimuli (that decreases with familiarity), and epistemic curiosity, a desire to acquire knowledge.
+Berlyne additionally distinguished specific versus diversive curiosity, where the former is a drive for a particular piece of information, and the latter is a general motivation for stimulation.
+More recent views of curiosity further limit the definition to information-seeking that is intrinsically-motivated, not linked to any obvious external reward [@Loewenstein1994; @Oudeyer2007].
+However, it is often difficult for observers to determine whether any given decision is intrinsically- or extrinsically-motivated.
+Modern theories also hold that the function of curiosity is inspired by awareness of a knowledge gap, and functions to drive behaviors that will result in learning [@Loewenstein1994].
+Similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
+Although these theories give us some sense of which situations and knowledge states should engender curiosity, both the mechanism and how actions are selected
 
@@
 
-Intuitive physics, play
+Although the question of what inspires a child's curiosity is difficult to determine, it's generally agreed that curiosity indicates awareness of a knowledge gap that the learner is interested in filling [@Loewenstein1994].
+Even young infants exhibit a preference to attend to novel stimuli over more familiar stimuli [e.g., @Fantz1964], and when surprising events do occur it has been shown to stimulate infants' exploration and subsequent learning [@Stahl2015].
+Moreover, infants are sensitive to the level of complexity of stimuli, preferring to attend to those of intermediate complexity (rather than simple or overly-complex)--a bias which may help them optimize their information gain [@Kidd2012; @Kidd2014].
+As theorized [@Piaget1952], exploratory play has been shown to be an opportunity for young children to learn [e.g., generalization: @Sim2017, causal structure: @Schulz2007; @Gweon2014].
 
-## Model subsection first?
+One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects.
 
-...or joint paradigm section, and then developmental data collection, model description and comparison
+## Computational Models of Curiosity
+
+[Sentence on other approaches: @Oudeyer2013; @Schmidhuber2010]
+
+Building on prior work that showed deep neural networks are capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], we use and extend a framework for constructing intrinsically-motivated artificial agents introduced in @Haber2018learning, described in the following.
+
+Model description here?
+
+(maybe make the below a joint "Paradigm" section, then human behavior, model behavior and comparison)
 
@@
 Drop choice is defined as the child's single selection of three drop objects to drop into the bin containing three different objects.
-The bin is divided into three quadrants of equal area. 
+The bin is divided into three sections of equal area. 
 Each target object resides in one of these three areas. 
@@
 
-If drop object collided with empty space, we recorded which target object quadrant it landed. 
-We also recorded events where drop object bounced from empty space or a target object then collided with other target object(s). 
+If the dropped object collided with empty space, we recorded the target object it landed closest to. 
+We also recorded events where the dropped object bounced from empty space or a target object then collided with other target object(s). 
 Number of collisions and with which target(s) was also coded.
@@
 
+Figure 6 shows participants' mean proportion of unique objects dropped as a function of age.
+Children of all ages sampled approximately equal proportions of the objects for dropping--roughly 70%, which is close to the 75% that would be expected if they were selected by chance (9 unique object occurring across 12 trials).
+
+```{r unique-drop-objects, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion of unique objects selected by participants.
+Error bars show boostrapped 95\\% confidence intervals."}
+# 12 trials, 9 objects; random selection would be 9/12 = 75%...
+uniq_s <- hum %>% group_by(SID, Age_Group) %>%
+  summarise(DropObjs = n_distinct(DropChoice), N=n(), prop=DropObjs/N)
+
+uniq <- uniq_s %>% group_by(Age_Group) %>%
+  tidyboot_mean(prop)
+
+ggplot(uniq, aes(x=Age_Group, y=mean)) + geom_point() +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
+  xlab("Age (years)") + ylab("Unique Objects Chosen") + ylim(0,1) + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
+  geom_hline(yintercept=.75, lty='dashed')
+```
+
 # Model

### 2020-01-17 paper/paper.Rmd
more results

@@
      simulated environment, and then compare the behavior of these agents to humans exploring the 
-     same stimuli. Here we propose a new paradigm for examining curiosity about physical interact
+     same stimuli. Here we propose a new experimental paradigm for examining children's--and curious
+     AI agents'--curiosity about objects' physical interactions, using a task that is both open-ended
+     enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
+     comparisons. We compare the choices of 51 children (2-6 years of age) to those of agents implementing 
+     different types of curiosity, and find broad exploration, but also systematic preferences ...
 
@@
 require(tidyboot)
+library(apa) # for generating APA-style text to report statistical tests
+library(ggpubr)
 ```
@@
 
-[Sentence on other approaches: @Oudeyer2013; @Schmidhuber2010]
+[Sentence or two on other approaches, e.g. @Oudeyer2013; @Schmidhuber2010]
 
@@
 
-Model description here?
+(Model description or just teaser here?)
 
@@
 
-```{r fig1-sets, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Sets of 3D objects used for dropping and as targets."}
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Sets of 3D objects used for dropping and as targets."}
 img <- png::readPNG("figs/drop_sets.png")
@@
 
-```{r fig2-task, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial."}
+```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial in which the participant chose to drop the pyramid from set A on the pentagonal prism in the target set (B)."}
 img <- png::readPNG("figs/DropTaskFigure.png")
@@
 If the dropped object collided with empty space, we recorded the target object it landed closest to. 
-We also recorded events where the dropped object bounced from empty space or a target object then collided with other target object(s). 
-Number of collisions and with which target(s) was also coded.
+We also recorded events where the dropped object bounced from empty space or a target object then collided with other target object(s), including the number of collisions and identity of the target(s) hit.
 
-Trials were excluded if child i) dropped object outside of the bin, ii) touched target object(s) prior to a drop, iii) dropped object during set change, iv) selected more than one object to drop, or iv) dropped (or threw) object from too high (>1.5 m).
+Trials were excluded if the child i) dropped an object outside the bin, ii) touched target object(s) prior to a drop, iii) dropped an object during set change, iv) selected more than one object to drop, or iv) dropped (or threw) object from too high (>1.5 m).
 Trials were also excluded if the experimenter made a mistake (e.g., used the wrong stimulus set or repeated a trial more than twice).
@@
 ```{r chance-comparison}
+hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)
 
@@
 
+targetloc_ch = table(hum$StimSet, hum$TargetSpace)
+Xa_tloc = chisq.test( colSums(targetloc_ch[,a]) ) # n.s.
+Xb_tloc = chisq.test( colSums(targetloc_ch[,b]) ) # n.s.
+Xc_tloc = chisq.test( colSums(targetloc_ch[,c]) ) # n.s.
+
+# 'misses' by age
+space_age = table(subset(hum, DropLocation=="space")$Age_Group)
+all_age = table(hum$Age_Group)
+#Xmiss_age = chisq.test(space_age, p=all_age / sum(all_age)) # n.s.
+prop_space = sum(space_age) / sum(all_age)
+
+age_s <- hum %>% 
+  group_by(SID, Age_Exact) %>%
+  summarise(miss=sum(DropLocation=="space"), N=n()) %>%
+  mutate(prop_miss = miss / N)
+age_miss = cor.test(age_s$prop_miss, as.numeric(age_s$Age_Exact))
 ```
@@
 We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
-We used a chi-square test of independence on children's choices (drop and target) from each set of objects (A, B, C).
-Children's drop choices from set A significantly differed from chance `r report_chisq(Xa_drop)`.
-Children's drop choices from set B also significantly differed from chance `r report_chisq(Xb_drop)`.
-Children's drop choices from set C did not significantly differ from chance `r report_chisq(Xc_drop)`.
-The 
-Of all the drops, many
-Children's target choices did not significantly differ from chance for set A `r report_chisq(Xa_targ)`, B `r report_chisq(Xb_targ)`, or C `r report_chisq(Xc_targ)`.
+We used chi-square test of independence on participants' drop choices from each set of objects (A, B, C).
+Participants' drop choices from set A significantly differed from chance `r report_chisq(Xa_drop)`, as did drop choices from set B `r report_chisq(Xb_drop)`.
+Participants' drop choices from set C did not significantly differ from chance `r report_chisq(Xc_drop)`.
+Table 1 shows a summary of participants' choice of drop objects per set.
+It is apparent that from set A, participants preferentially chose to drop the torus rather than the triangular prism (trig prism) or pyramid. 
+For set B, children more often avoided the octahedron, and instead chose the pipe or cone.
+Set C showed more equal rates of drop choice, but the dumbbell was somewhat more popular than the pentagonal prism (pentagon).
+
+What objects did children target with their drops?
+First, we noted that children very often did not hit any target object: on `r round(prop_space, 2)*100`% of trials, participants' dropped over empty space.
+It is not possible to determine whether children intentionally missed the available target objects, or whether their misses were errors due to noise in fine motor control.
+If the misses were just due to poor motor control, one might expect the number of misses by age to decrease, as older children should have better motor control.
+However, there was no significant correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(age_miss, format="rmarkdown", print=F)`), which may suggest that dropping objects on empty space may be of interest to children of all ages, and not solely determined by a lack of fine motor control.
+Thus, we first analyze drops where participants' dropped objects directly hit the target objects.
+Chi-square tests of children's target collisions revealed that they did not significantly differ from chance for set A `r report_chisq(Xa_targ)`, B `r report_chisq(Xb_targ)`, or C `r report_chisq(Xc_targ)`.
+Table 2 shows a summary of participants' choice of target objects per set.
+
+Finally, we examine a more lenient analysis children's choice of target location (i.e., the identity of the closest target), regardless of whether there was a collision of drop and target objects.
+Chi-square tests of children's target collisions once more found that they did not significantly differ from chance for set A `r report_chisq(Xa_tloc)`, B `r report_chisq(Xb_tloc)`, or C `r report_chisq(Xc_tloc)`.
+Table 3 shows a summary of participants' choice of target locations per set.
+
+In summary, children showed some consistent preferences in their choice of objects to drop from each set, but no systematic preference for targeting particular objects.
+We now investigate whether there were interactions of drop objects and targets that children found particularly appealing. [ToDo: big chisq test?]
+
+Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects?
+What proportion of the objects were targeted?
 
@@
 
-tA = get_table_string(target_ch, a)
-tB = get_table_string(target_ch, b)
-tC = get_table_string(target_ch, c)
-
 tabl <- tribble(~Set, ~`Drop Object (N)`, 
@@
 ```{r table2-target, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+tA = get_table_string(target_ch, a)
+tB = get_table_string(target_ch, b)
+tC = get_table_string(target_ch, c)
+
 tabl2 <- tribble(~Set, ~`Target Object (N)`, 
@@
 t2 <- xtable::xtable(tabl2, caption="Children's target object choices by set.")
-#tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-#                       caption = "This table prints across one column.")
 print(t2, type="latex", comment = F, table.placement = "H")
+```
+
+```{r table3-targetloc, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+tA = get_table_string(targetloc_ch, a)
+tB = get_table_string(targetloc_ch, b)
+tC = get_table_string(targetloc_ch, c)
+
+tabl3 <- tribble(~Set, ~`Target Location (N)`, 
+                "A", tA,
+                "B", tB,
+                "C", tC)
+t3 <- xtable::xtable(tabl3, caption="Children's target location choices by set.")
+print(t3, type="latex", comment = F, table.placement = "H")
 ```
@@
 ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
-ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
+fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
   geom_point(alpha=.8) +
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  geom_hline(yintercept=.33, lty='dashed')
+  geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
+#print(fig_drop)
 ```
@@
 ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
-ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
+fig_targ_hit <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
   geom_point(alpha=.8) +
@@
   #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Stimulus Set") + ylab("Rate of Target Object Choice") + ylim(0,.66) + 
+  xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,.66) + 
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   geom_hline(yintercept=.33, lty='dashed')
+#print(fig_targ_hit)
 ```
@@
 ```{r target-space, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
-
-hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)
 
@@
 ch_cond$TargetSpace <- factor(ch_cond$TargetSpace, levels = shapes)
-ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
+fig_targ_space <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
   geom_point(alpha=.8) +
@@
   #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Stimulus Set") + ylab("Rate of Target Location Choice") + ylim(0,.66) + 
+  xlab("Stimulus Set") + ylab("Rate of Targeted Location") + ylim(0,.66) + 
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   geom_hline(yintercept=.33, lty='dashed')
+#print(fig_targ_space)
 ```
 
-Figure 6 shows participants' mean proportion of unique objects dropped as a function of age.
+```{r combined-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects 1) chosen as objects for dropping, 2) hit as targets, and 3) whose drop location was closest to a target object, as a function of target/drop set pairing."}
+
+ggarrange(fig_drop, fig_targ_hit, fig_targ_space, nrow=1, 
+          #labels = c("Drop Choice", "Targeted Object Hit", "Targeted Location"),
+          common.legend=T, legend="bottom")
+```
+
+Figure 4 shows participants' mean proportion of unique objects dropped as a function of age.
 Children of all ages sampled approximately equal proportions of the objects for dropping--roughly 70%, which is close to the 75% that would be expected if they were selected by chance (9 unique object occurring across 12 trials).

### 2020-01-20 paper/paper.Rmd
removing blank template

@@
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.
+After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.^[1]
+
+[1]: The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).
 

### 2020-01-21 paper/paper.Rmd
minor edits

@@
 ```{r, load-data}
+tower = read.csv2("../analysis/human-data/curiobaby_drop-data - cool tower.csv", sep=',', header=T, stringsAsFactors=F)
 raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors=F)
@@
 Similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
-Although these theories give us some sense of which situations and knowledge states should engender curiosity, both the mechanism and how actions are selected
+Although these theories give us some sense of which situations and knowledge states should engender curiosity, both the mechanism and how actions are selected are not fully specified.
 
@@
 
-[1]: The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).
+^[1]: The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).
 
@@
 
-Each session's video was manually coded for object drop choice and drop location.
-Drop choice is defined as the child's single selection of three drop objects to drop into the bin containing three different objects.
-The bin is divided into three sections of equal area. 
-Each target object resides in one of these three areas. 
-Drop location was defined as the site of collision of drop object at the base of the bin. 
-Drop locations include either i) direct collision with one of three target objects, ii) collision in an empty space surrounding select target object, or iii) outside the bin.
-
-If the dropped object collided with empty space, we recorded the target object it landed closest to. 
+Each session's video was manually coded for drop object choice and target location per trial.
+Drop choice was defined as the participant's selection of one of the three available drop set objects, to be dropped into the bin containing the set of the three potential target objects. 
+The bin was divided into three wedge-shaped sections of equal area, demarcated with a thin black line.
+One of the target set's objects was placed in the middle of each section of the bin. 
+Target location was defined as either i) the object the dropped object collided with, ii) a collision with empty space inside the bin, or iii) falling outside the bin.
+If the dropped object collided with empty space, we also recorded the target object it landed closest to. 
 We also recorded events where the dropped object bounced from empty space or a target object then collided with other target object(s), including the number of collisions and identity of the target(s) hit.
@@
 age_miss = cor.test(age_s$prop_miss, as.numeric(age_s$Age_Exact))
+
+# now check DropChoice x TargetLocation interactions
+dto = table(hum$DropChoice, hum$DropLocation)[,c(1:4,6:8,10:11)] # drop 'outside' and 'space'
+Xdto = chisq.test(dto)
+
 ```
@@
 
-```{r drop-choice, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
+```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
 ch_cond <- hum %>% 
@@
 
-```{r combined-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects 1) chosen as objects for dropping, 2) hit as targets, and 3) whose drop location was closest to a target object, as a function of target/drop set pairing."}
+```{r combined-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects 1) chosen as objects for dropping, 2) hit as targets (pink dots represent hitting empty space), and 3) whose drop location was closest to a target object, as a function of target/drop set pairing."}
 
@@
   geom_hline(yintercept=.75, lty='dashed')
+```
+
+```{r drop-by-target, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Heatmap of participants' drop object choices by target location."}
+ch_loc <- hum %>% filter(DropLocation!="outside" & DropLocation!="space") %>%
+  group_by(DropChoice, DropLocation) %>% 
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ggplot(ch_loc, aes(x=DropLocation, y=DropChoice)) + geom_tile(aes(fill=freq)) + 
+  scale_fill_gradient(low = "white", high = "steelblue") +
+  xlab("Target Location") + ylab("Drop Object") +
+  ggthemes::theme_few()
 ```

### 2020-01-22 paper/paper.Rmd
intro writing

@@
 Curiosity is so strongly linked to learning that William James (1899) considered it to be "the impulse towards better cognition", a description that is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
-Taking this view of children [even infants: @Gopnik2009] as "little scientists", researchers have credited curiosity for inspiring behaviors ranging from novelty-seeking to exploration and play, and yet there is a major outstanding difficulty in curiosity research: there is no integrative theory of the mechanisms and basis for curiosity [@Kidd2015].
+Taking this view of children [even infants: @Gopnik2009] as "little scientists", researchers have credited curiosity for inspiring behaviors ranging from novelty-seeking to exploration and play, and yet there is a major outstanding difficulty in curiosity research: there is no integrative theory of the mechanisms and basis for curiosity [@Kidd2015].\footnote{Following @Kidd2015 we adopt a broad definition of curiosity as any mechanism that guides an organism to gain new information.}
 What combinations of stimuli and knowledge states inspire curiosity? 
-By what mechanism does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
+By what mechanism(s) does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
 
@@
 In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity.
-Below, we give a brief overview of theories of curiosity, relevant developmental empirical findings, and computational models instantiating curiosity.
+Below, we give a brief overview of theories of curiosity, relevant developmental empirical findings, and computational models instantiating curiosity in agents that are able to interact with the world in realistic simulated 3D environments.
 
@@
 Similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
+One theory developed to explain the discrepancy between infants' frequent preference for novel stimuli [e.g., @Fantz1964], as well as their occasional preference for familiar stimuli (e.g., faces), is the idea that infants prefer to attend to stimuli that are "moderately discrepant", i.e.
+that are only somewhat different than the infants' mental representations [@Kinney1976].
+Thus, as infants gain experience with various classes of stimuli, they will seek increasingly complex stimuli as their mental representations become more sophisticated [@Dember1957].
 Although these theories give us some sense of which situations and knowledge states should engender curiosity, both the mechanism and how actions are selected are not fully specified.
@@
 Although the question of what inspires a child's curiosity is difficult to determine, it's generally agreed that curiosity indicates awareness of a knowledge gap that the learner is interested in filling [@Loewenstein1994].
-Even young infants exhibit a preference to attend to novel stimuli over more familiar stimuli [e.g., @Fantz1964], and when surprising events do occur it has been shown to stimulate infants' exploration and subsequent learning [@Stahl2015].
+Even young infants often exhibit a preference to attend to novel stimuli over more familiar stimuli [e.g., @Fantz1964], and when surprising physical events do occur (e.g., an object appearing to have passed through a wall) it has been shown to stimulate infants' exploration and subsequent learning [@Stahl2015].
 Moreover, infants are sensitive to the level of complexity of stimuli, preferring to attend to those of intermediate complexity (rather than simple or overly-complex)--a bias which may help them optimize their information gain [@Kidd2012; @Kidd2014].
@@
 One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects. 
+Many studies of young infants' reasoning about physical objects have focused on occlusion, containment, and covering events, using surprisal (indexed via looking time) as a measure of knowledge [@Baillargeon2007].
+A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
+Here, we investigate toddlers' choices in a more complex
 
@@
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.^[1]
-
-^[1]: The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).
+After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.\footnote{The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).}
 
@@
 c = c("bowl", "dumbbell", "pentagon")
+
+hum <- hum %>% 
+  mutate(DropSet=ifelse(StimSet %in% c("ba","ca"), "A", ifelse(StimSet %in% c("ab","cb"), "B", "C")),
+         TargetSet=ifelse(StimSet %in% c("ab","ac"), "A", ifelse(StimSet %in% c("ba","bc"), "B", "C")))
 ```
@@
 The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
-The printed objects were all yellow, rigid plastic material and designed to fit comfortably in the child’s hand (dimension range: 3.8-10.1 cm).
+The printed objects were all yellow, rigid plastic material and designed to fit comfortably in a child's hand (dimension range: 3.8-10.1 cm).
 
@@
 # now check DropChoice x TargetLocation interactions
-dto = table(hum$DropChoice, hum$DropLocation)[,c(1:4,6:8,10:11)] # drop 'outside' and 'space'
+# maybe we do chisq.test on particular combinations? e.g., for DropSet A and TargetSet B?
+dA = subset(hum, DropSet=="A" & TargetSet=="B")
+dto = table(dA$DropChoice, dA$DropLocation)[,1:3]
+#dto = table(hum$DropChoice, hum$DropLocation)[,c(1:4,6:8,10:11)] # drop 'outside' and 'space'
 Xdto = chisq.test(dto)

### 2020-01-23 paper/paper.Rmd
reworked intro with Judy's help

@@
 
-Curiosity is a fundamental part of our motivation, driving everyday behaviors that we spend a surprising amount of time pursuing, from browsing the internet to reading novels, watching the news, and many other forms of information seeking.
-Curiosity is so strongly linked to learning that William James (1899) considered it to be "the impulse towards better cognition", a description that is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
-Taking this view of children [even infants: @Gopnik2009] as "little scientists", researchers have credited curiosity for inspiring behaviors ranging from novelty-seeking to exploration and play, and yet there is a major outstanding difficulty in curiosity research: there is no integrative theory of the mechanisms and basis for curiosity [@Kidd2015].\footnote{Following @Kidd2015 we adopt a broad definition of curiosity as any mechanism that guides an organism to gain new information.}
-What combinations of stimuli and knowledge states inspire curiosity? 
-By what mechanism(s) does curiosity motivate and drive action selection, and influence subsequent learning and behavior?
+<!-- Curiosity is important... end with core question about what gives rise to curiosity. -->
+Curiosity is a key driver of everyday behaviors, from children's exploratory play with a new toy to adults browsing the internet, we spend a surprising amount of time actively pursuing information about our world.
+Curiosity may even serve as the impetus for all learning: William James (1899) considered it to be "the impulse towards better cognition", a belief that is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
+From this view, children and even infants [@Gopnik2009] can be seen as "little scientists" who use curiosity to select causal interventions that help them learn about the physical world.
+However, a major outstanding difficulty in curiosity research: there is no integrative, testable theory of the mechanisms and basis for curiosity [@Kidd2015].
+More concretely, what relationship between stimuli and a learner's knowledge states engender curiosity, and how does this motivate a learner's choice of actions?
 
-Although several theories of curiosity (surveyed briefly below) partially address these issues, a gold standard for testing these theories would require a fully-instantiated theory of curiosity in an artificial agent whose behavior can be directly compared to that of humans.
-However, a further difficulty of this approach is selecting a task that adequately captures the general nature of curiosity: curiosity-driven human behavior is so wide-ranging that it is difficult to systematically compare to presently limited artificial agents.
-Behavioral investigations of children's exploratory play have often offered a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], but the real world offers many more degrees of freedom.
-The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model -- an inviting playground, a surprisingly complex device, or a novel research question. 
+<!-- desiderata for advancing theories of curiosity -->
+
+A fully-specified, testable theory of curiosity would minimally require three components.
+First, it is necessary to have a precise mechanism specifying how stimuli inspire curiosity. 
+Although some early verbal theories of curiosity acknowledge that novel stimuli demand our (and other animals') attention [e.g., @Berlyne1954], borne out in empirical data [e.g., @Fantz1964], but modern theories hold that learners may prefer to attend to stimuli that are "moderately discrepant" in comparison to our mental representations [@Kinney1976].
+These theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as we gain experience with classes of stimuli our preferences will tend toward more complex stimuli as our mental representations mature [@Dember1957].
+Empirical work has verified that infants are sensitive to the level of complexity of stimuli and prefer to attend to stimuli of intermediate complexity [rather than simple or overly-complex; @Kidd2012; @Kidd2014].
+Thus, similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed, but defining the perceptual and knowledge-based representations and how they are compared is an open question.
+
+Second, a testable theory of curiosity requires a detailed measure of curious behavior that records which interventions learners select in order to gain information about the properties of objects and laws that govern the physical world.
+People's curiosity-driven behavior comes in such a variety of contexts and utilizing such a wide repertoire of actions that it is quite difficult to choose an appropriate paradigm, particularly because the places where curiosity is most manifest tend to be those open-ended environments that are hardest to model -- an inviting playground, a surprisingly complex device, or a novel research question.
+Past studies of infant's physical reasoning ability have used looking time to measure their knowledge about physical events, given that infant's attend longer to surprising events [e.g., objects appearing to pass through a wall; @Stahl2015].
+Behavioral investigations of older children's exploratory play have also used simple attention duration measures to measure curiosity, for example offering children a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], and additionally tally the number of discovered functions.
+However, these attention and discovery measures do not quantify the overt actions that children choose, and typically do not offer more than one or two target objects for exploration.
+
+A third desiderata for a testable theory of curiosity is a linking function for evaluating the correspondence between the predictions of our computational theory and the observed patterns of action selection that people show in the same physical task.
+Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
+Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that infants are unsurprised by many physical interactions [@Baillargeon2007], but do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
+Recent computational models have proposed linking functions relating..
+in simulation [@Schmidhuber2010; @Oudeyer2013], but the predictions of these models have not yet been directly compared to human behavior in the same task to reveal how curiosity drives people's choice of causal interventions.
+
+<!-- High-level statement of our approach -->
 In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity.
-Below, we give a brief overview of theories of curiosity, relevant developmental empirical findings, and computational models instantiating curiosity in agents that are able to interact with the world in realistic simulated 3D environments.
+Our approach is to coordinate detailed measurement of stimulus and action selection with the construction of task-performing computational models evaluated on the same task and using the same metric, with the goal of developing a more robust, unified, and testable theory of curiosity's role in cognitive development.
 
-## Theories of Curiosity
+<!-- What we've learned from prior theoretical work, and how it falls short -->
 
-@Berlyne1954's influential theory of curiosity distinguished between perceptual curiosity, a desire to seek out novel stimuli (that decreases with familiarity), and epistemic curiosity, a desire to acquire knowledge.
-Berlyne additionally distinguished specific versus diversive curiosity, where the former is a drive for a particular piece of information, and the latter is a general motivation for stimulation.
-More recent views of curiosity further limit the definition to information-seeking that is intrinsically-motivated, not linked to any obvious external reward [@Loewenstein1994; @Oudeyer2007].
-However, it is often difficult for observers to determine whether any given decision is intrinsically- or extrinsically-motivated.
-Modern theories also hold that the function of curiosity is inspired by awareness of a knowledge gap, and functions to drive behaviors that will result in learning [@Loewenstein1994].
-Similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
-One theory developed to explain the discrepancy between infants' frequent preference for novel stimuli [e.g., @Fantz1964], as well as their occasional preference for familiar stimuli (e.g., faces), is the idea that infants prefer to attend to stimuli that are "moderately discrepant", i.e.
-that are only somewhat different than the infants' mental representations [@Kinney1976].
-Thus, as infants gain experience with various classes of stimuli, they will seek increasingly complex stimuli as their mental representations become more sophisticated [@Dember1957].
-Although these theories give us some sense of which situations and knowledge states should engender curiosity, both the mechanism and how actions are selected are not fully specified.
+<!-- A limitation of past theories of curiosity is that they are large part verbal descriptions, without formal, testable, mechanisms. -->
+<!-- An exception to this: @Schmidhuber2010 and @Oudeyer2013 --similar but different, and critically not evaluated against same children's behavior in the same situations -->
 
-## Related Behavioral Work
+<!-- What we've learned from prior behavioral work, and how our approach is different -->
 
-Although the question of what inspires a child's curiosity is difficult to determine, it's generally agreed that curiosity indicates awareness of a knowledge gap that the learner is interested in filling [@Loewenstein1994].
-Even young infants often exhibit a preference to attend to novel stimuli over more familiar stimuli [e.g., @Fantz1964], and when surprising physical events do occur (e.g., an object appearing to have passed through a wall) it has been shown to stimulate infants' exploration and subsequent learning [@Stahl2015].
-Moreover, infants are sensitive to the level of complexity of stimuli, preferring to attend to those of intermediate complexity (rather than simple or overly-complex)--a bias which may help them optimize their information gain [@Kidd2012; @Kidd2014].
-As theorized [@Piaget1952], exploratory play has been shown to be an opportunity for young children to learn [e.g., generalization: @Sim2017, causal structure: @Schulz2007; @Gweon2014].
+<!-- Looking time people: @Baillargeon2007 and other studies of infants' surprisal at physical events (occlusion, containment,  -->
+<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks) --  -->
 
-One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects. 
-Many studies of young infants' reasoning about physical objects have focused on occlusion, containment, and covering events, using surprisal (indexed via looking time) as a measure of knowledge [@Baillargeon2007].
-A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
-Here, we investigate toddlers' choices in a more complex
+<!-- Highlight main contributions of the paper -->
+
+<!-- One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects.  -->
+<!-- A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
+-->
 
 ## Computational Models of Curiosity
-
-[Sentence or two on other approaches, e.g. @Oudeyer2013; @Schmidhuber2010]
 

### 2020-01-23 paper/paper.Rmd
more intro / modeling

@@
 Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
-Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that infants are unsurprised by many physical interactions [@Baillargeon2007], but do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
-Recent computational models have proposed linking functions relating..
-in simulation [@Schmidhuber2010; @Oudeyer2013], but the predictions of these models have not yet been directly compared to human behavior in the same task to reveal how curiosity drives people's choice of causal interventions.
+Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that even very young infants are unsurprised by many physical interactions [see @Baillargeon2007], but these studies do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
+On the computational modeling side, reinforcement learning (RL) researchers have long realized the value of mechanisms that encourage actions that explore the state space in the absence of an apparent reward (which are often sparse), as actions with uncertain outcomes can result in the discovery of new policies with high expected values [@Schmidhuber2010].
+Others have built robot models that utilize a form of curiosity to help build predictive and control models of the world [@Oudeyer2007; @Oudeyer2013], although this work pre-trained models on a separate prediction task before implementing curosity-driven learning.
+These models' behavior has not yet been directly compared to human behavior in the same task to reveal whether the curiosity driving their behavior mimics people's selection of causal interventions.
 
 <!-- High-level statement of our approach -->
-In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity.
+In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity in a simulated 3D environment, carrying out the same task.
+The proposed task, described in detail below, presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
 Our approach is to coordinate detailed measurement of stimulus and action selection with the construction of task-performing computational models evaluated on the same task and using the same metric, with the goal of developing a more robust, unified, and testable theory of curiosity's role in cognitive development.
@@
 <!-- Looking time people: @Baillargeon2007 and other studies of infants' surprisal at physical events (occlusion, containment,  -->
-<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks) --  -->
+<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks)  -->
 
@@
 
-Building on prior work that showed deep neural networks are capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], we use and extend a framework for constructing intrinsically-motivated artificial agents introduced in @Haber2018learning, described in the following.
+Building on prior work that showed deep neural networks are capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], we use and extend a deep RL architecture for constructing intrinsically-motivated artificial agents introduced in @Haber2018learning.
+This agent's behavior is driven by two interacting neural networks: a *world-model* and a *self-model*, which are trained simultaneously. 
+The problem of the world-model is to predict the consequences of the agent's actions, through estimation of either the forward or inverse dynamics. 
+The self-model attempts to learn to predict the errors of the world-model. 
+The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will adversarially challenge the state of its world-model.
 
-(Model description or just teaser here?)
-
-(maybe make the below a joint "Paradigm" section, then human behavior, model behavior and comparison)
+(Full model description here, or just a teaser? Maybe also make the below a joint "Paradigm" section, then human behavior, model behavior and comparison)
 

### 2020-01-23 paper/paper.Rmd
Bria Sama George reworked intro!

@@
 <!-- Curiosity is important... end with core question about what gives rise to curiosity. -->
-Curiosity is a key driver of everyday behaviors, from children's exploratory play with a new toy to adults browsing the internet, we spend a surprising amount of time actively pursuing information about our world.
-Curiosity may even serve as the impetus for all learning: William James (1899) considered it to be "the impulse towards better cognition", a belief that is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
-From this view, children and even infants [@Gopnik2009] can be seen as "little scientists" who use curiosity to select causal interventions that help them learn about the physical world.
-However, a major outstanding difficulty in curiosity research: there is no integrative, testable theory of the mechanisms and basis for curiosity [@Kidd2015].
-More concretely, what relationship between stimuli and a learner's knowledge states engender curiosity, and how does this motivate a learner's choice of actions?
+Curiosity is a key driver of everyday behaviors.
+From children's exploratory play with a new toy to adults browsing the internet, we spend a surprising amount of time actively pursuing information about our world.
+Curiosity may even serve as the impetus for all learning: William James (1899) considered it to be "the impulse towards better cognition." This belief is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
+From this perspective, children and even infants [@Gopnik2009] can be seen as "little scientists" whose curiosity  selects causal interventions that help them learn about the physical world.
+However, there is no integrative, testable theory of the mechanisms and basis of curiosity [@Kidd2015].
+More concretely, how does a learner's knowledge state interact with their perception to engender curiosity, and how does curiosity motivate action?
 
@@
 A fully-specified, testable theory of curiosity would minimally require three components.
-First, it is necessary to have a precise mechanism specifying how stimuli inspire curiosity. 
-Although some early verbal theories of curiosity acknowledge that novel stimuli demand our (and other animals') attention [e.g., @Berlyne1954], borne out in empirical data [e.g., @Fantz1964], but modern theories hold that learners may prefer to attend to stimuli that are "moderately discrepant" in comparison to our mental representations [@Kinney1976].
-These theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as we gain experience with classes of stimuli our preferences will tend toward more complex stimuli as our mental representations mature [@Dember1957].
-Empirical work has verified that infants are sensitive to the level of complexity of stimuli and prefer to attend to stimuli of intermediate complexity [rather than simple or overly-complex; @Kidd2012; @Kidd2014].
-Thus, similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed, but defining the perceptual and knowledge-based representations and how they are compared is an open question.
+First, we need a precise mechanism that specifies how stimuli inspire curiosity. 
+Although some early verbal theories of curiosity acknowledge that novel stimuli capture our (and other animals') attention [e.g., @Berlyne1954,@Fantz1964], modern theories hold that learners prefer to attend to stimuli that provide optimal learning opportunities--that are "moderately discrepant" in comparison to our mental representations [@Kinney1976].
+Empirical work has verified that infants are indeed sensitive to the level of complexity of stimuli and prefer to attend to stimuli of intermediate complexity [rather than simple or overly-complex; @Kidd2012; @Kidd2014].
+Thus, these theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as our mental representations mature our preferences will tend toward more complex stimuli [@Dember1957].
+On these accounts, similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
+However, these theories have yet to define these perceptual and knowledge-based representations or specify how they are compared.
 
-Second, a testable theory of curiosity requires a detailed measure of curious behavior that records which interventions learners select in order to gain information about the properties of objects and laws that govern the physical world.
-People's curiosity-driven behavior comes in such a variety of contexts and utilizing such a wide repertoire of actions that it is quite difficult to choose an appropriate paradigm, particularly because the places where curiosity is most manifest tend to be those open-ended environments that are hardest to model -- an inviting playground, a surprisingly complex device, or a novel research question.
+<!-- The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model--an inviting playground or a surprisingly complex device. -->
+<!-- Curiosity-driven behavior comes in a variety of contexts and consists of a wide repertoire of actions.  -->
+
+<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->
+
+Second, we need finer-grained measures of curiosity-driven behaviors.
+What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world? 
 Past studies of infant's physical reasoning ability have used looking time to measure their knowledge about physical events, given that infant's attend longer to surprising events [e.g., objects appearing to pass through a wall; @Stahl2015].
-Behavioral investigations of older children's exploratory play have also used simple attention duration measures to measure curiosity, for example offering children a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], and additionally tally the number of discovered functions.
+Behavioral investigations of older children's exploratory play have also used simple attention duration measures to measure curiosity, for example offering children a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], and tallying the number of discovered functions.
 However, these attention and discovery measures do not quantify the overt actions that children choose, and typically do not offer more than one or two target objects for exploration. 
+Further, most environments that inspire curiosity tend to be more open-ended and afford a much wider variety of action choices.
 
-A third desiderata for a testable theory of curiosity is a linking function for evaluating the correspondence between the predictions of our computational theory and the observed patterns of action selection that people show in the same physical task.
+A third desiderata for a testable theory of curiosity is a linking function for evaluating the correspondence between the predictions of our computational theory and the observed patterns of action selection that infants and children show in the same physical task.
 Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
 Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that even very young infants are unsurprised by many physical interactions [see @Baillargeon2007], but these studies do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
+
 On the computational modeling side, reinforcement learning (RL) researchers have long realized the value of mechanisms that encourage actions that explore the state space in the absence of an apparent reward (which are often sparse), as actions with uncertain outcomes can result in the discovery of new policies with high expected values [@Schmidhuber2010].

### 2020-01-24 paper/paper.Rmd
worked on tower task analysis

@@
 
+### Tower Task
+
+1. height x continuous age
+First we examine tower height as a function of age. Y/N we find tower height increases with age.
+```{r}
+cor.test(hum$height_tallest, hum$age_rounded)
+```
+
+```{r, include=F} 
+ch_height <- hum %>% group_by(age_group, height_tallest) %>% 
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ggplot(ch_height, aes(x=age_group, y=height_tallest)) + 
+  geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8, aes(size=n)) +
+  scale_shape_manual(values=10:19) +
+  xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
+  langcog::scale_fill_solarized() + ggthemes::theme_few()
+```
+
+<!-- We find that towers vary in i) height, ii) stacks, and iii) components.  -->
+
+<!-- 1. height x age -->
+<!-- -First we examine tower height, of the tallest stack, as a function of age. We find tower height increases with age (cor.test).  -->
+
+<!-- 2a. number stacks x age -->
+<!-- -Number of stacks y/ n correlate with age. -->
+<!-- -what is "cool": younger and use of horizontal/adjacent tower building -->
+
+<!-- 2b. number collapses x age = intuitive physics (tower stability) -->
+<!-- -Hight and number of stacks due to stability issue. -->
+<!-- -Number of collapses -->
+
+<!-- 3. The structural components of the towers -->
+<!-- -support x supported -->
+<!-- -drop object probabilities correlate with objects used in tower? -->
+<!-- -first base selection as proxy of most interesting object  -->
+<!-- - base and top distribution  -->
+
 # Model

### 2020-01-26 paper/paper.Rmd
updates to intro

@@
 <!-- Curiosity is important... end with core question about what gives rise to curiosity. -->
-Curiosity is a key driver of everyday behaviors.
-From children's exploratory play with a new toy to adults browsing the internet, we spend a surprising amount of time actively pursuing information about our world.
-Curiosity may even serve as the impetus for all learning: William James (1899) considered it to be "the impulse towards better cognition." This belief is echoed in Piaget's [-@Piaget1952] theory of development, which holds that children actively construct their knowledge through physical exploration of the world.
-From this perspective, children and even infants [@Gopnik2009] can be seen as "little scientists" whose curiosity  selects causal interventions that help them learn about the physical world.
-However, there is no integrative, testable theory of the mechanisms and basis of curiosity [@Kidd2015].
-More concretely, how does a learner's knowledge state interact with their perception to engender curiosity, and how does curiosity motivate action?
+Curiosity is a hallmark aspect of human intelligence.
+From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences.
+However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009,@Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
+Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
 
-<!-- desiderata for advancing theories of curiosity -->
+The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational model of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational model and those taken by children on the same set of tasks.
 
@@
 
-1. height x continuous age
-First we examine tower height as a function of age. Y/N we find tower height increases with age.
+<!-- 1. height x continuous age -->
+<!-- First we examine tower height as a function of age. Y/N we find tower height increases with age. -->
 ```{r}
-cor.test(hum$height_tallest, hum$age_rounded)
+# cor.test(hum$height_tallest, hum$age_rounded)
 ```
@@
 ```{r, include=F} 
-ch_height <- hum %>% group_by(age_group, height_tallest) %>% 
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-ggplot(ch_height, aes(x=age_group, y=height_tallest)) + 
-  geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8, aes(size=n)) +
-  scale_shape_manual(values=10:19) +
-  xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
-  langcog::scale_fill_solarized() + ggthemes::theme_few()
+# ch_height <- hum %>% group_by(Age_Group, height_tallest) %>% 
+#   summarise(n = n()) %>%
+#   mutate(freq = n / sum(n)) 
+# 
+# ggplot(ch_height, aes(x=age_group, y=height_tallest)) + 
+#   geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8, aes(size=n)) +
+#   scale_shape_manual(values=10:19) +
+#   xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
+#   langcog::scale_fill_solarized() + ggthemes::theme_few()
 ```

### 2020-01-26 paper/paper.Rmd
more updates to intro

@@
 
-The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational model of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational model and those taken by children on the same set of tasks.
+The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.
 
-A fully-specified, testable theory of curiosity would minimally require three components.
-First, we need a precise mechanism that specifies how stimuli inspire curiosity. 
-Although some early verbal theories of curiosity acknowledge that novel stimuli capture our (and other animals') attention [e.g., @Berlyne1954,@Fantz1964], modern theories hold that learners prefer to attend to stimuli that provide optimal learning opportunities--that are "moderately discrepant" in comparison to our mental representations [@Kinney1976].
-Empirical work has verified that infants are indeed sensitive to the level of complexity of stimuli and prefer to attend to stimuli of intermediate complexity [rather than simple or overly-complex; @Kidd2012; @Kidd2014].
+<!-- A fully-specified, testable theory of curiosity would minimally require three components. -->
+
+<!-- First, we need a precise mechanism that specifies how stimuli inspire curiosity.  -->
+Our computational theory is inspired by classic verbal theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as other verbal theories proposing to explain curiosity-driven behavior as the manifestation of learners' preferences for stimuli that are "moderately discrepant" in comparison to our mental representations, and thereby provide opportunities to learn [@Kinney1976].
+Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
 Thus, these theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as our mental representations mature our preferences will tend toward more complex stimuli [@Dember1957].

### 2020-01-26 paper/paper.Rmd
more updates to 3rd para of intro

@@
 
-The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.
+The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.
 
@@
 <!-- First, we need a precise mechanism that specifies how stimuli inspire curiosity.  -->
-Our computational theory is inspired by classic verbal theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as other verbal theories proposing to explain curiosity-driven behavior as the manifestation of learners' preferences for stimuli that are "moderately discrepant" in comparison to our mental representations, and thereby provide opportunities to learn [@Kinney1976].
+Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
 Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
-Thus, these theories hold that curiosity is inspired by awareness of a knowledge gap [@Loewenstein1994], and that as our mental representations mature our preferences will tend toward more complex stimuli [@Dember1957].
-On these accounts, similar to other drives (e.g., hunger), curiosity is sated as relevant information is gained and the knowledge gap is closed.
-However, these theories have yet to define these perceptual and knowledge-based representations or specify how they are compared.
+According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
+<!-- Moreover, curiosity is thought of as being similar to other basic drives (e.g., hunger) in that learners are thought to become sated as relevant information is acquired and the knowledge gap is closed.
+-->
+Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
 

### 2020-01-26 paper/paper.Rmd
para 3

@@
 
-The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.
+The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
 
@@
 <!-- Curiosity-driven behavior comes in a variety of contexts and consists of a wide repertoire of actions.  -->
+<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->
+<!-- Second, we need finer-grained measures of curiosity-driven behaviors. -->
+<!-- What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world?  -->
 
-<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->
+Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITECITECITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
+However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge.
+For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015).
+Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014] However, what both of these looking-time and toy-exploration measures fail to capture are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009, @gureckis2012self].
+To address this limitation, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.
 
-Second, we need finer-grained measures of curiosity-driven behaviors.
-What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world? 
-Past studies of infant's physical reasoning ability have used looking time to measure their knowledge about physical events, given that infant's attend longer to surprising events [e.g., objects appearing to pass through a wall; @Stahl2015].
-Behavioral investigations of older children's exploratory play have also used simple attention duration measures to measure curiosity, for example offering children a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], and tallying the number of discovered functions.
-However, these attention and discovery measures do not quantify the overt actions that children choose, and typically do not offer more than one or two target objects for exploration. 
-Further, most environments that inspire curiosity tend to be more open-ended and afford a much wider variety of action choices.
-
-A third desiderata for a testable theory of curiosity is a linking function for evaluating the correspondence between the predictions of our computational theory and the observed patterns of action selection that infants and children show in the same physical task.
+Our strategy for evaluating the correspondence betweenour computational theory and the observed patterns of action selection is to  children show in the same physical task. 
 Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.

### 2020-01-26 paper/paper.Rmd
a bit of cleanup

@@
 
-<!-- A fully-specified, testable theory of curiosity would minimally require three components. -->
-
-<!-- First, we need a precise mechanism that specifies how stimuli inspire curiosity.  -->
 Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
@@
 According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
-<!-- Moreover, curiosity is thought of as being similar to other basic drives (e.g., hunger) in that learners are thought to become sated as relevant information is acquired and the knowledge gap is closed.
--->
 Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
 
-<!-- The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model--an inviting playground or a surprisingly complex device. -->
-<!-- Curiosity-driven behavior comes in a variety of contexts and consists of a wide repertoire of actions.  -->
-<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->
-<!-- Second, we need finer-grained measures of curiosity-driven behaviors. -->
-<!-- What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world?  -->
-
 Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITECITECITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
-However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge.
-For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015).
-Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014] However, what both of these looking-time and toy-exploration measures fail to capture are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009, @gureckis2012self].
-To address this limitation, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.
-
-Our strategy for evaluating the correspondence betweenour computational theory and the observed patterns of action selection is to  children show in the same physical task. 
-Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
-Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that even very young infants are unsurprised by many physical interactions [see @Baillargeon2007], but these studies do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
+However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge, and thus do not specify or constrain which events might moderately discrepant from this knowledge.
+For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015; @Baillargeon2007).
+Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
+Moreover, these studies have yet to directly constrain theories that predict which functions children will discover, and in what sequence.
+What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009, @gureckis2012self].
+To address these limitations, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.
 

### 2020-01-26 paper/paper.Rmd
paper

@@
 Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
+Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
+Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
 
@@
 
-On the computational modeling side, reinforcement learning (RL) researchers have long realized the value of mechanisms that encourage actions that explore the state space in the absence of an apparent reward (which are often sparse), as actions with uncertain outcomes can result in the discovery of new policies with high expected values [@Schmidhuber2010].
-Others have built robot models that utilize a form of curiosity to help build predictive and control models of the world [@Oudeyer2007; @Oudeyer2013], although this work pre-trained models on a separate prediction task before implementing curosity-driven learning.
-These models' behavior has not yet been directly compared to human behavior in the same task to reveal whether the curiosity driving their behavior mimics people's selection of causal interventions.
+<!-- High-level statement of our approach -->
+In sum, this paper presents a unified paradigm for advancing theories of curiosity and its role in guiding the development of knowledge about the physical world.
+We present: (1) a computational theory of intrinsic motivation instantiated in an artificial reinforcement-learning agent that explores a simulated 3D environment; (2) a novel dataset that measures children's actions in a novel physical exploration task; and (3) quantitative comparisons between the actions taken by the artificial agent and children on the same set of tasks.
+Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.
 
-<!-- High-level statement of our approach -->
-In this paper we propose a new paradigm that allows us to directly compare children's curiosity about physical interactions with that of an aritifical agent implementing different functional forms of curiosity in a simulated 3D environment, carrying out the same task.
-The proposed task, described in detail below, presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
-Our approach is to coordinate detailed measurement of stimulus and action selection with the construction of task-performing computational models evaluated on the same task and using the same metric, with the goal of developing a more robust, unified, and testable theory of curiosity's role in cognitive development.
+<!-- presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
+-->
 

### 2020-01-26 paper/paper.Rmd
fix in-text citations, and re-knit

@@
 From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences.
-However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009,@Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
+However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009;@Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
 Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
@@
 
-Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954,@Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
+Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
 Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
@@
 
-Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITECITECITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
+Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
 However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge, and thus do not specify or constrain which events might moderately discrepant from this knowledge.
@@
 Moreover, these studies have yet to directly constrain theories that predict which functions children will discover, and in what sequence.
-What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009, @gureckis2012self].
+What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009; @gureckis2012self].
 To address these limitations, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.

### 2020-01-29 paper/paper.Rmd
Update paper.Rmd

@@
 
-The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
+The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
 
@@
 
-### Tower Task
+### Tower Task Results
 
-<!-- 1. height x continuous age -->
-<!-- First we examine tower height as a function of age. Y/N we find tower height increases with age. -->
 ```{r}
-# cor.test(hum$height_tallest, hum$age_rounded)
+require(here)
+require(tidyboot)
+library(ggplot2)
+require(tidyverse)
+
+tower = read.csv2("../analysis/human-data/curiobaby_drop-data - cool tower.csv", sep=',', header=T, stringsAsFactors=F)
+hum = subset(tower, exclude!="Y")
+
+length(unique(tower$SID)) #61
+length(unique(hum$SID)) # 51 subjects
+
+hum$age_group = as.numeric(hum$age_group)
+hum$age_rounded = as.numeric(hum$age_rounded)
+hum$height_tallest = as.numeric(hum$height_tallest)
+hum$tallest_objects = as.character(hum$tallest_objects)
+hum$base_tallest = as.character(hum$base_tallest)
+
 ```
 
-```{r, include=F} 
-# ch_height <- hum %>% group_by(Age_Group, height_tallest) %>% 
-#   summarise(n = n()) %>%
-#   mutate(freq = n / sum(n)) 
-# 
-# ggplot(ch_height, aes(x=age_group, y=height_tallest)) + 
-#   geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8, aes(size=n)) +
-#   scale_shape_manual(values=10:19) +
-#   xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
-#   langcog::scale_fill_solarized() + ggthemes::theme_few()
+1. height x continuous age
+First we examine tower height as a function of age. Yes we find tower height increases with age.
+```{r}
+cor.test(hum$height_tallest, hum$age_rounded)
+```
+
+```{r}
+ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n))
+
+ggplot(ch_height, aes(x=age_rounded, y=height_tallest)) +
+  geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8) +
+  scale_shape_manual(values=10:19) +
+  xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
+  langcog::scale_fill_solarized() + ggthemes::theme_few()
+```
+
+2. support x supported (counts)
+```{r}
+tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
+df = data.frame(support=NA, supported=NA, n=NA)
+for(s in 1:nrow(tower)) {
+  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
+  print(objs)
+  for(i in 2:length(objs)) {
+    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
+  }
+}
+df = na.omit(df)
+hm <- df %>% group_by(support, supported) %>% count(N=n()) 
+hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
+  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
+```
+
+3. support x supported (probabilities)
+pr (supported object | support object)
+```{r}
+tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
+df = data.frame(support=NA, supported=NA, n=NA)
+for(s in 1:nrow(tower)) {
+  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
+  print(objs)
+  for(i in 2:length(objs)) {
+    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
+  }
+}
+df = na.omit(df)
+hm1 <- df %>% 
+  group_by(support, supported) %>% 
+  summarise(n = n()) %>% 
+  group_by(support) %>%
+  mutate(freq = n / sum(n))
+hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
+  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
+```
+
+4. base and top distribution
+```{r}
+ch_extremes <- hum %>% 
+  group_by(base_tallest) %>% 
+  count(N=n()) %>%
+  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")
+
+ch_extremes %>% 
+  ggplot(aes(x = base_tallest, y = N)) + geom_bar(stat = "identity")
+
 ```
@@
 <!-- -first base selection as proxy of most interesting object -->
-<!-- - base and top distribution  -->
+<!-- -base and top distribution -->
 

### 2020-02-02 analysis/model_analysis.Rmd
model data cleanup and inspection

---
title: "curiobaby_drop model analysis"
author: "George Kachergis"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
require(tidyverse)
```

## Load data

```{r, load-data}
load_model_data <- function(data_dir, policy_name) {
  dirs = paste("../analysis/agent-data", data_dir, sep='/')
  d = data.frame()
  for(dir in dirs) {
    subdirs <- list.files(dir, full.names=TRUE)
    for(sub in subdirs) {
      filenames <- list.files(sub, full.names=TRUE)
      for(f in filenames) {
        #tmp <- read.csv(f, header=T)
        tmp <- read.table(f, sep=',', header=T, stringsAsFactors = F)
        d = rbind(d, tmp)
      }
    }
  }
  d$policy = policy_name
  return(d)
}

cur = load_model_data("curiodrop_01_curious", "curious")
noncur = load_model_data("curiodrop_01_noncurious", "noncurious")
rand = load_model_data("random_policy", "random")
all = rbind(cur, noncur, rand)
names(all) # collision_count drop_target

drop_loc_cols = c("ground_object_1_distance_on_floor_contact",
                  "ground_object_2_distance_on_floor_contact",
                  "ground_object_3_distance_on_floor_contact")
all$ClosestObjDistance = apply(all[,drop_loc_cols], 1, min) # distance of closest object

# TargetSpace is object that is closest
md <- all %>% mutate(TargetSpace = case_when(
        ClosestObjDistance==ground_object_1_distance_on_floor_contact ~ ground_object_1,
        ClosestObjDistance==ground_object_2_distance_on_floor_contact ~ ground_object_2,
        ClosestObjDistance==ground_object_3_distance_on_floor_contact ~ ground_object_3
      )) %>% mutate(TargetSpace = case_when(
        TargetSpace=="RDumbbell" ~ "Dumbbell",
        TRUE ~ TargetSpace
      )) %>% mutate(DropChoice = case_when(
        dropped_object=="RDumbbell" ~ "Dumbbell",
        TRUE ~ dropped_object
      )) %>% mutate(DropLocation = case_when(
        drop_target=="floor" ~ "space",
        drop_target=="RDumbbell" ~ "Dumbbell",
        TRUE ~ drop_target
      ))

# create StimSet column 
md <- md %>% mutate(DropSet = case_when(
        drop_object_partitioning=="Bowl_Pentagon_RDumbbell" ~ "c",
        drop_object_partitioning=="Pyramid_Torus_TriangularPrism" ~ "a",
        drop_object_partitioning=="Cone_Octahedron_Pipe" ~ "b"
      )) %>% mutate(TargetSet = case_when(
        ground_object_partitioning=="Bowl_Pentagon_RDumbbell" ~ "c",
        ground_object_partitioning=="Pyramid_Torus_TriangularPrism" ~ "a",
        ground_object_partitioning=="Cone_Octahedron_Pipe" ~ "b"
      )) %>% mutate(StimSet = paste0(TargetSet, DropSet))

table(md$policy)

md <- md %>% select("episode", "policy", "StimSet", "DropChoice", "DropLocation", "TargetSpace", "DropSet", "TargetSet")

# episodes with same drop and target sets (does model show pref to drop objs on same objs like pilot children?)
same_dt = subset(md, DropSet==TargetSet)

# don't want these due to our pilot results (kids show same pref)
md <- md %>% filter(DropSet!=TargetSet)
save(md, file="agent-data/model_data.RData")
```

`r nrow(all)` simulations with the 9 desired objects. We filter the `r nrow(same_dt)` episodes that had the same drop set and target set, as this trial type was not used in the behavioral experiment.

```{r, collisions-and-distance}

hist(all$collision_count)
hist(all$ClosestObjDistance)
weird = subset(all, ClosestObjDistance<0) # 1715 episodes where the distance to closest object is -1 
table(weird$hit_object_before_ground) # FALSE for all 
table(weird$drop_target) # mostly floor, but some not
```

## Drop Preferences

```{r}

drops = table(md$policy, md$DropChoice)

round(drops / rowSums(drops), 2)

```

Collision count:
```{r}
round(table(all$collision_count) / sum(table(all$collision_count)), 2)
```

### 2020-02-04 paper/paper.Rmd
writing tower section

@@
 ```{r object-sets}
-shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism")
+shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism", "space")
 
@@
 ```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
-ch_cond <- hum %>% 
+drop_choice_plot <- function(dat, ymax=.66, shapes_vec) {
+  ch_cond <- dat %>% 
     group_by(StimSet, DropChoice) %>%
@@
   ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
+  ch_cond$DropChoice <- factor(ch_cond$DropChoice, levels=shapes_vec)
   fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
@@
     #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,.66) + 
+    xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,ymax) + 
     langcog::scale_fill_solarized() + ggthemes::theme_few() + 
     geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
+  return(fig_drop)
+}
+
+fig_drop <- drop_choice_plot(hum, shapes)
 #print(fig_drop)
@@
 hum$Target = hum$DropLocation
-ch_cond <- hum %>% 
+
+target_hit_plot <- function(dat, ymax=.66, shapes_vec) {
+  ch_cond <- dat %>% 
     filter(Target!="outside") %>%
@@
 
-ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
+  # need to add "space" as level of Target in human data
+  ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes_vec))
   fig_targ_hit <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
@@
     #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,.66) + 
+    xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,ymax) + 
     langcog::scale_fill_solarized() + ggthemes::theme_few() + 
     geom_hline(yintercept=.33, lty='dashed')
+}
 #print(fig_targ_hit)
+fig_targ_hit <- target_hit_plot(hum, ymax=.66, shapes)
 ```
@@
 
-```{r}
-require(here)
-require(tidyboot)
-library(ggplot2)
-require(tidyverse)
+```{r load-tower-data}
 
@@
 
+ht_age = cor.test(hum$age_rounded, hum$height_tallest)
 ```
 
-1. height x continuous age
-First we examine tower height as a function of age. Yes we find tower height increases with age.
-```{r}
-cor.test(hum$height_tallest, hum$age_rounded)
-```
+First we examine tower height as a function of age, finding that older children tend to build higher towers `r cor_apa(ht_age, format="rmarkdown", print=F)`.
 
-```{r}
+```{r plot-height-by-age, include=F}
 ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
@@
 2. support x supported (counts)
-```{r}
+```{r heatmap-support-by-supported-counts}
 tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
@@
 pr (supported object | support object)
-```{r}
+```{r heatmap-support-by-supported-probs}
 tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
@@
 4. base and top distribution
-```{r}
+```{r base-and-top-objects}
 ch_extremes <- hum %>% 
@@
 
-## Baseline Curiosity Policy
+## Random Policy
+
+## Noncurious Policy
 
@@
 ## Results
+```{r load-model-data}
+load("../analysis/agent-data/model_data.RData") # md
+
+Shapes = c(sort(unique(md$DropChoice)), "space")
+
+rand_drop <- drop_choice_plot(subset(md, policy=="random"), Shapes)
+curio_drop <- drop_choice_plot(subset(md, policy=="curious"), Shapes)
+noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), Shapes)
+
+md$Target = md$DropLocation
+
+rand_targ <- target_hit_plot(subset(md, policy=="random"), ymax=1, Shapes)
+curio_targ <- target_hit_plot(subset(md, policy=="curious"), ymax=1, Shapes)
+noncurio_targ <- target_hit_plot(subset(md, policy=="noncurious"), ymax=1, Shapes)
+```
+
+```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}
+
+ggarrange(rand_drop, curio_drop, noncurio_drop, 
+          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, 
+          labels = c("Random", "Curious", "Noncurious"),
+          common.legend=T, legend="bottom")
+```
 

### 2020-02-04 paper/paper.Rmd
better graphs

@@
 
-length(unique(tower$SID)) #61
-length(unique(hum$SID)) # 51 subjects
+#length(unique(tower$SID)) #61
+Nsubj_tower = length(unique(hum$SID)) # 51 subjects
 
@@
 
-First we examine tower height as a function of age, finding that older children tend to build higher towers `r cor_apa(ht_age, format="rmarkdown", print=F)`.
+The average height of the constructed towers was `r round(mean(na.omit(hum$height_tallest)), 1)` blocks.
+We examined tower height as a function of age, and found that older children tend to build higher towers (`r cor_apa(ht_age, format="rmarkdown", print=F)`).
 
-```{r plot-height-by-age, include=F}
+```{r plot-height-by-age, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Tower height by age."}
 ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
@@
 
-2. support x supported (counts)
-```{r heatmap-support-by-supported-counts}
+Next we examine the number of times participants supported each object with each other object. 
+```{r heatmap-support-by-supported-counts, include=T, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Counts of support and supported object relations in participants' towers."}
 tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
@@
   objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
-  print(objs)
+  #print(objs)
   for(i in 2:length(objs)) {
@@
 
-3. support x supported (probabilities)
-pr (supported object | support object)
-```{r heatmap-support-by-supported-probs}
+(Could instead show P(supported object | support object).)
+```{r heatmap-support-by-supported-probs, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Conditional probabilities of supported object given support object in participants' towers."}
 tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
@@
 
-4. base and top distribution
-```{r base-and-top-objects}
+<!-- Finally, we look at the distribution of tower heights as a function of the objects chosen as the base of the tower. -->
+
+```{r base-and-top-objects, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Distribution of base and top objects in participants' towers."}
 ch_extremes <- hum %>% 
@@
 <!-- We find that towers vary in i) height, ii) stacks, and iii) components. -->
-
-<!-- 1. height x age -->
-<!-- -First we examine tower height, of the tallest stack, as a function of age. We find tower height increases with age (cor.test). -->
 
@@
 
-rand_drop <- drop_choice_plot(subset(md, policy=="random"), Shapes)
-curio_drop <- drop_choice_plot(subset(md, policy=="curious"), Shapes)
-noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), Shapes)
+rand_drop <- drop_choice_plot(subset(md, policy=="random"), ymax=1, Shapes) + ggtitle("Random")
+curio_drop <- drop_choice_plot(subset(md, policy=="curious"), ymax=1, Shapes) + ggtitle("Curious")
+noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), ymax=1, Shapes) + ggtitle("Noncurious")
 
@@
 
-```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}
+```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=5.5, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}
 
 ggarrange(rand_drop, curio_drop, noncurio_drop, 
-          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, 
-          labels = c("Random", "Curious", "Noncurious"),
+          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, #labels = c("A", "B", "C"),
           common.legend=T, legend="bottom")

### 2020-07-21 analysis/exp2_analysis.Rmd
initial cleaning

---
title: "Drop Exp. 2 Analysis"
author: "George"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(here)
require(tidyverse)
require(tidyboot)

raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)
# row 1 is empty, row 2 should be header
d = raw[4:nrow(raw),]
names(d) = raw[2,]
d[,"NA"] = NULL
# duplicate column names
#names(d)[13]
#names(d)[21]

# "Why did you make that choice?"
explanations = d %>% select(Q42, Q43) # should also select relevant trials

# Q38-Q41 = which toy did you just drop? (catch trials)
#d = d %>% select(-Q38, -Q39, -Q40, -Q41, -Q42, -Q43) # duplicate column names
d$Q11 = NULL
d$Q38 = NULL
d$Q39 = NULL
d$Q40 = NULL
d$Q41 = NULL
d$Q42 = NULL
d$Q43 = NULL
d$`Random ID` = NULL
d$`Duration (in seconds)` = "Duration"
#write.csv(d, file="exp2_cleaned.csv")
```

### 2020-08-18 analysis/exp2_analysis.Rmd
adding developmental zoom data so far
latest online children drop data analysis

@@
 ---
-title: "Drop Exp. 2 Analysis"
+title: "Exp. 2 Analysis: 2AFC, adults vs. children"
 author: "George"
-date: "7/20/2020"
+date: Sys.Date()
 output: html_document
@@
 ```
+
+```{r}
+rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
+rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'
+
+cd <- rawch %>% filter(Exclude!="Y") %>% 
+  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes)
+
+# make long
+#cdl <- cd %>% pivot_longer()
+
+# first 10 columns are
+
+for(i in 3:ncol(cd)) {
+  tt = table(cd[,i])
+  bt = binom.test(tt, p=.5, alternative="two.sided")
+  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
+  print(round(tt / sum(tt), 2))
+}
+
+```
+
+```{r}
+hist(cd$Age)
+```
+
+```{r}
+
+```

### 2020-08-27 analysis/exp2_analysis.Rmd
added some initial model data for 2AFC experiment

@@
 
-```{r setup, include=FALSE}
+```{r libraries}
 knitr::opts_chunk$set(echo = TRUE)
@@
 require(tidyboot)
+```
 
+```{r load-model-data, include=F}
+mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
+
+names(mdat)
+mdat <- mdat %>% mutate(
+    train_stage = cut_number(model_train_steps, 2),
+    chose_target = ifelse(choice==target, 1, 0)
+  )
+
+mdat %>% group_by(drop, target, train_stage) %>% # alt, 
+  summarize(chose_target=mean(chose_target), n=n()) %>%
+  ggplot(aes(x=train_stage, y=chose_target, group=target, color=target)) + 
+  facet_wrap(.~ drop) + 
+  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1)
+
+mdat %>% distinct(drop, target, alt)
+```
+
+```{r load-human-data, include=FALSE}
 raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)

### 2020-09-01 analysis/exp2_analysis.Rmd
more prelim model data from Michael, updating children's drop data

@@
 mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
+mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
+mdat <- read_csv("agent-data/curiodrop_1.csv")
+mdat <- read_csv("agent-data/curiodrop_2.csv")
 
@@
 
+mdat %>% group_by(drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target), n=n())
+
 mdat %>% group_by(drop, target, train_stage) %>% # alt, 
@@
   facet_wrap(.~ drop) + 
-  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1)
+  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed")
 
-mdat %>% distinct(drop, target, alt)
+#mdat %>% distinct(drop, target, alt)
 ```
@@
 cd <- rawch %>% filter(Exclude!="Y") %>% 
-  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes)
+  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes, -Note)
 
@@
 
+# Octahedron   39  p= 0.003
+#   pyramid trig prism 
+#      0.74       0.26 
+# Pentagon   41  p= 0.001
+#    bowl pentagon 
+#    0.76     0.24 
+# Pyramid   41  p= 0.06
+# octahedron      torus 
+#      0.34       0.66 
+# Dumbbell_1   42  p= 0.02
+#      bowl octahedron 
+#      0.69       0.31 
 ```

### 2020-09-01 analysis/exp2_analysis.Rmd
updated analysis of children's Exp 2 data and comparison to model and adult data

@@
 title: "Exp. 2 Analysis: 2AFC, adults vs. children"
-author: "George"
-date: Sys.Date()
+author: "George & Sama"
+date: "`r Sys.Date()`"
 output: html_document
@@
 
-```{r libraries}
-knitr::opts_chunk$set(echo = TRUE)
+```{r libraries, echo=F}
+knitr::opts_chunk$set(echo = F, warning=F)
 
@@
 
-```{r load-model-data, include=F}
+# Load Model Data
+
+This is preliminary, not final model data.
+
+```{r load-model-data}
 mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
@@
 
-mdat %>% group_by(drop, target) %>% # alt, 
+model_trial_agg <- mdat %>% group_by(drop, target) %>% # alt, 
   summarize(chose_target=mean(chose_target), n=n())
@@
 
-```{r load-human-data, include=FALSE}
-raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)
+# Load Adult Data
+
+```{r load-human-data, include=F, echo=FALSE}
+raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
 # row 1 is empty, row 2 should be header
-d = raw[4:nrow(raw),]
-names(d) = raw[2,]
+d = raw[3:nrow(raw),]
+names(d) = raw[1,]
 d[,"NA"] = NULL
-# duplicate column names
-#names(d)[13]
-#names(d)[21]
+names(d) <- make.unique(names(d))
+d[which(is.na(d$Exclude)),]$Exclude = 'N'
 
@@
 # Q38-Q41 = which toy did you just drop? (catch trials)
-#d = d %>% select(-Q38, -Q39, -Q40, -Q41, -Q42, -Q43) # duplicate column names
-d$Q11 = NULL
-d$Q38 = NULL
-d$Q39 = NULL
-d$Q40 = NULL
-d$Q41 = NULL
-d$Q42 = NULL
-d$Q43 = NULL
-d$`Random ID` = NULL
-d$`Duration (in seconds)` = "Duration"
+d = d %>% 
+  dplyr::select(-Q11, -Q38, -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>%
+  rename(Duration = `Duration (in seconds)`)
 #write.csv(d, file="exp2_cleaned.csv")
+
+Nsubj = length(unique(d$ResponseId))
+# shown 1 object to drop, choose which target
+adult_long <- d %>%
+  pivot_longer(cols = 9:29,
+                   names_to = "drop",
+                   values_to = "choice",
+                   values_drop_na = FALSE) %>%
+    mutate(drop = tolower(drop)) %>%
+    mutate(drop = case_when(
+      drop=="torus.1" ~ "torus",
+      drop=="cone.1" ~ "cone",
+      drop=="pyramid.1" ~ "pyramid",
+      drop=="dumbbell.1" ~ "dumbbell",
+      drop=="octahedron.1" ~ "octahedron",
+      drop=="pipe.1" ~ "pipe",
+      drop=="trig prism.1" ~ "trig prism",
+      drop=="pentagon.1" ~ "pentagon",
+      drop=="sphere.1" ~ "sphere",
+      drop=="bowl.1" ~ "bowl",
+      drop=="torus.2" ~ "torus",
+      TRUE ~ drop
+    )) %>% mutate(Trial = rep(1:21, Nsubj)) %>% 
+  mutate(
+    target = rep(c("pentagon", "pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
+               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj), # matches relation (containment/support)
+    relation = rep(c("support", rep("contain", 10), rep("support", 10)), Nsubj) #c(rep(, 10), rep( , 10))
+  ) %>% 
+  mutate(chose_target = ifelse(choice == target, 1, 0)) %>%
+  filter(Trial!=1, Exclude!='Y') # remove training trial
+
+adult_trial_agg <- adult_long %>% group_by(drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
+
+# maybe look at Duration distribution at some point
+```
+At a trial level, are the adults' and model's choices correlated?
+
+```{r adult-model-correlation}
+# model vs. adult (trial level)
+cor.test(adult_trial_agg$chose_target, model_trial_agg$chose_target)
 ```
 
-```{r}
+# Load Child Data
+
+```{r load-child-data}
 rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
@@
 # make long
-#cdl <- cd %>% pivot_longer()
+Nsubj_ch = length(unique(cd$ID))
+# shown 1 object to drop, choose which target
+ch_long <- cd %>%
+  pivot_longer(cols = 4:23,
+                   names_to = "drop",
+                   values_to = "choice",
+                   values_drop_na = FALSE) %>%
+    mutate(drop = tolower(drop)) %>%
+    mutate(drop = case_when(
+      drop=="torus_1" ~ "torus",
+      drop=="cone_1" ~ "cone",
+      drop=="pyramid_1" ~ "pyramid",
+      drop=="dumbbell_1" ~ "dumbbell",
+      drop=="octahedron_1" ~ "octahedron",
+      drop=="pipe_1" ~ "pipe",
+      drop=="trig prism_1" ~ "trig prism",
+      drop=="pentagon_1" ~ "pentagon",
+      drop=="sphere_1" ~ "sphere",
+      drop=="bowl_1" ~ "bowl",
+      TRUE ~ drop
+    )) %>% mutate(Trial = rep(1:20, Nsubj_ch)) %>% 
+  mutate(
+    target = rep(c("pipe", "cone", "cone", "pyramid", "pipe", "bowl", "bowl", "bowl", "torus", "torus",
+               "bowl", "pentagon", "trig prism", "torus", "pentagon", "pipe", "trig prism", "pentagon", "pipe", "torus"), Nsubj_ch), # matches relation (containment/support)
+    relation = rep(c(rep("contain", 10), rep("support", 10)), Nsubj_ch) #c(rep(, 10), rep( , 10))
+  ) %>% 
+  mutate(chose_target = ifelse(choice == target, 1, 0))
 
-# first 10 columns are
+child_trial_agg <- ch_long %>% group_by(relation, drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
 
-for(i in 3:ncol(cd)) {
-  tt = table(cd[,i])
-  bt = binom.test(tt, p=.5, alternative="two.sided")
-  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
-  print(round(tt / sum(tt), 2))
-}
+cor.test(child_trial_agg$chose_target, adult_trial_agg$chose_target)
+
+trial_tab <- child_trial_agg %>% select(-n) %>% 
+  bind_cols(adult_target_choice = adult_trial_agg$chose_target) %>% 
+  rename(child_target_choice = chose_target) %>%
+  bind_cols(model_target_choice = model_trial_agg$chose_target)
+# t(18) = 2.42 p=.03 r=.50
+
+#for(i in 3:ncol(cd)) {
+#  tt = table(cd[,i])
+#  bt = binom.test(tt, p=.5, alternative="two.sided")
+#  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
+#  print(round(tt / sum(tt), 2))
+#}
 
@@
 #      0.69       0.31 
+knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
 ```
 
-```{r}
-hist(cd$Age)
+## Compare Children's and Adults' Relational Choices
+
+```{r compare-children-and-adults}
+pos = position_dodge(width = .9)
+
+adult_long <- adult_long %>% rename(ID = ResponseId) %>%
+  mutate(Age = "adult") %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target)
+
+combo_dat <- ch_long %>% mutate(ID = as.character(ID),
+                                Age = as.character(Age)) %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
+  bind_rows(adult_long) %>% 
+  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
+
+combo_dat %>% group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic()
 ```
 
+Still collecting data:
+
 ```{r}
-
+hist(cd$Age, main="")
 ```

### 2020-11-12 analysis/exp2_analysis.Rmd
updated analysis of children's Exp 2 data
finished split-half reliability (of subjects, not trials..)

@@
 cd <- rawch %>% filter(Exclude!="Y") %>% 
-  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes, -Note)
+  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Note, -Comments)
 
@@
 knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
+
+langcog::ggcorplot(select(trial_tab, child_target_choice, adult_target_choice, model_target_choice))
 ```
 
-## Compare Children's and Adults' Relational Choices
+## Compare Children's and Adult's Choices Per Trial
 
-```{r compare-children-and-adults}
-pos = position_dodge(width = .9)
-
+```{r per-trial-comparison}
 adult_long <- adult_long %>% rename(ID = ResponseId) %>%
@@
 
-combo_dat %>% group_by(ID, AgeGroup, relation) %>% # alt, 
+combo_dat %>% group_by(drop, target, relation, AgeGroup) %>%
+  summarise(chose_target = mean(chose_target, na.rm=T)) %>%
+  pivot_wider(names_from = AgeGroup, values_from = chose_target) %>%
+  ggplot(aes(x=adult, y=child, group=relation, color=relation)) + 
+    geom_point(alpha=.7) + theme_bw() + ylim(0,1) + xlim(0,1) + 
+  geom_abline(xintercept=0, slope=1, linetype="dashed") #+
+  #geom_text(aes(label=target)) #
+
+```
+
+## Compare Children's and Adults' Relational Choices
+
+```{r compare-children-and-adults}
+pos = position_dodge(width = .9)
+
+combo_dat %>% 
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
+                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
   summarize(chose_target=mean(chose_target, na.rm=T)) %>%
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
-  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic()
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
 ```
 
-Still collecting data:
+## Reliability
+
+Check reliability of responses within- and across-conditions (support and containment).
 
 ```{r}
-hist(cd$Age, main="")
+# library(psych) # has a (Cronbach's) alpha function that takes a covariance matrix
+
+# split subjects in half, check cor between halves
+split_half_subj_cor <- function(dat, nsim=100) {
+  subjs = unique(dat$ID)
+  cors = rep(NA, nsim)
+  for(i in 1:nsim) {
+    idx1 = sample(subjs, size=length(subjs)/2)
+    idx2 = setdiff(subjs, idx1) # nonsampled items
+    h1 <- dat %>% filter(is.element(ID, idx1)) %>% 
+      group_by(AgeGroup, Trial) %>%
+      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
+    h2 <- dat %>% filter(is.element(ID, idx2)) %>% 
+      group_by(AgeGroup, Trial) %>%
+      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
+    cors[i] = cor(h1$mean, h2$mean)
+  }
+  return(cors)
+}
+
+# overall
+sh_subj = split_half_subj_cor(combo_dat)
+mean(sh_subj) # .736
+
+sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
+mean(sh_subj_adult) # .791
+
+sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))
+mean(sh_subj_child) # .56
+
+sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
+mean(sh_subj_contain) # .649
+
+sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
+mean(sh_subj_support) # .619
+
+# split items in half, check cor between halves...GK: I don't think we care about this
+split_half_item_cor <- function(dat, nsim=100) {
+  trials = unique(dat$Trial)
+  cors = rep(NA, nsim)
+  for(i in 1:nsim) {
+    idx1 = sample(trials, size=length(trials)/2)
+    idx2 = setdiff(trials, idx1) # nonsampled items
+    # h1 <- dat %>% filter(is.element(idx1, Trials)) %>% group_by(ID, AgeGroup)
+
+    cors[i] = cor()
+  }
+  return(cors)
+}
+
 ```

### 2020-11-24 analysis/exp2_analysis.Rmd
nicer graphs

@@
 require(tidyboot)
+require(gridExtra)
 ```
@@
 
-```{r load-model-data}
+```{r load-model-data, include=F}
 mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
@@
 
-```{r load-human-data, include=F, echo=FALSE}
+```{r load-human-data, echo=FALSE}
 raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
@@
 
-```{r adult-model-correlation}
+```{r adult-model-correlation, include=F}
 # model vs. adult (trial level)
@@
 
-```{r load-child-data}
+```{r load-child-data, echo=F}
 rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
@@
 
+## Can we estimate a single item "interestingness" from the 2AFC data?
+
+```{r}
+table(ch_long$drop, ch_long$choice)
+```
+
 ## Compare Children's and Adult's Choices Per Trial
 
-```{r per-trial-comparison}
+```{r per-trial-comparison, fig.width=5, fig.height=5}
+# add vert and horiz error bars 
 adult_long <- adult_long %>% rename(ID = ResponseId) %>%
@@
 
-combo_dat %>% group_by(drop, target, relation, AgeGroup) %>%
-  summarise(chose_target = mean(chose_target, na.rm=T)) %>%
-  pivot_wider(names_from = AgeGroup, values_from = chose_target) %>%
-  ggplot(aes(x=adult, y=child, group=relation, color=relation)) + 
-    geom_point(alpha=.7) + theme_bw() + ylim(0,1) + xlim(0,1) + 
-  geom_abline(xintercept=0, slope=1, linetype="dashed") #+
+# 12 NAs somewhere
+
+combo_dat %>% group_by(drop, target, relation, ID) %>%
+  group_by(drop, target, relation, AgeGroup) %>%
+  tidyboot_mean(chose_target, na.rm=T) %>%
+  select(-n, -empirical_stat) %>%
+  pivot_wider(names_from = AgeGroup, values_from = c(mean, ci_lower, ci_upper)) %>%
+  ggplot(aes(x=mean_adult, y=mean_child, group=relation, color=relation)) + 
+    geom_point(alpha=.6) + 
+    geom_errorbar(aes(ymin=ci_lower_child, ymax=ci_upper_child), alpha=.6) +
+    geom_errorbarh(aes(xmin=ci_lower_adult, xmax=ci_upper_adult), alpha=.6) + 
+    theme_bw() + ylim(0,1) + xlim(0,1) + 
+    xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
+    geom_abline(xintercept=0, slope=1, linetype="dashed") +
+    geom_smooth(method = "lm") 
   #geom_text(aes(label=target)) #
@@
 
-combo_dat %>% 
+p1 <- combo_dat %>%
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", "child"),
+         AgeGroup = factor(AgeGroup, levels=c("child", "adult"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
+
+p2 <- combo_dat %>% 
   mutate(AgeGroup = ifelse(Age=="adult", "adult", 
@@
   geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
+
+grid.arrange(p1, p2, nrow = 1)
 ```
@@
 
-```{r}
+```{r, echo=T}
 # library(psych) # has a (Cronbach's) alpha function that takes a covariance matrix
@@
 sh_subj = split_half_subj_cor(combo_dat)
-mean(sh_subj) # .736
 
 sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
-mean(sh_subj_adult) # .791
 
 sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))
-mean(sh_subj_child) # .56
 
 sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
-mean(sh_subj_contain) # .649
 
 sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
-mean(sh_subj_support) # .619
 
 # split items in half, check cor between halves...GK: I don't think we care about this
-split_half_item_cor <- function(dat, nsim=100) {
-  trials = unique(dat$Trial)
-  cors = rep(NA, nsim)
-  for(i in 1:nsim) {
-    idx1 = sample(trials, size=length(trials)/2)
-    idx2 = setdiff(trials, idx1) # nonsampled items
-    # h1 <- dat %>% filter(is.element(idx1, Trials)) %>% group_by(ID, AgeGroup)
-
-    cors[i] = cor()
-  }
-  return(cors)
-}
 
 ```
+Split-half reliability for all subjects: `r round(mean(sh_subj),2)`.
+Split-half reliability for adults: `r round(mean(sh_subj_adult), 2)`.
+Split-half reliability for children: `r round(mean(sh_subj_child), 2)`.
+
+Split-half reliability for contain relations: `r round(mean(sh_subj_contain), 2)`.
+Split-half reliability for support relations: `r round(mean(sh_subj_support), 2)`.

### 2021-01-11 analysis/exp2_analysis.Rmd
CogSci skeleton to report online experiments

@@
 # shown 1 object to drop, choose which target
-ch_long <- cd %>%
+child_long <- cd %>%
   pivot_longer(cols = 4:23,
@@
 
-child_trial_agg <- ch_long %>% group_by(relation, drop, target) %>% # alt, 
+save(adult_long, child_long, file=here("paper/processed_data.RData"))
+
+child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
   summarize(chose_target=mean(chose_target, na.rm=T), n=n())
@@
 ```{r}
-table(ch_long$drop, ch_long$choice)
+table(child_long$drop, child_long$choice)
 ```
@@
 
-combo_dat <- ch_long %>% mutate(ID = as.character(ID),
+combo_dat <- child_long %>% mutate(ID = as.character(ID),
                                 Age = as.character(Age)) %>%

### 2021-01-11 paper/paper2021.Rmd
CogSci skeleton to report online experiments

--- 2020-02-04 paper/paper.Rmd
@@
 ---
-#title: "Modeling children's intrinsically-motivated curiosity about object interactions"
-#title: "Drop it like it's hot: Modeling children's curiosity about physical interactions"
-#title: "A drop in the bucket: Progress towards modeling children's curiosity about physical interactions"
-title: "What if you drop that? Modeling children's curiosity about physical interactions"
+title: "What if you drop that? Developmental changes in curiosity about physical interactions"
 bibliography: library.bib
@@
 author-information: > 
-    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
-    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}
+    \author{{\large \bf George (kachergis@stanford.edu)} \\ Department of Psychology, Stanford University \\ Madison, WI 53706 USA
+    \AND {\large \bf Judith Fan (SDJ@Macc.Wisc.Edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA}
 
@@
      enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
-     comparisons. We compare the choices of 51 children (2-6 years of age) to those of agents implementing 
-     different types of curiosity, and find broad exploration, but also systematic preferences ...
+     comparisons. We children's choices (N=XX; 2-6 years of age) to those of adults (N=XX), and find
+     systematic preference for drops affording particular relations (e.g., containment)
 
@@
 library(ggpubr)
+require(gridExtra)
 ```
@@
 ```{r, load-data}
-tower = read.csv2("../analysis/human-data/curiobaby_drop-data - cool tower.csv", sep=',', header=T, stringsAsFactors=F)
-raw = read.csv2("../analysis/human-data/curiobaby_drop-data - drop exp.csv", sep=',', header=T, stringsAsFactors=F)
-hum = subset(raw, Exclude!="Y")
+# preprocessed in analysis/exp2_analysis.Rmd
+load(file=here("paper/processed_data.RData"))
 
-hum = hum[-which(hum$StimSet=="bc" & hum$DropChoice=="bowl and dumbbell"),] # chose two - exclude
+Nch = length(unique(child_long$ID)) # 62
+Nad = length(unique(adult_long$ResponseId)) # 35
 
-s_tr <- hum %>% group_by(SID, Age_Group) %>% summarise(max=max(Trial)) %>% arrange(max)
-age = table(s_tr$Age_Group)
+age <- child_long %>% distinct(ID, Age) %>% group_by(Age) %>%
+  summarise(Age = mean(Age), N= n())
 ```
@@
 From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
-However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009;@Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
+However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
 Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
@@
 Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
-Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
+Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
 
@@
 What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009; @gureckis2012self].
-To address these limitations, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.
+To address these limitations, we developed a novel physical exploration task in which children, adults, or AI agents choose which series of physical experiments to perform and observe the results of each in real time.
 
@@
 
-(Full model description here, or just a teaser? Maybe also make the below a joint "Paradigm" section, then human behavior, model behavior and comparison)
-
-# Experiment
+# Experiment 1: Adults
 
@@
 ### Participants
-Participants were `r length(unique(raw$SID))` children recruited from the Children's Discovery Museum of San Jose and Bing Nursery School.
-Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r length(unique(hum$SID))` were analyzed, including `r age[1]` 2-year-olds, `r age[2]` 3-year-olds, `r age[3]` 4-year-olds, `r age[4]` 5-year-olds, and `r age[5]` 6-year-olds.\footnote{The collected sample differed from our planned sample size of 16 each of 3-, 4-, and 5-year-olds due to availability of participants (see preregistration: https://osf.io/37qvb/).}
+Participants were `r Nad` adults recruited online via Amazon Mechanical Turk.
 
@@
 
-```{r object-sets}
-shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism", "space")
+## Results
 
-a = c("pyramid", "torus", "trig prism")
-b = c("cone", "octahedron", "pipe")
-c = c("bowl", "dumbbell", "pentagon")
+```{r adult-agg}
+adult_trial_agg <- adult_long %>% group_by(drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
+```
 
-hum <- hum %>% 
-  mutate(DropSet=ifelse(StimSet %in% c("ba","ca"), "A", ifelse(StimSet %in% c("ab","cb"), "B", "C")),
-         TargetSet=ifelse(StimSet %in% c("ab","ac"), "A", ifelse(StimSet %in% c("ba","bc"), "B", "C")))
-```
+# Experiment 2: Children
+
+## Method
+
+### Participants
+Participants were `r Nch` children recruited online via XX.
+Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
+After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+
+### Materials
 
@@
 
-The set of 9 objects were divided into 3 subsets (A = {pyramid, torus, triangular prism}, B = {cone, octahedron, pipe}, and C = {bowl, dumbbell, pentagon}). 
-These subsets served as sets (A, B, C) of target or drop objects in six successive blocks of 2 trials, making a total of 12 trials per participant.
-For example, in Order 1, in the first block of 2 trials, set A served as the target objects from which the child chose to drop on the target objects (set B).
-The target:drop block sequence for Order 1 was A:B, B:C, C:A, A:C, B:A, C:B.
-The sequence for Order 2 was the reverse of Order 1: C:B, B:A, A:C, C:A, B:C, A:B.
-Participants were assigned to condition in counterbalanced order.
-
-Target objects were placed in a circular bin (25 in diameter x 10 in height). 
-The bin was divided with tape into sections of equal area, and one target object from the appropriate set was placed in the center of each third. 
-Drop objects were presented to participants on a table at approximately eye level.
-
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Sets of 3D objects used for dropping and as targets."}
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Set of 3D objects used for dropping and as targets.
+[REPLACE]"}
 img <- png::readPNG("figs/drop_sets.png")
@@
 We introduced children to a set of 3D-printed toy objects ("blocks").
-The child played a game where they could pick which of three blocks to drop in a bin containing three other blocks, to see what happens. 
+
 An example trial is illustrated in Figure 2.
-We then swapped target/drop blocks, based on assigned order sequence, and asked the child to do the same selection and dropping a dozen times. 
-Finally, we asked the child to build a "cool" tower with any of the toy blocks for about one minute.
 
-Based on piloting, we estimated the activity would would only require five minutes to complete. 
+Based on piloting, we estimated the activity would would only require X minutes to complete. 
 In both conditions, a video camera was used to record the play session from an angle above the bin, to show child's block selection and drop location as well as child's completed tower. 
-After child notified the researcher that they were finished building their tower, the session was completed and camera was turned off.
+After child notified the researcher that they were finished building their tower, the session was completed.
 
-```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial in which the participant chose to drop the pyramid from set A on the pentagonal prism in the target set (B)."}
+```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial in which the participant chose to drop the pyramid on the pentagonal prism.
+[REPLACE]"}
 img <- png::readPNG("figs/DropTaskFigure.png")
@@
 
-### Drop Coding Procedure
-
-Each session's video was manually coded for drop object choice and target location per trial.
-Drop choice was defined as the participant's selection of one of the three available drop set objects, to be dropped into the bin containing the set of the three potential target objects. 
-The bin was divided into three wedge-shaped sections of equal area, demarcated with a thin black line.
-One of the target set's objects was placed in the middle of each section of the bin. 
-Target location was defined as either i) the object the dropped object collided with, ii) a collision with empty space inside the bin, or iii) falling outside the bin.
-If the dropped object collided with empty space, we also recorded the target object it landed closest to. 
-We also recorded events where the dropped object bounced from empty space or a target object then collided with other target object(s), including the number of collisions and identity of the target(s) hit.
-
-Trials were excluded if the child i) dropped an object outside the bin, ii) touched target object(s) prior to a drop, iii) dropped an object during set change, iv) selected more than one object to drop, or iv) dropped (or threw) object from too high (>1.5 m).
-Trials were also excluded if the experimenter made a mistake (e.g., used the wrong stimulus set or repeated a trial more than twice).
-
 ## Results
 
-```{r chance-comparison}
-hum$TargetSpace = ifelse(hum$DropLocation=="space", hum$WhichSpace, hum$DropLocation)
+```{r child-data-agg}
+child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
 
-report_chisq <- function(X) {
-  # e.g. X^2 (2, N = 88) = 2.1, p = .35
-  pval = round(X$p.value, 3)
-  if(pval==0) { 
-    pval = ", p<.001" 
-  } else {
-    pval = paste0(", p=",pval)
-  }
-  return(paste0("($X^2$(", X$parameter, ", N=", sum(X$expected), ") = ", round(X$statistic,2), pval, ")"))
-}
+ch_ad_cor <- cor.test(child_trial_agg$chose_target, adult_trial_agg$chose_target)
 
-# see if children's choices (per subset) are random
-drop_ch = table(hum$StimSet, hum$DropChoice)
-# chisq.test(rbind(colSums(drop_ch[,a]), rep(sum(drop_ch[,a]/3), 3)) )
-
-Xa_drop = chisq.test( colSums(drop_ch[,a]) ) # p<.001
-Xb_drop = chisq.test( colSums(drop_ch[,b]) ) # p=.01
-Xc_drop = chisq.test( colSums(drop_ch[,c]) ) # p=.056
-
-target_ch = table(hum$StimSet, hum$DropLocation)
-
-Xa_targ = chisq.test( colSums(target_ch[,a]) ) # n.s.
-Xb_targ = chisq.test( colSums(target_ch[,b]) ) # n.s.
-Xc_targ = chisq.test( colSums(target_ch[,c]) ) # n.s.
-
-targetloc_ch = table(hum$StimSet, hum$TargetSpace)
-Xa_tloc = chisq.test( colSums(targetloc_ch[,a]) ) # n.s.
-Xb_tloc = chisq.test( colSums(targetloc_ch[,b]) ) # n.s.
-Xc_tloc = chisq.test( colSums(targetloc_ch[,c]) ) # n.s.
-
-# 'misses' by age
-space_age = table(subset(hum, DropLocation=="space")$Age_Group)
-all_age = table(hum$Age_Group)
-#Xmiss_age = chisq.test(space_age, p=all_age / sum(all_age)) # n.s.
-prop_space = sum(space_age) / sum(all_age)
-
-age_s <- hum %>% 
-  group_by(SID, Age_Exact) %>%
-  summarise(miss=sum(DropLocation=="space"), N=n()) %>%
-  mutate(prop_miss = miss / N)
-age_miss = cor.test(age_s$prop_miss, as.numeric(age_s$Age_Exact))
-
-# now check DropChoice x TargetLocation interactions
-# maybe we do chisq.test on particular combinations? e.g., for DropSet A and TargetSet B?
-dA = subset(hum, DropSet=="A" & TargetSet=="B")
-dto = table(dA$DropChoice, dA$DropLocation)[,1:3]
-#dto = table(hum$DropChoice, hum$DropLocation)[,c(1:4,6:8,10:11)] # drop 'outside' and 'space'
-Xdto = chisq.test(dto)
-
+trial_tab <- child_trial_agg %>% select(-n) %>% 
+  bind_cols(adult_target_choice = adult_trial_agg$chose_target) %>% 
+  rename(child_target_choice = chose_target) 
 ```
@@
 We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
-We used chi-square test of independence on participants' drop choices from each set of objects (A, B, C).
-Participants' drop choices from set A significantly differed from chance `r report_chisq(Xa_drop)`, as did drop choices from set B `r report_chisq(Xb_drop)`.
-Participants' drop choices from set C did not significantly differ from chance `r report_chisq(Xc_drop)`.
-Table 1 shows a summary of participants' choice of drop objects per set.
-It is apparent that from set A, participants preferentially chose to drop the torus rather than the triangular prism (trig prism) or pyramid. 
-For set B, children more often avoided the octahedron, and instead chose the pipe or cone.
-Set C showed more equal rates of drop choice, but the dumbbell was somewhat more popular than the pentagonal prism (pentagon).
 
-What objects did children target with their drops?
-First, we noted that children very often did not hit any target object: on `r round(prop_space, 2)*100`% of trials, participants' dropped over empty space.
-It is not possible to determine whether children intentionally missed the available target objects, or whether their misses were errors due to noise in fine motor control.
-If the misses were just due to poor motor control, one might expect the number of misses by age to decrease, as older children should have better motor control.
-However, there was no significant correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(age_miss, format="rmarkdown", print=F)`), which may suggest that dropping objects on empty space may be of interest to children of all ages, and not solely determined by a lack of fine motor control.
-Thus, we first analyze drops where participants' dropped objects directly hit the target objects.
-Chi-square tests of children's target collisions revealed that they did not significantly differ from chance for set A `r report_chisq(Xa_targ)`, B `r report_chisq(Xb_targ)`, or C `r report_chisq(Xc_targ)`.
+Were children's drop choices consistent with adults'?
+Correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(ch_ad_cor, format="rmarkdown", print=F)`).
 Table 2 shows a summary of participants' choice of target objects per set.
 
-Finally, we examine a more lenient analysis children's choice of target location (i.e., the identity of the closest target), regardless of whether there was a collision of drop and target objects.
-Chi-square tests of children's target collisions once more found that they did not significantly differ from chance for set A `r report_chisq(Xa_tloc)`, B `r report_chisq(Xb_tloc)`, or C `r report_chisq(Xc_tloc)`.
-Table 3 shows a summary of participants' choice of target locations per set.
+<!-- Finally, we examine a more lenient analysis children's choice of target location (i.e., the identity of the closest target), regardless of whether there was a collision of drop and target objects.
+-->
+<!-- Chi-square tests of children's target collisions once more found that ... -->
+<!-- Table 3 shows a summary of participants' choice of target locations per set. -->
 
-In summary, children showed some consistent preferences in their choice of objects to drop from each set, but no systematic preference for targeting particular objects.
-We now investigate whether there were interactions of drop objects and targets that children found particularly appealing. [ToDo: big chisq test?]
+<!-- In summary, children showed some consistent preferences in their choice of objects to drop from each set, but no systematic preference for targeting particular objects. -->
+<!-- We now investigate whether there were interactions of drop objects and targets that children found particularly appealing. [ToDo: big chisq test?] -->
 
-Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects?
+<!-- Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects?
 What proportion of the objects were targeted?
-
-```{r table1-drop, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
-get_table_string <- function(tableX, set) {
-  tt = sort(colSums(tableX[,set]))
-  tstr = paste(paste0(names(tt), " (", tt, "),"), collapse=' ')
-  tstr = gsub('.{1}$', '', tstr)
-  return(tstr)
-}
-dA = get_table_string(drop_ch, a)
-dB = get_table_string(drop_ch, b)
-dC = get_table_string(drop_ch, c)
-
-tabl <- tribble(~Set, ~`Drop Object (N)`, 
-                "A", dA,
-                "B", dB,
-                "C", dC)
-t1 <- xtable::xtable(tabl, caption="Children's drop object choices by set.")
-#tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-#                       caption = "This table prints across one column.")
-print(t1, type="latex", comment = F, table.placement = "H")
-```
-
-```{r table2-target, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
-tA = get_table_string(target_ch, a)
-tB = get_table_string(target_ch, b)
-tC = get_table_string(target_ch, c)
-
-tabl2 <- tribble(~Set, ~`Target Object (N)`, 
-                "A", tA,
-                "B", tB,
-                "C", tC)
-t2 <- xtable::xtable(tabl2, caption="Children's target object choices by set.")
-print(t2, type="latex", comment = F, table.placement = "H")
-```
-
-```{r table3-targetloc, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
-tA = get_table_string(targetloc_ch, a)
-tB = get_table_string(targetloc_ch, b)
-tC = get_table_string(targetloc_ch, c)
-
-tabl3 <- tribble(~Set, ~`Target Location (N)`, 
-                "A", tA,
-                "B", tB,
-                "C", tC)
-t3 <- xtable::xtable(tabl3, caption="Children's target location choices by set.")
-print(t3, type="latex", comment = F, table.placement = "H")
-```
+-->
 
@@
 
-fig_drop <- drop_choice_plot(hum, shapes)
-#print(fig_drop)
-```
-
-```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
-hum$Target = hum$DropLocation
-
-target_hit_plot <- function(dat, ymax=.66, shapes_vec) {
-  ch_cond <- dat %>% 
-    filter(Target!="outside") %>%
-    group_by(StimSet, Target) %>%
-    summarise(n = n()) %>%
-    mutate(freq = n / sum(n))
-
-  # need to add "space" as level of Target in human data
-  ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes_vec))
-  fig_targ_hit <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
-    geom_point(alpha=.8) +
-    scale_shape_manual(values=10:20) +
-    #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-    xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,ymax) + 
-    langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-    geom_hline(yintercept=.33, lty='dashed')
-}
-#print(fig_targ_hit)
-fig_targ_hit <- target_hit_plot(hum, ymax=.66, shapes)
-```
-
-```{r target-space, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
-
-ch_cond <- hum %>% 
-  filter(is.element(TargetSpace, shapes)) %>%
-  group_by(StimSet, TargetSpace) %>%
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-ch_cond$TargetSpace <- factor(ch_cond$TargetSpace, levels = shapes)
-fig_targ_space <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=TargetSpace, color=TargetSpace)) + # , size=n
-  geom_point(alpha=.8) +
-  scale_shape_manual(values=10:19) +
-  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Stimulus Set") + ylab("Rate of Targeted Location") + ylim(0,.66) + 
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  geom_hline(yintercept=.33, lty='dashed')
-#print(fig_targ_space)
-```
-
-```{r combined-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects 1) chosen as objects for dropping, 2) hit as targets (pink dots represent hitting empty space), and 3) whose drop location was closest to a target object, as a function of target/drop set pairing."}
-
-ggarrange(fig_drop, fig_targ_hit, fig_targ_space, nrow=1, 
-          #labels = c("Drop Choice", "Targeted Object Hit", "Targeted Location"),
-          common.legend=T, legend="bottom")
+#fig_drop <- drop_choice_plot(hum, shapes)
 ```
@@
 ```{r unique-drop-objects, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion of unique objects selected by participants.
-Error bars show boostrapped 95\\% confidence intervals."}
+Error bars show boostrapped 95\\% confidence intervals.", eval=F}
 # 12 trials, 9 objects; random selection would be 9/12 = 75%...
@@
 ```
-
-```{r drop-by-target, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Heatmap of participants' drop object choices by target location."}
-ch_loc <- hum %>% filter(DropLocation!="outside" & DropLocation!="space") %>%
-  group_by(DropChoice, DropLocation) %>% 
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-ggplot(ch_loc, aes(x=DropLocation, y=DropChoice)) + geom_tile(aes(fill=freq)) + 
-  scale_fill_gradient(low = "white", high = "steelblue") +
-  xlab("Target Location") + ylab("Drop Object") +
-  ggthemes::theme_few()
-```
-
-### Tower Task Results
-
-```{r load-tower-data}
-
-tower = read.csv2("../analysis/human-data/curiobaby_drop-data - cool tower.csv", sep=',', header=T, stringsAsFactors=F)
-hum = subset(tower, exclude!="Y")
-
-length(unique(tower$SID)) #61
-length(unique(hum$SID)) # 51 subjects
-
-hum$age_group = as.numeric(hum$age_group)
-hum$age_rounded = as.numeric(hum$age_rounded)
-hum$height_tallest = as.numeric(hum$height_tallest)
-hum$tallest_objects = as.character(hum$tallest_objects)
-hum$base_tallest = as.character(hum$base_tallest)
-
-ht_age = cor.test(hum$age_rounded, hum$height_tallest)
-```
-
-First we examine tower height as a function of age, finding that older children tend to build higher towers `r cor_apa(ht_age, format="rmarkdown", print=F)`.
-
-```{r plot-height-by-age, include=F}
-ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
-  summarise(n = n()) %>%
-  mutate(freq = n / sum(n))
-
-ggplot(ch_height, aes(x=age_rounded, y=height_tallest)) +
-  geom_smooth(method="lm", level=0.90) + geom_point(alpha=.8) +
-  scale_shape_manual(values=10:19) +
-  xlab("Age") + ylab("Height_Tallest") + ylim(0,10) +
-  langcog::scale_fill_solarized() + ggthemes::theme_few()
-```
-
-2. support x supported (counts)
-```{r heatmap-support-by-supported-counts}
-tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
-df = data.frame(support=NA, supported=NA, n=NA)
-for(s in 1:nrow(tower)) {
-  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
-  print(objs)
-  for(i in 2:length(objs)) {
-    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
-  }
-}
-df = na.omit(df)
-hm <- df %>% group_by(support, supported) %>% count(N=n()) 
-hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
-  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
-```
-
-3. support x supported (probabilities)
-pr (supported object | support object)
-```{r heatmap-support-by-supported-probs}
-tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
-df = data.frame(support=NA, supported=NA, n=NA)
-for(s in 1:nrow(tower)) {
-  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
-  print(objs)
-  for(i in 2:length(objs)) {
-    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
-  }
-}
-df = na.omit(df)
-hm1 <- df %>% 
-  group_by(support, supported) %>% 
-  summarise(n = n()) %>% 
-  group_by(support) %>%
-  mutate(freq = n / sum(n))
-hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
-  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
-```
-
-4. base and top distribution
-```{r base-and-top-objects}
-ch_extremes <- hum %>% 
-  group_by(base_tallest) %>% 
-  count(N=n()) %>%
-  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")
-
-ch_extremes %>% 
-  ggplot(aes(x = base_tallest, y = N)) + geom_bar(stat = "identity")
-
-```
-
-<!-- We find that towers vary in i) height, ii) stacks, and iii) components. -->
-
-<!-- 1. height x age -->
-<!-- -First we examine tower height, of the tallest stack, as a function of age. We find tower height increases with age (cor.test). -->
-
-<!-- 2a. number stacks x age -->
-<!-- -Number of stacks y/ n correlate with age. -->
-<!-- -what is "cool": younger and use of horizontal/adjacent tower building -->
-
-<!-- 2b. number collapses x age = intuitive physics (tower stability) -->
-<!-- -Hight and number of stacks due to stability issue. -->
-<!-- -Number of collapses -->
-
-<!-- 3. The structural components of the towers -->
-<!-- -support x supported -->
-<!-- -drop object probabilities correlate with objects used in tower? -->
-<!-- -first base selection as proxy of most interesting object -->
-<!-- -base and top distribution -->
-
-# Model
-
-## Random Policy
-
-## Noncurious Policy
-
-## Antagonistic Curiosity Policy
-
-## Results
-```{r load-model-data}
-load("../analysis/agent-data/model_data.RData") # md
-
-Shapes = c(sort(unique(md$DropChoice)), "space")
-
-rand_drop <- drop_choice_plot(subset(md, policy=="random"), Shapes)
-curio_drop <- drop_choice_plot(subset(md, policy=="curious"), Shapes)
-noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), Shapes)
-
-md$Target = md$DropLocation
-
-rand_targ <- target_hit_plot(subset(md, policy=="random"), ymax=1, Shapes)
-curio_targ <- target_hit_plot(subset(md, policy=="curious"), ymax=1, Shapes)
-noncurio_targ <- target_hit_plot(subset(md, policy=="noncurious"), ymax=1, Shapes)
-```
-
-```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}
-
-ggarrange(rand_drop, curio_drop, noncurio_drop, 
-          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, 
-          labels = c("Random", "Curious", "Noncurious"),
-          common.legend=T, legend="bottom")
-```
-
-## Comparison with Children
 

### 2021-01-12 paper/paper2021.Rmd
updated task figs

@@
 
+Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
+The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
+The printed objects were all yellow, rigid plastic material and designed to fit comfortably in a child's hand (dimension range: 3.8-10.1 cm).
+
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Set of 3D objects used for dropping and as targets."}
+img <- png::readPNG("figs/fig1-objects.png")
+grid::grid.raster(img)
+```
+
+## Procedure
+
+Participants were told they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
+An example trial is illustrated in Figure 2.
+
+```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial from Experiment 1 with adults.
+Trials in Experiment 2 (for children) were similar, but arranged for Zoom with the experimenter's face in the center."}
+img <- png::readPNG("figs/2AFC_DropTaskFig.png")
+grid::grid.raster(img)
+```
+
 ## Results
@@
 
-Stimuli were 3D-printed plastic objects produced using Blender 3D-modeling software. 
-The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
-The printed objects were all yellow, rigid plastic material and designed to fit comfortably in a child's hand (dimension range: 3.8-10.1 cm).
-
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Set of 3D objects used for dropping and as targets.
-[REPLACE]"}
-img <- png::readPNG("figs/drop_sets.png")
-grid::grid.raster(img)
-```
+The materials were the same as those used in Experiment 1.
 
@@
 After the parent provided informed consent, children were assigned to Order 1 or Order 2. Participants were assigned to condition in counterbalanced order.
-We introduced children to a set of 3D-printed toy objects ("blocks").
-
-An example trial is illustrated in Figure 2.
 
@@
 After child notified the researcher that they were finished building their tower, the session was completed.
-
-```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial in which the participant chose to drop the pyramid on the pentagonal prism.
-[REPLACE]"}
-img <- png::readPNG("figs/DropTaskFigure.png")
-grid::grid.raster(img)
-```
 

### 2021-01-13 paper/paper2021.Rmd
writing methods

@@
 
+To investigate the systematicity of people's preferences for physical interactions between objects, we began by studying adults, whom we might expect to be less idiosyncratic and thus more consistent than children in their choices.
+
 ## Method
@@
 ### Participants
-Participants were `r Nad` adults recruited online via Amazon Mechanical Turk.
+Participants were `r Nad` adults recruited online via Amazon Mechanical Turk who were paid $X for their participation.
 
@@
 Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
-The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, and triangular prism.
-The printed objects were all yellow, rigid plastic material and designed to fit comfortably in a child's hand (dimension range: 3.8-10.1 cm).
+The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, triangular prism, and ball (sphere; not pictured).
 
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Set of 3D objects used for dropping and as targets."}
+<!-- GK: possibly re-do this figure to have the proper orientations -->
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
 img <- png::readPNG("figs/fig1-objects.png")
@@
 
-## Procedure
+### Design
 
-Participants were told they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
-An example trial is illustrated in Figure 2.
+The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
+Participants were randomly assigned to each order.
+Each drop trial displayed an object X that is to be dropped on one of two other objects (Y or Z), as described in the following procedure.
+In the 20 trials, each of the above 3D objects was used twice as the drop object (X), and appeared at least twice (three times?? check) as potential targets.
+Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.
+That is, the target objects were chosen so that either (but not both) of them would be capable of either supporting or (partially) containing the dropped object.
+For example, if asked to drop the cone on either the torus or the octahedron, a containment relation could be achieved between the cone and the torus, but not the octahedron (and support is unlikely due to the small surface area of the octahedron).
+An example support relation is choosing to drop the pentagonal prism on the (equal diameter) pipe rather than the pyramid.
+Half of the 20 trials were designed to afford containment relations, and the other half afforded support relations.
+We refer to these designed containment and support relations as the "targets", and the alternatives objects as the "distractors".
+Distractors for each trial were the same for all participants, and were selected to 1) not afford containment/support of the dropped object, and 2) roughly equate the frequency of appearance of all 10 objects.
+
+### Procedure
+
+Participants were instructed that they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
+Participants were then given a practice trial (see Figure 2), in which they were told that they should imagine dropping a given object (the torus) on each of two toys (the dumbbell or the pentagonal prism) in a bin.
+They were than asked to choose which toy to drop the torus on, and prompted to choose the most most interesting or surprising combination.
+After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
+This was done to ensure that they understood the consequences of the choice they made.
+After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on, but without videos.
+Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (4-alternative forced choice).
+The goal of the catch trials was to encourage participants to attend to the objects and the choices they made.
+Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
+These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants.
 
@@
 
-The materials were the same as those used in Experiment 1.
+The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote.
+[Sama, maybe you can explain this and the procedure in a bit more detail? (example fig if we have space)]
 
@@
   rename(child_target_choice = chose_target)
+
+#knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
 ```
@@
 We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
+
+```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+adults' choices for each trial (dot), with bootstrapped 95\\% confidence intervals."}
+# add vert and horiz error bars 
+adult_long <- adult_long %>% rename(ID = ResponseId) %>%
+  mutate(Age = "adult") %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target)
+
+combo_dat <- child_long %>% mutate(ID = as.character(ID),
+                                Age = as.character(Age)) %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
+  bind_rows(adult_long) %>% 
+  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
+
+combo_dat %>% group_by(drop, target, relation, ID) %>%
+  group_by(drop, target, relation, AgeGroup) %>%
+  tidyboot_mean(chose_target, na.rm=T) %>%
+  select(-n, -empirical_stat) %>%
+  pivot_wider(names_from = AgeGroup, values_from = c(mean, ci_lower, ci_upper)) %>%
+  ggplot(aes(x=mean_adult, y=mean_child, group=relation, color=relation)) + 
+    geom_point(alpha=.6) + 
+    geom_errorbar(aes(ymin=ci_lower_child, ymax=ci_upper_child), alpha=.6) +
+    geom_errorbarh(aes(xmin=ci_lower_adult, xmax=ci_upper_adult), alpha=.6) + 
+    theme_bw() + ylim(0,1) + xlim(0,1) + 
+    xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
+    geom_abline(xintercept=0, slope=1, linetype="dashed") +
+    geom_smooth(method = "lm") 
+  #geom_text(aes(label=target)) #
+
+```
+
+```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
+pos = position_dodge(width = .9)
+
+p1 <- combo_dat %>%
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", "child"),
+         AgeGroup = factor(AgeGroup, levels=c("child", "adult"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
+
+p2 <- combo_dat %>% 
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
+                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
+
+#grid.arrange(p1, p2, nrow = 1)
+p2
+```
+
+Check reliability of responses within- and across-conditions (support and containment).
+
+```{r reliability}
+# split subjects in half, check cor between halves
+split_half_subj_cor <- function(dat, nsim=100) {
+  subjs = unique(dat$ID)
+  cors = rep(NA, nsim)
+  for(i in 1:nsim) {
+    idx1 = sample(subjs, size=length(subjs)/2)
+    idx2 = setdiff(subjs, idx1) # nonsampled items
+    h1 <- dat %>% filter(is.element(ID, idx1)) %>% 
+      group_by(AgeGroup, Trial) %>%
+      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
+    h2 <- dat %>% filter(is.element(ID, idx2)) %>% 
+      group_by(AgeGroup, Trial) %>%
+      summarise(mean = mean(chose_target, na.rm=T), .groups="keep")
+    cors[i] = cor(h1$mean, h2$mean)
+  }
+  return(cors)
+}
+
+# overall
+sh_subj = split_half_subj_cor(combo_dat)
+
+sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
+
+sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))
+
+sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
+
+sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
+
+# split items in half, check cor between halves...GK: I don't think we care about this
+
+```
+
+Split-half reliability for all subjects: `r round(mean(sh_subj),2)`.
+Split-half reliability for adults: `r round(mean(sh_subj_adult), 2)`.
+Split-half reliability for children: `r round(mean(sh_subj_child), 2)`.
+
+Split-half reliability for contain relations: `r round(mean(sh_subj_contain), 2)`.
+Split-half reliability for support relations: `r round(mean(sh_subj_support), 2)`.
 

### 2021-01-13 paper/paper2021.Rmd
exclusions

@@
 ### Participants
-Participants were `r Nad` adults recruited online via Amazon Mechanical Turk who were paid $X for their participation.
+Participants were 44 adults recruited online via Amazon Mechanical Turk who were paid $X for their participation.
 
@@
 Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (4-alternative forced choice).
-The goal of the catch trials was to encourage participants to attend to the objects and the choices they made.
+The goal of the catch trials was to encourage participants to attend to the objects and the choices they made, and to exclude any participants who were incorrect on 2 or more of the catch trials.
 Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
@@
 ## Results
+
+We analyzed data from the `r Nad` adults who completed the experiment and got more than 50% of the catch trials correct.
 

### 2021-01-14 paper/paper2021.Rmd
update child data

@@
      enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
-     comparisons. We children's choices (N=XX; 2-6 years of age) to those of adults (N=XX), and find
+     comparisons. We children's choices (N=66; 3-7 years of age) to those of adults (N=XX), and find
      systematic preference for drops affording particular relations (e.g., containment)
@@
 
-We analyzed data from the `r Nad` adults who completed the experiment and got more than 50% of the catch trials correct.
+We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct.
 
@@
 ### Participants
-Participants were `r Nch` children recruited online via XX.
+Participants were 73 children recruited online via XXX.
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+After exclusions [based on?], results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
 

### 2021-01-14 paper/paper2021.Rmd
Update paper2021.Rmd

@@
 ### Participants
-Participants were 44 adults recruited online via Amazon Mechanical Turk who were paid $X for their participation.
+Participants were 44 adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
 
@@
 Each drop trial displayed an object X that is to be dropped on one of two other objects (Y or Z), as described in the following procedure.
-In the 20 trials, each of the above 3D objects was used twice as the drop object (X), and appeared at least twice (three times?? check) as potential targets.
+In the 20 trials, each of the above 3D objects was used twice as the drop object (X), and appeared four times as potential targets.
 Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.

### 2021-01-14 paper/paper2021.Rmd
Update paper2021.Rmd

@@
 Participants were then given a practice trial (see Figure 2), in which they were told that they should imagine dropping a given object (the torus) on each of two toys (the dumbbell or the pentagonal prism) in a bin.
-They were than asked to choose which toy to drop the torus on, and prompted to choose the most most interesting or surprising combination.
+They were than asked to choose which toy to drop the torus on, and prompted to choose the most interesting or surprising combination.
 After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
@@
 After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on, but without videos.
-Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (4-alternative forced choice).
+Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (3-alternative forced choice).
 The goal of the catch trials was to encourage participants to attend to the objects and the choices they made, and to exclude any participants who were incorrect on 2 or more of the catch trials.
@@
 ### Participants
-Participants were 73 children recruited online via XXX.
+Participants were 73 children recruited online via Bing Nursery School and targeted Facebook Ads.
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
@@
 The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote.
+Introductory slides were added for informed consenting process and screen configuration, where researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
+
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
+img <- png::readPNG("figs/online-child-practice-trial")
+grid::grid.raster(img)
+```
+
 [Sama, maybe you can explain this and the procedure in a bit more detail? (example fig if we have space)]
@@
 
-After the parent provided informed consent, children were assigned to Order 1 or Order 2. Participants were assigned to condition in counterbalanced order.
+Based on piloting, we estimated the activity would would only require 10 minutes to complete.
+After the parent provided informed consent, children were assigned to Order 1 or Order 2.
+Participants were assigned to condition in counterbalanced order.
+In both conditions, a video recording was taken of the online session.
 
-Based on piloting, we estimated the activity would would only require X minutes to complete. 
-In both conditions, a video camera was used to record the play session from an angle above the bin, to show child's block selection and drop location as well as child's completed tower. 
-After child notified the researcher that they were finished building their tower, the session was completed.
+To accompany the practice  trial, children were shown the three physical objects on video, to ensure understanding of their 3D properties.
+Verbal responses were collected from children to indicate the slection of target object Y or Z.
+To prevent left/right mapping confusion, target objects Y and Z were overlayed on thirds of the screen with either red or green background color, which were counterbalanced across trials.
+The child was asked to verbally select target object and then to indicate whether it was on the "red side or the green side."
 

### 2021-01-15 paper/paper2021.Rmd
minor edits

@@
 <!-- GK: possibly re-do this figure to have the proper orientations -->
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
+```{r fig3-child-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
 img <- png::readPNG("figs/fig1-objects.png")
@@
 Participants were then given a practice trial (see Figure 2), in which they were told that they should imagine dropping a given object (the torus) on each of two toys (the dumbbell or the pentagonal prism) in a bin.
-They were than asked to choose which toy to drop the torus on, and prompted to choose the most interesting or surprising combination.
+They were then asked to choose which toy to drop the torus on, and prompted to choose the most interesting or surprising combination.
 After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
@@
 ```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
-img <- png::readPNG("figs/online-child-practice-trial")
+img <- png::readPNG("figs/online-child-practice-trial.png")
 grid::grid.raster(img)

### 2021-01-15 analysis/exp2_analysis.Rmd
new mturk data

@@
 ```{r load-human-data, echo=FALSE}
-raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
+#raw_old = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
+raw = read_csv("exp2-mturk-data/MturkAdultDrop DataRound2  - Combined.csv")
 # row 1 is empty, row 2 should be header
@@
 # Q38-Q41 = which toy did you just drop? (catch trials)
-d = d %>% 
-  dplyr::select(-Q11, -Q38, -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>%
+d = d %>% # Q38 no longer exists ..
+  dplyr::select(-Q11,  -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>% # -Q38,
   rename(Duration = `Duration (in seconds)`)

### 2021-01-15 analysis/exp2_analysis.Rmd
new mturk data incorporated

@@
 d = d %>% # Q38 no longer exists ..
-  dplyr::select(-Q11,  -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>% # -Q38,
+  dplyr::select(-Q11, -`Q38- Catch`, -`Q39- Catch`, -`Q40- Catch`, -`Q41- Catch`, -Q42, -Q43, -`Random ID`) %>% # -Q38,
   rename(Duration = `Duration (in seconds)`)

### 2021-01-15 paper/paper2021.Rmd
new mturk data incorporated

@@
 ### Participants
-Participants were 44 adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
+Participants were XX adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
 
@@
 
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
 img <- png::readPNG("figs/online-child-practice-trial.png")
@@
 ```
-
-[Sama, maybe you can explain this and the procedure in a bit more detail? (example fig if we have space)]
 

### 2021-01-15 paper/paper2021.Rmd
writing results

@@
      enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
-     comparisons. We children's choices (N=66; 3-7 years of age) to those of adults (N=XX), and find
-     systematic preference for drops affording particular relations (e.g., containment)
+     comparisons. We compared children's choices (N=66; 3-7 years of age) to those of adults (N=155), 
+     and find increasingly strong preference for choices affording particular relations (e.g., 
+     containment) across development, as well as an adult bias for choosing support relations.
 
@@
 Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
-Recent studies have provided empirical support for this basic idea: XX-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
+Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
 According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
@@
 Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
-However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge, and thus do not specify or constrain which events might moderately discrepant from this knowledge.
+However, the measures used in this literature have typically been coarse-grained with respect to infants' and children's physical knowledge, and thus do not specify or constrain which events might be moderately discrepant from this knowledge.
 For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015; @Baillargeon2007).
@@
 In sum, this paper presents a unified paradigm for advancing theories of curiosity and its role in guiding the development of knowledge about the physical world. 
-We present: (1) a computational theory of intrinsic motivation instantiated in an artificial reinforcement-learning agent that explores a simulated 3D environment; (2) a novel dataset that measures children's actions in a novel physical exploration task; and (3) quantitative comparisons between the actions taken by the artificial agent and children on the same set of tasks.
+We present: (1) a computational theory of intrinsic motivation instantiated in an artificial reinforcement-learning agent that explores a simulated 3D environment; (2) two datasets that measure adults' and children's actions in a novel physical exploration task; and (3) quantitative comparisons between the actions taken by the artificial agent and children on the same set of tasks.
 Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.
@@
 
-To investigate the systematicity of people's preferences for physical interactions between objects, we began by studying adults, whom we might expect to be less idiosyncratic and thus more consistent than children in their choices.
+To investigate the systematicity of people's preferences for physical interactions between objects, we began by studying adults, whom we might expect to be less idiosyncratic and thus more consistent in their choices than children.
+Our design is motivated by the results of a pilot study conducted in-person in January, 2020, in which we asked adults to select which of a pair of 3D-printed toy blocks (see Figure 1) they would like to drop on a given target object from the set, or vice-versa: on which of a given pair of target objects would they like to drop a given object.
+In the pilot study (N=15), the pairs of target or drop objects were chosen essentially at random, but were the same for all participants.
+We were surprised to find consistency in adults' preferences for many of the trials: especially when given a drop object and asked to choose one of two target objects, adults were quite often (75-90%) targeting that object that would either *contain* or *support* the dropped object (i.e., the pipe could contain the cone; the pentagonal prism could support the octahedron).
+This consistency in their choices is remarkable given that there are many other possible goals that people might choose in order to make something "interesting" happen: they might attempt to make the dropped object roll or bounce far from the target, or rebound in an unexpected direction, but in fact most people settled on attempting support or containment relations.
+Thus, we set out to examine the development of these preferences, first in a large adult sample, and then in young children, since some have characterized children as simply being noisy adults.
 
@@
 ### Participants
-Participants were XX adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
+Participants were 200 [check pre-exclusion] adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
 
@@
 Half of the 20 trials were designed to afford containment relations, and the other half afforded support relations.
-We refer to these designed containment and support relations as the "targets", and the alternatives objects as the "distractors".
+We refer to these designed containment and support relations as the "targets", and the alternative objects as the "distractors".
 Distractors for each trial were the same for all participants, and were selected to 1) not afford containment/support of the dropped object, and 2) roughly equate the frequency of appearance of all 10 objects.
@@
 
-We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct.
+We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (XX participants were excluded for not meeting this criterion).
+The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
+2) are they more consistent with trials that afford support or containment relations?
+and 3) are there other apparent factors that drive their preferences?
+Our analysis addresses each in turn.
+Table 1 shows the mean number of participants choosing the designed target relation for each of the 20 trials [should also show alternative target object?]. 
+Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance.
+As can be seen in Table 1, participants significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
 
 ```{r adult-agg}
-adult_trial_agg <- adult_long %>% group_by(drop, target) %>% # alt, 
-  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
+adult_trial_agg <- adult_long %>% group_by(drop, target, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>% # , n=n()
+  arrange(relation, desc(chose_target))
+```
+
+```{r adults-table, results="asis"}
+# how to do 2-col table? , fig.env = "figure*" 
+adtab <- xtable::xtable(adult_trial_agg, digits=2, 
+                       caption = "Adult target preferences per trial.")
+
+print(adtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
 ```

### 2021-01-15 paper/paper2021.Rmd
finished Exp 1 (adult) results

@@
 
+```{r}
+ad_subj_agg <- adult_long %>% group_by(ResponseId, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T))
+
+ad_rel_means <- ad_subj_agg %>% group_by(relation) %>% summarize(M=mean(chose_target))
+
+ad_supp_cont <- t.test(subset(ad_subj_agg, relation=="contain")$chose_target -
+         subset(ad_subj_agg, relation=="support")$chose_target)
+```
+
+Were adults more consistent in their choices on support or containment trials?
+Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations (M=`r round(ad_rel_means[1,]$M,2)`) than support relations (M=`r round(ad_rel_means[2,]$M,2)`; one-sample `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
+For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.
+
 # Experiment 2: Children
 
+Experiment 1 showed that adults show remarkably consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
+Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
+
 ## Method
+We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
 
@@
 ### Materials
-
 The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote. 
@@
 
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Children online study screen configuration."}
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
+Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
 img <- png::readPNG("figs/online-child-practice-trial.png")
@@
 
-Based on piloting, we estimated the activity would would only require 10 minutes to complete.
-After the parent provided informed consent, children were assigned to Order 1 or Order 2.
+Based on piloting, we estimated the activity would would require 10 minutes to complete. 
+After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders. 
 Participants were assigned to condition in counterbalanced order. 

### 2021-01-15 paper/paper2021.Rmd
writing Exp 2 results

@@
 This consistency in their choices is remarkable given that there are many other possible goals that people might choose in order to make something "interesting" happen: they might attempt to make the dropped object roll or bounce far from the target, or rebound in an unexpected direction, but in fact most people settled on attempting support or containment relations.
-Thus, we set out to examine the development of these preferences, first in a large adult sample, and then in young children, since some have characterized children as simply being noisy adults.
+Thus, we set out to examine the development of these preferences, first in a large adult sample, and then in young children.
+<!-- , since some have characterized children as simply being noisy adults.
+-->
 
@@
 To accompany the practice  trial, children were shown the three physical objects on video, to ensure understanding of their 3D properties. 
-Verbal responses were collected from children to indicate the slection of target object Y or Z.
-To prevent left/right mapping confusion, target objects Y and Z were overlayed on thirds of the screen with either red or green background color, which were counterbalanced across trials.
+Verbal responses were collected from children to indicate the selection of target object Y or Z. 
+To prevent left/right mapping confusion, target objects Y and Z were overlaid on thirds of the screen with either red or green background color, which were counterbalanced across trials. 
 The child was asked to verbally select target object and then to indicate whether it was on the "red side or the green side."
@@
 trial_tab <- child_trial_agg %>% select(-n) %>% 
-  bind_cols(adult_target_choice = adult_trial_agg$chose_target) %>% 
-  rename(child_target_choice = chose_target)
+  bind_cols(adult = adult_trial_agg$chose_target) %>% 
+  rename(child = chose_target) %>%
+  arrange(relation, desc(child))
 
@@
 
-We first examine children's choice of drop objects and target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
+```{r child-table, results="asis"}
+# how to do 2-col table? , fig.env = "figure*" 
+chtab <- xtable::xtable(trial_tab, digits=2, 
+                       caption = "Children's and adults' target preferences per trial.")
+
+print(chtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
+```
+
+We first examine children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
 

### 2021-01-15 paper/paper2021.Rmd
finished Exp 2 results, discussion rough draft

@@
 author-information: > 
-    \author{{\large \bf George (kachergis@stanford.edu)} \\ Department of Psychology, Stanford University \\ Madison, WI 53706 USA
-    \AND {\large \bf Judith Fan (SDJ@Macc.Wisc.Edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA}
+    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
+    \AND {\large \bf Judith Fan (jefan@ucsd.edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA
+    \AND {\large \bf Dan Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
+    \AND {\large \bf Michael C.~Frank} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA}
 
@@
 Our analysis addresses each in turn.
-Table 1 shows the mean number of participants choosing the designed target relation for each of the 20 trials [should also show alternative target object?]. 
-Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance.
+Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials [should also show alternative target object?]. 
+Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance [adjust criterion for multiple comparisons?].
 As can be seen in Table 1, participants significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
@@
 ```{r adult-agg}
-adult_trial_agg <- adult_long %>% group_by(drop, target, relation) %>% # alt, 
+adult_trial_agg <- adult_long %>% group_by(relation, drop, target) %>% # alt, 
   summarize(chose_target=mean(chose_target, na.rm=T)) %>% # , n=n()
@@
 
-Based on piloting, we estimated the activity would would require 10 minutes to complete. 
-After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders.
-Participants were assigned to condition in counterbalanced order. 
-In both conditions, a video recording was taken of the online session.
+Based on piloting, we estimated the activity would require 10 minutes to complete. 
+After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
+A video recording was taken of the online session.
 
@@
 
+We first examine children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
+Table 2 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1 [maybe just drop Table 1?].
+Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05 [use stricter for mult comparisons?
+Bonf=.0025]) from chance.
+Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
+On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
+
 ```{r child-data-agg}
@@
 ch_ad_cor <- cor.test(child_trial_agg$chose_target, adult_trial_agg$chose_target)
+# Were children's drop choices consistent with adults'? (trial-level, not sig)
+# Correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(ch_ad_cor, format="rmarkdown", print=F)`).
 
@@
 
+adult_long <- adult_long %>% rename(ID = ResponseId) %>%
+  mutate(Age = "adult") %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target)
+
+combo_dat <- child_long %>% mutate(ID = as.character(ID),
+                                Age = as.character(Age)) %>%
+  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
+  bind_rows(adult_long) %>% 
+  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
 #knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
+
+# support vs. contain relations in children
+ch_subj_agg <- child_long %>% group_by(ID, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T))
+
+ch_rel_means <- ch_subj_agg %>% group_by(relation) %>% summarize(M=mean(chose_target))
+
+ch_supp_cont <- t.test(subset(ad_subj_agg, relation=="contain")$chose_target -
+         subset(ad_subj_agg, relation=="support")$chose_target)
 ```
@@
 
-We first examine children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects.
+Were children more consistent in their choices on support or containment trials?
+As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations (M=`r round(ch_rel_means[1,]$M,2)`) than support relations (M=`r round(ch_rel_means[2,]$M,2)`; one-sample `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+Overall, children did not show a significant preference for choosing the support relation [should we add a regression with trial_type * age (3 - 18=adult)?].
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that grows with age, and that is stronger for containment.
 
-```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
-adults' choices for each trial (dot), with bootstrapped 95\\% confidence intervals."}
+```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
+pos = position_dodge(width = .9)
+
+combo_dat %>% 
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
+                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1) +
+  ylab("Proportion Choosing Target Relation") +
+  labs(fill = "Age Group")
+
+```
+
+## Comparison of Children's vs. Adults' Preferences
+
+Finally, we compare the trial-level preferences of children and adults.
+Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2). 
+If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to $y=0.5$. 
+At a glance, this seems to support the hypothesis that "children are noisy adults."
+We will re-examine this hypothesis with model-based predictions for each trial.
+
+```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.5, fig.height=3.75, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+adults' preferences on each trial (dot), with bootstrapped 95\\% confidence intervals."}
 # add vert and horiz error bars 
-adult_long <- adult_long %>% rename(ID = ResponseId) %>%
-  mutate(Age = "adult") %>%
-  select(ID, Age, Trial, choice, drop, target, relation, chose_target)
-
-combo_dat <- child_long %>% mutate(ID = as.character(ID),
-                                Age = as.character(Age)) %>%
-  select(ID, Age, Trial, choice, drop, target, relation, chose_target) %>%
-  bind_rows(adult_long) %>% 
-  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
-
 combo_dat %>% group_by(drop, target, relation, ID) %>%
@@
     geom_abline(xintercept=0, slope=1, linetype="dashed") +
-    geom_smooth(method = "lm") 
+    geom_smooth(method = "lm") +
+    theme(legend.position = "bottom")
   #geom_text(aes(label=target)) #
@@
 ```
-
-```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
-adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
-pos = position_dodge(width = .9)
-
-p1 <- combo_dat %>%
-  mutate(AgeGroup = ifelse(Age=="adult", "adult", "child"),
-         AgeGroup = factor(AgeGroup, levels=c("child", "adult"))) %>%
-  group_by(ID, AgeGroup, relation) %>% # alt, 
-  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
-  group_by(relation, AgeGroup) %>%
-  tidyboot_mean(chose_target) %>%
-  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
-  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
-
-p2 <- combo_dat %>% 
-  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
-                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
-  group_by(ID, AgeGroup, relation) %>% # alt, 
-  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
-  group_by(relation, AgeGroup) %>%
-  tidyboot_mean(chose_target) %>%
-  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
-  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
-
-#grid.arrange(p1, p2, nrow = 1)
-p2
-```
-
-Check reliability of responses within- and across-conditions (support and containment).
 
@@
 
+set.seed(42)
 # overall
-sh_subj = split_half_subj_cor(combo_dat)
-
+#sh_subj = split_half_subj_cor(combo_dat)
 sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
@@
 
-Split-half reliability for all subjects: `r round(mean(sh_subj),2)`.
-Split-half reliability for adults: `r round(mean(sh_subj_adult), 2)`.
-Split-half reliability for children: `r round(mean(sh_subj_child), 2)`.
-
-Split-half reliability for contain relations: `r round(mean(sh_subj_contain), 2)`.
-Split-half reliability for support relations: `r round(mean(sh_subj_support), 2)`.
-
-Were children's drop choices consistent with adults'?
-Correlation between children's individual proportion of "missed" targets and their age (`r cor_apa(ch_ad_cor, format="rmarkdown", print=F)`).
-Table 2 shows a summary of participants' choice of target objects per set.
+Finally, we also examined the split-half reliability of children's and adults' choices by repeatedly  splitting the samples in half and testing the correlation between the halves.
+Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`), and for children is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
+The overall split-half reliability on the containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and for support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
+[should we separately report these for adults and children?]
 
@@
 
+## Model Comparison
+
+Can these preferences be predicted by heuristic models of physical interactions?
+We implement and test a few models, generate relative preferences for the same drop objects and target object pairs used in Experiments 1 and 2, and see how well each model explains the strength of trial-level preferences seen in participants.
+
 # Discussion 
+This study aimed to investigate what physical interactions between objects most evoke curiosity.
+After finding surprising consistency in an in-person pilot study of adults, an online study designed to make possible the same support and containment relations between dropped and target objects replicated this finding of consistency: adults are interested in dropping objects into containers, and to a lesser degree on top of supporting objects.
+Experiment 2 found the same pattern in children, but with greater noise -- even to the extent that younger children were at-chance at choosing the support relation on most trials.
+
+Thus, we find an early-emerging interest in containment (cite Marianella Casasola and Leslie B. Cohen) that persists into adulthood, along with a weaker interest in support relations.
+Is containment inherently more satisfying, or is there greater interest because it is more achievable? (Less susceptible to small amounts of error)
+Are children less interested in relations that are more difficult to achieve with more motor noise?
+Or are they less aware (or simply less interested in) support?
+Or do children find some other goal relatively more enticing?
 

### 2021-01-15 paper/paper2021.Rmd
authors

@@
 author-information: > 
-    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
+    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \and {\large \bf Bria Long} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
     \AND {\large \bf Judith Fan (jefan@ucsd.edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA
-    \AND {\large \bf Dan Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
+    \AND {\large \bf Daniel Bear} \and {\large \bf Daniel Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
     \AND {\large \bf Michael C.~Frank} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA}

### 2021-01-16 models/generate_stimuli.py
beginning of stimuli generation for model code

@@ -1,0 +1,73 @@
+import os
+import drop
+
+OBJECT_INFO = {}
+
+CONTAIN_SCENARIOS = [('bowl', ['pyramid', 'trianular_prism']),
+                     ('cone', ['torus', 'octahedron']),
+                     ('dumbbell', ['pipe', 'pyramid']),
+                     ('octahedron', ['pipe', 'sphere']),
+                     ('pentagon', ['bowl', 'sphere']),
+                     ('pipe', ['cone', 'octahedron']),
+                     ('pyramid', ['torus', 'dumbbell']),
+                     ('sphere', ['bowl', 'pentagon']),
+                     ('torus', ['cone', 'dumbbell']),
+                     ('triangular prism', ['bowl', 'dumbbell'])]
+
+SUPPORT_SCENARIOS = [('bowl', ['torus', 'triangular prism']),
+                     ('cone', ['triangular prism', 'sphere']),
+                     ('dumbbell', ['pentagon', 'octahedron']),
+                     ('octahedron', ['pentagon', 'pyramid']),
+                     ('pentagon', ['pipe', 'pyramid']),
+                     ('pipe', ['torus', 'dumbbell']),
+                     ('pyramid', ['triangular prism', 'sphere']),
+                     ('sphere', ['pipe', 'cone']),
+                     ('torus', ['bowl', 'octahedron']),
+                     ('triangular prism', ['pentagon', 'cone'])]
+
+SCENARIO_TYPES = 10 * ['contain'] + 10 * ['support']
+
+SCENARIOS = CONTAIN_SCENARIOS + SUPPORT_SCENARIOS
+
+def get_drop_target_pairs(scenarios):
+    pairs = []
+    for sd, st in scenarios:
+        pairs.append((sd, st[0]))
+        pairs.append((sd, st[1]))
+    pairs = list(set(pairs))
+    return pairs
+
+
+def main(output_dir, num):
+    for (sd, st), tp in zip(SCENARIOS, SCENARIO_TYPE):
+        if isinstance(sd, str):
+            drop = sd 
+            drop_rotation = [0, 0, 0]
+            drop_scale = 1
+        else:
+            drop, drop_rotation, drop_scale = sd
+        if isinstance(st, str):
+            target = st
+            target_rotation = [0, 0, 0]
+            target_scale = 1
+        else:
+            target, target_rotation, target_scale = st
+
+        dc = drop.Drop(random=0,
+                       seed=0,
[…]

### 2021-01-17 models/generate_stimuli.py
minor bugfixes

@@ -1,5 +1,5 @@
 import os
-import drop
+import drop #how are we dealing with the fact that we might want to reuse controller code like this? drop controller is not in any package!
 
 OBJECT_INFO = {}
 
@@ -39,35 +39,43 @@ def get_drop_target_pairs(scenarios):
 
 
 def main(output_dir, num):
-    for (sd, st), tp in zip(SCENARIOS, SCENARIO_TYPE):
+    scenarios = get_drop_target_pairs(SCENARIOS)
+    print(scenarios)
+    scenes = list(zip(scenarios, SCENARIO_TYPES))
+    scenes = scenes[:1]
+    for (sd, st), tp in scenes:
         if isinstance(sd, str):
-            drop = sd 
+            drop_obj = sd 
             drop_rotation = [0, 0, 0]
             drop_scale = 1
         else:
-            drop, drop_rotation, drop_scale = sd
+            drop_obj, drop_rotation, drop_scale = sd
         if isinstance(st, str):
-            target = st
+            target_obj = st
             target_rotation = [0, 0, 0]
             target_scale = 1
         else:
-            target, target_rotation, target_scale = st
+            target_obj, target_rotation, target_scale = st
 
-        dc = drop.Drop(random=0,
+        dc = drop.Drop(randomize=0,
                        seed=0,
                        height_range=[0.75, 1.25],
                        drop_scale_range=[drop_scale, drop_scale],
                        drop_jitter=0.2,
                        drop_rotation=drop_rotation,
-                       drop_objects = [drop],
-                       target_obejcts = [target],
+                       drop_objects = [drop_obj],
+                       target_objects = [target_obj],
                        target_scale_range=[target_scale, target_scale],
                        target_rotation=target_rotation,
+                       camera_min_angle=0,
+                       camera_max_angle=0
         )
 
         suffix = '%s_on_%s_%s' % (drop, target, tp)
         output_path = os.path.join(output_dir, suffix)
         dc.run(num=num,
-               output_dir=output_path)
+               output_dir=output_path,
+               width=256,
+               height=256)
                
                        

### 2021-01-17 models/generate_stimuli.py
minpor

@@ -57,7 +57,9 @@ def main(output_dir, num):
         else:
             target_obj, target_rotation, target_scale = st
 
-        dc = drop.Drop(randomize=0,
+        dc = drop.Drop(launch_build=False,
+                       port=1075,
+                       randomize=0,
                        seed=0,
                        height_range=[0.75, 1.25],
                        drop_scale_range=[drop_scale, drop_scale],
@@ -71,7 +73,7 @@ def main(output_dir, num):
                        camera_max_angle=0
         )
 
-        suffix = '%s_on_%s_%s' % (drop, target, tp)
+        suffix = '%s_on_%s_%s' % (drop_obj, target_obj, tp)
         output_path = os.path.join(output_dir, suffix)
         dc.run(num=num,
                output_dir=output_path,

### 2021-01-17 models/generate_stimuli.py
bugfixes to stimulus generation

@@ -12,18 +12,18 @@ CONTAIN_SCENARIOS = [('bowl', ['pyramid', 'trianular_prism']),
                      ('pyramid', ['torus', 'dumbbell']),
                      ('sphere', ['bowl', 'pentagon']),
                      ('torus', ['cone', 'dumbbell']),
-                     ('triangular prism', ['bowl', 'dumbbell'])]
+                     ('triangular_prism', ['bowl', 'dumbbell'])]
 
-SUPPORT_SCENARIOS = [('bowl', ['torus', 'triangular prism']),
-                     ('cone', ['triangular prism', 'sphere']),
+SUPPORT_SCENARIOS = [('bowl', ['torus', 'triangular_prism']),
+                     ('cone', ['triangular_prism', 'sphere']),
                      ('dumbbell', ['pentagon', 'octahedron']),
                      ('octahedron', ['pentagon', 'pyramid']),
                      ('pentagon', ['pipe', 'pyramid']),
                      ('pipe', ['torus', 'dumbbell']),
-                     ('pyramid', ['triangular prism', 'sphere']),
+                     ('pyramid', ['triangular_prism', 'sphere']),
                      ('sphere', ['pipe', 'cone']),
                      ('torus', ['bowl', 'octahedron']),
-                     ('triangular prism', ['pentagon', 'cone'])]
+                     ('triangular_prism', ['pentagon', 'cone'])]
 
 SCENARIO_TYPES = 10 * ['contain'] + 10 * ['support']
 
@@ -40,7 +40,6 @@ def get_drop_target_pairs(scenarios):
 
 def main(output_dir, num):
     scenarios = get_drop_target_pairs(SCENARIOS)
-    print(scenarios)
     scenes = list(zip(scenarios, SCENARIO_TYPES))
     scenes = scenes[:1]
     for (sd, st), tp in scenes:
@@ -57,8 +56,8 @@ def main(output_dir, num):
         else:
             target_obj, target_rotation, target_scale = st
 
-        dc = drop.Drop(launch_build=False,
-                       port=1075,
+        dc = drop.Drop(#launch_build=False,
+                       #port=1075,
                        randomize=0,
                        seed=0,
                        height_range=[0.75, 1.25],
@@ -69,6 +68,7 @@ def main(output_dir, num):
                        target_objects = [target_obj],
                        target_scale_range=[target_scale, target_scale],
                        target_rotation=target_rotation,
+                       camera_radius=1.25,
                        camera_min_angle=0,
[…]

### 2021-01-17 models/generate_stimuli.py
minor

@@ -32,13 +32,14 @@ SCENARIOS = CONTAIN_SCENARIOS + SUPPORT_SCENARIOS
 def get_drop_target_pairs(scenarios):
     pairs = []
     for sd, st in scenarios:
-        pairs.append((sd, st[0]))
-        pairs.append((sd, st[1]))
-    pairs = list(set(pairs))
+        if (sd, st[0]) not in scenarios:
+            pairs.append((sd, st[0]))
+        if (sd, st[1]) not in scenarios:
+            pairs.append((sd, st[1]))
     return pairs
 
 
-def main(output_dir, num):
+def main(output_dir, num, launch_build=True, port=1071):
     scenarios = get_drop_target_pairs(SCENARIOS)
     scenes = list(zip(scenarios, SCENARIO_TYPES))
     scenes = scenes[:1]
@@ -56,8 +57,8 @@ def main(output_dir, num):
         else:
             target_obj, target_rotation, target_scale = st
 
-        dc = drop.Drop(#launch_build=False,
-                       #port=1075,
+        dc = drop.Drop(launch_build=launch_build,
+                       port=port,
                        randomize=0,
                        seed=0,
                        height_range=[0.75, 1.25],

### 2021-01-17 models/generate_stimuli.py
minor

@@ -1,3 +1,4 @@
+import time
 import os
 import drop #how are we dealing with the fact that we might want to reuse controller code like this? drop controller is not in any package!
 
@@ -42,7 +43,7 @@ def get_drop_target_pairs(scenarios):
 def main(output_dir, num, launch_build=True, port=1071):
     scenarios = get_drop_target_pairs(SCENARIOS)
     scenes = list(zip(scenarios, SCENARIO_TYPES))
-    scenes = scenes[:1]
+    #scenes = scenes[:1]
     for (sd, st), tp in scenes:
         if isinstance(sd, str):
             drop_obj = sd 
@@ -61,7 +62,7 @@ def main(output_dir, num, launch_build=True, port=1071):
                        port=port,
                        randomize=0,
                        seed=0,
-                       height_range=[0.75, 1.25],
+                       height_range=[1.1, 1.1],
                        drop_scale_range=[drop_scale, drop_scale],
                        drop_jitter=0.2,
                        drop_rotation=drop_rotation,
@@ -81,5 +82,5 @@ def main(output_dir, num, launch_build=True, port=1071):
                temp_path='tmp',
                width=256,
                height=256)
-               
+        time.sleep(10)
                        

### 2021-01-17 models/generate_stimuli.py
minor

@@ -44,43 +44,55 @@ def main(output_dir, num, launch_build=True, port=1071):
     scenarios = get_drop_target_pairs(SCENARIOS)
     scenes = list(zip(scenarios, SCENARIO_TYPES))
     #scenes = scenes[:1]
-    for (sd, st), tp in scenes:
+    for i, ((sd, st), tp) in enumerate(scenes):
         if isinstance(sd, str):
             drop_obj = sd 
-            drop_rotation = [0, 0, 0]
+            drop_rotation = {"x": 0, "y": 0, "z": 0}
             drop_scale = 1
         else:
             drop_obj, drop_rotation, drop_scale = sd
         if isinstance(st, str):
             target_obj = st
-            target_rotation = [0, 0, 0]
+            target_rotation = {"x": 0, "y": 0, "z": 0}
             target_scale = 1
         else:
             target_obj, target_rotation, target_scale = st
 
-        dc = drop.Drop(launch_build=launch_build,
+        suffix = '%s_on_%s_%s' % (drop_obj, target_obj, tp)
+        output_path = os.path.join(output_dir, suffix)
+        temp_path = 'tmp' 
+
+        if i == 0:
+            dc = drop.Drop(launch_build=launch_build,
                        port=port,
                        randomize=0,
                        seed=0,
-                       height_range=[1.1, 1.1],
+                       height_range=[1.2, 1.2],
                        drop_scale_range=[drop_scale, drop_scale],
                        drop_jitter=0.2,
-                       drop_rotation=drop_rotation,
+                       drop_rotation_range=drop_rotation,
                        drop_objects = [drop_obj],
                        target_objects = [target_obj],
                        target_scale_range=[target_scale, target_scale],
-                       target_rotation=target_rotation,
-                       camera_radius=1.25,
+                       target_rotation_range=target_rotation,
+                       camera_radius=1.5,
                        camera_min_angle=0,
-                       camera_max_angle=0
-        )
+                       camera_max_angle=0)
 
-        suffix = '%s_on_%s_%s' % (drop_obj, target_obj, tp)
-        output_path = os.path.join(output_dir, suffix)
-        dc.run(num=num,
-               output_dir=output_path,
-               temp_path='tmp',
-               width=256,
-               height=256)
-        time.sleep(10)
+            initialization_commands = dc.get_initialization_commands(width=256,
+                                                                     height=256)
+            dc.communicate(initialization_commands)
+        else:
[…]

### 2021-01-17 paper/paper2021.Rmd

@@
 Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
-Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than overly simple or overly complex stimuli; @Kidd2012; @Kidd2014].
+Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than simple or highly-complex stimuli [@Kidd2012; @Kidd2014].
 According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
@@
 
-Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
-However, the measures used in this literature have typically been coarse-grained with respect to infants' and children's physical knowledge, and thus do not specify or constrain which events might be moderately discrepant from this knowledge.
+Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE Spelke, Baillargeon..), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
+However, the measures used in this literature have typically focused on either children's ability to discriminate types of events, or their ability to carry out particular tasks (e.g., shape sorting), but have not examined which types of interactions children are most interested in testing.
 For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015; @Baillargeon2007).
@@
 Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance [adjust criterion for multiple comparisons?].
-As can be seen in Table 1, participants significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
+As can be seen in Table 1, adults participants ("adult" column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
 
@@
 
-```{r adults-table, results="asis"}
-# how to do 2-col table? , fig.env = "figure*" 
+```{r adults-table, results="asis", include=F}
 adtab <- xtable::xtable(adult_trial_agg, digits=2, 
@@
 
-Were adults more consistent in their choices on support or containment trials?
-Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations (M=`r round(ad_rel_means[1,]$M,2)`) than support relations (M=`r round(ad_rel_means[2,]$M,2)`; one-sample `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
-For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.
-
-# Experiment 2: Children
-
-Experiment 1 showed that adults show remarkably consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
-Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
-
-## Method
-We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
-
-### Participants
-Participants were 73 children recruited online via Bing Nursery School and targeted Facebook Ads.
-Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions [based on?], results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
-
-### Materials
-The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote. 
-Introductory slides were added for informed consenting process and screen configuration, where researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
-
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
-Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
-img <- png::readPNG("figs/online-child-practice-trial.png")
-grid::grid.raster(img)
-```
-
-### Procedure
-
-Based on piloting, we estimated the activity would require 10 minutes to complete. 
-After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
-A video recording was taken of the online session.
-
-To accompany the practice trial, children were shown the three physical objects on video, to ensure understanding of their 3D properties. 
-Verbal responses were collected from children to indicate the selection of target object Y or Z. 
-To prevent left/right mapping confusion, target objects Y and Z were overlaid on thirds of the screen with either red or green background color, which were counterbalanced across trials. 
-The child was asked to verbally select target object and then to indicate whether it was on the "red side or the green side."
-
-## Results
-
-We first examine children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
-Table 2 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1 [maybe just drop Table 1?].
-Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05 [use stricter for mult comparisons?
-Bonf=.0025]) from chance.
-Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
-On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
-
 ```{r child-data-agg}
@@
   rename(child = chose_target) %>%
-  arrange(relation, desc(child))
+  arrange(relation, desc(adult)) # desc(child)
 
@@
 ```
+
+Were adults more consistent in their choices on support or containment trials?
+Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations (M=`r round(ad_rel_means[1,]$M,2)`) than support relations (M=`r round(ad_rel_means[2,]$M,2)`; one-sample `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
+For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.
+
+# Experiment 2: Children
+
+Experiment 1 demonstrated that adults show remarkably consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
+Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
+
+## Method
+We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
+
+### Participants
+Participants were 73 children recruited online via Bing Nursery School and targeted Facebook Ads.
+Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
+After exclusions [based on?], results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+
+### Materials
+The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote. 
+Introductory slides were added for informed consenting process and screen configuration, where researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
+
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
+Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
+img <- png::readPNG("figs/online-child-practice-trial.png")
+grid::grid.raster(img)
+```
+
+### Procedure
+
+<!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
+After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
+A video recording was taken of the online session.
+
+To accompany the practice trial, children were shown the three physical objects on video, to ensure understanding of their 3D properties. 
+Verbal responses were collected from children to indicate the selection of target object Y or Z. 
+To prevent left/right mapping confusion, target objects Y and Z were overlaid on thirds of the screen with either red or green background color, which were counterbalanced across trials. 
+The child was asked to verbally select target object and then to indicate whether it was on the "red side or the green side."
+
+## Results
+
+We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
+Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1 [maybe just drop Table 1?].
+Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05 [use stricter for mult comparisons?
+Bonf=.0025]) from chance.
+Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
+On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
 

### 2021-01-18 models/generate_stimuli.py
updates

@@ -4,47 +4,124 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 
 OBJECT_INFO = {}
 
-CONTAIN_SCENARIOS = [('bowl', ['pyramid', 'trianular_prism']),
-                     ('cone', ['torus', 'octahedron']),
-                     ('dumbbell', ['pipe', 'pyramid']),
-                     ('octahedron', ['pipe', 'sphere']),
-                     ('pentagon', ['bowl', 'sphere']),
-                     ('pipe', ['cone', 'octahedron']),
-                     ('pyramid', ['torus', 'dumbbell']),
-                     ('sphere', ['bowl', 'pentagon']),
-                     ('torus', ['cone', 'dumbbell']),
-                     ('triangular_prism', ['bowl', 'dumbbell'])]
+CONTAIN_SCENARIOS = [
+                     (('bowl', {"x": 0, "y": 0, "z": 180}, 1.3), 
+                      ['pyramid', 
+                       ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
+                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.75),
+                      ['torus', 
+                      ('octahedron', {"x": 0, "y": 0, "z": 90}, 1)]),
+                     (('dumbbell', {"x": 90, "y": 0, "z": 0}, .4), 
+                      [('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 0.9, "y": 0.315, "z": 0.9}),
+                       ('pyramid', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        0.8)]),
+                     ('octahedron', 
+                      [('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 0.9, "y": 0.315, "z": 0.9}),
+                      'sphere']),
+                     (('pentagon',
+                       {"x": 0, "y": 0, "z": 0}, 
+                       {"x": 0.7, "y": 0.49, "z": 0.7}), 
+                      ['bowl', 
+                       ('sphere',{"x": 0, "y": 0, "z": 0}, 0.7)]),
+                     (('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 1, "y": 0.35, "z": 1}),
+                      ['cone', 
+                      ('octahedron', {"x": 0, "y": 0, "z": 90.}, 1)]),
+                     (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
[…]

### 2021-01-18 models/generate_stimuli.py
minor

@@ -4,7 +4,9 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 
 OBJECT_INFO = {}
 
-CONTAIN_SCENARIOS = [
+CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 1), 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.6), 
+                       ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
                      (('bowl', {"x": 0, "y": 0, "z": 180}, 1.3), 
                       ['pyramid', 
                        ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
@@ -41,9 +43,6 @@ CONTAIN_SCENARIOS = [
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 0.8, "y": 0.56, "z": 0.8})
                        ]),
-                     (('torus', {"x": 0, "y": 0, "z": 0}, 5), 
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.4), 
-                       'dumbbell']),
                      (('triangular_prism',
                        {"x": 0, "y": 0, "z": 90},
                        {"x": 1, "y": 0.6, "z": 0.6}),
@@ -94,9 +93,9 @@ SUPPORT_SCENARIOS = [
                         {"x": 0, "y": 0, "z": 0},
                         {"x": 1.1, "y": 0.35, "z": 1.1}),
                       'cone']),
-                     (('torus', {"x": 0, "y": 0, "z": 0}, 4), 
+                     (('torus', {"x": 0, "y": 0, "z": 0}, 1), 
                       ['bowl', 
-                       ('octahedron', {"x": 0, "y": 0, "z": 0}, 0.4)]),
+                       ('octahedron', {"x": 0, "y": 0, "z": 0}, 0.6)]),
                      ('triangular_prism', 
                       [('pentagon',
                         {"x": 0, "y": 0, "z": 0},

### 2021-01-18 models/run_script.py
basic run script

@@ -1,0 +1,3 @@
+import generate_stimuli as gs
+
+gs.main('curiodrop_stimuli', 3)

### 2021-01-19 models/generate_stimuli.py
basic model structure first pass

@@ -1,5 +1,7 @@
 import time
 import os
+import numpy as np
+
 import drop #how are we dealing with the fact that we might want to reuse controller code like this? drop controller is not in any package!
 
 OBJECT_INFO = {}
@@ -118,6 +120,26 @@ def get_drop_target_pairs(scenarios):
     return pairs
 
 
+class Rotator(object):
+    def __init__(self, range_dict, seed=0, initial=None):
+        if initial is None:
+            initial = {}
+        self.initial = initial
+        self.xmin, self.xmax = range_dict['x']
+        self.ymin, self.ymax = range_dict['y']
+        self.zmin, self.zmax = range_dict['z']
+        self.rng = np.random.RandomState(seed=seed)
+
+    def __call__(self):
+        xinit = self.initial.get('x', 0)
+        yinit = self.initial.get('y', 0)
+        zinit = self.initial.get('z', 0)
+        xrot = self.rng.uniform(xinit + self.xmin, xinit + self.xmax)
+        yrot = self.rng.uniform(yinit + self.ymin, yinit + self.ymax)
+        zrot = self.rng.uniform(zinit + self.zmin, zinit + self.zmax)
+        return {'x': xrot, 'y': yrot, 'z': zrot}
+
+
 def main(output_dir, num, launch_build=True, port=1071):
     scenarios = get_drop_target_pairs(SCENARIOS)
     for i, ((sd, st), tp) in enumerate(scenarios):
@@ -138,6 +160,12 @@ def main(output_dir, num, launch_build=True, port=1071):
         output_path = os.path.join(output_dir, suffix)
         temp_path = 'tmp' 
 
+        drop_rotation_range = Rotator({"x": [-20, 20],
+                                       "y": [-20, 20],
+                                       "z": [-20, 20]},
+                                       seed=i,
+                                       initial=drop_rotation)
+
         if i == 0:
             dc = drop.Drop(launch_build=launch_build,
                        port=port,
@@ -145,8 +173,8 @@ def main(output_dir, num, launch_build=True, port=1071):
                        seed=0,
                        height_range=[1.9, 1.9],
                        drop_scale_range=drop_scale,
-                       drop_jitter=0.1,
-                       drop_rotation_range=drop_rotation,
+                       drop_jitter=0.2,
+                       drop_rotation_range=drop_rotation_range,
                        drop_objects = [drop_obj],
                        target_objects = [target_obj],
                        target_scale_range=target_scale,
[…]

### 2021-01-19 models/model.py

@@ -1,0 +1,30 @@
+from frozendict import frozendict
+
+import numpy as numpy
+
+
+def softmax(x, beta=1):
+    numerator = np.exp(beta * x)
+    denominator = numerator.sum()
+    return numerator / denominator
+
+
+class CuriosityBinaryChoice(object):
+	def __init__(self,
+			     curiosity_function,
+			     linking_function=softmax,
+			     curiosity_kwargs=frozendict({}),
+			     linking_kwargs=frozendict({})):
+		self.curiosity_function = curiosity_function
+		self.linking_function = linking_function
+		self.curiosity_kwargs = curiosity_kwargs
+		self.linking_kwargs = linking_kwargs
+
+	def judgement(self, data):
+		data_left, data_right = data
+		m0 = self.curiosity(data_left, **self.curiosity_kwargs)
+		m1 = self.curiosity(data_right, **self.curiosity_kwargs)
+		judgement = self.linking_function([m0, m1], **self.linking_kwargs)
+		return {'curiosity_left': m0,
+			    'curiosity_right': m1,
+			    'judgement': judgement}

### 2021-01-19 models/model.py
beginning to code specific models

@@ -3,6 +3,10 @@ from frozendict import frozendict
 import numpy as numpy
 
 
+################
+#####BASICS#####
+################
+
 def softmax(x, beta=1):
     numerator = np.exp(beta * x)
     denominator = numerator.sum()
@@ -28,3 +32,151 @@ class CuriosityBinaryChoice(object):
 		return {'curiosity_left': m0,
 			    'curiosity_right': m1,
 			    'judgement': judgement}
+
+
+##############
+#####TIME#####
+##############
+
+def avg_len(data):
+	"""mean length of time before objects come to rest
+	"""
+	time_list = [len(d['frames'].keys()) for d in data]
+	return np.mean(time_list)
+
+
+def len_std(data):
+	"""std in length of time before objects come to rest
+	"""
+	time_list = [len(d['frames'].keys()) for d in data]
+	return np.std(time_list)
+
+
+def sharpe_ratio(x):
+	return np.mean(x) / np.std(x)
+
+
+def len_inverse_sharpe_ratio(data):
+	"""
+	length std normalized by mean length
+	see https://en.wikipedia.org/wiki/Sharpe_ratio
+	"""
+	time_list = [len(d['frames'].keys()) for d in data]
+	return 1./sharpe_ratio(time_list)
+
+
+
+###################
+#####POSITIONS#####
+###################
+
+def get_last_frame_id(d):
+	"""helper function getting last frame number of trial
+	"""
+	fnames = list(map(int, list(d['frames'].keys())))
+	fnames.sort()
+	return fnames[-1]
+
+
+def get_last_frame_positions(data):
+	"""helper function getting positions of objects at last frame
+	"""
+	posvecs = []
+	for d in data:
+		lf = get_last_frame_id(d)
+		posvec = np.asarray(f['frames'][lf]['objects']['positions'][:])
+		posvecs.append(posvec)
+	#shape is (num_trials, num_objects, 3)
+	posvecs = np.array(posvecs)
+	return posvecs
+
+
+def get_positions(data, object_inds=None):
+	"""
+	helper function getting all positions of all frames in all trials
+	returns a list rather than an array since the len of the trials will be different
+	"""
+	posfunc = lambda x: get_positions_from_frames(x,
+						     object_inds=object_inds)
+	return list(map(posfunc, data))
+
+
+def get_positions_from_frames(d, object_inds=None):
+	"""helper function getting positions for all frames in a trial
+	returns array of shape (num_frames, num_objects_in_selection, 3)
+	"""
+	pos = []
[…]

### 2021-01-20 models/model.py
additional models

@@ -1,6 +1,4 @@
-from frozendict import frozendict
-
-import numpy as numpy
+import numpy as np
 
 
 ################
@@ -17,8 +15,12 @@ class CuriosityBinaryChoice(object):
 	def __init__(self,
 			     curiosity_function,
 			     linking_function=softmax,
-			     curiosity_kwargs=frozendict({}),
-			     linking_kwargs=frozendict({})):
+			     curiosity_kwargs=None,
+			     linking_kwargs=None):
+		if curiosity_kwargs is None:
+			curiosity_kwargs = {}
+		if linking_kwargs is None:
+			lining_kwargs = {}
 		self.curiosity_function = curiosity_function
 		self.linking_function = linking_function
 		self.curiosity_kwargs = curiosity_kwargs
@@ -26,8 +28,8 @@ class CuriosityBinaryChoice(object):
 
 	def judgement(self, data):
 		data_left, data_right = data
-		m0 = self.curiosity(data_left, **self.curiosity_kwargs)
-		m1 = self.curiosity(data_right, **self.curiosity_kwargs)
+		m0 = self.curiosity_function(data_left, **self.curiosity_kwargs)
+		m1 = self.curiosity_function(data_right, **self.curiosity_kwargs)
 		judgement = self.linking_function([m0, m1], **self.linking_kwargs)
 		return {'curiosity_left': m0,
 			    'curiosity_right': m1,
@@ -106,13 +108,41 @@ def get_positions_from_frames(d, object_inds=None):
 	returns array of shape (num_frames, num_objects_in_selection, 3)
 	"""
 	pos = []
-	for f in d['frames'].values():
-		p = _f['objects']['positions'][:]
+	frame_inds = list(d['frames'].keys())
+	frame_inds.sort()
+	for f_ind in frame_inds:
+		f = d['frames'][f_ind]
+		p = f['objects']['positions'][:]
 		if object_inds is not None:
 			p = p[:, object_inds]
 		pos.append(p)
 	return np.array(pos)
 
+
+def get_velocities(data, object_inds=None):
+	"""
+	helper function getting all positions of all frames in all trials
+	returns a list rather than an array since the len of the trials will be different
+	"""
+	posfunc = lambda x: get_velocities_from_frames(x,
+						     object_inds=object_inds)
+	return list(map(posfunc, data))
+
+
+def get_velocities_from_frames(d, object_inds=None):
[…]

### 2021-01-20 models/model.py
minor

@@ -227,13 +227,15 @@ def get_collision_frames(d):
 	return collision_frames
 
 
-def velocity_std_after_first_collision(data, objects=None, window=5):
+def normed_velocity_std_after_first_collision(data, objects=None, window=5):
     fcfs = list(map(get_first_collision_frame, data))
     object_inds = get_object_inds(objects)
     vels = get_velocities(data, object_inds=object_inds)
     #V is of shape (num_trials, window, num_objects, 3)
     V = np.array([v[fcf:fcf + window] for v, fcf in zip(vels, fcfs) if fcf is not None])
     Vm = V.mean(axis=1)
-    return np.sqrt(Vm.var(axis=0).sum())
+    Vn = np.linalg.norm(Vm, axis=2)
+    W = Vm / Vn[:, :, np.newaxis]
+    return np.sqrt(W.var(axis=0).sum())
 
 

### 2021-01-21 models/generate_stimuli.py
minor

@@ -6,16 +6,16 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 
 OBJECT_INFO = {}
 
-CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 1), 
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.6), 
+CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.8), 
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
                      (('bowl', {"x": 0, "y": 0, "z": 180}, 1.3), 
                       ['pyramid', 
                        ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
-                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.75),
-                      ['torus', 
+                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.8),
+                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
                       ('octahedron', {"x": 0, "y": 0, "z": 90}, 1)]),
-                     (('dumbbell', {"x": 90, "y": 0, "z": 0}, .4), 
+                     (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
                       [('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 0.9, "y": 0.315, "z": 0.9}),
@@ -35,10 +35,11 @@ CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 1),
                      (('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 1, "y": 0.35, "z": 1}),
-                      ['cone', 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.8), 
                       ('octahedron', {"x": 0, "y": 0, "z": 90.}, 1)]),
                      (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
-                      ['torus', ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.6)]),
+                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.9),
[…]

### 2021-01-21 models/run_script.py
minor

@@ -1,3 +1,3 @@
 import generate_stimuli as gs
 
-gs.main('curiodrop_stimuli', 3)
+gs.main('curiodrop_stimuli', 1)

### 2021-01-21 models/generate_stimuli.py
minor

@@ -7,12 +7,12 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 OBJECT_INFO = {}
 
 CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.8), 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
                      (('bowl', {"x": 0, "y": 0, "z": 180}, 1.3), 
                       ['pyramid', 
                        ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
-                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.8),
+                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.9),
                       [('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
                       ('octahedron', {"x": 0, "y": 0, "z": 90}, 1)]),
                      (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
@@ -30,18 +30,18 @@ CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.9),
                      (('pentagon',
                        {"x": 0, "y": 0, "z": 0}, 
                        {"x": 0.7, "y": 0.49, "z": 0.7}), 
-                      ['bowl', 
+                      [('bowl', {"x": 0, "y": 0, "z": 0}, 1.3), 
                        ('sphere',{"x": 0, "y": 0, "z": 0}, 0.7)]),
                      (('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 1, "y": 0.35, "z": 1}),
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.8), 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
                       ('octahedron', {"x": 0, "y": 0, "z": 90.}, 1)]),
                      (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
                       [('torus', {"x": 0, "y": 0, "z": 0}, 0.9),
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
                      (('sphere', {"x": 0, "y": 0, "z": 0}, 0.8), 
[…]

### 2021-01-21 models/generate_stimuli.py
minor

@@ -6,31 +6,31 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 
 OBJECT_INFO = {}
 
-CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
+CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
                       [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
-                     (('bowl', {"x": 0, "y": 0, "z": 180}, 1.3), 
+                     (('bowl', {"x": 0, "y": 0, "z": 180}, 1.15), 
                       ['pyramid', 
                        ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
                      (('cone', {"x": 0, "y": 0, "z": 180}, 0.9),
-                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.9), 
+                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
                       ('octahedron', {"x": 0, "y": 0, "z": 90}, 1)]),
                      (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
                       [('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
-                        {"x": 0.9, "y": 0.315, "z": 0.9}),
+                        {"x": 1, "y": 0.35, "z": 1}),
                        ('pyramid', 
                         {"x": 0, "y": 0, "z": 0}, 
                         0.8)]),
                      ('octahedron', 
                       [('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
-                        {"x": 0.9, "y": 0.315, "z": 0.9}),
+                        {"x": 1, "y": 0.35, "z": 1}),
                       'sphere']),
                      (('pentagon',
                        {"x": 0, "y": 0, "z": 0}, 
                        {"x": 0.7, "y": 0.49, "z": 0.7}), 
-                      [('bowl', {"x": 0, "y": 0, "z": 0}, 1.3), 
+                      [('bowl', {"x": 0, "y": 0, "z": 0}, 1.15), 
                        ('sphere',{"x": 0, "y": 0, "z": 0}, 0.7)]),
                      (('pipe', 
[…]

### 2021-01-21 models/generate_stimuli.py
different parameters for jitter

@@ -172,15 +172,15 @@ def main(output_dir, num, launch_build=True, port=1071):
                        port=port,
                        randomize=0,
                        seed=0,
-                       height_range=[1.9, 1.9],
+                       height_range=[2.6, 2.6],
                        drop_scale_range=drop_scale,
-                       drop_jitter=0.2,
+                       drop_jitter=0.3,
                        drop_rotation_range=drop_rotation_range,
                        drop_objects = [drop_obj],
                        target_objects = [target_obj],
                        target_scale_range=target_scale,
                        target_rotation_range=target_rotation,
-                       camera_radius=1.5,
+                       camera_radius=2.5,
                        camera_min_angle=0,
                        camera_max_angle=0)
 

### 2021-01-21 models/generate_stimuli.py
different parameters for jitter

@@ -174,7 +174,7 @@ def main(output_dir, num, launch_build=True, port=1071):
                        seed=0,
                        height_range=[2.6, 2.6],
                        drop_scale_range=drop_scale,
-                       drop_jitter=0.3,
+                       drop_jitter=0.4,
                        drop_rotation_range=drop_rotation_range,
                        drop_objects = [drop_obj],
                        target_objects = [target_obj],

### 2021-01-21 models/generate_stimuli.py
different parameters for jitter

@@ -172,7 +172,7 @@ def main(output_dir, num, launch_build=True, port=1071):
                        port=port,
                        randomize=0,
                        seed=0,
-                       height_range=[2.6, 2.6],
+                       height_range=[2.1, 2.1],
                        drop_scale_range=drop_scale,
                        drop_jitter=0.4,
                        drop_rotation_range=drop_rotation_range,

### 2021-01-21 models/generate_stimuli.py
different parameters for jitter

@@ -6,6 +6,10 @@ import drop #how are we dealing with the fact that we might want to reuse contro
 
 OBJECT_INFO = {}
 
+
+#OCT_ROT = 90
+OCT_ROT = 0
+
 CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
                       [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
@@ -14,7 +18,7 @@ CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8),
                        ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
                      (('cone', {"x": 0, "y": 0, "z": 180}, 0.9),
                       [('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
-                      ('octahedron', {"x": 0, "y": 0, "z": 90}, 1)]),
+                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
                      (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
                       [('pipe', 
                         {"x": 0, "y": 0, "z": 0}, 
@@ -36,7 +40,7 @@ CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8),
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 1, "y": 0.35, "z": 1}),
                       [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
-                      ('octahedron', {"x": 0, "y": 0, "z": 90.}, 1)]),
+                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
                      (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
                       [('torus', {"x": 0, "y": 0, "z": 0}, 0.8),
                        ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
@@ -69,7 +73,7 @@ SUPPORT_SCENARIOS = [
                         {"x": 0, "y": 0, "z": 0}, 
                         {"x": 1, "y": 0.7, "z": 1}),
                       'octahedron']),
-                     (('octahedron', {"x": 0, "y": 0, "z": 90.}, 1), 
[…]

### 2021-01-21 models/model.py
stay collision model

@@ -239,3 +239,25 @@ def normed_velocity_std_after_first_collision(data, objects=None, window=5):
     return np.sqrt(W.var(axis=0).sum())
 
 
+def get_collision_types(d)
+	fn = d['frames'].keys()
+	fn.sort()
+    ct = [d['frames'][k]['collisions']['states'][:].flatten().tolist() for k in fn]
+    ct1 = np.asarray(list((map(lambda x: x[0].decode('utf-8') if len(x) else '', ct))))
+    return ct1
+
+
+def percentage_stay_collision(data):
+	stays = []
+	for d in data:
+		ct = get_collision_types(d)
+		stay = ct[-2] == 'stay'
+		stays.append(stay)
+	stays = np.array(stays)
+	return np.mean(stays)
+
+
+
+
+
+

### 2021-01-21 models/model.py
support model

@@ -12,28 +12,28 @@ def softmax(x, beta=1):
 
 
 class CuriosityBinaryChoice(object):
-	def __init__(self,
-			     curiosity_function,
-			     linking_function=softmax,
-			     curiosity_kwargs=None,
-			     linking_kwargs=None):
-		if curiosity_kwargs is None:
-			curiosity_kwargs = {}
-		if linking_kwargs is None:
-			lining_kwargs = {}
-		self.curiosity_function = curiosity_function
-		self.linking_function = linking_function
-		self.curiosity_kwargs = curiosity_kwargs
-		self.linking_kwargs = linking_kwargs
+    def __init__(self,
+                 curiosity_function,
+                 linking_function=softmax,
+                 curiosity_kwargs=None,
+                 linking_kwargs=None):
+        if curiosity_kwargs is None:
+            curiosity_kwargs = {}
+        if linking_kwargs is None:
+            lining_kwargs = {}
+        self.curiosity_function = curiosity_function
+        self.linking_function = linking_function
+        self.curiosity_kwargs = curiosity_kwargs
+        self.linking_kwargs = linking_kwargs
 
-	def judgement(self, data):
-		data_left, data_right = data
-		m0 = self.curiosity_function(data_left, **self.curiosity_kwargs)
-		m1 = self.curiosity_function(data_right, **self.curiosity_kwargs)
-		judgement = self.linking_function([m0, m1], **self.linking_kwargs)
-		return {'curiosity_left': m0,
-			    'curiosity_right': m1,
-			    'judgement': judgement}
+    def judgement(self, data):
+        data_left, data_right = data
+        m0 = self.curiosity_function(data_left, **self.curiosity_kwargs)
+        m1 = self.curiosity_function(data_right, **self.curiosity_kwargs)
+        judgement = self.linking_function([m0, m1], **self.linking_kwargs)
+        return {'curiosity_left': m0,
+                'curiosity_right': m1,
+                'judgement': judgement}
 
 
 ##############
@@ -41,30 +41,30 @@ class CuriosityBinaryChoice(object):
 ##############
 
 def avg_len(data):
-	"""mean length of time before objects come to rest
-	"""
-	time_list = [len(d['frames'].keys()) for d in data]
-	return np.mean(time_list)
+    """mean length of time before objects come to rest
+    """
+    time_list = [len(d['frames'].keys()) for d in data]
+    return np.mean(time_list)
 
 
 def len_std(data):
[…]

### 2021-01-21 models/model.py
bugfix

@@ -238,7 +238,7 @@ def normed_velocity_std_after_first_collision(data, objects=None, window=5):
 
 
 def get_collision_types(d, collision_key='collisions'):
-    fn = d['frames'].keys()
+    fn = list(d['frames'].keys())
     fn.sort()
     ct = [d['frames'][k][collision_key]['states'][:].flatten().tolist() for k in fn]
     ct1 = np.asarray(list((map(lambda x: x[0].decode('utf-8') if len(x) else '', ct))))
@@ -249,7 +249,7 @@ def get_collision_ids(d, collision_key='collisions'):
     """
     helper function returning the ids of objects in collisions at each frame within a trial
     """
-    fn = d['frames'].keys()
+    fn = list(d['frames'].keys())
     fn.sort()
     ids = [np.unique(d['frames'][k][collision_key]['object_ids'][:]) for k in fn]
     return ids

### 2021-01-21 models/model.py
bugfix

@@ -264,7 +264,7 @@ def get_support(d):
     also supported by the floor.  
     """
     c_ids = get_collision_ids(d)
-    c_ids_env = get_collision_ids(d, collision_key='env_collision')
+    c_ids_env = get_collision_ids(d, collision_key='env_collisions')
     support = ((len(c_ids[-2]) == 2) and (len(c_ids_env[-2]) <= 1))
     return support  
 

### 2021-01-21 models/model.py
bugfix

@@ -269,7 +269,7 @@ def get_support(d):
     return support  
 
 
-def percentage_supports(data):
+def support_probability(data):
     """model expressing empirical likelihood of a support relationship
     arising at the end of a trial
     """
@@ -281,8 +281,7 @@ def support_std(data):
     """model expressing empirical standard deviation in the distribution of
     whether a support relationship will arise at the end of a trial
     """
-    supports = list(map(get_support, data))
-    m = np.mean(supports)
+    m = support_probability(data)
     #std for binomial variable is sqrt(mean * (1 - mean))
     return np.sqrt(m * (1 - m))
 

### 2021-01-21 models/experimental.py
intrastructure for extracting stats

@@ -1,0 +1,121 @@
+#OCT_ROT = 90
+OCT_ROT = 0
+
+CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
+                       ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
+                     (('bowl', {"x": 0, "y": 0, "z": 180}, 1.15), 
+                      ['pyramid', 
+                       ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
+                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.9),
+                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
+                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
+                     (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
+                      [('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 1, "y": 0.35, "z": 1}),
+                       ('pyramid', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        0.8)]),
+                     ('octahedron', 
+                      [('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 1, "y": 0.35, "z": 1}),
+                      'sphere']),
+                     (('pentagon',
+                       {"x": 0, "y": 0, "z": 0}, 
+                       {"x": 0.7, "y": 0.49, "z": 0.7}), 
+                      [('bowl', {"x": 0, "y": 0, "z": 0}, 1.15), 
+                       ('sphere',{"x": 0, "y": 0, "z": 0}, 0.7)]),
+                     (('pipe', 
+                        {"x": 0, "y": 0, "z": 0}, 
+                        {"x": 1, "y": 0.35, "z": 1}),
+                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
+                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
+                     (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
+                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.8),
+                       ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
[…]

### 2021-01-21 models/generate_stimuli.py

@@ -3,126 +3,9 @@ import os
 import numpy as np
 
 import drop #how are we dealing with the fact that we might want to reuse controller code like this? drop controller is not in any package!
-
-OBJECT_INFO = {}
-
-
-#OCT_ROT = 90
-OCT_ROT = 0
-
-CONTAIN_SCENARIOS = [(('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
-                       ('dumbbell', {"x": 0, "y": 0, "z": 0}, 0.5)]),
-                     (('bowl', {"x": 0, "y": 0, "z": 180}, 1.15), 
-                      ['pyramid', 
-                       ('triangular_prism', {"x": 0, "y": 90., "z": 0}, 1)]),
-                     (('cone', {"x": 0, "y": 0, "z": 180}, 0.9),
-                      [('torus', {"x": 0, "y": 0, "z": 0}, 0.8), 
-                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
-                     (('dumbbell', {"x": 90, "y": 0, "z": 0}, .5), 
-                      [('pipe', 
-                        {"x": 0, "y": 0, "z": 0}, 
-                        {"x": 1, "y": 0.35, "z": 1}),
-                       ('pyramid', 
-                        {"x": 0, "y": 0, "z": 0}, 
-                        0.8)]),
-                     ('octahedron', 
-                      [('pipe', 
-                        {"x": 0, "y": 0, "z": 0}, 
-                        {"x": 1, "y": 0.35, "z": 1}),
-                      'sphere']),
-                     (('pentagon',
-                       {"x": 0, "y": 0, "z": 0}, 
-                       {"x": 0.7, "y": 0.49, "z": 0.7}), 
-                      [('bowl', {"x": 0, "y": 0, "z": 0}, 1.15), 
-                       ('sphere',{"x": 0, "y": 0, "z": 0}, 0.7)]),
-                     (('pipe', 
-                        {"x": 0, "y": 0, "z": 0}, 
-                        {"x": 1, "y": 0.35, "z": 1}),
-                      [('cone', {"x": 0, "y": 0, "z": 0}, 0.9), 
-                      ('octahedron', {"x": 0, "y": 0, "z": OCT_ROT}, 1)]),
-                     (('pyramid', {"x": 0, "y": 0, "z": 180}, 1), 
[…]

### 2021-01-21 models/model.py

@@ -1,5 +1,14 @@
 import numpy as np
+import h5py
+import os
+try:
+    import cPickle as pickle
+except:
+    import pickle
 
+from experimental import (SCENARIOS, 
+                          scenario_pathname,
+                          get_drop_target_pairs)
 
 ################
 #####BASICS#####
@@ -20,7 +29,7 @@ class CuriosityBinaryChoice(object):
         if curiosity_kwargs is None:
             curiosity_kwargs = {}
         if linking_kwargs is None:
-            lining_kwargs = {}
+            linking_kwargs = {}
         self.curiosity_function = curiosity_function
         self.linking_function = linking_function
         self.curiosity_kwargs = curiosity_kwargs
@@ -170,19 +179,20 @@ def obj_final_position_std(data, objects=None):
     return total_std
 
 
+def get_radii(data, objects=None):
+    """helper function"""
+    object_inds = get_object_inds(objects)
+    positions = get_positions(data, object_inds=object_inds)
+    radii = [np.sqrt((pos**2).sum(axis=2)) for pos in positions]
+    return radii
+
+
 def avg_final_radius(data, objects=None):
     """model expressing avg final radius of objects
        mean is taken over trials and objects of radius of objects at last time point
     """
     radii = get_radii(data, objects=objects)
     return np.mean([rad[-1].mean() for rad in radii])
-
-
-def get_radii(data, objects=None):
-    object_inds = get_object_inds(objects)
-    positions = get_positions(data, object_inds=object_inds)
-    radii = [np.sqrt((pos**2).sum(axis=2)) for pos in positions]
-    return radii
 
 
 def avg_max_radius(data, objects=None):
@@ -286,5 +296,55 @@ def support_std(data):
     return np.sqrt(m * (1 - m))
 
 
+#=====
+model_funcs = [avg_len, 
+               len_std,
+               len_inverse_sharpe_ratio,
+               (obj_final_position_std, {'objects': 'drop'}),
+               (obj_final_position_std, {'objects': 'target'}),
+               (avg_final_radius, {'objects': 'drop'}),
+               (avg_final_radius, {'objects': 'target'}),
+               (avg_max_radius, {'objects': 'drop'}),
+               (avg_max_radius, {'objects': 'target'}),
+               (max_radius_std, {'objects': 'drop'}),
+               (max_radius_std, {'objects': 'target'}),
[…]

### 2021-01-21 models/model.py
minor

@@ -342,6 +342,7 @@ def get_all_stats(base_dir, out_dir):
     for ((sd, st), tp) in scenarios:
         sname = scenario_pathname(sd, st, tp)
         path = os.path.join(base_dir, sname)
+        print('Getting stats for %s' % sname)
         outcomes = get_stats(path)
         outpath = os.path.join(out_dir, sname)
         with open(outpath, 'w') as _f:

### 2021-01-21 models/model.py
update

@@ -337,7 +337,7 @@ def get_stats(dirn):
 
 def get_all_stats(base_dir, out_dir):
     if not os.path.exists(out_dir):
-        os.mkdirs(out_dir)
+        os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
     for ((sd, st), tp) in scenarios:
         sname = scenario_pathname(sd, st, tp)

### 2021-01-21 models/model.py
update

@@ -340,7 +340,15 @@ def get_all_stats(base_dir, out_dir):
         os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
     for ((sd, st), tp) in scenarios:
-        sname = scenario_pathname(sd, st, tp)
+        if isinstance(sd, str):
+            drop_obj = sd 
+        else:
+            drop_obj = sd[0]
+        if isinstance(st, str):
+            target_obj = st
+        else:
+            target_obj = st[0]
+        sname = scenario_pathname(drop_obj, target_obj, tp)
         path = os.path.join(base_dir, sname)
         print('Getting stats for %s' % sname)
         outcomes = get_stats(path)

### 2021-01-21 models/model.py
update

@@ -325,7 +325,7 @@ def get_stats(dirn):
             mf, kwargs = m
             argk = list(kwargs.keys())
             argk.sort()
-            argstr = '_'.join([str(k) + '=' + str(arg[k]) for k in argk])
+            argstr = '_'.join([str(k) + '=' + str(argk[k]) for k in argk])
             name = mf.__name__ + '_' + argstr
         else:
             mf = m

### 2021-01-21 models/model.py
update

@@ -325,7 +325,7 @@ def get_stats(dirn):
             mf, kwargs = m
             argk = list(kwargs.keys())
             argk.sort()
-            argstr = '_'.join([str(k) + '=' + str(argk[k]) for k in argk])
+            argstr = '_'.join([str(k) + '=' + str(kwargs[k]) for k in argk])
             name = mf.__name__ + '_' + argstr
         else:
             mf = m

### 2021-01-21 models/model.py
update

@@ -95,7 +95,7 @@ def get_last_frame_positions(data):
     posvecs = []
     for d in data:
         lf = get_last_frame_id(d)
-        posvec = np.asarray(f['frames'][lf]['objects']['positions'][:])
+        posvec = np.asarray(d['frames'][lf]['objects']['positions'][:])
         posvecs.append(posvec)
     #shape is (num_trials, num_objects, 3)
     posvecs = np.array(posvecs)

### 2021-01-21 models/model.py
update

@@ -84,7 +84,7 @@ def len_inverse_sharpe_ratio(data):
 def get_last_frame_id(d):
     """helper function getting last frame number of trial
     """
-    fnames = list(map(int, list(d['frames'].keys())))
+    fnames = list(d['frames'].keys())
     fnames.sort()
     return fnames[-1]
 

### 2021-01-21 models/model.py
update

@@ -331,6 +331,7 @@ def get_stats(dirn):
             mf = m
             kwargs = {}
             name = mf.__name__
+        print('... getting %s' % name)
         outcomes[name] = mf(data, **kwargs)
     return outcomes
 

### 2021-01-21 models/model.py
bugfix

@@ -354,7 +354,7 @@ def get_all_stats(base_dir, out_dir):
         print('Getting stats for %s' % sname)
         outcomes = get_stats(path)
         outpath = os.path.join(out_dir, sname)
-        with open(outpath, 'w') as _f:
+        with open(outpath, 'wb') as _f:
             pickle.dump(outcomes, _f)
 
 

### 2021-01-21 models/model.py
processing in parallel

@@ -1,6 +1,7 @@
 import numpy as np
 import h5py
 import os
+from multiprocessing import Pool
 try:
     import cPickle as pickle
 except:
@@ -333,28 +334,37 @@ def get_stats(dirn):
             name = mf.__name__
         print('... getting %s' % name)
         outcomes[name] = mf(data, **kwargs)
+    for d in data:
+        d.close()
     return outcomes
+
+
+def get_and_save_stats(sd, st, tp, base_dir, out_dir):
+    if isinstance(sd, str):
+        drop_obj = sd 
+    else:
+        drop_obj = sd[0]
+    if isinstance(st, str):
+        target_obj = st
+    else:
+        target_obj = st[0]
+    sname = scenario_pathname(drop_obj, target_obj, tp)
+    path = os.path.join(base_dir, sname)
+    print('Getting stats for %s' % sname)
+    outcomes = get_stats(path)
+    outpath = os.path.join(out_dir, sname)
+    with open(outpath, 'wb') as _f:
+        pickle.dump(outcomes, _f)
 
 
 def get_all_stats(base_dir, out_dir):
     if not os.path.exists(out_dir):
         os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
-    for ((sd, st), tp) in scenarios:
-        if isinstance(sd, str):
-            drop_obj = sd 
-        else:
-            drop_obj = sd[0]
-        if isinstance(st, str):
-            target_obj = st
-        else:
-            target_obj = st[0]
-        sname = scenario_pathname(drop_obj, target_obj, tp)
-        path = os.path.join(base_dir, sname)
-        print('Getting stats for %s' % sname)
-        outcomes = get_stats(path)
-        outpath = os.path.join(out_dir, sname)
-        with open(outpath, 'wb') as _f:
-            pickle.dump(outcomes, _f)
+    pool = multiprocessing.Pool()
+    for i in range(len(scenarios)):
+        ((sd, st), tp) = scenarios[i]
+        pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))
+    pool.join()
 
 

### 2021-01-21 models/model.py
processing in parallel

@@ -361,7 +361,7 @@ def get_all_stats(base_dir, out_dir):
     if not os.path.exists(out_dir):
         os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
-    pool = multiprocessing.Pool()
+    pool = Pool()
     for i in range(len(scenarios)):
         ((sd, st), tp) = scenarios[i]
         pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))

### 2021-01-21 models/model.py
processing in parallel

@@ -362,9 +362,12 @@ def get_all_stats(base_dir, out_dir):
         os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
     pool = Pool()
+    outs = []
     for i in range(len(scenarios)):
         ((sd, st), tp) = scenarios[i]
-        pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))
+        out = pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))
+        outs.append(out)
+    done = [out.get() for out in outs]
     pool.join()
 
 

### 2021-01-21 models/model.py
processing in parallel

@@ -368,6 +368,7 @@ def get_all_stats(base_dir, out_dir):
         out = pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))
         outs.append(out)
     done = [out.get() for out in outs]
+    pool.close()
     pool.join()
 
 

### 2021-01-21 models/model.py
we'll see

@@ -6,6 +6,8 @@ try:
     import cPickle as pickle
 except:
     import pickle
+import sklearn.svm as svm
+import sklearn.metrics as sk_metrics
 
 from experimental import (SCENARIOS, 
                           scenario_pathname,
@@ -184,7 +186,7 @@ def get_radii(data, objects=None):
     """helper function"""
     object_inds = get_object_inds(objects)
     positions = get_positions(data, object_inds=object_inds)
-    radii = [np.sqrt((pos**2).sum(axis=2)) for pos in positions]
+    radii = [np.sqrt(((pos**2)[:, :, [0, 2]]).sum(axis=2)) for pos in positions]
     return radii
 
 
@@ -297,7 +299,20 @@ def support_std(data):
     return np.sqrt(m * (1 - m))
 
 
-#=====
+def nonlinearity_of_support_dependence_on_initial_pos(data):
+    supports = list(map(get_support, data))
+    radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
+    radii = np.array(list(map(radfunc, data))).reshape((-1, 1))
+    cls = svm.LinearSVC()
+    cls.fit(radii, supports)
+    preds = cls.predict(radii)
+    return sk_metrics.f1_score(preds, supports)
+
+
+########################
+#####INFRASTRUCTURE#####
+########################
+
 model_funcs = [avg_len, 
                len_std,
                len_inverse_sharpe_ratio,
@@ -365,10 +380,13 @@ def get_all_stats(base_dir, out_dir):
     outs = []
     for i in range(len(scenarios)):
         ((sd, st), tp) = scenarios[i]
-        out = pool.apply_async(get_and_save_stats, (sd, st, tp, base_dir, out_dir))
+        out = pool.apply_async(get_and_save_stats, 
+                               (sd, st, tp, base_dir, out_dir))
         outs.append(out)
     done = [out.get() for out in outs]
     pool.close()
     pool.join()
+
+
 
 

### 2021-01-21 models/model.py
we'll see

@@ -306,7 +306,7 @@ def nonlinearity_of_support_dependence_on_initial_pos(data):
     cls = svm.LinearSVC()
     cls.fit(radii, supports)
     preds = cls.predict(radii)
-    return sk_metrics.f1_score(preds, supports)
+    return sk_metrics.f1_score(preds, supports), preds, support
 
 
 ########################

### 2021-01-21 models/model.py
we'll see

@@ -306,7 +306,7 @@ def nonlinearity_of_support_dependence_on_initial_pos(data):
     cls = svm.LinearSVC()
     cls.fit(radii, supports)
     preds = cls.predict(radii)
-    return sk_metrics.f1_score(preds, supports), preds, support
+    return sk_metrics.f1_score(preds, supports), preds, supports
 
 
 ########################

### 2021-01-21 models/model.py
some kind of measure of sharpness of support response to noise

@@ -299,14 +299,14 @@ def support_std(data):
     return np.sqrt(m * (1 - m))
 
 
-def nonlinearity_of_support_dependence_on_initial_pos(data):
+def sharpness_of_support_posjitter_response(data):
     supports = list(map(get_support, data))
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = np.array(list(map(radfunc, data))).reshape((-1, 1))
     cls = svm.LinearSVC()
     cls.fit(radii, supports)
     preds = cls.predict(radii)
-    return sk_metrics.f1_score(preds, supports), preds, supports
+    return sk_metrics.f1_score(preds, supports)
 
 
 ########################
@@ -327,7 +327,8 @@ model_funcs = [avg_len,
                (normed_velocity_std_after_first_collision, {'objects': 'drop'}),
                (normed_velocity_std_after_first_collision, {'objects': 'target'}),
                support_probability,
-               support_std
+               support_std,
+               sharpness_of_support_posjitter_response
               ]
 
 

### 2021-01-22 models/model.py
some kind of measure of sharpness of support response to noise

@@ -301,6 +301,8 @@ def support_std(data):
 
 def sharpness_of_support_posjitter_response(data):
     supports = list(map(get_support, data))
+    if np.unique(supports) == 1:
+        return 0
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = np.array(list(map(radfunc, data))).reshape((-1, 1))
     cls = svm.LinearSVC()
@@ -387,7 +389,5 @@ def get_all_stats(base_dir, out_dir):
     done = [out.get() for out in outs]
     pool.close()
     pool.join()
-
-
 
 

### 2021-01-22 models/model.py
bugfix

@@ -301,7 +301,7 @@ def support_std(data):
 
 def sharpness_of_support_posjitter_response(data):
     supports = list(map(get_support, data))
-    if np.unique(supports) == 1:
+    if len(np.unique(supports)) == 1:
         return 0
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = np.array(list(map(radfunc, data))).reshape((-1, 1))

### 2021-01-22 models/model.py
collect stats

@@ -1,11 +1,12 @@
-import numpy as np
-import h5py
 import os
 from multiprocessing import Pool
 try:
     import cPickle as pickle
 except:
     import pickle
+import numpy as np
+import h5py
+import pandas as pd
 import sklearn.svm as svm
 import sklearn.metrics as sk_metrics
 
@@ -389,5 +390,29 @@ def get_all_stats(base_dir, out_dir):
     done = [out.get() for out in outs]
     pool.close()
     pool.join()
+
+
+def collect_stats(dirn, outpath):
+    scenarios = get_drop_target_pairs(SCENARIOS)
+    records = {}
+    for i in range(len(scenarios)):
+        ((sd, st), tp) = scenarios[i]
+        if isinstance(sd, str):
+            drop_obj = sd 
+        else:
+            drop_obj = sd[0]
+        if isinstance(st, str):
+            target_obj = st
+        else:
+            target_obj = st[0]
+        sname = scenario_pathname(drop_obj, target_obj, tp)
+        outpath = os.path.join(dirn, sname)
+        with open(outpath, 'rb') as _f:
+            outcomes = pickle.loads(_f.read())
+            records.append(outcomes)
+    features = pd.DataFrame(records)
+    features.to_csv(outpath, index=False))
+
+
 
 

### 2021-01-22 models/model.py
typo

@@ -411,7 +411,7 @@ def collect_stats(dirn, outpath):
             outcomes = pickle.loads(_f.read())
             records.append(outcomes)
     features = pd.DataFrame(records)
-    features.to_csv(outpath, index=False))
+    features.to_csv(outpath, index=False)
 
 
 

### 2021-01-22 models/model.py
typo

@@ -394,7 +394,7 @@ def get_all_stats(base_dir, out_dir):
 
 def collect_stats(dirn, outpath):
     scenarios = get_drop_target_pairs(SCENARIOS)
-    records = {}
+    records = []
     for i in range(len(scenarios)):
         ((sd, st), tp) = scenarios[i]
         if isinstance(sd, str):

### 2021-01-22 models/model.py
debugging

@@ -396,6 +396,7 @@ def collect_stats(dirn, outpath):
     scenarios = get_drop_target_pairs(SCENARIOS)
     records = []
     for i in range(len(scenarios)):
+        print(i)
         ((sd, st), tp) = scenarios[i]
         if isinstance(sd, str):
             drop_obj = sd 

### 2021-01-22 models/model.py
debugging

@@ -396,7 +396,6 @@ def collect_stats(dirn, outpath):
     scenarios = get_drop_target_pairs(SCENARIOS)
     records = []
     for i in range(len(scenarios)):
-        print(i)
         ((sd, st), tp) = scenarios[i]
         if isinstance(sd, str):
             drop_obj = sd 
@@ -407,8 +406,8 @@ def collect_stats(dirn, outpath):
         else:
             target_obj = st[0]
         sname = scenario_pathname(drop_obj, target_obj, tp)
-        outpath = os.path.join(dirn, sname)
-        with open(outpath, 'rb') as _f:
+        pth = os.path.join(dirn, sname)
+        with open(pth, 'rb') as _f:
             outcomes = pickle.loads(_f.read())
             records.append(outcomes)
     features = pd.DataFrame(records)

### 2021-01-22 models/model.py
bugfix

@@ -409,6 +409,9 @@ def collect_stats(dirn, outpath):
         pth = os.path.join(dirn, sname)
         with open(pth, 'rb') as _f:
             outcomes = pickle.loads(_f.read())
+            outcomes['drop_object'] = drop_obj
+            outcomes['target_object'] = target_obj
+            outcomes['condition'] = tp
             records.append(outcomes)
     features = pd.DataFrame(records)
     features.to_csv(outpath, index=False)

### 2021-01-22 models/model.py
cosmit

@@ -359,14 +359,7 @@ def get_stats(dirn):
 
 
 def get_and_save_stats(sd, st, tp, base_dir, out_dir):
-    if isinstance(sd, str):
-        drop_obj = sd 
-    else:
-        drop_obj = sd[0]
-    if isinstance(st, str):
-        target_obj = st
-    else:
-        target_obj = st[0]
+    drop_obj, target_obj = get_object_names(sd, st)
     sname = scenario_pathname(drop_obj, target_obj, tp)
     path = os.path.join(base_dir, sname)
     print('Getting stats for %s' % sname)
@@ -392,19 +385,24 @@ def get_all_stats(base_dir, out_dir):
     pool.join()
 
 
+def get_object_names(sd, st):
+    if isinstance(sd, str):
+        drop_obj = sd 
+    else:
+        drop_obj = sd[0]
+    if isinstance(st, str):
+        target_obj = st
+    else:quit()
+        target_obj = st[0]
+    return drop_obj, target_obj
+
+
 def collect_stats(dirn, outpath):
     scenarios = get_drop_target_pairs(SCENARIOS)
     records = []
     for i in range(len(scenarios)):
         ((sd, st), tp) = scenarios[i]
-        if isinstance(sd, str):
-            drop_obj = sd 
-        else:
-            drop_obj = sd[0]
-        if isinstance(st, str):
-            target_obj = st
-        else:
-            target_obj = st[0]
+        drop_obj, target_obj = get_object_names(sd, st)
         sname = scenario_pathname(drop_obj, target_obj, tp)
         pth = os.path.join(dirn, sname)
         with open(pth, 'rb') as _f:

### 2021-01-22 models/model.py
run script

@@ -392,7 +392,7 @@ def get_object_names(sd, st):
         drop_obj = sd[0]
     if isinstance(st, str):
         target_obj = st
-    else:quit()
+    else:
         target_obj = st[0]
     return drop_obj, target_obj
 

### 2021-01-22 models/run.py

@@ -1,0 +1,43 @@
+from argparse import ArgumentParser
+
+import model
+import generate_stimuli
+
+def get_args():
+
+    parser = ArgumentParser()
+
+    parser.add_argument("--stimulus_dir",
+                        type=str,
+                        default=None,
+                        help="dirname where stimuli are saved")
+
+    parser.add_argument("--stats_dir",
+                        type=str,
+                        default=None,
+                        help="dirname where stats are saved")
+
+
+    parser.add_argument("--feature_path",
+                        type=str,
+                        default=None,
+                        help="file where stats are collected into a csv") 
+
+    parser.add_argument("--num_trials",
+                        type=int,
+                        default=100,
+                        help="num trials per condition") 
+    
+    args = parser.parse_args()
+    return args
+
+if __name__ == "__main__":
+    args = get_args()
+    stimulus_dir = args.stimulus_dir
+    stats_dir = args.stats_dir
+    feature_path = args.feature_path
+    num_trials = args.num_trials
+    generate_stimuli.main(stimulus_dir, num_trials)
+    model.get_all_stats(stimulus_dir, stats_dir)
+    model.collect_stats(stimulus_dir, feature_path)
+    

### 2021-01-22 analysis/model_analysis_v2.Rmd
fitting model features to choice data

---
title: "curiobaby_drop model analysis"
author: "George Kachergis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
require(tidyverse)
require(here)
```

## Load data

```{r, load-data}
raw <- read.table(here("models/model_stats.csv"), sep=',')
cnames <- raw[1,]
mdat <- raw[2:nrow(raw),]
names(mdat) = cnames
for(c in 1:(ncol(mdat)-3)) {
  mdat[,c] = as.numeric(mdat[,c])
}
mdat$trial = rep(1:20, each=2)
# right now, each trial is 2 rows, 
# uniquely identified with drop_object x condition
#mdat %>% distinct(drop_object, condition)

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism"))

# selects given feature and returns wide df that can be compared with behavioral data
get_feature_df <- function(mdat, fname) {
  fdf <- mdat[,c(fname,"drop","target","relation")] %>%
    pivot_wider(id_cols = c("drop","relation"), names_from = "target", values_from = fname) %>%
    arrange(relation,drop)
}

save(mdat, file=here("models/model_data.RData"))
```

# Fit to adult choice proportions

```{r}
load(file=here("paper/processed_data.RData"))

# ToDo: hold out half the subjects and CV on other half
adult_trial_agg <- adult_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>% # , n=n()
  arrange(relation, desc(chose_target))

#hum_ad <- adult_trial_agg %>%
#  pivot_wider(id_cols = c("drop","relation"), names_from = "target", values_from = chose_target) %>%
#  arrange(relation,drop)

softmax <- function(weights, beta=1) {
  num <- exp(beta * weights)
  return(num / sum(num))
}

get_model_target_choice_props <- function(feat_df, hum_df, beta) {
  hum_df <- hum_df %>% arrange(relation, drop) # same order as model df
  hum_df$Model_targ_prop = 0
  for(i in 1:nrow(hum_df)) {
    mod_cols = which(!is.na(feat_df[i,1:ncol(feat_df)]))[3:4]
    mod_choice = softmax(feat_df[i,mod_cols], beta=beta)
    hum_df[i,]$Model_targ_prop = as.numeric(mod_choice[hum_df[i,]$target] / sum(mod_choice))
  }
  return(hum_df)
}

evalFit <- function(feat_df, hum_df, beta) {
  hum_df <- get_model_target_choice_props(feat_df, hum_df, beta)
  r = with(hum_df, cor(chose_target, Model_targ_prop))
  return(-r) # return negative cor since DEoptim minimizes
}

require(DEoptim)

feat_names = names(mdat)[1:(ncol(mdat)-3)]
# for each feature, want to fit beta to maximize correlation between human and model choices
#feat_df <- get_feature_df(mdat, feat_names[1])

adult_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=adult_trial_agg)
}
```

# Compare to children's choices

```{r}
child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

child_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
```

### 2021-01-22 models/model.py
maybe fixed all-0 bug in obj_final features??

@@ -90,7 +90,7 @@ def get_last_frame_id(d):
     """
     fnames = list(d['frames'].keys())
     fnames.sort()
-    return fnames[-1]
+    return fnames[-2]
 
 
 def get_last_frame_positions(data):

### 2021-01-22 analysis/model_analysis_v2.Rmd

@@
   mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
-         target = replace(target, target=="triangular_prism", "trig prism"))
+         target = replace(target, target=="triangular_prism", "trig prism")) %>%
+  select(-`obj_final_position_std_objects=drop`, -`obj_final_position_std_objects=target`)
+# these cols are all 0...
 
@@
 
-feat_names = names(mdat)[1:(ncol(mdat)-3)]
+feat_names = names(mdat)[1:(ncol(mdat)-4)]
 # for each feature, want to fit beta to maximize correlation between human and model choices
@@
   feat_df <- get_feature_df(mdat, feat)
+  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
   adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
@@
   feat_df <- get_feature_df(mdat, feat)
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=30, itermax=50), 
                 feat_df=feat_df, hum_df=child_trial_agg)
@@
 ```
+
+```{r}
+adult_mfit <- tibble()
+child_mfit <- tibble()
+
+for(f in names(adult_fits)) {
+  adult_mfit = bind_rows(adult_mfit, c(feature=f, 
+                                       beta=as.numeric(unlist(adult_fits[[f]]$optim$bestmem)), 
+                                       r=-adult_fits[[f]]$optim$bestval))
+  child_mfit = bind_rows(child_mfit, c(feature=f, 
+                                       beta=as.numeric(unlist(child_fits[[f]]$optim$bestmem)), 
+                                       r=-child_fits[[f]]$optim$bestval))
+}
+
+adult_mfit <- adult_mfit %>% 
+  mutate(beta = as.numeric(beta),
+         r = as.numeric(r)) %>%
+  arrange(desc(r))
+
+adult_mfit
+```
+
+```{r children}
+child_mfit <- child_mfit %>% 
+  mutate(beta = as.numeric(beta),
+         r = as.numeric(r)) %>%
+  arrange(desc(r))
+
+child_mfit
+```
+```{r}
+save(mdat, child_mfit, adult_mfit, file=here("models/model_data.RData"))
+```

### 2021-01-22 models/model.py
maybe fixed all-0 bug in obj_final features??

@@ -178,7 +178,7 @@ def obj_final_position_std(data, objects=None):
     object_inds = get_object_inds(objects)
     posvecs = get_last_frame_positions(data)
     if object_inds is not None:
-        posvecs = posvecs[object_inds]
+        posvecs = posvecs[:, object_inds]
     total_std = np.sqrt(posvecs.var(axis=0).sum(axis=0).sum(axis=0))
     return total_std
 

### 2021-01-22 models/model.py
some more models

@@ -183,6 +183,14 @@ def obj_final_position_std(data, objects=None):
     return total_std
 
 
+def obj_final_position_invstd(data, objects=None):
+    """
+    model expressing 1 - total std in final positions 
+    of objects (can be subselected for specific object)
+    """
+    return 1 - obj_final_position_std(data, objects=objects)
+
+
 def get_radii(data, objects=None):
     """helper function"""
     object_inds = get_object_inds(objects)
@@ -300,13 +308,13 @@ def support_std(data):
     return np.sqrt(m * (1 - m))
 
 
-def sharpness_of_support_posjitter_response(data):
+def sharpness_of_support_posjitter_response(data, C=1):
     supports = list(map(get_support, data))
     if len(np.unique(supports)) == 1:
         return 0
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = np.array(list(map(radfunc, data))).reshape((-1, 1))
-    cls = svm.LinearSVC()
+    cls = svm.LinearSVC(C=C)
     cls.fit(radii, supports)
     preds = cls.predict(radii)
     return sk_metrics.f1_score(preds, supports)
@@ -321,6 +329,8 @@ model_funcs = [avg_len,
                len_inverse_sharpe_ratio,
                (obj_final_position_std, {'objects': 'drop'}),
                (obj_final_position_std, {'objects': 'target'}),
+               (obj_final_position_invstd, {'objects': 'drop'}),
+               (obj_final_position_invstd, {'objects': 'target'}),
                (avg_final_radius, {'objects': 'drop'}),
                (avg_final_radius, {'objects': 'target'}),
                (avg_max_radius, {'objects': 'drop'}),
@@ -332,6 +342,8 @@ model_funcs = [avg_len,
                support_probability,
                support_std,
                sharpness_of_support_posjitter_response
+               (sharpness_of_support_posjitter_response, {'C': 1e-5}),
+               (sharpness_of_support_posjitter_response, {'C': 1e5}),
               ]
 
 

### 2021-01-22 models/model.py
typo

@@ -341,7 +341,7 @@ model_funcs = [avg_len,
                (normed_velocity_std_after_first_collision, {'objects': 'target'}),
                support_probability,
                support_std,
-               sharpness_of_support_posjitter_response
+               sharpness_of_support_posjitter_response,
                (sharpness_of_support_posjitter_response, {'C': 1e-5}),
                (sharpness_of_support_posjitter_response, {'C': 1e5}),
               ]

### 2021-01-22 models/model.py
improved model of sharpness?

@@ -320,6 +320,18 @@ def sharpness_of_support_posjitter_response(data, C=1):
     return sk_metrics.f1_score(preds, supports)
 
 
+def nonlinearity_of_support_posjitter_response(data):
+    supports = list(map(get_support, data))
+    if len(np.unique(supports)) == 1:
+        return 0
+    radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
+    radii = list(map(radfunc, data))
+    out = stats.linregress(radii, supports)
+    r = out.value
+    pv = 1 - out.pvalue
+    return {'r': r, 'pv': pv}
+
+
 ########################
 #####INFRASTRUCTURE#####
 ########################
@@ -344,6 +356,7 @@ model_funcs = [avg_len,
                sharpness_of_support_posjitter_response,
                (sharpness_of_support_posjitter_response, {'C': 1e-5}),
                (sharpness_of_support_posjitter_response, {'C': 1e5}),
+               nonlinearity_of_support_posjitter_response
               ]
 
 
@@ -364,7 +377,12 @@ def get_stats(dirn):
             kwargs = {}
             name = mf.__name__
         print('... getting %s' % name)
-        outcomes[name] = mf(data, **kwargs)
+        result = mf(data, **kwargs)
+        if hasttr(result, 'keys'):
+            new_d = {name + '_' + k: v for k, v in result.items()}
+            outcomes.update(new_d)
+        else:
+            outcomes[name] = result
     for d in data:
         d.close()
     return outcomes

### 2021-01-22 models/model.py
bugfix

@@ -327,9 +327,9 @@ def nonlinearity_of_support_posjitter_response(data):
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
     out = stats.linregress(radii, supports)
-    r = out.value
+    absr = np.abs(out.rvalue)
     pv = 1 - out.pvalue
-    return {'r': r, 'pv': pv}
+    return {'r': absr, 'pv': pv}
 
 
 ########################

### 2021-01-22 models/model.py
typo

@@ -378,7 +378,7 @@ def get_stats(dirn):
             name = mf.__name__
         print('... getting %s' % name)
         result = mf(data, **kwargs)
-        if hasttr(result, 'keys'):
+        if hasattr(result, 'keys'):
             new_d = {name + '_' + k: v for k, v in result.items()}
             outcomes.update(new_d)
         else:

### 2021-01-22 models/model.py
typo

@@ -9,6 +9,7 @@ import h5py
 import pandas as pd
 import sklearn.svm as svm
 import sklearn.metrics as sk_metrics
+import scipy.stats as stats
 
 from experimental import (SCENARIOS, 
                           scenario_pathname,

### 2021-01-22 models/model.py
typo

@@ -324,7 +324,7 @@ def sharpness_of_support_posjitter_response(data, C=1):
 def nonlinearity_of_support_posjitter_response(data):
     supports = list(map(get_support, data))
     if len(np.unique(supports)) == 1:
-        return 0
+        return 0, 0
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
     out = stats.linregress(radii, supports)

### 2021-01-22 models/model.py
typo

@@ -324,7 +324,7 @@ def sharpness_of_support_posjitter_response(data, C=1):
 def nonlinearity_of_support_posjitter_response(data):
     supports = list(map(get_support, data))
     if len(np.unique(supports)) == 1:
-        return 0, 0
+        return {'r': 0, 'pv': 0}
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
     out = stats.linregress(radii, supports)

### 2021-01-22 models/model.py
minor

@@ -292,45 +292,43 @@ def get_support(d):
     return support  
 
 
-def support_probability(data):
+def support(data):
     """model expressing empirical likelihood of a support relationship
     arising at the end of a trial
     """
     supports = list(map(get_support, data))
-    return np.mean(supports)
 
+    #basic statistics
+    m = np.mean(supports)
+    s = np.sqrt(m * (1 - m))
+    result = {'probability': m, 'std': s}
 
-def support_std(data):
-    """model expressing empirical standard deviation in the distribution of
-    whether a support relationship will arise at the end of a trial
-    """
-    m = support_probability(data)
-    #std for binomial variable is sqrt(mean * (1 - mean))
-    return np.sqrt(m * (1 - m))
-
-
-def sharpness_of_support_posjitter_response(data, C=1):
-    supports = list(map(get_support, data))
-    if len(np.unique(supports)) == 1:
-        return 0
-    radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
-    radii = np.array(list(map(radfunc, data))).reshape((-1, 1))
-    cls = svm.LinearSVC(C=C)
-    cls.fit(radii, supports)
-    preds = cls.predict(radii)
-    return sk_metrics.f1_score(preds, supports)
-
-
-def nonlinearity_of_support_posjitter_response(data):
-    supports = list(map(get_support, data))
-    if len(np.unique(supports)) == 1:
-        return {'r': 0, 'pv': 0}
+    #sharpness as measured by categorization accuracy
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
-    out = stats.linregress(radii, supports)
-    absr = np.abs(out.rvalue)
-    pv = 1 - out.pvalue
-    return {'r': absr, 'pv': pv}
+    radii_rs = np.array(radii).reshape((-1, 1)) 
+    Cs = [1, 1e-5, 1e5]
+    for C in Cs:
+        if len(np.unique(supports)) == 1:
+            score = 0
+        else:
+            cls = svm.LinearSVC(C=C)
+            cls.fit(radii_rs, supports)
+            preds = cls.predict(radii)
+            score = sk_metrics.f1_score(preds, supports)
+        result['response_sharpness_C=%s' % str(C)] = score
+
+    #sharpness as measured by linearity
+    if len(np.unique(supports)) == 1:
+        absr = pv = 0
+    else:
+        out = stats.linregress(radii, supports)
[…]

### 2021-01-22 models/model.py
typo

@@ -314,7 +314,7 @@ def support(data):
         else:
             cls = svm.LinearSVC(C=C)
             cls.fit(radii_rs, supports)
-            preds = cls.predict(radii)
+            preds = cls.predict(radii_rs)
             score = sk_metrics.f1_score(preds, supports)
         result['response_sharpness_C=%s' % str(C)] = score
 

### 2021-01-23 models/model.py
correlation plot

@@ -10,6 +10,7 @@ import pandas as pd
 import sklearn.svm as svm
 import sklearn.metrics as sk_metrics
 import scipy.stats as stats
+import matplotlib.pyplot as plt
 
 from experimental import (SCENARIOS, 
                           scenario_pathname,
@@ -421,7 +422,7 @@ def get_object_names(sd, st):
     return drop_obj, target_obj
 
 
-def collect_stats(dirn, outpath):
+def collect_stats(dirn, featpath, figpath):
     scenarios = get_drop_target_pairs(SCENARIOS)
     records = []
     for i in range(len(scenarios)):
@@ -436,8 +437,15 @@ def collect_stats(dirn, outpath):
             outcomes['condition'] = tp
             records.append(outcomes)
     features = pd.DataFrame(records)
-    features.to_csv(outpath, index=False)
-
+    features.to_csv(featpath, index=False)
+    K = list(filter(lambda x: x not in ['drop_object', 'target_object', 'condition'],
+               features.columns))
+    C = np.array([[stats.pearsonr(x[k1], x[k2])[0] for k1 in K] for k2 in K])
+    cbar = plt.matshow(C)
+    plt.colorbar(cbar)
+    plt.xticks(np.arange(C.shape[0]), K, rotation=90)
+    plt.yticks(np.arange(C.shape[0]), K, rotation=0)
+    plt.savefig(figpath)
 
 
 

### 2021-01-23 analysis/model_analysis_v2.Rmd

--- 2021-01-22 analysis/model_analysis_v2.Rmd
@@
          target = replace(target, target=="triangular_prism", "trig prism")) 
+  #select(-`obj_final_position_std_objects=drop`, -`obj_final_position_std_objects=target`)
+# these cols are all 0...
 
@@
 
-softmax <- function(weights, beta=1) {
-  num <- exp(beta * weights)
+softmax <- function(weights, beta=1, smooth=1e-7) {
+  weights = weights + smooth
+  probs = (weights / sum(weights)) # normalize first
+  num <- exp(beta * probs)
   return(num / sum(num))
@@
   hum_df <- get_model_target_choice_props(feat_df, hum_df, beta)
-  r = with(hum_df, cor(chose_target, Model_targ_prop))
-  return(-r) # return negative cor since DEoptim minimizes
+  #r = with(hum_df, cor(chose_target, Model_targ_prop))
+  mse = with(hum_df, sum((chose_target - Model_targ_prop)^2)) / nrow(hum_df)
+  return(mse) # return negative cor since DEoptim minimizes
 }
@@
   feat_df <- get_feature_df(mdat, feat)
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
@@
   feat_df <- get_feature_df(mdat, feat)
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                 feat_df=feat_df, hum_df=child_trial_agg)
@@
 ```
+
+```{r}
+adult_mfit <- tibble()
+child_mfit <- tibble()
+
+for(f in names(adult_fits)) {
+  adult_mfit = bind_rows(adult_mfit, c(feature=f, 
+                                       beta=as.numeric(unlist(adult_fits[[f]]$optim$bestmem)), 
+                                       mse=adult_fits[[f]]$optim$bestval))
+  child_mfit = bind_rows(child_mfit, c(feature=f, 
+                                       beta=as.numeric(unlist(child_fits[[f]]$optim$bestmem)), 
+                                       mse=child_fits[[f]]$optim$bestval))
+}
+
+adult_mfit <- adult_mfit %>% 
+  mutate(beta = as.numeric(beta),
+         mse = as.numeric(mse)) %>%
+  arrange(mse)
+
+```
+
+```{r children}
+child_mfit <- child_mfit %>% 
+  mutate(beta = as.numeric(beta),
+         mse = as.numeric(mse)) %>%
+  arrange(mse)
+
+fit_tab <- child_mfit %>% rename(child_mse = mse, child_beta = beta) %>%
+  left_join(adult_mfit %>% rename(adult_mse = mse, adult_beta = beta)) %>% 
+  arrange(adult_mse)
+
+knitr::kable(fit_tab, digits = 2)
+```
+
+```{r}
+fits <- child_mfit %>% mutate(AgeGroup = "children") %>% 
+  bind_rows(adult_mfit %>% mutate(AgeGroup = "adults"))
+
+save(mdat, fits, file=here("models/model_data.RData"))
+```
+
+```{r, eval=F}
+fits %>% ggplot(aes(x=beta, y=mse, color=AgeGroup)) +
+  #geom_text(aes(label=feature)) + 
+  geom_point() +
+  theme_minimal()
+```
+So generally, children's choices are best explained by small values of beta (.5, the minimum tested).
+
+What do the predicted choice proportions from the best feature for each age group look like?
+
+```{r}
+require(ggpubr)
+
+plot_model_preds <- function(feat_name, fits, hum_data, age="adults") {
+  beta = subset(fits, AgeGroup==age & feature==feat_name)$beta
+  md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
+  md %>% ggplot(aes(x=chose_target, y=Model_targ_prop, color=relation)) +
+    geom_abline(slope=1, intercept=0, linetype="dashed") +
+    geom_point(alpha=.5) + 
+    xlab("Human Choice Probability") + 
+    ylab("Model Choice Probability") +
+    ggtitle(paste0(feat_name,": ",age)) + theme_minimal() + 
+    xlim(0,1) + ylim(0,1)
+}
+
+ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults")
+ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children")
+
+ggarrange(ad_supp, ch_supp, nrow=1, common.legend = T)
+```
+
+```{r}
+ad <- plot_model_preds("sharpness_of_support_posjitter_response", fits, adult_trial_agg, age="adults")
+ch <- plot_model_preds("sharpness_of_support_posjitter_response", fits, child_trial_agg, age="children")
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```
+
+```{r}
+ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults")
+ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children")
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```
+
+```{r}
+ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults")
+ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children")
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```

### 2021-01-23 models/model.py
correlation plot

@@ -440,7 +440,8 @@ def collect_stats(dirn, featpath, figpath):
     features.to_csv(featpath, index=False)
     K = list(filter(lambda x: x not in ['drop_object', 'target_object', 'condition'],
                features.columns))
-    C = np.array([[stats.pearsonr(x[k1], x[k2])[0] for k1 in K] for k2 in K])
+    C = np.array([[stats.pearsonr(features[k1],
+                                  features[k2])[0] for k1 in K] for k2 in K])
     cbar = plt.matshow(C)
     plt.colorbar(cbar)
     plt.xticks(np.arange(C.shape[0]), K, rotation=90)

### 2021-01-23 models/model.py
attempt to not have figure ticks cut off (not successful)

@@ -11,6 +11,8 @@ import sklearn.svm as svm
 import sklearn.metrics as sk_metrics
 import scipy.stats as stats
 import matplotlib.pyplot as plt
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
 
 from experimental import (SCENARIOS, 
                           scenario_pathname,
@@ -446,7 +448,7 @@ def collect_stats(dirn, featpath, figpath):
     plt.colorbar(cbar)
     plt.xticks(np.arange(C.shape[0]), K, rotation=90)
     plt.yticks(np.arange(C.shape[0]), K, rotation=0)
-    plt.savefig(figpath)
+    plt.savefig(figpath, bbox_inches='tight')
 
 
 

### 2021-01-23 analysis/model_analysis_v2.Rmd
added new features

@@
 
-save(mdat, file=here("models/model_data.RData"))
 ```
@@
 
-knitr::kable(fit_tab, digits = 2)
+knitr::kable(fit_tab, digits = 3)
 ```
@@
   #geom_text(aes(label=feature)) + 
-  geom_point() +
+  geom_point(alpha=.5) +
   theme_minimal()

### 2021-01-25 analysis/model_analysis_v2.Rmd
tried combinations of features

@@
          target = replace(target, target=="triangular_prism", "trig prism"))
-  #select(-`obj_final_position_std_objects=drop`, -`obj_final_position_std_objects=target`)
-# these cols are all 0...
+
+colMeans(mdat[,1:22])
+# obj_final_position_invstd_objects=drop = -0.2980893  should that be negative?
+
+# engineer some features: 
+# combine target + drop target features
+mdat_eng <- mdat %>%
+  mutate(obj_final_position_std = 
+           `obj_final_position_std_objects=drop` + 
+           `obj_final_position_std_objects=target`,
+         normed_velocity_std_after_first_collision_objects = 
+           `normed_velocity_std_after_first_collision_objects=drop` + 
+           `normed_velocity_std_after_first_collision_objects=target`,
+         avg_final_radius_objects = 
+           `avg_final_radius_objects=drop` + 
+           `avg_final_radius_objects=target`,
+         avg_max_radius_objects = 
+           `avg_max_radius_objects=drop` + 
+           `avg_max_radius_objects=target`,
+         max_radius_std_objects = 
+           `max_radius_std_objects=drop` + 
+           `max_radius_std_objects=target`,
+         support_combo = 
+           support_probability + 
+           support_std + 
+           `support_response_sharpness_C=1e-05`, # add one of support_response_linearity_r or _pv ?
+         len_combo = avg_len + len_std + len_inverse_sharpe_ratio
+         ) %>%
+  select(-`obj_final_position_std_objects=drop`, 
+         -`obj_final_position_std_objects=target`,
+         -`normed_velocity_std_after_first_collision_objects=drop`,
+         -`normed_velocity_std_after_first_collision_objects=target`,
+         -`avg_final_radius_objects=drop`,
+         -`avg_final_radius_objects=target`,
+         -`avg_max_radius_objects=drop`,
+         -`avg_max_radius_objects=target`,
+         -`max_radius_std_objects=drop`,
+         -`max_radius_std_objects=target`,
+         -support_probability, 
+         -support_std,
+         -`support_response_sharpness_C=1`,
+         -`support_response_sharpness_C=1e-05`,
+         -`support_response_sharpness_C=100000.0`,
+         -avg_len, -len_inverse_sharpe_ratio, -len_std,
+         -support_response_linearity_pv, -support_response_linearity_r,
+         -`obj_final_position_invstd_objects=target`,
+         -`obj_final_position_invstd_objects=drop`
+         )
 
@@
 
+## Now try engineered features
+
+```{r adult-eng-feats}
+feat_names2 = names(mdat_eng)[5:ncol(mdat_eng)]
+
+for(feat in feat_names2) {
+  feat_df <- get_feature_df(mdat_eng, feat)
+  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+                feat_df=feat_df, hum_df=adult_trial_agg)
+  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+                feat_df=feat_df, hum_df=child_trial_agg)
+}
+
+```
+
 ```{r}
@@
 
-plot_model_preds <- function(feat_name, fits, hum_data, age="adults") {
+plot_model_preds <- function(feat_name, fits, hum_data, age="adults", mdat) {
   beta = subset(fits, AgeGroup==age & feature==feat_name)$beta
@@
     geom_abline(slope=1, intercept=0, linetype="dashed") +
-    geom_point(alpha=.5) + 
+    geom_point(alpha=.5) + geom_smooth(method='lm') + 
     xlab("Human Choice Probability") + 
@@
 
-ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults")
-ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children")
+ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults", mdat)
+ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children", mdat)
 
@@
 ```{r}
-ad <- plot_model_preds("sharpness_of_support_posjitter_response", fits, adult_trial_agg, age="adults")
-ch <- plot_model_preds("sharpness_of_support_posjitter_response", fits, child_trial_agg, age="children")
+ad <- plot_model_preds("support_combo", fits, adult_trial_agg, age="adults", mdat_eng)
+ch <- plot_model_preds("support_combo", fits, child_trial_agg, age="children", mdat_eng)
 
@@
 ```{r}
-ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults")
-ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children")
+ad <- plot_model_preds("support_response_sharpness_C=1e-05", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=1e-05", fits, child_trial_agg, age="children", mdat)
 
@@
 ```{r}
-ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults")
-ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children")
+ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children", mdat)
 
@@
 ```
+
+```{r}
+ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children", mdat)
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```

### 2021-01-28 analysis/model_analysis_v2.Rmd
starting to add model section

@@
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
@@
   feat_df <- get_feature_df(mdat, feat)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                 feat_df=feat_df, hum_df=child_trial_agg)
@@
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=5, DEoptim.control(reltol=.001, NP=20, itermax=50), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                 feat_df=feat_df, hum_df=child_trial_agg)
@@
 
-save(mdat, fits, file=here("models/model_data.RData"))
+save(mdat, mdat_eng, fits, file=here("models/model_data.RData"))
 ```
@@
 plot_model_preds <- function(feat_name, fits, hum_data, age="adults", mdat) {
-  beta = subset(fits, AgeGroup==age & feature==feat_name)$beta
+  beta = 1 #subset(fits, AgeGroup==age & feature==feat_name)$beta
   md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
@@
 ```
+
+```{r}
+ad <- plot_model_preds("avg_final_radius_objects=target", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("avg_final_radius_objects=target", fits, child_trial_agg, age="children", mdat)
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```

### 2021-01-28 paper/paper2021.Rmd
starting to add model section

@@
 
-The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
+The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity. 
+First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
+We then present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior.
+Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
 
@@
 
+<!--
 ## Computational Models of Curiosity
@@
 The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will adversarially challenge the state of its world-model.
+-->
 
@@
 ### Participants
-Participants were 200 [check pre-exclusion] adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
+Participants were 200 adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
 
@@
 
-We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (XX participants were excluded for not meeting this criterion).
+We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
 The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
@@
 and 3) are there other apparent factors that drive their preferences?
-Our analysis addresses each in turn.
+Our analysis addresses each question in turn.
 Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials [should also show alternative target object?]. 
@@
 
-Finally, we also examined the split-half reliability of children's and adults' choices by repeatedly  splitting the samples in half and testing the correlation between the halves.
+We also examined the split-half reliability of children's and adults' choices by repeatedly  splitting the samples in half and testing the correlation between the halves.
 Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`), and for children is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
@@
 
-<!-- Finally, we examine a more lenient analysis children's choice of target location (i.e., the identity of the closest target), regardless of whether there was a collision of drop and target objects.
--->
-<!-- Chi-square tests of children's target collisions once more found that ... -->
-<!-- Table 3 shows a summary of participants' choice of target locations per set. -->
-
-<!-- In summary, children showed some consistent preferences in their choice of objects to drop from each set, but no systematic preference for targeting particular objects. -->
-<!-- We now investigate whether there were interactions of drop objects and targets that children found particularly appealing. [ToDo: big chisq test?] -->
-
 <!-- Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects?
@@
 -->
-
-```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
-drop_choice_plot <- function(dat, ymax=.66, shapes_vec) {
-  ch_cond <- dat %>% 
-    group_by(StimSet, DropChoice) %>%
-    summarise(n = n()) %>%
-    mutate(freq = n / sum(n))
-
-  ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
-  ch_cond$DropChoice <- factor(ch_cond$DropChoice, levels=shapes_vec)
-  fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
-    geom_point(alpha=.8) +
-    scale_shape_manual(values=10:19) +
-    #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-    xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,ymax) + 
-    langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-    geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
-  return(fig_drop)
-}
-
-#fig_drop <- drop_choice_plot(hum, shapes)
-```
 
@@
 
-## Model Comparison
+## Comparison to Physical Simulations
 
-Can these preferences be predicted by heuristic models of physical interactions?
-We implement and test a few models, generate relative preferences for the same drop objects and target object pairs used in Experiments 1 and 2, and see how well each model explains the strength of trial-level preferences seen in participants.
+```{r load-model-data}
+load(here("models/model_data.RData")) # mdat, mdat_eng, fits
+```
+
+Can children's and adults' preferences be predicted by heuristic models of the simulated physical interactions?
+Using a physics engine and 3D models of the objects we showed to participants, we constructed a simulation of each trial of the experiment.
+For each trial's the two possible drop object choices, we ran 100 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
+We selected features that we thought may provide good metrics for what people would found interesting. 
+For example, we collected for each drop the mean length of time before both objects come to rest (*avg_len*), as well as the standard deviation (SD) of that time (*len_std*).
+Some features were calculated separately for drop and target objects, such as: the SD of the object's final position (*obj_final_position_std_objects*) as well as the inverse of that (*obj_final_position_invstd_objects*), the mean final distance from the drop location (*avg_final_radius_objects*), the maximum final distance from the drop location (*avg_max_radius_objects*), the ...
+(*max_radius_std_objects*), ...
+(*normed_velocity_std_after_first_collision_objects*)
+<!-- support_probability, support_std, support_response_linearity_r, support_response_linearity_pv  -->
+<!--len_inverse_sharpe_ratio, support_response_sharpness_C=1 -->
+
+We measure each of these features across each possible drop in the experiment 100 times, and then use the resulting metrics to generate relative preferences for each of the drop choices on each trial.
+Finally, we compare how well each of these simple heuristic models account for children's and adults' drop preferences on each trial.
 
@@
 
-Thus, we find an early-emerging interest in containment (cite Marianella Casasola and Leslie B. Cohen) that persists into adulthood, along with a weaker interest in support relations.
+Thus, we find an early-emerging interest in containment [@Casasola2003] that persists into adulthood, along with a weaker interest in support relations.
 Is containment inherently more satisfying, or is there greater interest because it is more achievable? (Less susceptible to small amounts of error)

### 2021-01-29 models/model.py
gridsearchCV model

@@ -8,6 +8,7 @@ import numpy as np
 import h5py
 import pandas as pd
 import sklearn.svm as svm
+from sklearn.model_selection import GridSearchCV
 import sklearn.metrics as sk_metrics
 import scipy.stats as stats
 import matplotlib.pyplot as plt
@@ -308,7 +309,7 @@ def support(data):
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
     radii_rs = np.array(radii).reshape((-1, 1)) 
-    Cs = [1, 1e-5, 1e5]
+    Cs = [1, 1e-1, 1e1, 1e-2, 1e2, 1e-3, 1e3, 1e-4, 1e4, 1e-5, 1e5]
     for C in Cs:
         if len(np.unique(supports)) == 1:
             score = 0
@@ -318,6 +319,13 @@ def support(data):
             preds = cls.predict(radii_rs)
             score = sk_metrics.f1_score(preds, supports)
         result['response_sharpness_C=%s' % str(C)] = score
+    svc = svm.LinerSVC()
+    cls = GridSearchCV(svc, {'C': Cs})
+    cls.fit(radii_rs, supports)
+    preds = cls.predict(radii_rs)
+    score = sk_metrics.f1_score(preds, supports)
+    best_C = cls.best_params_['C']
+    result['response_sharpness_GridSearchCV_C=%s' % str(C)] = score
 
     #sharpness as measured by linearity
     if len(np.unique(supports)) == 1:

### 2021-01-29 models/model.py
minor

@@ -11,8 +11,6 @@ import sklearn.svm as svm
 import sklearn.metrics as sk_metrics
 import scipy.stats as stats
 import matplotlib.pyplot as plt
-from matplotlib import rcParams
-rcParams.update({'figure.autolayout': True})
 
 from experimental import (SCENARIOS, 
                           scenario_pathname,

### 2021-01-29 models/model.py
bugfix

@@ -327,7 +327,7 @@ def support(data):
     preds = cls.predict(radii_rs)
     score = sk_metrics.f1_score(preds, supports)
     best_C = cls.best_params_['C']
-    result['response_sharpness_GridSearchCV_C=%s' % str(C)] = score
+    result['response_sharpness_GridSearchCV_C=%s' % str(best_C)] = score
 
     #sharpness as measured by linearity
     if len(np.unique(supports)) == 1:

### 2021-01-29 models/model.py
bugfix

@@ -321,7 +321,7 @@ def support(data):
             preds = cls.predict(radii_rs)
             score = sk_metrics.f1_score(preds, supports)
         result['response_sharpness_C=%s' % str(C)] = score
-    svc = svm.LinerSVC()
+    svc = svm.LinearSVC()
     cls = GridSearchCV(svc, {'C': Cs})
     cls.fit(radii_rs, supports)
     preds = cls.predict(radii_rs)

### 2021-01-29 models/model.py
bugfix

@@ -300,6 +300,7 @@ def support(data):
     """model expressing empirical likelihood of a support relationship
     arising at the end of a trial
     """
+    print('... getting supports')
     supports = list(map(get_support, data))
 
     #basic statistics
@@ -308,6 +309,7 @@ def support(data):
     result = {'probability': m, 'std': s}
 
     #sharpness as measured by categorization accuracy
+    print('... getting svc results')
     radfunc = lambda x: np.linalg.norm(x['static']['drop_position'][[0, 2]])
     radii = list(map(radfunc, data))
     radii_rs = np.array(radii).reshape((-1, 1)) 
@@ -315,21 +317,35 @@ def support(data):
     for C in Cs:
         if len(np.unique(supports)) == 1:
             score = 0
+            acc = 0
         else:
+            print('... getting svc results C = %s' % str(C))
             cls = svm.LinearSVC(C=C)
             cls.fit(radii_rs, supports)
             preds = cls.predict(radii_rs)
             score = sk_metrics.f1_score(preds, supports)
+            acc = sk_metrics.accuracy_score(preds, supports)
         result['response_sharpness_C=%s' % str(C)] = score
-    svc = svm.LinearSVC()
-    cls = GridSearchCV(svc, {'C': Cs})
-    cls.fit(radii_rs, supports)
-    preds = cls.predict(radii_rs)
-    score = sk_metrics.f1_score(preds, supports)
-    best_C = cls.best_params_['C']
-    result['response_sharpness_GridSearchCV_C=%s' % str(best_C)] = score
+        result['response_sharpness_accuracy_C=%s' str(C)] = acc
+    print('... getting gridsearch svc results')
+    if len(np.unique(supports)) == 1:
+        score = 0
+        acc = 0
+        result['response_sharpness_GridSearchCV'] = score
+        result['response_sharpness_accuacy_GridSearchCV'] = acc
+    else:
+        svc = svm.LinearSVC()
+        cls = GridSearchCV(svc, {'C': Cs})
+        cls.fit(radii_rs, supports)
+        preds = cls.predict(radii_rs)
+        score = sk_metrics.f1_score(preds, supports)
+        acc = sk_metrics.accuracy_score(preds, supports)
+        best_C = cls.best_params_['C']
+        result['response_sharpness_GridSearchCV_C=%s' % str(best_C)] = score
+        result['response_sharpness_accuacy_GridSearchCV_C=%s' % str(best_C)] = acc
 
[…]

### 2021-01-29 models/model.py
more stats over 250 samples

@@ -324,13 +324,11 @@ def support(data):
             score = sk_metrics.f1_score(preds, supports)
             acc = sk_metrics.accuracy_score(preds, supports)
         result['response_sharpness_C=%s' % str(C)] = score
-        result['response_sharpness_accuracy_C=%s' str(C)] = acc
+        result['response_sharpness_accuracy_C=%s' % str(C)] = acc
     print('... getting gridsearch svc results')
     if len(np.unique(supports)) == 1:
         score = 0
         acc = 0
-        result['response_sharpness_GridSearchCV'] = score
-        result['response_sharpness_accuacy_GridSearchCV'] = acc
     else:
         svc = svm.LinearSVC()
         cls = GridSearchCV(svc, {'C': Cs})
@@ -338,9 +336,8 @@ def support(data):
         preds = cls.predict(radii_rs)
         score = sk_metrics.f1_score(preds, supports)
         acc = sk_metrics.accuracy_score(preds, supports)
-        best_C = cls.best_params_['C']
-        result['response_sharpness_GridSearchCV_C=%s' % str(best_C)] = score
-        result['response_sharpness_accuacy_GridSearchCV_C=%s' % str(best_C)] = acc
+    result['response_sharpness_GridSearchCV'] = score
+    result['response_sharpness_accuracy_GridSearchCV'] = acc
 
     #sharpness as measured by linearity
     print('... getting linearity results')

### 2021-01-29 paper/paper2021.Rmd
incorporated Mike's edits, except some of intro

@@
 ---
-title: "What if you drop that? Developmental changes in curiosity about physical interactions"
+# Mike has a better title git stashed but G can't remember it..
+# old: What if you drop that? Developmental changes in curiosity about physical interactions
+title: "Using physical simulations to predict children's and adults' preference for physical interactions"
 bibliography: library.bib
@@
      and find increasingly strong preference for choices affording particular relations (e.g., 
-     containment) across development, as well as an adult bias for choosing support relations.
+     containment) across development, as well as an adult bias for choosing a support relation.
 
@@
 First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
-We then present a computational theory of how a learner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior.
+We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., measuring likelihood of a dropped object coming to rest on a target object), and test whether these features predict people's preferences in the same task.
 Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
 
-Our computational theory is inspired by classic descriptive theories that posited that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
-Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than simple or highly-complex stimuli [@Kidd2012; @Kidd2014].
-According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
-Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
-Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
-Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
-
-Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE Spelke, Baillargeon..), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
+Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE Spelke, @Baillargeon2007), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
 However, the measures used in this literature have typically focused on either children's ability to discriminate types of events, or their ability to carry out particular tasks (e.g., shape sorting), but have not examined which types of interactions children are most interested in testing.
@@
 <!-- High-level statement of our approach -->
-In sum, this paper presents a unified paradigm for advancing theories of curiosity and its role in guiding the development of knowledge about the physical world. 
-We present: (1) a computational theory of intrinsic motivation instantiated in an artificial reinforcement-learning agent that explores a simulated 3D environment; (2) two datasets that measure adults' and children's actions in a novel physical exploration task; and (3) quantitative comparisons between the actions taken by the artificial agent and children on the same set of tasks.
+In sum, this paper presents a paradigm for testing and building theories of curiosity, and defining its role in guiding the development of knowledge about the physical world. 
+We present a study that measures adults' (Experiment 1) and children's (Experiment 2) preferences in a novel physical exploration task, a set of 20 heuristic models of curiosity that operate on simulations of this same task in a 3D environment, and comparisons between the preferences of children, adults, and these heuristic models on the same set of trials.
 Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.
@@
 
-<!--
+<!-- move this paragraph to GD if we want to discuss goals?
 ## Computational Models of Curiosity
@@
 
-```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Example trial from Experiment 1 with adults.
-Trials in Experiment 2 (for children) were similar, but arranged for Zoom with the experimenter's face in the center."}
+```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
 img <- png::readPNG("figs/2AFC_DropTaskFig.png")
@@
 We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
-The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
+<!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
 2) are they more consistent with trials that afford support or containment relations?
 and 3) are there other apparent factors that drive their preferences?
-Our analysis addresses each question in turn.
-Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials [should also show alternative target object?]. 
+Our analysis addresses each question in turn. -->
+Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
 Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance [adjust criterion for multiple comparisons?].
@@
 
-ad_supp_cont <- t.test(subset(ad_subj_agg, relation=="contain")$chose_target -
-         subset(ad_subj_agg, relation=="support")$chose_target)
+ad_supp_cont <- t.test(x=subset(ad_subj_agg, relation=="contain")$chose_target, 
+                       y=subset(ad_subj_agg, relation=="support")$chose_target, paired=T)
 ```
@@
 
-ch_supp_cont <- t.test(subset(ad_subj_agg, relation=="contain")$chose_target -
-         subset(ad_subj_agg, relation=="support")$chose_target)
+ch_supp_cont <- t.test(x=subset(ad_subj_agg, relation=="contain")$chose_target,
+                       y=subset(ad_subj_agg, relation=="support")$chose_target, paired=T)
 ```
+
+Were adults more consistent in their choices on support or containment trials?
+Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
+<!--For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.-->
 
@@
 
-Were adults more consistent in their choices on support or containment trials?
-Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations (M=`r round(ad_rel_means[1,]$M,2)`) than support relations (M=`r round(ad_rel_means[2,]$M,2)`; one-sample `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
-For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.
-
 # Experiment 2: Children
 
-Experiment 1 demonstrated that adults show remarkably consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
+Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
 Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
@@
 ### Participants
-Participants were 73 children recruited online via Bing Nursery School and targeted Facebook Ads.
+Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook Ads.
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions [based on?], results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+<!-- Sama: notes on exclusions?
+-->
 
@@
 Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1 [maybe just drop Table 1?].
-Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05 [use stricter for mult comparisons?
-Bonf=.0025]) from chance.
+Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance.
+<!-- stricter crit for mult comparisons?
+Bonf=.0025 -->
 Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
@@
 Were children more consistent in their choices on support or containment trials?
-As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations (M=`r round(ch_rel_means[1,]$M,2)`) than support relations (M=`r round(ch_rel_means[2,]$M,2)`; one-sample `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
 Overall, children did not show a significant preference for choosing the support relation [should we add a regression with trial_type * age (3 - 18=adult)?].
-Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that grows with age, and that is stronger for containment.
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
 
@@
 
+<!-- moved from old Intro: rewrite to discuss Haber et al. more -->
+Thexe results will serve as a test set for evaluating computational theories of curiosity, which in turn are inspired by classic descriptive theories positing that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
+Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than simple or highly-complex stimuli [@Kidd2012; @Kidd2014].
+According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
+Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
+Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
+Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
+
 # Acknowledgements

### 2021-01-30 paper/paper2021.Rmd
new model fits and new intro from Bria

@@
 
-<!-- Curiosity is important... end with core question about what gives rise to curiosity. -->
 Curiosity is a hallmark aspect of human intelligence. 
@@
 Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
+
+The goal of the current paper is to help close this gap by proposing a novel paradigm to advance our theoretical understanding of curiosity, specifically within the domain of physical object interactions [@kubricht2017intuitive].
+First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
+We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., measuring likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
+<!-- Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
+-->
+
+We take inspiration from a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact [@hespos2012physics; @smith2018developing; @Baillargeon2007].
+Children both spend a remarkably amount of time across exploring how different objects and surfaces interact during naturalistic play [@fenson1976] and spend longer time exploring objects that appear to violate physical laws (e.g., an object that appears to pass through a wall; @Stahl2015; @Baillargeon2007).
+ In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self].
+However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of physical interactions or exploratory behavior.
+Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
+We developed a novel physical exploration task in which children, adults, or AI agents choose which series of physical experiments to perform and observe the results of each in real time.
+
+<!-- High-level statement of our approach -->
+In sum, this paper presents a paradigm and model for testing theories of curiosity about physical interactions. 
+<!-- and defining its role in guiding the development of knowledge about the physical world.  -->
+First, we measured adults' and children's (3-7 years of age) preferences in a novel physical exploration task; participants were asked to choose one of two objects (e.g., a sphere, a dumbbell, see Figure 1) to drop onto a target object (e.g., a pyramid) with the goal of the creating the most interesting physical interaction (see Figure 2).
+We then explore the predictive power of a variety of heuristic models of curiosity that operate on simulations of this same task with these same objects in a 3D environment. 
+We propose that using task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of our curiosity about the physical world.
+
+<!-- presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
+-->
+
+<!-- What we've learned from prior theoretical work, and how it falls short -->
+<!-- A limitation of past theories of curiosity is that they are large part verbal descriptions, without formal, testable, mechanisms. -->
+<!-- An exception to this: @Schmidhuber2010 and @Oudeyer2013 --similar but different, and critically not evaluated against same children's behavior in the same situations -->
+
+<!-- What we've learned from prior behavioral work, and how our approach is different -->
+<!-- Looking time people: @Baillargeon2007 and other studies of infants' surprisal at physical events (occlusion, containment,  -->
+<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks)  -->
+
+<!-- Highlight main contributions of the paper -->
+<!-- One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects.  -->
+<!-- A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
+-->
+
+<!-- OLD INTRO: delete all?
 
@@
 
-<!-- High-level statement of our approach -->
 In sum, this paper presents a paradigm for testing and building theories of curiosity, and defining its role in guiding the development of knowledge about the physical world. 
@@
 Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.
-
-<!-- presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
--->
-
-<!-- What we've learned from prior theoretical work, and how it falls short -->
-
-<!-- A limitation of past theories of curiosity is that they are large part verbal descriptions, without formal, testable, mechanisms. -->
-<!-- An exception to this: @Schmidhuber2010 and @Oudeyer2013 --similar but different, and critically not evaluated against same children's behavior in the same situations -->
-
-<!-- What we've learned from prior behavioral work, and how our approach is different -->
-
-<!-- Looking time people: @Baillargeon2007 and other studies of infants' surprisal at physical events (occlusion, containment,  -->
-<!-- Ullman -- not about curiosity, but about intuitive physics learning from observation in simplified 2D domains (e.g., colliding hockey pucks)  -->
-
-<!-- Highlight main contributions of the paper -->
-
-<!-- One rich domain that young children are in the midst of learning about is the properties and affordances of physical objects.  -->
-<!-- A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
 -->
@@
 ```
+
+<!-- Maybe code the type of goals stated by the parents? -->
 
@@
 ```
-
-Can children's and adults' preferences be predicted by heuristic models of the simulated physical interactions?
-Using a physics engine and 3D models of the objects we showed to participants, we constructed a simulation of each trial of the experiment.
-For each trial's the two possible drop object choices, we ran 100 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
+Using a physics engine and 3D models of the objects that were shown to participants, we constructed a simulation of each trial of the experiment and attempted to predict children's and adults' choices using a variety of heuristic models of the simulated physical interactions.
+For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
 We selected features that we thought may provide good metrics for what people would found interesting. 

### 2021-01-31 models/model.py
initial attempt at stats variance

@@ -19,40 +19,6 @@ from experimental import (SCENARIOS,
                           scenario_pathname,
                           get_drop_target_pairs)
 
-################
-#####BASICS#####
-################
-
-def softmax(x, beta=1):
-    numerator = np.exp(beta * x)
-    denominator = numerator.sum()
-    return numerator / denominator
-
-
-class CuriosityBinaryChoice(object):
-    def __init__(self,
-                 curiosity_function,
-                 linking_function=softmax,
-                 curiosity_kwargs=None,
-                 linking_kwargs=None):
-        if curiosity_kwargs is None:
-            curiosity_kwargs = {}
-        if linking_kwargs is None:
-            linking_kwargs = {}
-        self.curiosity_function = curiosity_function
-        self.linking_function = linking_function
-        self.curiosity_kwargs = curiosity_kwargs
-        self.linking_kwargs = linking_kwargs
-
-    def judgement(self, data):
-        data_left, data_right = data
-        m0 = self.curiosity_function(data_left, **self.curiosity_kwargs)
-        m1 = self.curiosity_function(data_right, **self.curiosity_kwargs)
-        judgement = self.linking_function([m0, m1], **self.linking_kwargs)
-        return {'curiosity_left': m0,
-                'curiosity_right': m1,
-                'judgement': judgement}
-
 
 ##############
 #####TIME#####
@@ -381,11 +347,42 @@ model_funcs = [avg_len,
               ]
 
 
-def get_stats(dirn):
+def get_splits(n, k, seed=0):
+    rng = np.random.RandomState(seed=seed)
+    splits = []
+    for i in range(k):
+        p = rng.permutation(n)
+        lsplit = p[: n / 2]
+        rsplit = p[n / 2: ]
+        splits.append((lsplit, rsplit))
+    return splits
+
+
+def get_result(mf, data, kwargs, splits):
+    output = mf(data, **kwargs)
+    if hasattr(output, 'keys'):
+        result = {name + '_' + k: {'all': v, 'splits': []} for k, v in output.items()}
+    else:
+        result = {name: {'all': output, 'splits': []}}
+    for lsplit, rsplit in splits:
+        ldata = [data[i] for i in lsplit]
+        rdata = [data[i] for i in rsplit]
+        loutput = mf(ldata, **kwargs)
+        routput = mf(rdata, **kwargs)
+        if hasattr(loutput, 'keys'):
+            for k in loutput:
[…]

### 2021-01-31 analysis/model_analysis_v2.Rmd

@@
 ```{r, load-data}
-raw <- read.table(here("models/model_stats.csv"), sep=',')
+
+colMeans(mdat[,1:22])
+# obj_final_position_invstd_objects=drop = -0.2980893  should that be negative?
+
+load_data <- function(fname) {
+  raw <- read.table(here(paste0("models/",fname,".csv")), sep=',')
   cnames <- raw[1,]
@@
     mdat[,c] = as.numeric(mdat[,c])
+    if(min(mdat[,c]) < 0) mdat[,c] = mdat[,c] + min(mdat[,c])
+    print(paste("shifting",c,"so minimum is 0"))
   }
@@
          target = replace(target, target=="triangular_prism", "trig prism"))
+  return(mdat)
+}
 
-colMeans(mdat[,1:22])
-# obj_final_position_invstd_objects=drop = -0.2980893  should that be negative?
+# just 100 drops per trial
+mdat100 <- load_data("model_stats")
+
+mdat <- load_data("model_stats250")
+
+sort(colMeans(mdat[,1:43]))
+# mean of obj_final_position_invstd_objects=drop is negative..
+# mean of avg_len is 235, and len_std is 45 (much larger than typical feature mean on order of .1 - 1.0)
+# scale these cols? (only matters for their combination)
+mdat$avg_len = mdat$avg_len / max(mdat$avg_len)
+mdat$len_std = mdat$len_std / max(mdat$len_std)
 
@@
 mdat_eng <- mdat %>%
-  mutate(obj_final_position_std = 
-           `obj_final_position_std_objects=drop` + 
-           `obj_final_position_std_objects=target`,
+  rowwise() %>%
+  mutate(obj_final_position_std = mean(`obj_final_position_std_objects=drop`,
+                                       `obj_final_position_std_objects=target`),
          normed_velocity_std_after_first_collision_objects = 
-           `normed_velocity_std_after_first_collision_objects=drop` + 
-           `normed_velocity_std_after_first_collision_objects=target`,
-         avg_final_radius_objects = 
-           `avg_final_radius_objects=drop` + 
-           `avg_final_radius_objects=target`,
-         avg_max_radius_objects = 
-           `avg_max_radius_objects=drop` + 
-           `avg_max_radius_objects=target`,
-         max_radius_std_objects = 
-           `max_radius_std_objects=drop` + 
-           `max_radius_std_objects=target`,
-         support_combo = 
-           support_probability + 
-           support_std + 
-           `support_response_sharpness_C=1e-05`, # add one of support_response_linearity_r or _pv ?
-         len_combo = avg_len + len_std + len_inverse_sharpe_ratio
+           mean(`normed_velocity_std_after_first_collision_objects=drop`,
+                `normed_velocity_std_after_first_collision_objects=target`),
+         avg_final_radius_objects = mean(`avg_final_radius_objects=drop`, 
+                                         `avg_final_radius_objects=target`),
+         avg_max_radius_objects = mean(`avg_max_radius_objects=drop`,
+                                       `avg_max_radius_objects=target`),
+         max_radius_std_objects = mean(`max_radius_std_objects=drop`,
+                                       `max_radius_std_objects=target`),
+         support_combo = mean(support_probability, support_std, 
+                              `support_response_sharpness_C=1`, # add support_response_linearity_r or _pv ?
+                              `support_response_sharpness_accuracy_C=1`),
+         support_sharpness_mean = mean(`support_response_sharpness_C=1e-05`,
+                                       `support_response_sharpness_C=0.0001`,
+                                       `support_response_sharpness_C=0.001`,
+                                       `support_response_sharpness_C=0.01`,
+                                       `support_response_sharpness_C=0.1`,
+                                       `support_response_sharpness_C=1`,
+                                       `support_response_sharpness_C=10.0`,
+                                       `support_response_sharpness_C=100.0`,
+                                       `support_response_sharpness_C=1000.0`,
+                                       `support_response_sharpness_C=10000.0`,
+                                       `support_response_sharpness_C=100000.0`),
+         support_sharpness_accuracy_mean = mean(
+            `support_response_sharpness_accuracy_C=1e-05`,
+             `support_response_sharpness_accuracy_C=0.0001`,
+             `support_response_sharpness_accuracy_C=0.001`,
+             `support_response_sharpness_accuracy_C=0.01`,
+             `support_response_sharpness_accuracy_C=0.1`,
+             `support_response_sharpness_accuracy_C=1`,
+             `support_response_sharpness_accuracy_C=10.0`,
+             `support_response_sharpness_accuracy_C=100.0`,
+             `support_response_sharpness_accuracy_C=1000.0`,
+             `support_response_sharpness_accuracy_C=10000.0`,
+             `support_response_sharpness_accuracy_C=100000.0`),
+         support_response_linearity_mean = mean(support_response_linearity_pv, 
+                                                support_response_linearity_r),
+         len_combo = mean(avg_len, len_std, len_inverse_sharpe_ratio)
          ) %>%
-  select(-`obj_final_position_std_objects=drop`, 
-         -`obj_final_position_std_objects=target`,
-         -`normed_velocity_std_after_first_collision_objects=drop`,
-         -`normed_velocity_std_after_first_collision_objects=target`,
-         -`avg_final_radius_objects=drop`,
-         -`avg_final_radius_objects=target`,
-         -`avg_max_radius_objects=drop`,
-         -`avg_max_radius_objects=target`,
-         -`max_radius_std_objects=drop`,
-         -`max_radius_std_objects=target`,
-         -support_probability, 
-         -support_std,
-         -`support_response_sharpness_C=1`,
-         -`support_response_sharpness_C=1e-05`,
-         -`support_response_sharpness_C=100000.0`,
-         -avg_len, -len_inverse_sharpe_ratio, -len_std,
-         -support_response_linearity_pv, -support_response_linearity_r,
-         -`obj_final_position_invstd_objects=target`,
-         -`obj_final_position_invstd_objects=drop`
-         )
+  select(obj_final_position_std, 
+         normed_velocity_std_after_first_collision_objects, 
+         avg_final_radius_objects,
+         avg_max_radius_objects,
+         max_radius_std_objects,
+         support_combo, 
+         support_sharpness_mean,
+         support_sharpness_accuracy_mean,
+         len_combo,
+         drop, target, relation)
 
@@
 }
+# softmax(c(.7,.3), beta=2)
 
@@
 
+child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
+
 adult_fits = list()
+child_fits = list()
 for(feat in feat_names) {
@@
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
-}
-```
-
-# Compare to children's choices
-
-```{r}
-child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
-  summarize(chose_target=mean(chose_target, na.rm=T), n=n())
-
-child_fits = list()
-for(feat in feat_names) {
-  feat_df <- get_feature_df(mdat, feat)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=child_trial_agg)
@@
 ```{r adult-eng-feats}
-feat_names2 = names(mdat_eng)[5:ncol(mdat_eng)]
+feat_names2 = names(mdat_eng)[1:(ncol(mdat_eng)-3)]
 
@@
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
+  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
+  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=child_trial_agg)

### 2021-01-31 models/model.py
minor bugfixes

@@ -347,13 +347,13 @@ def get_splits(n, k, seed=0):
     splits = []
     for i in range(k):
         p = rng.permutation(n)
-        lsplit = p[: n / 2]
-        rsplit = p[n / 2: ]
+        lsplit = p[: n // 2]
+        rsplit = p[n // 2: ]
         splits.append((lsplit, rsplit))
     return splits
 
 
-def get_result(mf, data, kwargs, splits):
+def get_result(mf, data, kwargs, name, splits):
     output = mf(data, **kwargs)
     if hasattr(output, 'keys'):
         result = {name + '_' + k: {'all': v, 'splits': []} for k, v in output.items()}
@@ -377,7 +377,7 @@ def get_stats(dirn, num_splits=100):
     paths = [os.path.join(dirn, l) for l in L]
     data = [h5py.File(path, mode='r') for path in paths]
     outcomes = {}
-    splits = get_splits(len(data), num_splits=num_splits)
+    splits = get_splits(len(data), num_splits)
     for m in model_funcs:
         if hasattr(m, '__len__'):
             mf, kwargs = m
@@ -390,25 +390,25 @@ def get_stats(dirn, num_splits=100):
             kwargs = {}
             name = mf.__name__
         print('... getting %s' % name)
-        result = get_result(mf, data, kwargs, splits)
+        result = get_result(mf, data, kwargs, name, splits)
         outcomes.update(result)
     for d in data:
         d.close()
     return outcomes
 
 
-def get_and_save_stats(sd, st, tp, base_dir, out_dir):
+def get_and_save_stats(sd, st, tp, base_dir, out_dir, num_splits=100):
     drop_obj, target_obj = get_object_names(sd, st)
     sname = scenario_pathname(drop_obj, target_obj, tp)
     path = os.path.join(base_dir, sname)
     print('Getting stats for %s' % sname)
-    outcomes = get_stats(path)
+    outcomes = get_stats(path, num_splits=num_splits)
     outpath = os.path.join(out_dir, sname)
     with open(outpath, 'wb') as _f:
         pickle.dump(outcomes, _f)
 
 
-def get_all_stats(base_dir, out_dir):
+def get_all_stats(base_dir, out_dir, num_splits=100):
     if not os.path.exists(out_dir):
         os.makedirs(out_dir)
     scenarios = get_drop_target_pairs(SCENARIOS)
@@ -417,7 +417,7 @@ def get_all_stats(base_dir, out_dir):
     for i in range(len(scenarios)):
[…]

### 2021-01-31 models/model.py
potential better handling of stats caching

@@ -22,17 +22,18 @@ from experimental import (SCENARIOS,
 #####TIME#####
 ##############
 
-def avg_len(data):
-    """mean length of time before objects come to rest
-    """
-    time_list = [len(d['frames'].keys()) for d in data]
+def get_time_list(data):
+    return [len(d['frames'].keys()) for d in data]
+
+
+def avg_len(time_list):
+    """mean length of time before objects come to rest"""
     return np.mean(time_list)
 
 
-def len_std(data):
+def len_std(time_list):
     """std in length of time before objects come to rest
     """
-    time_list = [len(d['frames'].keys()) for d in data]
     return np.std(time_list)
 
 
@@ -40,14 +41,12 @@ def sharpe_ratio(x):
     return np.mean(x) / np.std(x)
 
 
-def len_inverse_sharpe_ratio(data):
+def len_inverse_sharpe_ratio(time_list):
     """
     length std normalized by mean length
     see https://en.wikipedia.org/wiki/Sharpe_ratio
     """
-    time_list = [len(d['frames'].keys()) for d in data]
     return 1./sharpe_ratio(time_list)
-
 
 
 ###################
@@ -139,25 +138,29 @@ def get_object_inds(objects):
     return object_inds
 
 
-def obj_final_position_std(data, objects=None):
-    """
-    model expressing total std in final positions 
-    of objects (can be subselected for specific object)
-    """
+def get_posvecs(data, objects=None):
     object_inds = get_object_inds(objects)
     posvecs = get_last_frame_positions(data)
     if object_inds is not None:
         posvecs = posvecs[:, object_inds]
-    total_std = np.sqrt(posvecs.var(axis=0).sum(axis=0).sum(axis=0))
-    return total_std
+    return posvecs
 
 
-def obj_final_position_invstd(data, objects=None):
+def obj_final_position_std(posvecs):
+    """
+    model expressing total std in final positions 
+    of objects (can be subselected for specific object)
+    """
+    posvecs = np.array(posvecs)
+    return np.sqrt(posvecs.var(axis=0).sum(axis=0).sum(axis=0))
+
+
+def obj_final_position_invstd(posvecs):
     """
     model expressing 1 - total std in final positions 
     of objects (can be subselected for specific object)
     """
-    return 1 - obj_final_position_std(data, objects=objects)
+    return 1 - obj_final_position_std(posvecs, objects=objects)
 
 
 def get_radii(data, objects=None):
[…]

### 2021-01-31 models/model.py
various updates including variability of stats

@@ -160,7 +160,7 @@ def obj_final_position_invstd(posvecs):
     model expressing 1 - total std in final positions 
     of objects (can be subselected for specific object)
     """
-    return 1 - obj_final_position_std(posvecs, objects=objects)
+    return 1 - obj_final_position_std(posvecs)
 
 
 def get_radii(data, objects=None):
@@ -216,20 +216,28 @@ def get_collision_frames(d):
     return collision_frames
 
 
+def onelist(*k):
+    return np.ones(k).tolist()
+
+
 def normed_velocity_after_first_collision(data, objects=None, window=5):
     fcfs = list(map(get_first_collision_frame, data))
     object_inds = get_object_inds(objects)
     vels = get_velocities(data, object_inds=object_inds)
     #V is of shape (num_trials, window, num_objects, 3)
-    V = np.array([v[fcf:fcf + window] for v, fcf in zip(vels, fcfs) if fcf is not None])
+    V = np.array([v[fcf:fcf + window] if fcf is not None else onelist(window, len(object_inds), 3) for v, fcf in zip(vels, fcfs)])
     return V
 
 
 def normed_velocity_std_after_first_collision(V):
-    Vm = V.mean(axis=1)
-    Vn = np.linalg.norm(Vm, axis=2)
-    W = Vm / Vn[:, :, np.newaxis]
-    return np.sqrt(W.var(axis=0).sum())
+    V = np.array(V)
+    #V is of shape (num_trials, window, num_objects, 3)
+    Vm = V.mean(axis=1) #mean over window, so Vm is of shape (num_trials, num_objects, 3)
+    Vn = np.linalg.norm(Vm, axis=2) #norm over vector components
+    W = Vm / Vn[:, :, np.newaxis] 
+    Wvar = W.var(axis=0).sum() #total variance over trials, summed over objects
+    Wstd = np.sqrt(Wvar) #get std
+    return Wstd
 
 
 def get_collision_types(d, collision_key='collisions'):
@@ -258,7 +266,6 @@ def get_support(d):
     relationships, but ignores situations when one object is leaning the other but is 
     also supported by the floor.  
     """
-    print('... getting supports')
     c_ids = get_collision_ids(d)
     c_ids_env = get_collision_ids(d, collision_key='env_collisions')
     support = ((len(c_ids[-2]) == 2) and (len(c_ids_env[-2]) <= 1))
@@ -266,6 +273,7 @@ def get_support(d):
 
 
[…]

### 2021-01-31 analysis/model_analysis_v2.Rmd

@@
 require(here)
+
+FIT_MODELS = F
 ```
@@
 
-```{r, load-data}
-
-colMeans(mdat[,1:22])
-# obj_final_position_invstd_objects=drop = -0.2980893  should that be negative?
+```{r, load-data, echo=F}
 
@@
 
+mdat <- mdat %>% left_join(mdat_eng)
+
 # selects given feature and returns wide df that can be compared with behavioral data
@@
 
-```{r}
+```{r, echo=F}
 load(file=here("paper/processed_data.RData"))
@@
   for(i in 1:nrow(hum_df)) {
-    mod_cols = which(!is.na(feat_df[i,1:ncol(feat_df)]))[3:4]
+    mod_cols = which(!is.na(feat_df[i,1:ncol(feat_df)]))[3:4] # CHECK THIS
     mod_choice = softmax(feat_df[i,mod_cols], beta=beta)
@@
 
-evalFit <- function(feat_df, hum_df, beta) {
+evalFit <- function(feat_df, hum_df, beta, cor_objective=F, relation=NA) {
   hum_df <- get_model_target_choice_props(feat_df, hum_df, beta)
-  #r = with(hum_df, cor(chose_target, Model_targ_prop))
+  if(!is.na(relation)) {
+    hum_df <- subset(hum_df, relation==relation)
+  }
+  r = with(hum_df, cor(chose_target, Model_targ_prop))
   mse = with(hum_df, sum((chose_target - Model_targ_prop)^2)) / nrow(hum_df) 
+  if(cor_objective) mse = mse - r # also try to minimize -correlation
   return(mse) # return negative cor since DEoptim minimizes
@@
 
-feat_names = names(mdat)[1:(ncol(mdat)-4)]
+feat_names = setdiff(names(mdat), c("drop","target","relation","trial"))
 # for each feature, want to fit beta to maximize correlation between human and model choices
@@
   summarize(chose_target=mean(chose_target, na.rm=T), n=n())
+```
 
-adult_fits = list()
-child_fits = list()
+## Fit models to all trials (MSE objective)
+
+Find best-fitting betas per feature for children and adults, contain and support trials together.
+
+```{r fit-models-to-all-trials-mse, echo=F, eval=FIT_MODELS}
+#adult_fits = list()
+#child_fits = list()
+all_trials_mse <- tibble()
+
 for(feat in feat_names) {
@@
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+  adult_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=adult_trial_agg)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+  child_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                 feat_df=feat_df, hum_df=child_trial_agg)
+  all_trials_mse <- bind_rows(all_trials_mse, c(Age = "adults", feature=feat, beta=as.numeric(unlist(adult_fit$optim$bestmem)), 
+                          mse = adult_fit$optim$bestval))
+  all_trials_mse <- bind_rows(all_trials_mse, c(Age = "children", feature=feat, 
+                          beta = as.numeric(unlist(child_fit$optim$bestmem)), 
+                          mse = child_fit$optim$bestval))
 }
+
+all_trials_mse_r <- all_trials_mse_r %>% mutate(beta = as.numeric(beta),
+                                                mse = as.numeric(mse))
+
+save(all_trials_mse, file=here("models/all_trials_mse.RData"))
 ```
 
-## Now try engineered features
+## Fit models to all trials (MSE + r objective)
 
-```{r adult-eng-feats}
-feat_names2 = names(mdat_eng)[1:(ncol(mdat_eng)-3)]
+```{r fit-models-to-all-trials-mse-and-r, echo=F, eval=FIT_MODELS}
+all_trials_mse_r <- tibble()
 
-for(feat in feat_names2) {
-  feat_df <- get_feature_df(mdat_eng, feat)
+for(feat in feat_names) {
+  feat_df <- get_feature_df(mdat, feat)
   #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
-  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
-                feat_df=feat_df, hum_df=adult_trial_agg)
-  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
-                feat_df=feat_df, hum_df=child_trial_agg)
+  adult_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=adult_trial_agg, cor_objective=T)
+  child_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=child_trial_agg, cor_objective=T)
+  all_trials_mse_r <- bind_rows(all_trials_mse_r, c(Age = "adults", feature=feat, beta=as.numeric(unlist(adult_fit$optim$bestmem)), 
+                          mse = adult_fit$optim$bestval))
+  all_trials_mse_r <- bind_rows(all_trials_mse_r, c(Age = "children", feature=feat, 
+                          beta = as.numeric(unlist(child_fit$optim$bestmem)), 
+                          mse = child_fit$optim$bestval))
 }
+
+all_trials_mse_r <- all_trials_mse_r %>% mutate(beta = as.numeric(beta),
+                                                mse = as.numeric(mse))
 
@@
 
-```{r}
-adult_mfit <- tibble()
-child_mfit <- tibble()
+## Fit separately to contain and support trials (MSE)
 
-for(f in names(adult_fits)) {
-  adult_mfit = bind_rows(adult_mfit, c(feature=f, 
-                                       beta=as.numeric(unlist(adult_fits[[f]]$optim$bestmem)), 
-                                       mse=adult_fits[[f]]$optim$bestval))
-  child_mfit = bind_rows(child_mfit, c(feature=f, 
-                                       beta=as.numeric(unlist(child_fits[[f]]$optim$bestmem)), 
-                                       mse=child_fits[[f]]$optim$bestval))
+```{r fit-models-to-supp-cont-trials-mse, echo=F, eval=FIT_MODELS}
+supp_trials_mse <- tibble()
+cont_trials_mse <- tibble()
+
+for(feat in feat_names) {
+  feat_df <- get_feature_df(mdat, feat)
+  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
+  adult_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=adult_trial_agg, relation="support")
+  child_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=child_trial_agg, relation="support")
+  supp_trials_mse <- bind_rows(supp_trials_mse, c(Age = "adults", feature=feat, beta=as.numeric(unlist(adult_fit$optim$bestmem)), 
+                          mse = adult_fit$optim$bestval))
+  supp_trials_mse <- bind_rows(supp_trials_mse, c(Age = "children", feature=feat, 
+                          beta = as.numeric(unlist(child_fit$optim$bestmem)), 
+                          mse = child_fit$optim$bestval))
 }
 
-adult_mfit <- adult_mfit %>% 
-  mutate(beta = as.numeric(beta),
-         mse = as.numeric(mse)) %>%
-  arrange(mse)
+supp_trials_mse <- supp_trials_mse %>% mutate(beta = as.numeric(beta),
+                                                mse = as.numeric(mse))
 
+for(feat in feat_names) {
+  feat_df <- get_feature_df(mdat, feat)
+  adult_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=adult_trial_agg, relation="contain")
+  child_fit = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
+                feat_df=feat_df, hum_df=child_trial_agg, relation="contain")
+  cont_trials_mse <- bind_rows(cont_trials_mse, c(Age = "adults", feature=feat, beta=as.numeric(unlist(adult_fit$optim$bestmem)), 
+                          mse = adult_fit$optim$bestval))
+  cont_trials_mse <- bind_rows(cont_trials_mse, c(Age = "children", feature=feat, 
+                          beta = as.numeric(unlist(child_fit$optim$bestmem)), 
+                          mse = child_fit$optim$bestval))
+}
+
+cont_trials_mse <- cont_trials_mse %>% mutate(beta = as.numeric(beta),
+                                                mse = as.numeric(mse))
+
+save(mdat, all_trials_mse, all_trials_mse_r, 
+     supp_trials_mse, cont_trials_mse, file=here("models/model_data.RData"))
 ```
 
-```{r children}
-child_mfit <- child_mfit %>% 
-  mutate(beta = as.numeric(beta),
-         mse = as.numeric(mse)) %>%
-  arrange(mse)
+## Fit separately to contain and support trials (MSE + r)
 
-fit_tab <- child_mfit %>% rename(child_mse = mse, child_beta = beta) %>%
-  left_join(adult_mfit %>% rename(adult_mse = mse, adult_beta = beta)) %>% 
-  arrange(adult_mse)
+NOT DONE
+
+```{r}
+load(here("models/model_data.RData"))
+```
+
+## Fits to all trials
+
+```{r, echo=F}
+fit_tab <- all_trials_mse %>% pivot_wider( names_from = Age, values_from = c(beta, mse)) %>%
+  arrange(mse_adults)
 
@@
 
-```{r}
-fits <- child_mfit %>% mutate(AgeGroup = "children") %>% 
-  bind_rows(adult_mfit %>% mutate(AgeGroup = "adults"))
+## Fits to all trials (MSE + r)
 
-save(mdat, mdat_eng, fits, file=here("models/model_data.RData"))
+```{r, echo=F}
+all_trials_mse_r <- all_trials_mse_r %>% mutate(beta = as.numeric(beta),
+                                                mse = as.numeric(mse))
+
+fit_tab <- all_trials_mse_r %>% pivot_wider( names_from = Age, values_from = c(beta, mse)) %>%
+  arrange(mse_adults)
+
+knitr::kable(fit_tab, digits = 3)
+```
+
+## Fits to support trials (MSE)
+
+```{r, echo=F}
+fit_tab <- supp_trials_mse %>% pivot_wider( names_from = Age, values_from = c(beta, mse)) %>%
+  arrange(mse_adults)
+
+knitr::kable(fit_tab, digits = 3)
+```
+
+## Fits to support trials (MSE)
+
+```{r, echo=F}
+fit_tab <- cont_trials_mse %>% pivot_wider(names_from = Age, values_from = c(beta, mse)) %>%
+  arrange(mse_adults)
+
+knitr::kable(fit_tab, digits = 3)
 ```
@@
 ```{r}
-ad <- plot_model_preds("support_response_sharpness_C=1e-05", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_response_sharpness_C=1e-05", fits, child_trial_agg, age="children", mdat)
+ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children", mdat)
 
@@
 ```{r}
-ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children", mdat)
+ad <- plot_model_preds("support_response_sharpness_C=0.0001", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=0.0001", fits, child_trial_agg, age="children", mdat)
 
@@
 ```
+
+```{r}
+ad <- plot_model_preds("support_response_linearity_r", fits, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_linearity_r", fits, child_trial_agg, age="children", mdat)
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```
+
+```{r}
+ad <- plot_model_preds("support_sharpness_mean", fits, adult_trial_agg, age="adults", mdat_eng)
+ch <- plot_model_preds("support_sharpness_mean", fits, child_trial_agg, age="children", mdat_eng)
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```

### 2021-01-31 paper/paper2021.Rmd

@@
 The overall split-half reliability on the containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and for support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
-[should we separately report these for adults and children?]
-
-<!-- Finally, we analyze how exploratory children were in their responses: across the 12 trials, what proportion of the 9 available objects did each child utilize as drop objects?
-What proportion of the objects were targeted?
--->
-
-Figure 4 shows participants' mean proportion of unique objects dropped as a function of age.
-Children of all ages sampled approximately equal proportions of the objects for dropping--roughly 70%, which is close to the 75% that would be expected if they were selected by chance (9 unique object occurring across 12 trials).
-
-```{r unique-drop-objects, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion of unique objects selected by participants.
-Error bars show boostrapped 95\\% confidence intervals.", eval=F}
-# 12 trials, 9 objects; random selection would be 9/12 = 75%...
-uniq_s <- hum %>% group_by(SID, Age_Group) %>%
-  summarise(DropObjs = n_distinct(DropChoice), N=n(), prop=DropObjs/N)
-
-uniq <- uniq_s %>% group_by(Age_Group) %>%
-  tidyboot_mean(prop)
-
-ggplot(uniq, aes(x=Age_Group, y=mean)) + geom_point() +
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  xlab("Age (years)") + ylab("Unique Objects Chosen") + ylim(0,1) + 
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  geom_hline(yintercept=.75, lty='dashed')
-```
+<!-- [should we separately report these for adults and children?] -->
 
@@
 <!--len_inverse_sharpe_ratio, support_response_sharpness_C=1 -->
-
-We measure each of these features across each possible drop in the experiment 100 times, and then use the resulting metrics to generate relative preferences for each of the drop choices on each trial.
+[ToDo: describe *skillsiness*]
+We measure each of these features in 250 simulations of each possible drop in the experiment, and then use the resulting metrics to generate relative preferences for each of the drop choices on each trial.
 Finally, we compare how well each of these simple heuristic models account for children's and adults' drop preferences on each trial.
 
+```{r}
+# plot the best feature for children, adults, 
+```
+
 # Discussion 
-This study aimed to investigate what physical interactions between objects most evoke curiosity.
+This study aimed 1) to measure the consistency of children's and adults' preferences for particular object interactions, and 2) to determine whether people's interest was predicted by particular features of the imagined physical interactions between objects.
 After finding surprising consistency in an in-person pilot study of adults, an online study designed to make possible the same support and containment relations between dropped and target objects replicated this finding of consistency: adults are interested in dropping objects into containers, and to a lesser degree on top of supporting objects.

### 2021-01-31 models/model.py
comments

@@ -340,6 +340,15 @@ def support(supports_and_radii):
 ########################
 #####INFRASTRUCTURE#####
 ########################
+"""all data processing statistics are described with two functions
+    (f, g)
+where:
+   -- g takes a list of hdf5s and produces a per-trial statistic
+
+and
+
+   -- f takes the outcomes of the per-trial statistics and returns a final summary scalar
+"""
 
 model_funcs = [{'func': (avg_len, get_time_list)}, 
                {'func': (len_std, get_time_list)},
@@ -375,6 +384,8 @@ model_funcs = [{'func': (avg_len, get_time_list)},
 
 
 def get_splits(n, k, seed=0):
+    """constructs splits for computing split-half reliability
+    """
     rng = np.random.RandomState(seed=seed)
     splits = []
     for i in range(k):
@@ -386,6 +397,18 @@ def get_splits(n, k, seed=0):
 
 
 def get_result(mf, df, data, kwargs, name, splits):
+    """
+    computes statistics for all trials as well as a set of split-halfs of trials
+    return is a dictionary:
+         {statistics_name: {'all': value_for_all_trials,
+                            'splits': [(a_0, b_0), (a_1, b_1) ...]
+                           }
+         }
+
+         where a_i / b_i = statistic for left / right split i
+
+    """
+
     data_out = df(data, **kwargs)
     output = mf(data_out)
     if hasattr(output, 'keys'):

### 2021-01-31 models/run.py

@@ -21,7 +21,22 @@ def get_args():
     parser.add_argument("--feature_path",
                         type=str,
                         default=None,
-                        help="file where stats are collected into a csv") 
+                        help="file where stats are collected into a csv")
+
+    parser.add_argument("--feature_std_path",
+                        type=str,
+                        default=None,
+                        help="file where stats stds are collected into a csv") 
+
+    parser.add_argument("--corr_path",
+                        type=str,
+                        default=None,
+                        help="file where split-half reliabilities are saved") 
+
+    parser.add_argument("--fig_path",
+                        type=str,
+                        default=None,
+                        help="file where statistics correlation figure is saved") 
 
     parser.add_argument("--num_trials",
                         type=int,
@@ -36,8 +51,15 @@ if __name__ == "__main__":
     stimulus_dir = args.stimulus_dir
     stats_dir = args.stats_dir
     feature_path = args.feature_path
+    feature_std_path = args.feature_std_path
+    corr_path = args.corr_path
+    fig_path = args.fig_path
     num_trials = args.num_trials
     generate_stimuli.main(stimulus_dir, num_trials)
     model.get_all_stats(stimulus_dir, stats_dir)
-    model.collect_stats(stimulus_dir, feature_path)
+    model.collect_stats(stimulus_dir,
+                        feature_path,
+                        feat_std_path,
+                        corr_path,
+                        fig_path)
     

### 2021-01-31 analysis/model_analysis_v2.Rmd
cleaning up model evaluation report

@@
 
-## Load data
+## Preprocessing
 
-```{r, load-data, echo=F}
+```{r, load-data, echo=F, FIT_MODELS=F}
 
@@
 mdat <- mdat %>% left_join(mdat_eng)
+```
 
+# Load human data
+
+Define helper functions
+
+```{r, echo=F}
 # selects given feature and returns wide df that can be compared with behavioral data
@@
 
-```
-
-# Fit to adult choice proportions
-
-```{r, echo=F}
 load(file=here("paper/processed_data.RData"))
@@
   if(!is.na(relation)) {
-    hum_df <- subset(hum_df, relation==relation)
+    hum_df <- hum_df[which(hum_df$relation==relation),]
   }
@@
 }
-
-require(DEoptim)
 
@@
 ```{r fit-models-to-all-trials-mse, echo=F, eval=FIT_MODELS}
-#adult_fits = list()
-#child_fits = list()
+require(DEoptim)
+
 all_trials_mse <- tibble()
@@
 
-## Fit separately to contain and support trials (MSE + r)
-
-NOT DONE
+Could also fit separately to contain and support trials with MSE - r objective...
 
@@
 
-## Fits to all trials (MSE + r)
+## Fits to all trials (MSE - r)
 
@@
 ```{r, echo=F}
-fit_tab <- supp_trials_mse %>% pivot_wider( names_from = Age, values_from = c(beta, mse)) %>%
+fit_tab <- supp_trials_mse %>% pivot_wider(names_from = Age, values_from = c(beta, mse)) %>%
   arrange(mse_adults)
@@
 
-## Fits to support trials (MSE)
+## Fits to containment trials (MSE)
 
@@
 
-```{r, eval=F}
-fits %>% ggplot(aes(x=beta, y=mse, color=AgeGroup)) +
-  #geom_text(aes(label=feature)) + 
-  geom_point(alpha=.5) +
-  theme_minimal()
-```
-So generally, children's choices are best explained by small values of beta (.5, the minimum tested).
+What do the predicted choice proportions from the best features for each age group look like?
+Let's look at the best feature for each each group from each fit method.
 
-What do the predicted choice proportions from the best feature for each age group look like?
-
-```{r}
+```{r, echo=F, message=F}
 require(ggpubr)
@@
 plot_model_preds <- function(feat_name, fits, hum_data, age="adults", mdat) {
-  beta = 1 #subset(fits, AgeGroup==age & feature==feat_name)$beta
+  this_dat = subset(fits, Age==age & feature==feat_name)
   md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
@@
     geom_abline(slope=1, intercept=0, linetype="dashed") +
-    geom_point(alpha=.5) + geom_smooth(method='lm') + 
+    geom_point(alpha=.5) + geom_smooth(method='lm', formula=y ~ x) + 
     xlab("Human Choice Probability") + 
@@
     ggtitle(paste0(feat_name,": ",age)) + theme_minimal() + 
-    xlim(0,1) + ylim(0,1)
+    xlim(0,1) + ylim(0,1) +
+    annotate("text", x=.5, y=0.05, 
+             label = paste0("beta = ",round(this_dat$beta,2),", MSE = ",round(this_dat$mse, 3))) # 
 }
+```
 
-ad_supp <- plot_model_preds("support_probability", fits, adult_trial_agg, age="adults", mdat)
-ch_supp <- plot_model_preds("support_probability", fits, child_trial_agg, age="children", mdat)
+## Plots of other best-fitting features for all trials (MSE fits)
+
+```{r, echo=F, message=F}
+ad_supp <- plot_model_preds("support_probability", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch_supp <- plot_model_preds("support_probability", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("support_combo", fits, adult_trial_agg, age="adults", mdat_eng)
-ch <- plot_model_preds("support_combo", fits, child_trial_agg, age="children", mdat_eng)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("support_combo", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_combo", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("support_std", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_std", fits, child_trial_agg, age="children", mdat)
+```{r, echo=F, message=F}
+ad <- plot_model_preds("support_std", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_std", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("support_response_sharpness_C=0.0001", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_response_sharpness_C=0.0001", fits, child_trial_agg, age="children", mdat)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("len_inverse_sharpe_ratio", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("len_inverse_sharpe_ratio", fits, child_trial_agg, age="children", mdat)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("len_inverse_sharpe_ratio", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("len_inverse_sharpe_ratio", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("avg_final_radius_objects=target", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("avg_final_radius_objects=target", fits, child_trial_agg, age="children", mdat)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("avg_final_radius_objects=target", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("avg_final_radius_objects=target", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("support_response_linearity_r", fits, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_response_linearity_r", fits, child_trial_agg, age="children", mdat)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("support_response_linearity_r", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_linearity_r", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
-```{r}
-ad <- plot_model_preds("support_sharpness_mean", fits, adult_trial_agg, age="adults", mdat_eng)
-ch <- plot_model_preds("support_sharpness_mean", fits, child_trial_agg, age="children", mdat_eng)
+```{r,  echo=F, message=F}
+ad <- plot_model_preds("support_sharpness_mean", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_sharpness_mean", all_trials_mse, child_trial_agg, age="children", mdat)
 

### 2021-02-01 analysis/model_analysis_v2.Rmd
final model explorations

@@
 require(here)
+require(kableExtra)
 
@@
 
-```{r, load-data, echo=F, FIT_MODELS=F}
+```{r, load-data, echo=F, eval=FIT_MODELS}
 
@@
     if(min(mdat[,c]) < 0) mdat[,c] = mdat[,c] + min(mdat[,c])
-    print(paste("shifting",c,"so minimum is 0"))
+    #print(paste("shifting",c,"so minimum is 0"))
   }
@@
 
-Define helper functions
+And define helper functions
 
@@
 
-feat_names = setdiff(names(mdat), c("drop","target","relation","trial"))
-# for each feature, want to fit beta to maximize correlation between human and model choices
-#feat_df <- get_feature_df(mdat, feat_names[1])
-
 child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
@@
 
-## Fit models to all trials (MSE + r objective)
+## Fit models to all trials (MSE - r objective)
 
@@
 
-```{r}
+```{r load-model-data, echo=F}
 load(here("models/model_data.RData"))
+
+feat_names = setdiff(names(mdat), c("drop","target","relation","trial"))
+# for each feature, want to fit beta to maximize correlation between human and model choices
+#feat_df <- get_feature_df(mdat, feat_names[1])
 ```
+
+## Feature correlations
+
+Some of these features are perfectly correlated and even have identical values: e.g. support_probability and support_combo.
+All of the support_response_sharpness features with C<=.01 (C=.1 and above behave differently).
+All of the support_response_sharpness_accuracy features with C<=.01 (C=.1 and above behave differently).
+We remove some of these from the below tables.
+
+```{r, echo=F, include=F}
+get_feature_cor <- function(feat1, feat2, mdat) {
+  supp_prob <- get_feature_df(mdat, feat1) %>%
+    pivot_longer(3:12, names_to="target", values_drop_na=T)
+  supp_combo <- get_feature_df(mdat, feat2) %>%
+    pivot_longer(3:12, names_to="target", values_drop_na=T)
+  return(list(r=cor(supp_combo$value, supp_prob$value), SSE=sum((supp_combo$value - supp_prob$value)^2)))
+}
+
+get_feature_cor("support_probability", "support_combo", mdat)
+# same (1)
+
+# support_response_sharpness_C=0.01 or C=.001 almost as good for children
+get_feature_cor("support_probability", "support_response_sharpness_C=0.01", mdat)
+# .91
+
+get_feature_cor("support_response_sharpness_C=0.001", "support_response_sharpness_C=0.01", mdat) # 1 
+get_feature_cor("support_response_sharpness_C=0.001", "support_response_sharpness_C=0.0001", mdat) # 1
+get_feature_cor("support_response_sharpness_C=0.001", "support_response_sharpness_C=1e-05", mdat) # 1
+
+get_feature_cor("support_response_sharpness_C=0.1", "support_response_sharpness_C=0.01", mdat) # .95
+get_feature_cor("support_response_sharpness_C=0.1", "support_response_sharpness_C=1", mdat) # .94
+
+get_feature_cor("support_response_sharpness_accuracy_C=0.001", "support_response_sharpness_accuracy_C=0.01", mdat) # 1
+get_feature_cor("support_response_sharpness_accuracy_C=0.0001", "support_response_sharpness_accuracy_C=0.01", mdat)
+
+# remove some of the identical features
+all_trials_mse <- all_trials_mse %>% filter(feature!="support_combo",
+                                            feature!="support_sharpness_mean",
+                                            feature!="support_response_sharpness_C=0.0001", # keep .01
+                                            feature!="support_response_sharpness_C=0.001",
+                                            feature!="support_response_sharpness_C=1e-05",
+                                            feature!="support_response_sharpness_accuracy_C=0.0001",
+                                            feature!="support_response_sharpness_accuracy_C=0.001",
+                                            feature!="support_response_sharpness_accuracy_C=1e-05")
+all_trials_mse_r <- all_trials_mse_r %>% filter(feature!="support_combo",
+                                            feature!="support_sharpness_mean",
+                                            feature!="support_response_sharpness_C=0.0001", # keep .01
+                                            feature!="support_response_sharpness_C=0.001",
+                                            feature!="support_response_sharpness_C=1e-05",
+                                            feature!="support_response_sharpness_accuracy_C=0.0001",
+                                            feature!="support_response_sharpness_accuracy_C=0.001",
+                                            feature!="support_response_sharpness_accuracy_C=1e-05")
+supp_trials_mse <- supp_trials_mse %>% filter(feature!="support_combo",
+                                            feature!="support_sharpness_mean",
+                                            feature!="support_response_sharpness_C=0.0001", # keep .01
+                                            feature!="support_response_sharpness_C=0.001",
+                                            feature!="support_response_sharpness_C=1e-05",
+                                            feature!="support_response_sharpness_accuracy_C=0.0001",
+                                            feature!="support_response_sharpness_accuracy_C=0.001",
+                                            feature!="support_response_sharpness_accuracy_C=1e-05")
+cont_trials_mse <- cont_trials_mse %>% filter(feature!="support_combo",
+                                            feature!="support_sharpness_mean",
+                                            feature!="support_response_sharpness_C=0.0001", # keep .01
+                                            feature!="support_response_sharpness_C=0.001",
+                                            feature!="support_response_sharpness_C=1e-05",
+                                            feature!="support_response_sharpness_accuracy_C=0.0001",
+                                            feature!="support_response_sharpness_accuracy_C=0.001",
+                                            feature!="support_response_sharpness_accuracy_C=1e-05")
+```
+
+We have `r length(feat_names)` features from 250 simulated drops per combination to optimize softmax betas for.
+The tables below show fits and betas for the best-fitting 10 features (sorted by adult fit).
 
@@
 
-knitr::kable(fit_tab, digits = 3)
+knitr::kable(fit_tab[1:10,], digits = 3)
 ```
@@
 
-```{r, echo=F, message=F}
+```{r plot-model-vs-human, echo=F, message=F}
 require(ggpubr)
@@
   this_dat = subset(fits, Age==age & feature==feat_name)
-  md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, beta)
+  md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, this_dat$beta)
   md %>% ggplot(aes(x=chose_target, y=Model_targ_prop, color=relation)) +
@@
     ylab("Model Choice Probability") +
-    ggtitle(paste0(feat_name,": ",age)) + theme_minimal() + 
+    ggtitle(paste0(age,": ",feat_name)) + theme_minimal() + 
     xlim(0,1) + ylim(0,1) +
@@
 
-## Plots of other best-fitting features for all trials (MSE fits)
+## Best feature from fitting all trials (MSE)
 
-```{r, echo=F, message=F}
-ad_supp <- plot_model_preds("support_probability", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch_supp <- plot_model_preds("support_probability", all_trials_mse, child_trial_agg, age="children", mdat)
+When fit with MSE, the best-fitting feature for both children and adults is support probability, shown below with betas optimized separately for adults' and children's data.
+Note that although the MSE is quite low, the correlation between model and human responding for each trial is negative.
 
-ggarrange(ad_supp, ch_supp, nrow=1, common.legend = T)
-```
+```{r}
+ch_feat <- all_trials_mse %>% filter(Age=="children") %>%
+  arrange(mse)
 
-```{r,  echo=F, message=F}
-ad <- plot_model_preds("support_combo", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_combo", all_trials_mse, child_trial_agg, age="children", mdat)
+ad_feat <- all_trials_mse %>% filter(Age=="adults") %>%
+  arrange(mse)
+
+supp_std_prob_cor <- get_feature_cor("support_std", "support_probability", mdat) # .72
+
+supp_resp_sharp_prob_cor <- get_feature_cor("support_response_sharpness_C=0.01", "support_probability", mdat)
+
+ad <- plot_model_preds("support_probability", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_probability", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 
+The next-best feature for adults was support_std, which has r=`r round(supp_std_prob_cor$r, 2)` with the support_probability feature.
+The next-best feature for children was support_response_sharpness_C=0.01 (or C=.001, .0001, or 1e-05), which has r=`r round(supp_resp_sharp_prob_cor$r, 2)` with the support_probability feature.
+These second-best features are shown below.
+
 ```{r, echo=F, message=F}
 ad <- plot_model_preds("support_std", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_std", all_trials_mse, child_trial_agg, age="children", mdat)
-
-ggarrange(ad, ch, nrow=1, common.legend = T)
-```
-
-```{r,  echo=F, message=F}
-ad <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, adult_trial_agg, age="adults", mdat)
 ch <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, child_trial_agg, age="children", mdat)
@@
 
-```{r,  echo=F, message=F}
-ad <- plot_model_preds("len_inverse_sharpe_ratio", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("len_inverse_sharpe_ratio", all_trials_mse, child_trial_agg, age="children", mdat)
+# Best feature from fitting all trials (MSE - r)
+
+When fit with a combined MSE and r objective, the best-fitting feature for both children and adults is support_response_sharpness_C=0.01, shown below with betas optimized separately for adults' and children's data.
+
+```{r}
+ch_feat <- all_trials_mse_r %>% filter(Age=="children") %>%
+  arrange(mse) # support_response_sharpness_C=0.01, then support_response_sharpness_C=0.1
+
+ad_feat <- all_trials_mse_r %>% filter(Age=="adults") %>%
+  arrange(mse) # support_response_sharpness_C=0.01, then normed_velocity_std_after_first_collision_objects=target
+
+supp_res_sharp_pt01_pt1 <- get_feature_cor("support_response_sharpness_C=0.01", "support_response_sharpness_C=0.1", mdat) # .95
+
+supp_resp_sharp_norm_vel_targ <- get_feature_cor("support_response_sharpness_C=0.01", "normed_velocity_std_after_first_collision_objects=target", mdat)
+
+ad <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse_r, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse_r, child_trial_agg, age="children", mdat)
 
@@
 ```
+
+The next-best feature for adults was normed_velocity_std_after_first_collision_objects=target, which has r=`r round(supp_resp_sharp_norm_vel_targ$r, 2)` with the support_response_sharpness_C=0.01 feature.
+The next-best feature for children was support_response_sharpness_C=0.1, which has r=`r round(supp_res_sharp_pt01_pt1$r, 2)` with the support_response_sharpness_C=0.01 feature.
+These second-best features are shown below.
+
+```{r, echo=F, message=F}
+ad <- plot_model_preds("normed_velocity_std_after_first_collision_objects=target", all_trials_mse_r, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=0.1", all_trials_mse_r, child_trial_agg, age="children", mdat)
+
+ggarrange(ad, ch, nrow=1, common.legend = T)
+```
+
+## Best features from fitting containment trials (MSE)
+
+The best-fitting feature from fitting only containment trials was support_probability, for both children and adults:
+
+```{r}
+ch_feat <- cont_trials_mse %>% filter(Age=="children") %>%
+  arrange(mse) %>% slice(1) # support_probability then support_response_sharpness_C=10.0
+
+ad_feat <- cont_trials_mse %>% filter(Age=="adults") %>%
+  arrange(mse) %>% slice(1) # support_probability then support_std (beta=10 !)
+
+knitr::kable(bind_rows(ch_feat, ad_feat), digits=3)
+```
+
+## Best features from fitting support trials (MSE)
+
+The best-fitting feature for support trials for children was normed_velocity_std_after_first_collision_objects, and for adults was support_response_linearity_r (although support_probability was not far behind for adults):
+
+```{r}
+ch_feat <- supp_trials_mse %>% filter(Age=="children") %>%
+  arrange(mse) %>% slice(1) #
+
+ad_feat <- supp_trials_mse %>% filter(Age=="adults") %>%
+  arrange(mse) %>% slice(1) # support_probability then support_std (beta=10 !)
+
+bind_rows(ch_feat, ad_feat) %>% kable(digits=3)
+```
+
+### Other promising features: avg_final_radius_objects=target
+
+avg_final_radius_objects=target shows positive correlations with children's and adults' preferences, but for many of the trials (both contain and support) the model chooses the target with small probability.
 
@@
 
+### Other promising features: support_response_sharpness_C=0.01
+
+support_response_sharpness_C=0.01 has a fairly good MSE in particular for children, and also shows a positive correlation with children's preferences on containment trials.
+
 ```{r,  echo=F, message=F}
-ad <- plot_model_preds("support_response_linearity_r", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_response_linearity_r", all_trials_mse, child_trial_agg, age="children", mdat)
+ad <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, adult_trial_agg, age="adults", mdat)
+ch <- plot_model_preds("support_response_sharpness_C=0.01", all_trials_mse, child_trial_agg, age="children", mdat)
 
@@
 ```
-
-```{r,  echo=F, message=F}
-ad <- plot_model_preds("support_sharpness_mean", all_trials_mse, adult_trial_agg, age="adults", mdat)
-ch <- plot_model_preds("support_sharpness_mean", all_trials_mse, child_trial_agg, age="children", mdat)
-
-ggarrange(ad, ch, nrow=1, common.legend = T)
-```

### 2021-02-01 analysis/model_analysis_v2.Rmd
added model plot

@@
     mdat[,c] = as.numeric(mdat[,c])
-    if(min(mdat[,c]) < 0) mdat[,c] = mdat[,c] + min(mdat[,c])
-    #print(paste("shifting",c,"so minimum is 0"))
+    if(min(mdat[,c]) < 0) {
+      mdat[,c] = mdat[,c] + min(mdat[,c])
+      print(paste("shifting",c,"so minimum is 0"))
+    }
   }
@@
 # just 100 drops per trial
-mdat100 <- load_data("model_stats")
+#mdat100 <- load_data("model_stats")
 
 mdat <- load_data("model_stats250")
+
+# model split-half correlations and stds
+mdat_cor <- read_csv(here("models/model_stats250_corr.csv")) 
+# avg_len NA, but all others ~.997 - .999
+#View(mdat_cor)
+
+mdat_std <- load_data("model_stats250_std")
+mdat_std$drop = mdat$drop
+mdat_std$target = mdat$target
+mdat_std$relation = mdat$relation
+mdat_std$trial = mdat$trial
 
@@
   for(i in 1:nrow(hum_df)) {
-    mod_cols = which(!is.na(feat_df[i,1:ncol(feat_df)]))[3:4] # CHECK THIS
+    mod_cols = which(!is.na(feat_df[i,1:ncol(feat_df)]))[3:4] 
     mod_choice = softmax(feat_df[i,mod_cols], beta=beta)
@@
 ```
-
-Could also fit separately to contain and support trials with MSE - r objective...
 
@@
 ```{r}
+get_model_error_bars <- function(feat_name, mdat_std) {
+  # have std per drop, so we avg per trial (?) 
+  # (could get SEM for N=250 drops ?)
+  mdat_std <- mdat_std %>% arrange(relation, drop)
+  sd_trial <- rowMeans(matrix(mdat_std[,feat_name], nrow=20, byrow=T))
+  return(sd_trial)
+}
+
 ch_feat <- all_trials_mse %>% filter(Age=="children") %>%
@@
   arrange(mse)
+
+ad_df = get_model_target_choice_props(get_feature_df(mdat, "support_probability"), adult_trial_agg, ad_feat[2,]$beta)
+ad_df$model_sd = get_model_error_bars("support_probability", mdat_std)
+
+ch_df = get_model_target_choice_props(get_feature_df(mdat, "support_probability"), child_trial_agg, ch_feat[1,]$beta)
+ch_df$model_sd = get_model_error_bars("support_probability", mdat_std)
+
+save(ad_df, ch_df, file=here("models/support_probability_fit_df.RData"))
 
@@
 ch <- plot_model_preds("support_probability", all_trials_mse, child_trial_agg, age="children", mdat)
+# ToDo: add error bars to each trial for model (from mdat_std) and from humans...
 
 ggarrange(ad, ch, nrow=1, common.legend = T)
+```
+
+### How much of the total explainable variance (e.g. relative to measurement noise) is explained by the best model for the adult data?
+
+```{r}
+md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, this_dat$beta)
+
 ```

### 2021-02-01 paper/paper2021.Rmd
added model plot

@@
     xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
-    geom_abline(xintercept=0, slope=1, linetype="dashed") +
+    geom_abline(intercept=0, slope=1, linetype="dashed") +
     geom_smooth(method = "lm") +
@@
 ```{r load-model-data}
-load(here("models/model_data.RData")) # mdat, mdat_eng, fits
+load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
+load(here("models/support_probability_fit_df.RData")) # ad_df, ch_df - model (w SD) vs. human (need 95%CIs)
+
+mdat <- ad_df %>% mutate(AgeGroup="adult") %>% 
+  bind_rows(ch_df %>% mutate(AgeGroup="child") %>% select(-n)) %>% 
+  mutate(mod_ci_lower = Model_targ_prop - 1.96*model_sd,
+         mod_ci_upper = Model_targ_prop + 1.96*model_sd) # 95% should fall within +/-1.96 SDs of mean
+# now just need 95% CIs for human data
 ```
@@
 
-```{r}
-# plot the best feature for children, adults, 
+```{r human-vs-model-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=5.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of model's vs.
+participants' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
+pos = position_dodge(width = .9)
+
+hum_ag <- combo_dat %>% group_by(drop, target, relation, ID) %>%
+  group_by(drop, target, relation, AgeGroup) %>%
+  tidyboot_mean(chose_target, na.rm=T) %>%
+  select(-n, -empirical_stat)
+
+hum_mod <- hum_ag %>% left_join(mdat)
+
+hum_mod %>%
+  ggplot(aes(x=mean, y=Model_targ_prop, group=relation, color=relation)) + 
+    geom_point(alpha=.6) + 
+    geom_errorbar(aes(ymin=mod_ci_lower, ymax=mod_ci_upper), alpha=.6) +
+    geom_errorbarh(aes(xmin=ci_lower, xmax=ci_upper), alpha=.6) + 
+    facet_wrap(~ AgeGroup, nrow=2) +
+    theme_bw() + ylim(0,1) + xlim(0,1) + 
+    xlab("Human Choice Proportions") + ylab("Model Choice Proportions") + 
+    geom_abline(intercept=0, slope=1, linetype="dashed") +
+    geom_smooth(method = "lm") +
+    theme(legend.position = "top")
+
 ```
@@
 <!-- moved from old Intro: rewrite to discuss Haber et al. more -->
-Thexe results will serve as a test set for evaluating computational theories of curiosity, which in turn are inspired by classic descriptive theories positing that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
+These results will serve as a test set for evaluating computational theories of curiosity, which in turn are inspired by classic descriptive theories positing that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
 Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than simple or highly-complex stimuli [@Kidd2012; @Kidd2014].

### 2021-02-01 paper/paper2021.Rmd
wrote up model results

@@
 
+best_fits <- subset(all_trials_mse, feature=="support_probability")
+
 mdat <- ad_df %>% mutate(AgeGroup="adult") %>% 
@@
 ```
-Using a physics engine and 3D models of the objects that were shown to participants, we constructed a simulation of each trial of the experiment and attempted to predict children's and adults' choices using a variety of heuristic models of the simulated physical interactions.
+
+Using a physics engine [@gan2020threedworld] and 3D models of the objects that were shown to participants, we constructed a simulation of for each drop interaction in the experiment and attempted to predict children's and adults' choices using a variety of heuristic models based on the simulated physical interactions.
 For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
-We selected features that we thought may provide good metrics for what people would found interesting. 
-For example, we collected for each drop the mean length of time before both objects come to rest (*avg_len*), as well as the standard deviation (SD) of that time (*len_std*).
-Some features were calculated separately for drop and target objects, such as: the SD of the object's final position (*obj_final_position_std_objects*) as well as the inverse of that (*obj_final_position_invstd_objects*), the mean final distance from the drop location (*avg_final_radius_objects*), the maximum final distance from the drop location (*avg_max_radius_objects*), the ...
-(*max_radius_std_objects*), ...
-(*normed_velocity_std_after_first_collision_objects*)
+We selected features that we thought may provide good metrics for what people could find interesting. 
+For example, we collected for each drop the mean length of time before both objects come to rest, as well as the standard deviation (SD) of that time.
+Some features were calculated separately for drop and target objects, such as the SD of each object's final position, the mean and maximum final distance of each object from the drop location, and the normed velocity of each object after first collision.
+We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position.
+Note that the model's definition of support does not distinguish support from containment.
 <!-- support_probability, support_std, support_response_linearity_r, support_response_linearity_pv  -->
 <!--len_inverse_sharpe_ratio, support_response_sharpness_C=1 -->
-[ToDo: describe *skillsiness*]
-We measure each of these features in 250 simulations of each possible drop in the experiment, and then use the resulting metrics to generate relative preferences for each of the drop choices on each trial.
-Finally, we compare how well each of these simple heuristic models account for children's and adults' drop preferences on each trial.
 
-```{r human-vs-model-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=5.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of model's vs.
-participants' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
+We measure each of these features in 250 simulations of each possible drop in the experiment, and then use the resulting values to generate relative preferences for each of the drop choices on each trial.
+A model's preference on any given trial was assumed to be proportional to the relative magnitude of the feature values for the possible physical interactions on that trial, scaled by a softmax parameter $\beta$.
+For each model (feature), we optimized $\beta$ separately to find best-fitting values for children's and adults' drop preferences, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
+
+### Results 
+The best-fitting feature was $Pr(support)$ for both children ($\beta =$ `r round(best_fits$beta[2],2)`, MSE = `r round(best_fits$mse[2], 2)`) and adults ($\beta =$ `r round(best_fits$beta[1],2)`, MSE = `r round(best_fits$mse[1], 2)`).
+<!-- other support-related features also fared well -->
+Figure 6 shows this model's fitted preferences plotted against those of children and adults.
+Although the model captures people's overall mean preference for the target relations, the trial-level correlation with human behavior is not very high (overall $r=$ `r round(cor(mdat$chose_target, mdat$Model_targ_prop),2)`).
+
+```{r human-vs-model-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=4.75, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of $Pr(support)$ model's vs.
+participants' choices for each type of trial, with 95\\% CIs."}
 pos = position_dodge(width = .9)
@@
 
-hum_mod %>%
+hum_mod %>% mutate(AgeGroup = ifelse(AgeGroup=="adult", "adults", "children")) %>%
   ggplot(aes(x=mean, y=Model_targ_prop, group=relation, color=relation)) + 
@@
     geom_smooth(method = "lm") +
-    theme(legend.position = "top")
+    theme(legend.position = "none")
 
@@
 This study aimed 1) to measure the consistency of children's and adults' preferences for particular object interactions, and 2) to determine whether people's interest was predicted by particular features of the imagined physical interactions between objects.
-After finding surprising consistency in an in-person pilot study of adults, an online study designed to make possible the same support and containment relations between dropped and target objects replicated this finding of consistency: adults are interested in dropping objects into containers, and to a lesser degree on top of supporting objects.
+In an online study that gave adults the opportunity to make drop choices that could result in either a likely support or likely containment relation on each trial, we found that adults consistently chose targets likely to contain the dropped object, and to a lesser degree chose target objects that were likely to support the dropped object.
 Experiment 2 found the same pattern in children, but with greater noise -- even to the extent that younger children were at-chance at choosing the support relation on most trials.

### 2021-02-01 paper/paper2021.Rmd
editing

@@
 First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
-We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., measuring likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
+We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
 <!-- Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
@@
 Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
-We developed a novel physical exploration task in which children, adults, or AI agents choose which series of physical experiments to perform and observe the results of each in real time.
 
-<!-- High-level statement of our approach -->
-In sum, this paper presents a paradigm and model for testing theories of curiosity about physical interactions. 
-<!-- and defining its role in guiding the development of knowledge about the physical world.  -->
+We developed a novel physical exploration task in which children, adults, or AI agents can choose which series of physical experiments to perform, <!-- and observe the results of each in real time.-->
+and then demonstrate how this paradigm can be used to test theories of curiosity about physical interactions. 
 First, we measured adults' and children's (3-7 years of age) preferences in a novel physical exploration task; participants were asked to choose one of two objects (e.g., a sphere, a dumbbell, see Figure 1) to drop onto a target object (e.g., a pyramid) with the goal of the creating the most interesting physical interaction (see Figure 2).
@@
 <!-- A study of 9- to 16-month-olds found that infants' violation of expectations about a novel toy's hidden properties (e.g., making a sound) drives them to explore similar toys for longer [@Baldwin1993].
--->
-
-<!-- OLD INTRO: delete all?
-
-The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity. 
-First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
-We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., measuring likelihood of a dropped object coming to rest on a target object), and test whether these features predict people's preferences in the same task.
-Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
-
-Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITE Spelke, @Baillargeon2007), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory.
-However, the measures used in this literature have typically focused on either children's ability to discriminate types of events, or their ability to carry out particular tasks (e.g., shape sorting), but have not examined which types of interactions children are most interested in testing.
-For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015; @Baillargeon2007).
-Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
-Moreover, these studies have yet to directly constrain theories that predict which functions children will discover, and in what sequence. 
-What both of the standard looking-time and toy-exploration measures fail to capture when characterizing children's curiosity are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009; @gureckis2012self].
-To address these limitations, we developed a novel physical exploration task in which children, adults, or AI agents choose which series of physical experiments to perform and observe the results of each in real time.
-
-In sum, this paper presents a paradigm for testing and building theories of curiosity, and defining its role in guiding the development of knowledge about the physical world. 
-We present a study that measures adults' (Experiment 1) and children's (Experiment 2) preferences in a novel physical exploration task, a set of 20 heuristic models of curiosity that operate on simulations of this same task in a 3D environment, and comparisons between the preferences of children, adults, and these heuristic models on the same set of trials.
-Overall, our approach of coordinating the development of task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of how curiosity guides cognitive development.
 -->
@@
 ### Participants
-Participants were 200 adults recruited online via Amazon Mechanical Turk who were paid $1 for their participation.
+Participants were 200 adults recruited online via Amazon Mechanical Turk who were paid $1 for participating.
 

### 2021-02-01 paper/paper2021.Rmd
minor edits

@@
 We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
-Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1 [maybe just drop Table 1?].
+Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1. 
 Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance.
@@
 As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
-Overall, children did not show a significant preference for choosing the support relation [should we add a regression with trial_type * age (3 - 18=adult)?].
+Overall, children did not show a significant preference for choosing the support relation. <!-- [should we add a regression with trial_type * age (3 - 18=adult)?] -->
 Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
 
-```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Children's vs.
 adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}

### 2021-02-01 analysis/model_analysis_v2.Rmd
editing

@@
 
-save(all_trials_mse, file=here("models/all_trials_mse.RData"))
 ```
@@
                                                 mse = as.numeric(mse))
-
 ```
@@
 
-save(ad_df, ch_df, file=here("models/support_probability_fit_df.RData"))
+supp_prob_beta1 <- 
+  bind_rows(get_model_target_choice_props(get_feature_df(mdat, "support_probability"), adult_trial_agg, beta=1) %>% mutate(AgeGroup="adults"),
+            get_model_target_choice_props(get_feature_df(mdat, "support_probability"), child_trial_agg, beta=1) %>% mutate(AgeGroup="children") %>% select(-n))
+
+supp_resp_sharp_beta1 <- 
+  bind_rows(get_model_target_choice_props(get_feature_df(mdat, "support_response_sharpness_C=0.01"), adult_trial_agg, beta=1) %>% mutate(AgeGroup="adults"),
+            get_model_target_choice_props(get_feature_df(mdat, "support_response_sharpness_C=0.01"), child_trial_agg, beta=1) %>% mutate(AgeGroup="children") %>% select(-n))
+
+supp_resp_sharp_beta_opt <- 
+  bind_rows(get_model_target_choice_props(get_feature_df(mdat, "support_response_sharpness_C=0.01"), adult_trial_agg, beta=1.94) %>% mutate(AgeGroup="adults"),
+            get_model_target_choice_props(get_feature_df(mdat, "support_response_sharpness_C=0.01"), child_trial_agg, beta=0.810) %>% mutate(AgeGroup="children") %>% select(-n))
+
+save(ad_df, ch_df, supp_prob_beta1, supp_resp_sharp_beta1, supp_resp_sharp_beta_opt,
+     file=here("models/support_probability_fit_df.RData"))
 
@@
 ```{r}
-md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, this_dat$beta)
+#md <- get_model_target_choice_props(get_feature_df(mdat, feat_name), hum_data, this_dat$beta)
 

### 2021-02-01 paper/paper2021.Rmd
editing

@@
      simulated environment, and then compare the behavior of these agents to humans exploring the 
-     same stimuli. Here we propose a new experimental paradigm for examining children's--and curious
-     AI agents'--curiosity about objects' physical interactions, using a task that is both open-ended
-     enough to allow room for curiosity, but also constrained enough to make detailed behavioral 
-     comparisons. We compared children's choices (N=66; 3-7 years of age) to those of adults (N=155), 
-     and find increasingly strong preference for choices affording particular relations (e.g., 
-     containment) across development, as well as an adult bias for choosing a support relation.
+     same stimuli. Here we propose a new experimental paradigm for examining children's--and 
+     AI agents'--curiosity about objects' physical interactions by letting them choose which object to 
+     target when dropping a given object. We compared adults' (N=155) and children's choices (N=66; 
+     3-7 year-olds) and found that adults show a strong preference for choices affording a containment
+     relation, a preference that is also shown by children. Adults alone also make choices consistent 
+     with achieving support relations. We contextualize our results using heuristic models based on 
+     physics simulations of the same scenarios judged by participants.
 
@@
 In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self].
-However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of physical interactions or exploratory behavior.
+However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of exploration or of physics learning.
 Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
@@
 ### Participants
-Participants were 200 adults recruited online via Amazon Mechanical Turk who were paid $1 for participating.
+200 adults were recruited via Amazon Mechanical Turk and were paid $1 for participating.
 
@@
 An example support relation is choosing to drop the pentagonal prism on the (equal diameter) pipe rather than the pyramid.
-Half of the 20 trials were designed to afford containment relations, and the other half afforded support relations.
-We refer to these designed containment and support relations as the "targets", and the alternative objects as the "distractors".
+10 of the 20 trials were designed to afford containment relations, and the other 10 afforded support relations.
+We refer to the objects affording the designed containment and support relations as *targets*, and the alternative objects as *distractors*.
 Distractors for each trial were the same for all participants, and were selected to 1) not afford containment/support of the dropped object, and 2) roughly equate the frequency of appearance of all 10 objects.
@@
 This was done to ensure that they understood the consequences of the choice they made.
-After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on, but without videos.
+After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on.
 Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (3-alternative forced choice).
-The goal of the catch trials was to encourage participants to attend to the objects and the choices they made, and to exclude any participants who were incorrect on 2 or more of the catch trials.
-Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
-These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants.
+The catch trials were meant to encourage attention to the objects, and participants who were incorrect on two or more of the catch trials were excluded.
+<!-- Finally, there were two free response explanation trials mixed among the drop trials, querying participants, "Why did you make that choice?"
+These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants. -->
 
@@
 ## Results
-
 We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
@@
 Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
-Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance [adjust criterion for multiple comparisons?].
-As can be seen in Table 1, adults participants ("adult" column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
+Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance.
+<!-- [adjust criterion for multiple comparisons?] -->
+As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
 
@@
 ### Participants
-Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook Ads.
+Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads.
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
@@
 ### Materials
-The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a Keynote. 
-Introductory slides were added for informed consenting process and screen configuration, where researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
+The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3. 
+<!-- Introductory slides were added for informed consenting process and screen configuration, where the researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
+-->
 
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.75, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.55, fig.height=2.35, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
 Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
@@
 A video recording was taken of the online session.
-
-To accompany the practice trial, children were shown the three physical objects on video, to ensure understanding of their 3D properties. 
-Verbal responses were collected from children to indicate the selection of target object Y or Z. 
-To prevent left/right mapping confusion, target objects Y and Z were overlaid on thirds of the screen with either red or green background color, which were counterbalanced across trials. 
-The child was asked to verbally select target object and then to indicate whether it was on the "red side or the green side."
+To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
+Children were asked to verbally select target object Y or Z, and then asked to confirm whether they wanted to select the object on the red or green side of the screen, in order to prevent left/right confusion.
+The sides on which target objects and colors appeared were counterbalanced across trials.
 
@@
 
-```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.5, fig.height=3.75, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.3, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
 adults' preferences on each trial (dot), with bootstrapped 95\\% confidence intervals."}
@@
 load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
-load(here("models/support_probability_fit_df.RData")) # ad_df, ch_df - model (w SD) vs. human (need 95%CIs)
+load(here("models/support_probability_fit_df.RData")) 
+# ad_df, ch_df - model (w SD) vs. human (need 95%CIs)
 
@@
 # now just need 95% CIs for human data
+
+# Mike suggests also reporting Pr(support) MSE / r for beta=1
+supp_prob_beta1_cors <- supp_prob_beta1 %>% group_by(AgeGroup) %>%
+  summarise(r = cor(chose_target, Model_targ_prop), # # adult: -.35 child: -.48
+            mse = mean((chose_target - Model_targ_prop)^2)) # .035 .026
+
+supp_prob_beta_opt_cors <- mdat %>% group_by(AgeGroup) %>%
+  summarise(r = cor(chose_target, Model_targ_prop), # # adult: -.35 child: -.49
+            mse = mean((chose_target - Model_targ_prop)^2)) #
+
+supp_resp_sharp_beta_opt_cors <- supp_resp_sharp_beta_opt %>% group_by(AgeGroup) %>%
+  summarise(r = cor(chose_target, Model_targ_prop), # adults: .45, children: .40
+            mse = mean((chose_target - Model_targ_prop)^2)) # .054 .016
+
+supp_resp_sharp_beta1_cors <- supp_resp_sharp_beta1 %>% group_by(AgeGroup) %>%
+  summarise(r = cor(chose_target, Model_targ_prop), # adults: .45 children: .40
+            mse = mean((chose_target - Model_targ_prop)^2)) # .059 .016
 ```
@@
 For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
-We selected features that we thought may provide good metrics for what people could find interesting. 
-For example, we collected for each drop the mean length of time before both objects come to rest, as well as the standard deviation (SD) of that time.
+We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean length of time before both objects come to rest, as well as the standard deviation (SD) of that time.
 Some features were calculated separately for drop and target objects, such as the SD of each object's final position, the mean and maximum final distance of each object from the drop location, and the normed velocity of each object after first collision.
@@
 
-We measure each of these features in 250 simulations of each possible drop in the experiment, and then use the resulting values to generate relative preferences for each of the drop choices on each trial.
+We measured each of these features in 250 simulations of each possible drop in the experiment, and then used the resulting values to generate relative preferences for the drop choices on each trial. 
 A model's preference on any given trial was assumed to be proportional to the relative magnitude of the feature values for the possible physical interactions on that trial, scaled by a softmax parameter $\beta$.
@@
 ### Results 
-The best-fitting feature was $Pr(support)$ for both children ($\beta =$ `r round(best_fits$beta[2],2)`, MSE = `r round(best_fits$mse[2], 2)`) and adults ($\beta =$ `r round(best_fits$beta[1],2)`, MSE = `r round(best_fits$mse[1], 2)`).
+The best-fitting feature was $Pr(support)$ for both children ($\beta =$ `r round(best_fits$beta[2],2)`, MSE = `r round(best_fits$mse[2], 3)`) and adults ($\beta =$ `r round(best_fits$beta[1],2)`, MSE = `r round(best_fits$mse[1], 3)`).\footnote{For $\beta=1$, adult MSE = `r round(supp_prob_beta1_cors$mse[1],3)`, child MSE = `r round(supp_prob_beta1_cors$mse[2],3)` for $Pr(support)$.}
 <!-- other support-related features also fared well -->
 Figure 6 shows this model's fitted preferences plotted against those of children and adults.
-Although the model captures people's overall mean preference for the target relations, the trial-level correlation with human behavior is not very high (overall $r=$ `r round(cor(mdat$chose_target, mdat$Model_targ_prop),2)`).
+Although the model captured people's overall mean preference for the target relations, the trial-level correlation with human behavior was negative (adults $r=$ `r round(supp_prob_beta_opt_cors$r[1],2)`, children $r=$ `r round(supp_prob_beta_opt_cors$r[2],2)`, with similar values for $\beta = 1$).
+The support response sharpness model fit slightly worse (children $\beta = 0.81$, MSE = 0.016) and adults ($\beta = 1.94$, MSE = 0.054), but its responses were positively correlated with people's (adults $r =$ `r round(supp_resp_sharp_beta_opt_cors$r[1], 2)`, children $r =$ `r round(supp_resp_sharp_beta_opt_cors$r[2],2)`).\footnote{For $\beta=1$, adult MSE = `r round(supp_resp_sharp_beta1_cors$mse[1],3)`, child MSE = `r round(supp_resp_sharp_beta1_cors$mse[2],3)` for support response sharpness, with very similar correlations.}
 

### 2021-02-02 paper/paper2021.Rmd
wrote GD, edited to fit 6 pages (almost)

@@
 First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
-We then present a set of heuristic models of curiosity based on a variety of metrics of simulated interactions (e.g., likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
-<!-- Finally, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
+We then present a set of heuristic models of curiosity based on a variety of metrics of simulated physical interactions (e.g., likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
+<!-- Finally, we sketch how future work can test the correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
 -->
@@
 and then demonstrate how this paradigm can be used to test theories of curiosity about physical interactions. 
-First, we measured adults' and children's (3-7 years of age) preferences in a novel physical exploration task; participants were asked to choose one of two objects (e.g., a sphere, a dumbbell, see Figure 1) to drop onto a target object (e.g., a pyramid) with the goal of the creating the most interesting physical interaction (see Figure 2).
-We then explore the predictive power of a variety of heuristic models of curiosity that operate on simulations of this same task with these same objects in a 3D environment. 
-We propose that using task-performing computational models and detailed measurement of human action selection on the same tasks has the promise to lead to more robust and precise theories of our curiosity about the physical world.
-
-<!-- presents learners (children or the agent) with a set of objects from which they can select one to drop in a bin containing a set of target objects, with the potential to create one or more collisions during the drop.
--->
+First, we measured people's choices in a novel physical exploration task, in which participants were told that they would drop a given object (e.g., a sphere, a torus; see Figure 1) onto one of two target objects (e.g., a dumbbell, a pentagonal prism; see Figure 2), with the goal of the creating the most interesting physical interaction.
+We recorded adults' and children's (3-7 years of age) choices for a set of trials in which some of the drop objects could plausibly end up *supported* by one of the target objects, and for a set of trials in which some of the drop objects could end up *contained* by one of the targets -- although the other potential targets likely also offered affordances of interest.
+After examining the consistency of people's preferences, we tested the predictive power of a variety of heuristic models of curiosity that operate on simulations of this task with these same objects in a 3D environment.
+Our results suggest that using detailed measurement of human action selection and computational models based on simulations of the same tasks promises to lead to more robust and precise theories of human curiosity about the physical world, and how it develops.
 
@@
 
-<!-- move this paragraph to GD if we want to discuss goals?
-## Computational Models of Curiosity
-
-Building on prior work that showed deep neural networks are capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], we use and extend a deep RL architecture for constructing intrinsically-motivated artificial agents introduced in @Haber2018learning.
-This agent's behavior is driven by two interacting neural networks: a *world-model* and a *self-model*, which are trained simultaneously. 
-The problem of the world-model is to predict the consequences of the agent's actions, through estimation of either the forward or inverse dynamics. 
-The self-model attempts to learn to predict the errors of the world-model. 
-The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will adversarially challenge the state of its world-model.
--->
-
 # Experiment 1: Adults
@@
 ## Method
-
+\vspace{-4pt}
 ### Participants
@@
 ### Materials
-
+\vspace{-4pt}
 Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
@@
 <!-- GK: possibly re-do this figure to have the proper orientations -->
-```{r fig3-child-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
+```{r fig3-child-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.2, fig.height=2.9, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
 img <- png::readPNG("figs/fig1-objects.png")
@@
 ### Design
-
+\vspace{-4pt}
 The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
@@
 Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.
-That is, the target objects were chosen so that either (but not both) of them would be capable of either supporting or (partially) containing the dropped object.
+That is, the target objects were chosen so that one of them would be capable of either supporting or  containing the dropped object.
 For example, if asked to drop the cone on either the torus or the octahedron, a containment relation could be achieved between the cone and the torus, but not the octahedron (and support is unlikely due to the small surface area of the octahedron).
@@
 ### Procedure
+
+```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.4, fig.height=3.3, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
+img <- png::readPNG("figs/2AFC_DropTaskFig.png")
+grid::grid.raster(img)
+```
 
@@
 These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants. -->
-
-```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
-img <- png::readPNG("figs/2AFC_DropTaskFig.png")
-grid::grid.raster(img)
-```
 
@@
 
-```{r child-table, results="asis"}
-# how to do 2-col table? , fig.env = "figure*" 
-chtab <- xtable::xtable(trial_tab, digits=2, 
-                       caption = "Children's and adults' target preferences per trial.")
-
-print(chtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
-```
-
-<!-- Maybe code the type of goals stated by the parents? -->
-
-# Experiment 2: Children
-
-Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
-Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
-
-## Method
-We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
-
-### Participants
-Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads.
-Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
-<!-- Sama: notes on exclusions?
--->
-
-### Materials
-The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3. 
-<!-- Introductory slides were added for informed consenting process and screen configuration, where the researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
--->
-
-```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.55, fig.height=2.35, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
-Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
-img <- png::readPNG("figs/online-child-practice-trial.png")
-grid::grid.raster(img)
-```
-
-### Procedure
-
-<!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
-After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
-A video recording was taken of the online session.
-To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
-Children were asked to verbally select target object Y or Z, and then asked to confirm whether they wanted to select the object on the red or green side of the screen, in order to prevent left/right confusion.
-The sides on which target objects and colors appeared were counterbalanced across trials.
-
-## Results
-
-We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
-Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1. 
-Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance.
-<!-- stricter crit for mult comparisons?
-Bonf=.0025 -->
-Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
-On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
-
-Were children more consistent in their choices on support or containment trials?
-As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
-Overall, children did not show a significant preference for choosing the support relation. <!-- [should we add a regression with trial_type * age (3 - 18=adult)?] -->
-Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
-
-```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Children's vs.
-adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
-pos = position_dodge(width = .9)
-
-combo_dat %>% 
-  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
-                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
-  group_by(ID, AgeGroup, relation) %>% # alt, 
-  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
-  group_by(relation, AgeGroup) %>%
-  tidyboot_mean(chose_target) %>%
-  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
-  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1) +
-  ylab("Proportion Choosing Target Relation") +
-  labs(fill = "Age Group")
-
-```
-
-## Comparison of Children's vs. Adults' Preferences
-
-Finally, we compare the trial-level preferences of children and adults.
-Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2). 
-If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to $y=0.5$. 
-At a glance, this seems to support the hypothesis that "children are noisy adults."
-We will re-examine this hypothesis with model-based predictions for each trial.
-
-```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.3, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
-adults' preferences on each trial (dot), with bootstrapped 95\\% confidence intervals."}
-# add vert and horiz error bars 
-combo_dat %>% group_by(drop, target, relation, ID) %>%
-  group_by(drop, target, relation, AgeGroup) %>%
-  tidyboot_mean(chose_target, na.rm=T) %>%
-  select(-n, -empirical_stat) %>%
-  pivot_wider(names_from = AgeGroup, values_from = c(mean, ci_lower, ci_upper)) %>%
-  ggplot(aes(x=mean_adult, y=mean_child, group=relation, color=relation)) + 
-    geom_point(alpha=.6) + 
-    geom_errorbar(aes(ymin=ci_lower_child, ymax=ci_upper_child), alpha=.6) +
-    geom_errorbarh(aes(xmin=ci_lower_adult, xmax=ci_upper_adult), alpha=.6) + 
-    theme_bw() + ylim(0,1) + xlim(0,1) + 
-    xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
-    geom_abline(intercept=0, slope=1, linetype="dashed") +
-    geom_smooth(method = "lm") +
-    theme(legend.position = "bottom")
-  #geom_text(aes(label=target)) #
-
-```
-
 ```{r reliability}
@@
 
-We also examined the split-half reliability of children's and adults' choices by repeatedly  splitting the samples in half and testing the correlation between the halves.
-Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`), and for children is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
-The overall split-half reliability on the containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and for support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
+Finally, we examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
+Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
+
+```{r child-table, results="asis"}
+# how to do 2-col table? , fig.env = "figure*" 
+chtab <- xtable::xtable(trial_tab, digits=2, 
+                       caption = "Children's and adults' target preferences per trial.")
+
+print(chtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
+```
+
+<!-- Maybe code the type of goals stated by the parents? -->
+
+# Experiment 2: Children
+\vspace{-4pt}
+Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
+Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
+
+## Method
+\vspace{-4pt}
+We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
+
+### Participants
+\vspace{-4pt}
+Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads.
+Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
+After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+<!-- Sama: notes on exclusions?
+-->
+
+### Materials
+\vspace{-4pt}
+The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3. 
+<!-- Introductory slides were added for informed consenting process and screen configuration, where the researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
+-->
+
+```{r fig1-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=2.55, fig.height=2.35, set.cap.width=T, num.cols.cap=1, fig.cap = "Zoom screen configuration for children in Experiment 2.
+Parents were asked to place the experimenter's video feed in the bottom center so the experimenter could point up to the drop object and left and right at each target choice."}
+img <- png::readPNG("figs/online-child-practice-trial.png")
+grid::grid.raster(img)
+```
+
+### Procedure
+\vspace{-4pt}
+<!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
+After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
+A video recording was taken of the online session.
+To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
+Children were asked to verbally select target object Y or Z, and then asked to confirm whether they wanted to select the object on the red or green side of the screen, in order to prevent left/right confusion.
+The sides on which target objects and colors appeared were counterbalanced across trials.
+
+## Results
+\vspace{-4pt}
+We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
+Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1. 
+Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance.
+<!-- stricter crit for mult comparisons?
+Bonf=.0025 -->
+Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
+On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
+
+Were children more consistent in their choices on support or containment trials?
+As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+Overall, children did not show a significant preference for choosing the support relation. <!-- [should we add a regression with trial_type * age (3 - 18=adult)?] -->
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
+
+```{r adults-vs-children-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=3.25, set.cap.width=T, num.cols.cap=1, fig.cap = "Children's vs.
+adults' choices for each type of trial, with bootstrapped 95\\% confidence intervals."}
+pos = position_dodge(width = .9)
+
+combo_dat %>% 
+  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
+                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
+  group_by(ID, AgeGroup, relation) %>% # alt, 
+  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
+  group_by(relation, AgeGroup) %>%
+  tidyboot_mean(chose_target) %>%
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
+  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1) +
+  ylab("Proportion Choosing Target Relation") +
+  labs(fill = "Age Group")
+
+```
+
+## Comparison of Children's vs. Adults' Preferences
+\vspace{-4pt}
+Finally, we compare the trial-level preferences of children and adults.
+Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2). 
+If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to $y=0.5$. 
+At a glance, this seems to support the hypothesis that "children are noisy adults."
+We will re-examine this hypothesis with model-based predictions for each trial.
+
+```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.3, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
+adults' preferences on each trial (dot), with bootstrapped 95\\% confidence intervals."}
+# add vert and horiz error bars 
+combo_dat %>% group_by(drop, target, relation, ID) %>%
+  group_by(drop, target, relation, AgeGroup) %>%
+  tidyboot_mean(chose_target, na.rm=T) %>%
+  select(-n, -empirical_stat) %>%
+  pivot_wider(names_from = AgeGroup, values_from = c(mean, ci_lower, ci_upper)) %>%
+  ggplot(aes(x=mean_adult, y=mean_child, group=relation, color=relation)) + 
+    geom_point(alpha=.6) + 
+    geom_errorbar(aes(ymin=ci_lower_child, ymax=ci_upper_child), alpha=.6) +
+    geom_errorbarh(aes(xmin=ci_lower_adult, xmax=ci_upper_adult), alpha=.6) + 
+    theme_bw() + ylim(0,1) + xlim(0,1) + 
+    xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
+    geom_abline(intercept=0, slope=1, linetype="dashed") +
+    geom_smooth(method = "lm") +
+    theme(legend.position = "bottom")
+  #geom_text(aes(label=target)) #
+
+```
+
+The split-half reliability for children's choices is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
+The overall split-half reliability of children and adults on containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and on support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
 <!-- [should we separately report these for adults and children?] -->
@@
 Experiment 2 found the same pattern in children, but with greater noise -- even to the extent that younger children were at-chance at choosing the support relation on most trials.
+In sum, our behavioral study found that infant's early-emerging interest in containment [@Casasola2003] may extend through childhood and persist into adulthood, along with a weaker interest in support relations.
 
-Thus, we find an early-emerging interest in containment [@Casasola2003] that persists into adulthood, along with a weaker interest in support relations.
+Given the high split-half reliability of choices on this task, particularly for adults ($r = .95$, children's $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
+We tested a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but the feature that best predicted both children's and adults' responses was the probability that a dropped object would come to rest atop a target object (*Pr(support)*).
+<!-- Adults were best fit by a softmax $\beta = 1.18$, while children were best modeled by $\beta = 0.5$, meaning that as far as this model is concerned children are "noisy" adults.
+-->
+However, on a trial level this model's choices were negatively correlated with people's. 
+One of the next best-fitting models was the sensitivity of *Pr(support)* to perturbations in the initial starting conditions, which broadly was able to capture people's stronger preference in *contain* condition trials relative to *support* condition trials, but still did not capture item-level variation in people's choices within condition.
+On balance, although much of the variation in this dataset is unexplained, it is encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic models based on simulations of the same physical task we asked participants to merely imagine.
+
+We suggest that these results can fruitfully serve as a test set for evaluating more complex computational  theories of curiosity such as the proposal that learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and that curiosity will change as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
+These theories are starting to be implemented in deep neural networks, which have recently been shown to be capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016].
+@Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
+These networks are trained simultaneously to solve different problems: the world-model attempts to predict the consequences of the agent's actions (either the forward or inverse dynamics), while the self-model attempts to learn to predict the errors of the world-model.
+The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will challenge its world-model. 
+In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare these agents' behavior to people's in the same tasks.
+Curiosity has inspired curiosity in researchers for decades, but only recently have the tools come along that make these theories testable.
+
+<!--
+According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
+Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
+Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
+Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
+-->
+<!--
 Is containment inherently more satisfying, or is there greater interest because it is more achievable? (Less susceptible to small amounts of error)
@@
 Or do children find some other goal relatively more enticing?
-
-<!-- moved from old Intro: rewrite to discuss Haber et al. more -->
-These results will serve as a test set for evaluating computational theories of curiosity, which in turn are inspired by classic descriptive theories positing that curiosity-driven behavior was the consequence of attentional capture by novel stimuli [e.g., @Berlyne1954; @Fantz1964], as well as theories providing qualitative explanations for curiosity-driven behavior as the result of learners' preferences for stimuli that are "moderately discrepant" in relation to their current knowledge state, and thereby provide opportunities to learn [@Kinney1976].
-Recent studies have provided empirical support for this basic idea: 7- to 8-month-old infants are sensitive to stimulus complexity and prefer to look at moderately complex stimuli rather than simple or highly-complex stimuli [@Kidd2012; @Kidd2014].
-According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
-Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
-Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
-Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
+-->
 

### 2021-02-03 paper/paper2021.Rmd
incorporated Bria's edits

@@
 
-We developed a novel physical exploration task in which children, adults, or AI agents can choose which series of physical experiments to perform, <!-- and observe the results of each in real time.-->
+We thus developed a novel physical exploration task in which children, adults, or AI agents can choose which series of physical experiments to perform, <!-- and observe the results of each in real time.-->
 and then demonstrate how this paradigm can be used to test theories of curiosity about physical interactions. 
@@
 This consistency in their choices is remarkable given that there are many other possible goals that people might choose in order to make something "interesting" happen: they might attempt to make the dropped object roll or bounce far from the target, or rebound in an unexpected direction, but in fact most people settled on attempting support or containment relations.
-Thus, we set out to examine the development of these preferences, first in a large adult sample, and then in young children.
-<!-- , since some have characterized children as simply being noisy adults.
--->
+Thus, we set out to examine the development of these preferences, first in a large adult sample in order to have high reliability for later model comparisons, and then in young children.
 
@@
 
-## Results
-We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
-<!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
-2) are they more consistent with trials that afford support or containment relations?
-and 3) are there other apparent factors that drive their preferences?
-Our analysis addresses each question in turn. -->
-Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
-Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance.
-<!-- [adjust criterion for multiple comparisons?] -->
-As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance.
-
-```{r adult-agg}
+```{r}
 adult_trial_agg <- adult_long %>% group_by(relation, drop, target) %>% # alt, 
@@
   arrange(relation, desc(chose_target))
-```
 
-```{r adults-table, results="asis", include=F}
-adtab <- xtable::xtable(adult_trial_agg, digits=2, 
-                       caption = "Adult target preferences per trial.")
-
-print(adtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
-```
-
-```{r}
 ad_subj_agg <- adult_long %>% group_by(ResponseId, relation) %>% # alt, 
@@
 
-Were adults more consistent in their choices on support or containment trials?
-Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
-<!--For the five support trials for which adults showed no significant preference, we will return to discuss alternative hypotheses after looking at children's preferences in Experiment 2.-->
-
 ```{r reliability}
@@
 
+## Results
+We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
+<!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
+2) are they more consistent with trials that afford support or containment relations?
+and 3) are there other apparent factors that drive their preferences?
+Our analysis addresses each question in turn.
+-->
+Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
+Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
+Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance. 
+As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance, suggesting that many participants found the prospect of dropping on the distractor object at least equally enticing.
+
 Finally, we examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
 Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
+
+```{r adults-table, results="asis", include=F}
+adtab <- xtable::xtable(adult_trial_agg, digits=2, 
+                       caption = "Adult target preferences per trial.")
+
+print(adtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
+```
 
@@
 Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
-Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest.
+Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest than adults, or may simply show more idiosyncratic choice patterns.
 
@@
 \vspace{-4pt}
-Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads.
+Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
 Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
 After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
-<!-- Sama: notes on exclusions?
--->
 
@@
 \vspace{-4pt}
+Were children more consistent in their choices on support or containment trials?
+As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+Overall, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
 We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
@@
 On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
-
-Were children more consistent in their choices on support or containment trials?
-As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
-Overall, children did not show a significant preference for choosing the support relation. <!-- [should we add a regression with trial_type * age (3 - 18=adult)?] -->
-Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
+The split-half reliability for children's choices is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
 
@@
 
+The overall split-half reliability of children and adults on containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and on support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
+<!-- [should we separately report these for adults and children?] -->
 ```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.3, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
@@
 ```
-
-The split-half reliability for children's choices is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
-The overall split-half reliability of children and adults on containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and on support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
-<!-- [should we separately report these for adults and children?] -->
 
@@
 
+<!--
 # Acknowledgements
-
 This work was funded by HAI seed grant #. 
 We thank X and Y for helpful comments. 
+-->
 

### 2021-02-03 paper/paper2021.Rmd
paper stuff

--- 2021-02-02 paper/paper2021.Rmd
@@
 # old: What if you drop that? Developmental changes in curiosity about physical interactions
-title: "Using physical simulations to predict children's and adults' preference for physical interactions"
+title: "Using physical simulations to predict children's and adults' preferences in physical interactions"
 bibliography: library.bib
@@
      simulated environment, and then compare the behavior of these agents to humans exploring the 
-     same stimuli. Here we propose a new experimental paradigm for examining children's--and 
-     AI agents'--curiosity about objects' physical interactions by letting them choose which object to 
-     target when dropping a given object. We compared adults' (N=155) and children's choices (N=66; 
-     3-7 year-olds) and found that adults show a strong preference for choices affording a containment
+     same stimuli. Here we propose a new experimental paradigm for examining children's -- and 
+     AI agents' -- curiosity about objects' physical interactions.
+     We let them choose which object to 
+     drop another object onto in order to create the most interesting effect. We compared adults' (N=155) and children's choices (N=66; 
+     3-7 year-olds) and found that adults show a strong preference for drops that could potentially result in a containment
      relation, a preference that is also shown by children. Adults alone also make choices consistent 
-     with achieving support relations. We contextualize our results using heuristic models based on 
-     physics simulations of the same scenarios judged by participants.
+     with achieving support relations. We contextualize our results using heuristic computational models based on 
+     3D physical simulations of the same scenarios judged by participants.
 
@@
 From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
-However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
-Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
+Although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
+Moreover, extant theories have rarely provided precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans, in part because curiosity tends to result in complex, open-ended behaviors that are difficult to quantify.
 

### 2021-02-03 paper/paper2021.Rmd
model table with beta=1

--- 2021-02-03 paper/paper2021.Rmd
@@
 require(gridExtra)
+require(kableExtra)
 ```
@@
 
-sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
-
-sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
-
+#sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
+sh_ch_contain = split_half_subj_cor(subset(combo_dat, relation=="contain" & AgeGroup=="child"))
+sh_ad_contain = split_half_subj_cor(subset(combo_dat, relation=="contain" & AgeGroup=="adult"))
+#sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
+sh_ch_support = split_half_subj_cor(subset(combo_dat, relation=="support" & AgeGroup=="child"))
+sh_ad_support = split_half_subj_cor(subset(combo_dat, relation=="support" & AgeGroup=="adult"))
 # split items in half, check cor between halves...GK: I don't think we care about this
@@
 Finally, we examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
-Based on 100 random samples, the split-half reliability for adults is *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
+Based on 100 random samples, the split-half reliability for adults was *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
+The split-half reliability of adults' choices on containment trials was *r* = `r round(mean(sh_ad_contain), 2)` (sd=`r round(sd(sh_ad_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ad_support), 2)` (sd=`r round(sd(sh_ad_support), 2)`).
 
@@
 The split-half reliability for children's choices is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
+The split-half reliability of children's choices on containment trials was *r* = `r round(mean(sh_ch_contain), 2)` (sd=`r round(sd(sh_ch_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ch_support), 2)` (sd=`r round(sd(sh_ch_support), 2)`).
 
@@
 
-The overall split-half reliability of children and adults on containment trials is *r* = `r round(mean(sh_subj_contain), 2)` (sd=`r round(sd(sh_subj_contain), 2)`), and on support trials is *r* = `r round(mean(sh_subj_support), 2)` (sd=`r round(sd(sh_subj_support), 2)`).
-<!-- [should we separately report these for adults and children?] -->
 ```{r adults-vs-children, fig.env = "figure", fig.pos = "h", fig.align="center", fig.width=3.3, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of children's vs.
@@
 ### Results
-The best-fitting feature was $Pr(support)$ for both children ($\beta =$ `r round(best_fits$beta[2],2)`, MSE = `r round(best_fits$mse[2], 3)`) and adults ($\beta =$ `r round(best_fits$beta[1],2)`, MSE = `r round(best_fits$mse[1], 3)`).\footnote{For $\beta=1$, adult MSE = `r round(supp_prob_beta1_cors$mse[1],3)`, child MSE = `r round(supp_prob_beta1_cors$mse[2],3)` for $Pr(support)$.}
-<!-- other support-related features also fared well -->
+
+```{r human-vs-model-table, results="asis"}
+# now we just have a table of selected features that were moderately correlated with people's choices
+load(here("models/model_preds_beta1.RData"))
+
+described_features = c("support_response_sharpness_C=1",
+                       "normed_velocity_std_after_first_collision_objects=target",
+                       "normed_velocity_std_after_first_collision_objects=drop",
+                       "avg_max_radius_objects=target",
+                       "avg_max_radius_objects=drop",
+                       "obj_final_position_invstd_objects=target",
+                       "obj_final_position_invstd_objects=drop",
+                       "avg_final_radius_objects=target",
+                       "avg_final_radius_objects=drop",
+                       "avg_len",
+                       "len_std",
+                       "support_probability")
+
+supp_trials <- supp_trials %>% rename(`Support` = r) %>%
+  select(-mse)
+
+cont_trials <- cont_trials %>% rename(`Contain` = r) %>%
+  select(-mse)
+
+# combine all_trials, supp_trials, and cont_trials
+mod_tab <- all_trials %>% select(-mse) %>%
+  rename(`All` = r) %>% 
+  left_join(supp_trials) %>%
+  left_join(cont_trials) %>%
+  filter(is.element(feature, described_features)) %>%
+  arrange(desc(`All`), feature)  %>%
+  mutate(Age = ifelse(Age=="children", "Child:", "Adult:")) %>%
+  pivot_wider(names_from=Age, values_from=c(`All`, `Support`, `Contain`), 
+              names_glue = "{Age} {.value}") %>%
+  arrange(desc(`Adult: All`)) %>%
+  mutate(feature = case_when(feature == 'support_response_sharpness_C=1' ~ 'Supp. Sharpness',
+                             feature == 'support_probability' ~ 'Pr(support)',
+                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Target Velocity',
+                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Drop Obj. Velocity',
+                             feature == 'avg_len' ~ 'Avg. Distance',
+                             feature == 'len_std' ~ 'Distance SD',
+                             feature == 'obj_final_position_invstd_objects=target' ~ 'Target Pos. 1/SD',
+                             feature == 'obj_final_position_invstd_objects=drop' ~ 'Drop Obj Pos. 1/SD',
+                             feature == 'avg_final_radius_objects=target' ~ 'Avg. Target Radius',
+                             feature == 'avg_final_radius_objects=drop' ~ 'Avg. Drop Obj Radius',
+                             feature == 'avg_max_radius_objects=drop' ~ 'Max Drop Obj Radius',
+                             feature == 'avg_max_radius_objects=target' ~ 'Max Target Radius',
+                             TRUE ~ feature))
+
+#modtab <- xtable::xtable(mod_tab, digits=2, caption = "Correlations of model and human responses.")
+#modtab %>% kable(digits=2)
+#print(modtab, type="latex", comment = F, include.rownames = F, table.placement = "H")
+
+mod_tab <- as.matrix(mod_tab)
+# bold max value per column
+for(c in 2:ncol(mod_tab)) {
+  mod_tab[,c] = round(as.numeric(mod_tab[,c]), 2)
+  max_row = which(as.numeric(mod_tab[,c])==max(as.numeric(mod_tab[,c])))
+  mod_tab[max_row,c] = cell_spec(mod_tab[max_row,c], "latex", bold = T)
+}
+
+kable(mod_tab, "latex", booktabs = T, escape=F, digits = 2, caption="Correlations ($r$) of model and human responses.") %>%
+  column_spec(column = 2:ncol(mod_tab), width=c("1cm","1cm","1.3cm","1.3cm","1.3cm","1.3cm")) %>%
+  kable_styling(latex_options = "scale_down") 
+```
+
+<!-- The best-fitting feature was $Pr(support)$ for both children ($\beta =$ `r round(best_fits$beta[2],2)`, MSE = `r round(best_fits$mse[2], 3)`) and adults ($\beta =$ `r round(best_fits$beta[1],2)`, MSE = `r round(best_fits$mse[1], 3)`).\footnote{For $\beta=1$, adult MSE = `r round(supp_prob_beta1_cors$mse[1],3)`, child MSE = `r round(supp_prob_beta1_cors$mse[2],3)` for $Pr(support)$.}
 Figure 6 shows this model's fitted preferences plotted against those of children and adults.
@@
 The support response sharpness model fit slightly worse (children $\beta = 0.81$, MSE = 0.016) and adults ($\beta = 1.94$, MSE = 0.054), but its responses were positively correlated with people's (adults $r =$ `r round(supp_resp_sharp_beta_opt_cors$r[1], 2)`, children $r =$ `r round(supp_resp_sharp_beta_opt_cors$r[2],2)`).\footnote{For $\beta=1$, adult MSE = `r round(supp_resp_sharp_beta1_cors$mse[1],3)`, child MSE = `r round(supp_resp_sharp_beta1_cors$mse[2],3)` for support response sharpness, with very similar correlations.}
+-->
 
-```{r human-vs-model-relational-choices, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=4.75, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of $Pr(support)$ model's vs.
+```{r human-vs-model-relational-choices, eval=F, include=F, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.25, fig.height=4.75, set.cap.width=T, num.cols.cap=1, fig.cap = "Comparison of $Pr(support)$ model's vs.
 participants' choices for each type of trial, with 95\\% CIs."}

### 2021-02-04 paper/paper2021.Rmd
rewrote model results

@@
 # old: What if you drop that? Developmental changes in curiosity about physical interactions
-title: "Using physical simulations to predict children's and adults' preference for physical interactions"
+title: "Using physics simulations to predict children's and adults' preference for physical interactions"
 bibliography: library.bib
@@
 If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to $y=0.5$. 
-At a glance, this seems to support the hypothesis that "children are noisy adults."
-We will re-examine this hypothesis with model-based predictions for each trial.
+<!-- At a glance, this seems to support the hypothesis that "children are noisy adults."
+We will re-examine this hypothesis with model-based predictions for each trial. -->
 
@@
 
-## Comparison to Physical Simulations
-
+## Comparison to Physics Simulations
+\vspace{-4pt}
 ```{r load-model-data}
@@
 For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
-We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean length of time before both objects come to rest, as well as the standard deviation (SD) of that time.
-Some features were calculated separately for drop and target objects, such as the SD of each object's final position, the mean and maximum final distance of each object from the drop location, and the normed velocity of each object after first collision.
-We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position.
-Note that the model's definition of support does not distinguish support from containment.
-<!-- support_probability, support_std, support_response_linearity_r, support_response_linearity_pv  -->
-<!--len_inverse_sharpe_ratio, support_response_sharpness_C=1 -->
+We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean amount of time before both objects come to rest (*M(Move Time)*), as well as the standard deviation of that time (*SD(Move Time)*).
+Some features were calculated separately for drop and target objects, such as the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and the SD of the normed velocity of each object after first collision (e.g., *Vel(Target)*).
+We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position (*Supp.
+Sharpness*).
+Note that the model's definition of support does not explicitly distinguish support from containment.
+
+<!--Supp. Sharpness = support_response_sharpness_C=1 -->
 
@@
 A model's preference on any given trial was assumed to be proportional to the relative magnitude of the feature values for the possible physical interactions on that trial, scaled by a softmax parameter $\beta$.
-For each model (feature), we optimized $\beta$ separately to find best-fitting values for children's and adults' drop preferences, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
+For each model (feature), we optimized $\beta$ separately to find best-fitting values for children's and adults' choice proportions, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
 
 ### Results
+
+Examination of the fitted model preferences revealed that none of them achieved a good fit to human preferences.
+For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, but explained no trial-level variation and was in fact negatively correlated with people's choices, overall.
+Thus, instead of reporting predictions from fitted $\beta$s for each feature, we show in Table 2 the correlation between model preferences (with softmax $\beta = 1$) vs.
+adults' and children's choice proportions, both to all trials and separately for containment and support trials.
+The feature with the strongest correlation to adults is Vel(Target) ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while contain trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
+The feature with the strongest correlation to children is *Supp. Sharpness* ($r=.18$), but like adults, children's support trial choices were better correlated with *1/SD(Target Pos)* ($r=.41$).
+Children's containment trial choices were most correlated with *Max(Target Dist)* ($r=.43$), but *Vel(Drop Object)*, the most related to adults' containment trials, was not far behind ($r=.41$).
+Many of the other features show weak or even moderate negative correlations with people's choices.
 
@@
                              feature == 'support_probability' ~ 'Pr(support)',
-                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Target Velocity',
-                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Drop Obj. Velocity',
-                             feature == 'avg_len' ~ 'Avg. Distance',
-                             feature == 'len_std' ~ 'Distance SD',
-                             feature == 'obj_final_position_invstd_objects=target' ~ 'Target Pos. 1/SD',
-                             feature == 'obj_final_position_invstd_objects=drop' ~ 'Drop Obj Pos. 1/SD',
-                             feature == 'avg_final_radius_objects=target' ~ 'Avg. Target Radius',
-                             feature == 'avg_final_radius_objects=drop' ~ 'Avg. Drop Obj Radius',
-                             feature == 'avg_max_radius_objects=drop' ~ 'Max Drop Obj Radius',
-                             feature == 'avg_max_radius_objects=target' ~ 'Max Target Radius',
+                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Vel(Target)',
+                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Vel(Drop Obj)',
+                             feature == 'avg_len' ~ 'M(Move Time)',
+                             feature == 'len_std' ~ 'SD(Move Time)',
+                             feature == 'obj_final_position_invstd_objects=target' ~ '1/SD(Target Pos)',
+                             feature == 'obj_final_position_invstd_objects=drop' ~ '1/SD(Drop Obj Pos)',
+                             feature == 'avg_final_radius_objects=target' ~ 'M(Target Dist)',
+                             feature == 'avg_final_radius_objects=drop' ~ 'M(Drop Obj Dist)',
+                             feature == 'avg_max_radius_objects=drop' ~ 'Max(Drop Obj Dist)',
+                             feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
                              TRUE ~ feature))
@@
 We suggest that these results can fruitfully serve as a test set for evaluating more complex computational  theories of curiosity such as the proposal that learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and that curiosity will change as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
-These theories are starting to be implemented in deep neural networks, which have recently been shown to be capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016].
-@Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
+These theories are starting to be implemented in deep neural networks, which have recently been found capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
+<!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
 These networks are trained simultaneously to solve different problems: the world-model attempts to predict the consequences of the agent's actions (either the forward or inverse dynamics), while the self-model attempts to learn to predict the errors of the world-model.
 The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will challenge its world-model. 
+-->
 In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare these agents' behavior to people's in the same tasks.

### 2021-02-04 paper/paper2021.Rmd
minor edits throughout

@@
 ## Results
-We analyzed data from the `r Nad` adults who completed the experiment and got at least 3 of the 4 catch trials correct (45 participants were excluded for not meeting this criterion).
+We analyzed data from the `r Nad` adults who completed the experiment and answered at least 3 of the 4 catch trials correctly (45 participants were excluded for not meeting this criterion).
 <!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations?
@@
 
-Finally, we examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
+Further, these trial effects were quite reliable across participants.
+We examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
 Based on 100 random samples, the split-half reliability for adults was *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
@@
 After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
-A video recording was taken of the online session.
+<!-- A video recording was taken of the online session. -->
 To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
@@
 \vspace{-4pt}
-Were children more consistent in their choices on support or containment trials?
-As for adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
-Overall, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
-Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age, and that was stronger for containment.
-We examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects. 
+<!-- Were children more consistent in their choices on support or containment trials? -->
+Similar to adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+Unlike adults, however, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age and was overall stronger for containment.
+
+<!-- We next examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects.  -->
+We next examined trial-level effects in children.
 Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1.
@@
 On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
-The split-half reliability for children's choices is *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
+These item effects were relatively reliable, though noisier than that of adults: the split-half reliability for children's choices was *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
 The split-half reliability of children's choices on containment trials was *r* = `r round(mean(sh_ch_contain), 2)` (sd=`r round(sd(sh_ch_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ch_support), 2)` (sd=`r round(sd(sh_ch_support), 2)`).
@@
 \vspace{-4pt}
-Finally, we compare the trial-level preferences of children and adults.
-Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2). 
-If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to $y=0.5$. 
-<!-- At a glance, this seems to support the hypothesis that "children are noisy adults."
-We will re-examine this hypothesis with model-based predictions for each trial. -->
+Finally, we compared the trial-level preferences of children and adults.
+Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type. 
+(visualizing the same data presented in Table 2).
+If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
+At a glance, these results seem to support the hypothesis that "children are noisy adults" in this tasks and suggests some consistency in the trial-level effects across development.
+<!-- We will re-examine this hypothesis with model-based predictions for each trial. --> -->
 
@@
 
-Using a physics engine [@gan2020threedworld] and 3D models of the objects that were shown to participants, we constructed a simulation of for each drop interaction in the experiment and attempted to predict children's and adults' choices using a variety of heuristic models based on the simulated physical interactions.
-For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop calculated a variety of features measuring the state of the model after the drop was completed.
+Using a physics engine [@gan2020threedworld] and 3D models of the objects that were shown to participants, we constructed a simulation of each drop interaction in each trial.
+We then assessed how well a variety of heuristic models based on these simulated physical interactions could predict children's and adults' choices.
+For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop we calculated a variety of features measuring the state of the model after the drop was completed.
 We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean amount of time before both objects come to rest (*M(Move Time)*), as well as the standard deviation of that time (*SD(Move Time)*).
-Some features were calculated separately for drop and target objects, such as the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and the SD of the normed velocity of each object after first collision (e.g., *Vel(Target)*).
+Some features were calculated separately for drop and target objects, such as how variable each object's final positions tend to be (e.g., the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and how variable the speed of each objects tend to be after collision (e.g., *Vel(Target)*).
+<!-- SD of the normed velocity of each object after first collision (e.g.,  -->
 We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position (*Supp.
@@
 adults' and children's choice proportions, both to all trials and separately for containment and support trials.
-The feature with the strongest correlation to adults is Vel(Target) ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while contain trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
+The feature with the strongest correlation to adults is *Vel(Target)* ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while containment trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
 The feature with the strongest correlation to children is *Supp. Sharpness* ($r=.18$), but like adults, children's support trial choices were better correlated with *1/SD(Target Pos)* ($r=.41$).
@@
 
-Given the high split-half reliability of choices on this task, particularly for adults ($r = .95$, children's $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
+Given the high 
+<!-- split-half -->
+reliability of choices on this task, particularly for adults ($r = .95$, children's $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
 We tested a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but the feature that best predicted both children's and adults' responses was the probability that a dropped object would come to rest atop a target object (*Pr(support)*).
@@
 
-We suggest that these results can fruitfully serve as a test set for evaluating more complex computational  theories of curiosity such as the proposal that learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and that curiosity will change as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
-These theories are starting to be implemented in deep neural networks, which have recently been found capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
+At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity.
+For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
+These theories are starting to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
 <!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
@@
 Curiosity has inspired curiosity in researchers for decades, but only recently have the tools come along that make these theories testable.
+We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real-world.
 

### 2021-02-04 paper/paper2021.Rmd
GD edits

@@
 
-Given the high 
-<!-- split-half -->
-reliability of choices on this task, particularly for adults ($r = .95$, children's $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
-We tested a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but the feature that best predicted both children's and adults' responses was the probability that a dropped object would come to rest atop a target object (*Pr(support)*).
-<!-- Adults were best fit by a softmax $\beta = 1.18$, while children were best modeled by $\beta = 0.5$, meaning that as far as this model is concerned children are "noisy" adults.
--->
-However, on a trial level this model's choices were negatively correlated with people's. 
-One of the next best-fitting models was the sensitivity of *Pr(support)* to perturbations in the initial starting conditions, which broadly was able to capture people's stronger preference in *contain* condition trials relative to *support* condition trials, but still did not capture item-level variation in people's choices within condition.
-On balance, although much of the variation in this dataset is unexplained, it is encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic models based on simulations of the same physical task we asked participants to merely imagine.
+Given the high reliability of choices on this task, particularly for adults ($r = .95$, children $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
+We tested a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but not one of these features explained much of the trial-level variance in people's choices.
+Instead, we found a few features that were partially correlated with people's choices: for example, the inverse standard deviation of the target's final position was the best predictor of both children's ($r=.41$) and adults' choices ($r=.41$) on support trials.
+For containment trials, the normed velocity of the drop object after first collision was most correlated with adults' choices ($r=.54$) and moderately with children's ($r=.41$), but children's choices were also correlated with the maximum and mean distance traveled by the target ($r=.43$ and $r=.42$).
+On balance, although much systematic variation in this dataset is unaccounted for, it is somewhat encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic models based on simulations of the same physical task we asked participants to merely imagine.
 
-At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity.
+At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm of "dropping it like it's hot" may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity.
 For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
-These theories are starting to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
+These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
 <!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
@@
 In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare these agents' behavior to people's in the same tasks.
-Curiosity has inspired curiosity in researchers for decades, but only recently have the tools come along that make these theories testable.
+The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 
 We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real-world.

### 2021-02-04 paper/paper2021.Rmd
Dogg, S.

@@
 If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
-At a glance, these results seem to support the hypothesis that "children are noisy adults" in this tasks and suggests some consistency in the trial-level effects across development.
-<!-- We will re-examine this hypothesis with model-based predictions for each trial. --> -->
+At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task and suggests some consistency in the trial-level effects across development. 
+This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.
 
@@
 # Discussion 
-This study aimed 1) to measure the consistency of children's and adults' preferences for particular object interactions, and 2) to determine whether people's interest was predicted by particular features of the imagined physical interactions between objects.
+This study aimed to 1) measure the consistency of children's and adults' preferences for particular object interactions, and 2) determine whether people's interest was predicted by particular features of the imagined physical interactions between objects.
 In an online study that gave adults the opportunity to make drop choices that could result in either a likely support or likely containment relation on each trial, we found that adults consistently chose targets likely to contain the dropped object, and to a lesser degree chose target objects that were likely to support the dropped object.
@@
 
-At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm of "dropping it like it's hot" may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity.
+At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity.
 For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
@@
 -->
-In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare these agents' behavior to people's in the same tasks.
+In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people and "drop it like it's hot" [@Snoop].
 The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 

### 2021-02-04 paper/paper2021.Rmd
small edits

@@
 Finally, we compared the trial-level preferences of children and adults.
-Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type. 
-(visualizing the same data presented in Table 2).
+Figure 5 shows adults' (Experiment 1) vs.
+children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
 If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
-At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task and suggests some consistency in the trial-level effects across development. 
+At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task as well as suggesting some consistency in the trial-level effects across development. 
 This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.
@@
 Examination of the fitted model preferences revealed that none of them achieved a good fit to human preferences.
-For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, but explained no trial-level variation and was in fact negatively correlated with people's choices, overall.
+For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained no trial-level variation and was in fact negatively correlated with people's choices.
 Thus, instead of reporting predictions from fitted $\beta$s for each feature, we show in Table 2 the correlation between model preferences (with softmax $\beta = 1$) vs.
@@
                              feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
-                             TRUE ~ feature))
+                             TRUE ~ feature)) %>%
+  rename(Feature = feature)
 

### 2021-02-04 paper/paper2021.Rmd
Edits to model results section

@@
 A model's preference on any given trial was assumed to be proportional to the relative magnitude of the feature values for the possible physical interactions on that trial, scaled by a softmax parameter $\beta$.
-For each model (feature), we optimized $\beta$ separately to find best-fitting values for children's and adults' choice proportions, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
+For each model (feature), we also optimized $\beta$ separately to find best-fitting values for children's and adults' choice proportions, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
 
 ### Results 
+Overall, we found a few of these features were modestly correlated with people's choices.
+Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs.
+adults' and children's choice proportions, both to all trials and separately for containment and support trials.
+When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*Vel(Target)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
+For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*). 
+For containment trials, adults' choices were most correlated with the velocity of the dropped object (*Vel(Drop Obj)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
+Many of the other features show weak or even moderate negative correlations with people's choices.
 
-Examination of the fitted model preferences revealed that none of them achieved a good fit to human preferences.
-For example, while the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained no trial-level variation and was in fact negatively correlated with people's choices.
-Thus, instead of reporting predictions from fitted $\beta$s for each feature, we show in Table 2 the correlation between model preferences (with softmax $\beta = 1$) vs.
-adults' and children's choice proportions, both to all trials and separately for containment and support trials.
-The feature with the strongest correlation to adults is *Vel(Target)* ($r=.33$), but adults' support trials were more correlated with *1/SD(Target Pos)* ($r=.39$), while containment trials were most correlated with *Vel(Drop Obj)* ($r=.54$).
-The feature with the strongest correlation to children is *Supp. Sharpness* ($r=.18$), but like adults, children's support trial choices were better correlated with *1/SD(Target Pos)* ($r=.41$).
-Children's containment trial choices were most correlated with *Max(Target Dist)* ($r=.43$), but *Vel(Drop Object)*, the most related to adults' containment trials, was not far behind ($r=.41$).
-Many of the other features show weak or even moderate negative correlations with people's choices.
+Examination of the fitted model preferences, in contrast, revealed that none of them achieved a good fit to human preferences.
+While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained no trial-level variation and was in fact negatively correlated with people's choices.
+This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r$=.97 for adults and $r$=.76 for children, the best fitting feature only achieved XX.
 

### 2021-02-04 analysis/model_analysis_v2.Rmd

@@
   if(cor_objective) mse = mse - r # also try to minimize -correlation
-  return(mse) # return negative cor since DEoptim minimizes
+  return(list(mse=mse, r=r)) # return negative cor since DEoptim minimizes
 }
@@
      supp_trials_mse, cont_trials_mse, file=here("models/model_data.RData"))
+```
+
+## Get all feature correlations with Beta=1
+
+```{r fit-models-to-supp-cont-trials-mse, echo=F, eval=FIT_MODELS}
+supp_trials <- tibble()
+cont_trials <- tibble()
+all_trials <- tibble()
+
+feat_names = c("support_response_sharpness_C=1",
+                       "normed_velocity_std_after_first_collision_objects=target",
+                       "normed_velocity_std_after_first_collision_objects=drop",
+                       "avg_max_radius_objects=target",
+                       "avg_max_radius_objects=drop",
+                       "obj_final_position_invstd_objects=target",
+                       "obj_final_position_invstd_objects=drop",
+                       "avg_final_radius_objects=target",
+                       "avg_final_radius_objects=drop",
+                       "avg_len",
+                       "len_std",
+                       "support_probability")
+
+for(feat in feat_names) {
+  feat_df <- get_feature_df(mdat, feat)
+  # get r and mse values for beta=1
+  adult_all <- evalFit(feat_df, adult_trial_agg, 1)
+  adult_supp <- evalFit(feat_df, adult_trial_agg, 1, relation="support")
+  adult_cont <- evalFit(feat_df, adult_trial_agg, 1, relation="contain")
+
+  child_all <- evalFit(feat_df, child_trial_agg, 1)
+  child_supp <- evalFit(feat_df, child_trial_agg, 1, relation="support")
+  child_cont <- evalFit(feat_df, child_trial_agg, 1, relation="contain")
+
+  supp_trials <- bind_rows(supp_trials, c(Age = "adults", feature=feat,  
+                          mse = adult_supp$mse, r = adult_supp$r))
+  supp_trials <- bind_rows(supp_trials, c(Age = "children", feature=feat, 
+                          mse = child_supp$mse, r = child_supp$r))
+
+  cont_trials <- bind_rows(cont_trials, c(Age = "adults", feature=feat, 
+                          mse = adult_cont$mse, r = adult_cont$r))
+  cont_trials <- bind_rows(cont_trials, c(Age = "children", feature=feat, 
+                          mse = child_cont$mse, r = child_cont$r))
+
+  all_trials <- bind_rows(all_trials, c(Age = "adults", feature=feat,
+                          mse = adult_all$mse, r = adult_all$r))
+  all_trials <- bind_rows(all_trials, c(Age = "children", feature=feat,
+                          mse = child_all$mse, r = child_all$r))
+}
+
+supp_trials <- supp_trials %>% mutate(r = as.numeric(r), mse = as.numeric(mse)) %>%
+  arrange(desc(r))
+cont_trials <- cont_trials %>% mutate(r = as.numeric(r), mse = as.numeric(mse)) %>%
+  arrange(desc(r))
+all_trials <- all_trials %>% mutate(r = as.numeric(r), mse = as.numeric(mse)) %>%
+  arrange(desc(r))
+
+save(mdat, all_trials, supp_trials, cont_trials, file=here("models/model_preds_beta1.RData"))
 ```

### 2021-02-04 paper/paper2021.Rmd

@@
 # old: What if you drop that? Developmental changes in curiosity about physical interactions
-title: "Using physics simulations to predict children's and adults' preference for physical interactions"
+title: "Predicting children's and adults' preferences in physical interactions via physics simulation"
 bibliography: library.bib
@@
                       fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
+                      echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 From infants exploring the objects in their environment to scientists exploring the frontiers of our solar system, humans are highly motivated to seek out new knowledge and experiences. 
-However, although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
-Moreover, extant theories have rarely provided quantitatively precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans.
+Although such exploratory behavior has long been recognized as a critical component of human learning [@james1983talks] and cognitive development [@Gopnik2009; @Piaget1952], formal theories that explain human curiosity and how it drives exploratory behavior have remained elusive [@Kidd2015].
+Moreover, extant theories have rarely provided precise enough predictions to be directly compared to empirical measurements of curiosity-driven behavior in humans, in part because curiosity tends to result in complex, open-ended behaviors that are difficult to quantify.
 
 The goal of the current paper is to help close this gap by proposing a novel paradigm to advance our theoretical understanding of curiosity, specifically within the domain of physical object interactions [@kubricht2017intuitive].
-First, we present an empirical investigation of the pattern of actions taken by children and adults in a novel physical exploration task. 
-We then present a set of heuristic models of curiosity based on a variety of metrics of simulated physical interactions (e.g., likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
+First, we present an empirical investigation of the pattern of choices taken by children and adults in a novel task. 
+We then present a set of heuristic models of this behavior based on a variety of metrics of simulated physical interactions (e.g., likelihood of a dropped object coming to rest on a target object), and test the degree to which these features predict children and adults' behaviors in the same task.
 <!-- Finally, we sketch how future work can test the correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.
@@
 We take inspiration from a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact [@hespos2012physics; @smith2018developing; @Baillargeon2007].
-Children both spend a remarkably amount of time across exploring how different objects and surfaces interact during naturalistic play [@fenson1976] and spend longer time exploring objects that appear to violate physical laws (e.g., an object that appears to pass through a wall; @Stahl2015; @Baillargeon2007).
+Children both spend a remarkably amount of time across exploring how different objects and surfaces interact during naturalistic play [@fenson1976] and spend longer time exploring objects that appear to violate physical laws [e.g., an object that appears to pass through a wall; @Stahl2015; @Baillargeon2007].
 In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self].
@@
 and then demonstrate how this paradigm can be used to test theories of curiosity about physical interactions. 
-First, we measured people's choices in a novel physical exploration task, in which participants were told that they would drop a given object (e.g., a sphere, a torus; see Figure 1) onto one of two target objects (e.g., a dumbbell, a pentagonal prism; see Figure 2), with the goal of the creating the most interesting physical interaction.
-We recorded adults' and children's (3-7 years of age) choices for a set of trials in which some of the drop objects could plausibly end up *supported* by one of the target objects, and for a set of trials in which some of the drop objects could end up *contained* by one of the targets -- although the other potential targets likely also offered affordances of interest.
-After examining the consistency of people's preferences, we tested the predictive power of a variety of heuristic models of curiosity that operate on simulations of this task with these same objects in a 3D environment.
-Our results suggest that using detailed measurement of human action selection and computational models based on simulations of the same tasks promises to lead to more robust and precise theories of human curiosity about the physical world, and how it develops.
+First, we measured people's choices in a novel task, in which participants were told that they would drop a given object (e.g., a sphere, a torus; see Figure 1) onto one of two target objects (e.g., a dumbbell, a pentagonal prism; see Figure 2), with the goal of the creating the most interesting physical interaction.
+We recorded adults' and children's (3--7 years of age) choices for a set of trials in which some of the drop objects could plausibly end up *supported* by one of the target objects, and for a set of trials in which some of the drop objects could end up *contained* by one of the targets -- although the other potential targets likely also offered affordances of interest.
+After examining the consistency of people's preferences, we tested the predictive power of a variety of heuristic features derived from simulations of this task using a 3D environment. 
+<!-- Our results suggest that using detailed measurement of human action selection and computational models based on simulations of the same tasks promises to lead to more robust and precise theories of human curiosity about the physical world, and how it develops.
+-->
 
@@
 ## Method
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 ### Participants
@@
 ### Materials
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
@@
 ### Design
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
@@
 
-```{r fig2-task, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.4, fig.height=3.3, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
-img <- png::readPNG("figs/2AFC_DropTaskFig.png")
-grid::grid.raster(img)
-```
-
 Participants were instructed that they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
@@
 These free responses were examined to determine if participants had particular goals in mind when making a choice, and how prevalent those goals were among participants. -->
+
+```{r fig2-task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.4, fig.height=3.3, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
+img <- png::readPNG("figs/2AFC_DropTaskFig.png")
+grid::grid.raster(img)
+```
 
@@
 Further, these trial effects were quite reliable across participants.
-We examined the split-half reliability of adults' choices by repeatedly splitting the samples in half and testing the correlation between the halves.
-Based on 100 random samples, the split-half reliability for adults was *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
-The split-half reliability of adults' choices on containment trials was *r* = `r round(mean(sh_ad_contain), 2)` (sd=`r round(sd(sh_ad_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ad_support), 2)` (sd=`r round(sd(sh_ad_support), 2)`).
+We examined the split-half reliability of adults' choices by repeatedly splitting the data and testing the correlation between the halves.
+With 100 random samples, reliability for adults was *r* = `r round(mean(sh_subj_adult), 2)` (sd=`r round(sd(sh_subj_adult), 2)`).
+Reliability was *r* = `r round(mean(sh_ad_contain), 2)` (sd=`r round(sd(sh_ad_contain), 2)`) for containment trials and  *r* = `r round(mean(sh_ad_support), 2)` (sd=`r round(sd(sh_ad_support), 2)`) for support trials.
 
@@
 # Experiment 2: Children
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
@@
 ## Method
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
@@
 ### Participants
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
@@
 ### Materials
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3. 
@@
 ### Procedure
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 <!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
@@
 ## Results
-\vspace{-4pt}
+<!-- \vspace{-4pt} -->
 <!-- Were children more consistent in their choices on support or containment trials? -->
@@
 Unlike adults, however, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
-Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group, showing a preference for the designed relations that increased with age and was overall stronger for containment.
+Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group.
+Preferences increased with age and were overall stronger for containment.
 
@@
 
-## Comparison of Children's vs. Adults' Preferences
-\vspace{-4pt}
-Finally, we compared the trial-level preferences of children and adults.
+### Comparison of Children's vs. Adults' Preferences
+<!-- \vspace{-4pt} -->
+<!-- Finally, we compared the trial-level preferences of children and adults. -->
 Figure 5 shows adults' (Experiment 1) vs.
 children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
-If they corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
+If adults' and children's judgments corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
 At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task as well as suggesting some consistency in the trial-level effects across development. 
@@
 
-## Comparison to Physics Simulations
-\vspace{-4pt}
+# Comparison to Physics Simulations
+<!-- \vspace{-4pt} -->
 ```{r load-model-data}
@@
 
-Using a physics engine [@gan2020threedworld] and 3D models of the objects that were shown to participants, we constructed a simulation of each drop interaction in each trial.
-We then assessed how well a variety of heuristic models based on these simulated physical interactions could predict children's and adults' choices.
+We next attempted to predict adults' and children's judgments using a 3D model of the physical interactions instantiated in our paradigm.
+We constructed a simulation of each drop interaction in each trial using a physics engine [@gan2020threedworld] and 3D models of the objects (the same models that we had printed and used in the videos and photos in the experimental paradigm).
+We then assessed how well a variety of heuristic features based on these simulated physical interactions could predict choice data.
+
+## Physical interaction model and features
+
 For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop we calculated a variety of features measuring the state of the model after the drop was completed.
@@
 
-We measured each of these features in 250 simulations of each possible drop in the experiment, and then used the resulting values to generate relative preferences for the drop choices on each trial. 
+We averaged each of these features across simulations and then used the resulting values to generate relative preferences for the drop choices on each trial. 
 A model's preference on any given trial was assumed to be proportional to the relative magnitude of the feature values for the possible physical interactions on that trial, scaled by a softmax parameter $\beta$.
 For each model (feature), we also optimized $\beta$ separately to find best-fitting values for children's and adults' choice proportions, with the objective of minimizing mean squared error (MSE) between model and human choice proportions across all 20 trials.
+<!-- ; this optimization did not result in a better fit to the choice data, so we focus here on results when $\beta=1$. -->
 
-### Results 
-Overall, we found a few of these features were modestly correlated with people's choices.
+## Results
+
+Overall, a few of these features were modestly correlated with people's choices.
 Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs.
@@
 When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*Vel(Target)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
-For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*). 
-For containment trials, adults' choices were most correlated with the velocity of the dropped object (*Vel(Drop Obj)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
-Many of the other features show weak or even moderate negative correlations with people's choices.
+<!-- For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).
+-->
+<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*Vel(Drop Obj)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
+-->
+Many of the other features showed weak or even moderate negative correlations with people's choices.
 
-Examination of the fitted model preferences, in contrast, revealed that none of them achieved a good fit to human preferences.
-While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained no trial-level variation and was in fact negatively correlated with people's choices.
+Examination of the models with $\beta$ optimized, in contrast, revealed that none  achieved a good fit to human preferences.
+While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained essentially no trial-level variation and was in fact negatively correlated with choices.
 This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r$=.97 for adults and $r$=.76 for children, the best fitting feature only achieved XX.
@@
 
-# Discussion 
+# General Discussion
+
 This study aimed to 1) measure the consistency of children's and adults' preferences for particular object interactions, and 2) determine whether people's interest was predicted by particular features of the imagined physical interactions between objects.
 In an online study that gave adults the opportunity to make drop choices that could result in either a likely support or likely containment relation on each trial, we found that adults consistently chose targets likely to contain the dropped object, and to a lesser degree chose target objects that were likely to support the dropped object.
-Experiment 2 found the same pattern in children, but with greater noise -- even to the extent that younger children were at-chance at choosing the support relation on most trials.
-In sum, our behavioral study found that infant's early-emerging interest in containment [@Casasola2003] may extend through childhood and persist into adulthood, along with a weaker interest in support relations.
+Experiment 2 found the same pattern in children, but with attenuated preferences, especially in the youngest children.
+One interpretation of these results is that infants' early-emerging interest in containment [@Casasola2003] may be related to older children's and adults' interest in stochastic interactions that have some possibility of producing containment relations.
 
-Given the high reliability of choices on this task, particularly for adults ($r = .95$, children $r = .61$), we tested how well heuristic models of curiosity based on simulations of the physical interactions could predict participants' preferences of target objects on each trial.
-We tested a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but not one of these features explained much of the trial-level variance in people's choices.
-Instead, we found a few features that were partially correlated with people's choices: for example, the inverse standard deviation of the target's final position was the best predictor of both children's ($r=.41$) and adults' choices ($r=.41$) on support trials.
-For containment trials, the normed velocity of the drop object after first collision was most correlated with adults' choices ($r=.54$) and moderately with children's ($r=.41$), but children's choices were also correlated with the maximum and mean distance traveled by the target ($r=.43$ and $r=.42$).
-On balance, although much systematic variation in this dataset is unaccounted for, it is somewhat encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic models based on simulations of the same physical task we asked participants to merely imagine.
+Given the high reliability of choices on this task, particularly for adults ($r = .95$, children $r = .61$), we tested how well heuristic features of the physical interactions could predict these choices.
+We explored a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but not one of these features explained much of the trial-level variance in people's choices.
+<!-- Instead, we found a few features that were partially correlated with people's choices: for example, the inverse standard deviation of the target's final position was the best predictor of both children's and adults' choices on support trials.
+-->
+<!-- For containment trials, the normed velocity of the drop object after first collision was most correlated with adults' choices and moderately with children's, but children's choices were also correlated with the maximum and mean distance traveled by the target.
+-->
+On balance, although much systematic variation in this dataset is unaccounted for, it is somewhat encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic features based on simulations of the same physical task we asked participants to merely imagine.
 

### 2021-02-04 paper/paper2021.Rmd
extra para
final edits

@@
 ## Method
-<!-- \vspace{-4pt} -->
 ### Participants
@@
 ### Materials
-<!-- \vspace{-4pt} -->
 Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
@@
 ### Design
-<!-- \vspace{-4pt} -->
 The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
@@
 
-```{r fig2-task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.4, fig.height=3.3, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
+```{r fig2-task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.5, fig.height=3.4, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
 img <- png::readPNG("figs/2AFC_DropTaskFig.png")
@@
 
+```{r noise-ceiling, echo=F}
+
+calc_noise_ceiling <- function(split_half_cors) {
+  rD = (2 * split_half_cors) / (1 + split_half_cors)
+  return(sqrt(mean(rD)))
+}
+
+noise_ceiling_adult = calc_noise_ceiling(sh_subj_adult) # .99
+noise_ceiling_child = calc_noise_ceiling(sh_subj_child) # .87
+
+#calc_noise_ceiling(sh_ch_contain) # .66
+#calc_noise_ceiling(sh_ad_contain) # .96
+
+#calc_noise_ceiling(sh_ch_support) # .88
+#calc_noise_ceiling(sh_ad_support) # .97
+
+```
+
 ## Results
@@
 -->
-Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
+Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r apa::t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
 Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
@@
 # Experiment 2: Children
-<!-- \vspace{-4pt} -->
+
 Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
@@
 ## Method
-<!-- \vspace{-4pt} -->
 We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.
@@
 ### Participants
-<!-- \vspace{-4pt} -->
 Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
@@
 ### Materials
-<!-- \vspace{-4pt} -->
 The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3.
-<!-- Introductory slides were added for informed consenting process and screen configuration, where the researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3).
--->
 
@@
 ### Procedure
-<!-- \vspace{-4pt} -->
 <!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
@@
 ## Results
-<!-- \vspace{-4pt} -->
 <!-- Were children more consistent in their choices on support or containment trials? -->
-Similar to adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
+Similar to adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r apa::t_apa(ch_supp_cont, format="rmarkdown", print=F)`).
 Unlike adults, however, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
@@
 
-<!-- We next examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects.  -->
 We next examined trial-level effects in children. 
@@
 Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance. 
-<!-- stricter crit for mult comparisons?
-Bonf=.0025 -->
 Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
@@
 ### Comparison of Children's vs. Adults' Preferences
-<!-- \vspace{-4pt} -->
 <!-- Finally, we compared the trial-level preferences of children and adults. -->
@@
 # Comparison to Physics Simulations
-<!-- \vspace{-4pt} -->
 ```{r load-model-data}
@@
 We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean amount of time before both objects come to rest (*M(Move Time)*), as well as the standard deviation of that time (*SD(Move Time)*).
-Some features were calculated separately for drop and target objects, such as how variable each object's final positions tend to be (e.g., the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and how variable the speed of each objects tend to be after collision (e.g., *Vel(Target)*).
+Some features were calculated separately for drop and target objects, such as how variable each object's final positions tend to be (e.g., the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and how variable the velocity of each object tends to be after the first collision (e.g., *SD(Target Vel)*).
 <!-- SD of the normed velocity of each object after first collision (e.g.,  -->
@@
 Overall, a few of these features were modestly correlated with people's choices. 
-Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs.
-adults' and children's choice proportions, both to all trials and separately for containment and support trials.
-When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*Vel(Target)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
+Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
+When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*SD(Target Vel)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
 <!-- For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).
 -->
-<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*Vel(Drop Obj)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
+<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
 -->
@@
 While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained essentially no trial-level variation and was in fact negatively correlated with choices.
-This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r$=.97 for adults and $r$=.76 for children, the best fitting feature only achieved XX.
+This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r=$ `r round(noise_ceiling_adult, 2)` for adults and $r=$ `r round(noise_ceiling_child, 2)` for children, the best-fitting feature accounted for very little of that.
 
@@
                              feature == 'support_probability' ~ 'Pr(support)',
-                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Vel(Target)',
-                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Vel(Drop Obj)',
+                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'SD(Target Vel)',
+                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'SD(Drop Obj Vel)',
                              feature == 'avg_len' ~ 'M(Move Time)',
@@
 In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people and "drop it like it's hot" [@Snoop].
+
 The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 

### 2021-05-03 paper/paper2021.Rmd
minor revisions for CogSci

@@
 
-The goal of the current paper is to help close this gap by proposing a novel paradigm to advance our theoretical understanding of curiosity, specifically within the domain of physical object interactions [@kubricht2017intuitive].
+The goal of the current paper is to help close this gap by proposing a novel paradigm to advance our theoretical understanding of curiosity, specifically within the domain of physical object interactions [@kubricht2017intuitive; @bramley2018].
 First, we present an empirical investigation of the pattern of choices taken by children and adults in a novel task. 
@@
 We take inspiration from a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact [@hespos2012physics; @smith2018developing; @Baillargeon2007].
-Children both spend a remarkably amount of time across exploring how different objects and surfaces interact during naturalistic play [@fenson1976] and spend longer time exploring objects that appear to violate physical laws [e.g., an object that appears to pass through a wall; @Stahl2015; @Baillargeon2007].
-In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self].
+Children both spend a remarkable amount of time across exploring how different objects and surfaces interact during naturalistic play [@fenson1976] and spend longer time exploring objects that appear to violate physical laws [e.g., an object that appears to pass through a wall; @Stahl2015; @Baillargeon2007].
+In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self; @allen2020].
 However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of exploration or of physics learning.
@@
 After examining the consistency of people's preferences, we tested the predictive power of a variety of heuristic features derived from simulations of this task using a 3D environment.
+<!-- cite @gerstenberg2020 about here? -->
 <!-- Our results suggest that using detailed measurement of human action selection and computational models based on simulations of the same tasks promises to lead to more robust and precise theories of human curiosity about the physical world, and how it develops.
@@
 In the pilot study (N=15), the pairs of target or drop objects were chosen essentially at random, but were the same for all participants.
-We were surprised to find consistency in adults' preferences for many of the trials: especially when given a drop object and asked to choose one of two target objects, adults were quite often (75-90%) targeting that object that would either *contain* or *support* the dropped object (i.e., the pipe could contain the cone; the pentagonal prism could support the octahedron).
+We were surprised to find consistency in adults' preferences for many of the trials: especially when given a drop object and asked to choose one of two target objects, adults were quite often (75-90%) targeting the object that would either *contain* or *support* the dropped object (i.e., the pipe could contain the cone; the pentagonal prism could support the octahedron).
 This consistency in their choices is remarkable given that there are many other possible goals that people might choose in order to make something "interesting" happen: they might attempt to make the dropped object roll or bounce far from the target, or rebound in an unexpected direction, but in fact most people settled on attempting support or containment relations.

### 2021-05-08 paper/paper2021.Rmd
Minor changes + paragraph at end of intro to preview results

@@
 # Introduction 
-
 Curiosity is a hallmark aspect of human intelligence. 
@@
 We recorded adults' and children's (3--7 years of age) choices for a set of trials in which some of the drop objects could plausibly end up *supported* by one of the target objects, and for a set of trials in which some of the drop objects could end up *contained* by one of the targets -- although the other potential targets likely also offered affordances of interest.
-After examining the consistency of people's preferences, we tested the predictive power of a variety of heuristic features derived from simulations of this task using a 3D environment.
+After examining children's and adult's preferences, we tested the predictive power of a variety of heuristic features derived from simulations of this task using a 3D environment.
+To preview our results, we found a surprising amount of consistency in how both children and adults chose to explore the relationships between different objects -- but that this consistency was not easily explained by any of simple heuristic features that we tested.
+We propose that these kinds of physical exploration task are a promising tested for adjudicating between different embodied models of curiosity.
+
 <!-- cite @gerstenberg2020 about here? -->
@@
 # Experiment 1: Adults
-
 To investigate the systematicity of people's preferences for physical interactions between objects, we began by studying adults, whom we might expect to be less idiosyncratic and thus more consistent in their choices than children.
@@
 -->
-In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people and "drop it like it's hot" [@Snoop].
+In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people when asked to "drop it like it's hot" [@Snoop].
 
@@
 
-<!--
-According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957].
+<!--According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957]
 Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.

### 2021-05-10 paper/paper2021.Rmd
CogSci revisions

@@
      same stimuli. Here we propose a new experimental paradigm for examining children's -- and 
-     AI agents' -- curiosity about objects' physical interactions.
-     We let them choose which object to 
-     drop another object onto in order to create the most interesting effect. We compared adults' (N=155) and children's choices (N=66; 
-     3-7 year-olds) and found that adults show a strong preference for drops that could potentially result in a containment
-     relation, a preference that is also shown by children. Adults alone also make choices consistent 
-     with achieving support relations. We contextualize our results using heuristic computational models based on 
+     AI agents' -- curiosity about objects' physical interactions. We let them choose which object 
+     to drop another object onto in order to create the most interesting effect. 
+     We compared adults' (N=155) and children's choices (N=66; 3-7 year-olds) and found that both 
+     children and adults show a strong preference for choosing target objects that could potentially 
+     contain the dropped object.
+     Adults alone also make choices consistent with achieving support relations. 
+     We contextualize our results using heuristic computational models based on 
      3D physical simulations of the same scenarios judged by participants.
@@
 #      in_header: preamble.tex
-#final-submission: \cogscifinalcopy
+final-submission: \cogscifinalcopy
 ---
@@
 However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of exploration or of physics learning.
-Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014].
+Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014; @hoicka2016].
+<!-- though see @sim2017-->
 
@@
 We recorded adults' and children's (3--7 years of age) choices for a set of trials in which some of the drop objects could plausibly end up *supported* by one of the target objects, and for a set of trials in which some of the drop objects could end up *contained* by one of the targets -- although the other potential targets likely also offered affordances of interest.
-After examining children's and adult's preferences, we tested the predictive power of a variety of heuristic features derived from simulations of this task using a 3D environment.
-To preview our results, we found a surprising amount of consistency in how both children and adults chose to explore the relationships between different objects -- but that this consistency was not easily explained by any of simple heuristic features that we tested.
-We propose that these kinds of physical exploration task are a promising tested for adjudicating between different embodied models of curiosity.
+After examining children's and adult's preferences, we tested the predictive power of a variety of heuristic features derived from the simulated physics of this task in a 3D environment.
+To preview our results, we found a surprising amount of consistency in how both children and adults chose to explore the relationships between different objects -- but that this consistency was not easily explained by any of the simple heuristic features that we tested.
+We propose that this type of physical exploration task is a promising test for adjudicating between different embodied models of curiosity.
 
@@
 <!-- GK: possibly re-do this figure to have the proper orientations -->
-```{r fig3-child-sets, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.2, fig.height=2.9, set.cap.width=T, num.cols.cap=1, fig.cap = "Nine of the 10 3D objects used for dropping and as targets (not pictured: ball)."}
-img <- png::readPNG("figs/fig1-objects.png")
+```{r fig1-objects, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=4.0, set.cap.width=T, num.cols.cap=1, fig.cap = "(Top) Nine of the 10 3D objects used for dropping and as targets (not pictured: ball).
+(Bottom) Example support and containment relations."}
+img <- png::readPNG("figs/fig1_objects_support_contain_examples.png")
 grid::grid.raster(img)
@@
 
-<!--
 # Acknowledgements
-This work was funded by HAI seed grant #. 
-We thank X and Y for helpful comments. 
--->
+This work was funded by a Stanford University Human-centered Artificial Intelligence seed grant.
 

### 2021-05-10 paper/paper2021.Rmd
cogsci revisions

@@
 author-information: > 
-    \author{{\large \bf George Kachergis (kachergis@stanford.edu)} \and {\large \bf Sama Radwan} \and {\large \bf Bria Long} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA
-    \AND {\large \bf Judith Fan (jefan@ucsd.edu)} \\ Department of Psychology, University of San Diego \\ Madison, WI 53706 USA
-    \AND {\large \bf Daniel Bear} \and {\large \bf Daniel Yamins} \\ Departments of Psychology & Computer Science, Stanford University \\ Palo Alto, CA 94305 USA
-    \AND {\large \bf Michael C.~Frank} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94305 USA}
+    \author{
+    {\large \bf George Kachergis}$^1,\star$, {\large \bf Samaher Radwan}$^1$, {\large \bf Bria Long}$^1$,  
+    {\large \bf Judith Fan}$^2$, \\
+    $^{\star}$\texttt{kachergis@stanford.edu} \\
+    {\large \bf Daniel Bear}$^{1,3}$, {\large \bf Daniel Yamins}$^{1,3}$, {\large \bf Michael C.~Frank}$^1$ \\ 
+    $^1$Department of Psychology, Stanford University \\
+    $^2$Department of Psychology, University of California at San Diego \\
+    $^3$Department of Computer Science, Stanford University}
 
@@
 require(kableExtra)
+require(papaja)
 ```
@@
 ```{r human-vs-model-table, results="asis"} 
+# to make double-wide, need to modify tex file to \begin{table*} / \end{table*}
 # now we just have a table of selected features that were moderately correlated with people's choices
@@
 
-kable(mod_tab, "latex", booktabs = T, escape=F, digits = 2, caption="Correlations ($r$) of model and human responses.") %>%
-  column_spec(column = 2:ncol(mod_tab), width=c("1cm","1cm","1.3cm","1.3cm","1.3cm","1.3cm")) %>%
-  kable_styling(latex_options = "scale_down") 
+#kable(mod_tab, "latex", booktabs = T, escape=F, digits = 2, caption="Correlations ($r$) of model and human responses.") 
+  #column_spec(column = 2:ncol(mod_tab), width=c("1cm","1cm","1.3cm","1.3cm","1.3cm","1.3cm")) %>%
+  #kable_styling(latex_options = "scale_down") 
+apa_table(mod_tab, format="latex", digits=2, escape=F, span_text_columns=T,
+          align = c("l", rep("r", ncol(mod_tab)-1)), # font_size = "small", 
+          caption="Correlations ($r$) of model and human responses.")
 ```
@@
 Given the high reliability of choices on this task, particularly for adults ($r = .95$, children $r = .61$), we tested how well heuristic features of the physical interactions could predict these choices.
+In light of findings that people often single out one of several possible causes as "the" cause in judgements of physical causation [e.g., @gerstenberg2020], we might expect to find single features that are predictive of people's choices.
 We explored a wide range of features that we thought might be proportional to people's interest in particular object interactions (e.g., how far a dropped object might end up from the drop location), but not one of these features explained much of the trial-level variance in people's choices.
-<!-- Instead, we found a few features that were partially correlated with people's choices: for example, the inverse standard deviation of the target's final position was the best predictor of both children's and adults' choices on support trials.
--->
-<!-- For containment trials, the normed velocity of the drop object after first collision was most correlated with adults' choices and moderately with children's, but children's choices were also correlated with the maximum and mean distance traveled by the target.
--->
+Instead, we found a few features that were partially correlated with people's choices: for example, the best predictor of both children's and adult's choices on support trials was the inverse standard deviation of the target's final position, but the strength of this correlation was only moderate ($r \approx 0.4$).
+For containment trials, the normed velocity of the drop object after first collision was most correlated with adults' choices and moderately with children's, but children's choices were also correlated with the maximum and mean distance traveled by the target.
 On balance, although much systematic variation in this dataset is unaccounted for, it is somewhat encouraging that people's interest in physical interactions can be in part accounted for by simple heuristic features based on simulations of the same physical task we asked participants to merely imagine.

### 2021-05-10 paper/paper2021.Rmd
final edits

@@
     \author{
-    {\large \bf George Kachergis}$^1,\star$, {\large \bf Samaher Radwan}$^1$, {\large \bf Bria Long}$^1$,  
+    {\large \bf George Kachergis}$^{1,\star}$, {\large \bf Samaher Radwan}$^1$, {\large \bf Bria Long}$^1$,  
     {\large \bf Judith Fan}$^2$, \\
@@
 require(gridExtra)
+require(papaja)
 require(kableExtra)
-require(papaja)
 ```
@@
 
-<!-- GK: possibly re-do this figure to have the proper orientations -->
 ```{r fig1-objects, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=4.0, set.cap.width=T, num.cols.cap=1, fig.cap = "(Top) Nine of the 10 3D objects used for dropping and as targets (not pictured: ball).
@@
 Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.
-That is, the target objects were chosen so that one of them would be capable of either supporting or  containing the dropped object.
+That is, the target objects were chosen so that one of them would be capable of either supporting or  containing the dropped object (see examples: Figure 1, bottom).
 For example, if asked to drop the cone on either the torus or the octahedron, a containment relation could be achieved between the cone and the torus, but not the octahedron (and support is unlikely due to the small surface area of the octahedron).
@@
 ### Procedure
-
 Participants were instructed that they would be helping choose which toys to include in a new set of children's blocks in order to make them the most interesting.
@@
   bind_rows(adult_long) %>% 
-  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult"))
+  mutate(AgeGroup = ifelse(Age!="adult", "child", "adult")) %>%
+  mutate(Age = factor(Age, levels=c("3","4","5","6","7","adult")))
 #knitr::kable(trial_tab %>% arrange(relation, desc(adult_target_choice)), digits=2)
@@
 Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance. 
-As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance, suggesting that many participants found the prospect of dropping on the distractor object at least equally enticing.
+As can be seen in Table 1, adult participants significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance, suggesting that many participants found the prospect of dropping on the distractor object at least equally enticing.
 
@@
 
-<!-- Maybe code the type of goals stated by the parents? -->
+```{r regression, eval=F, include=F}
+require(lme4)
+m1 <- lmer(chose_target ~ AgeGroup * relation + (1|ID) + (1|Trial), data=combo_dat)
+summary(m1) # children less likely to choose target than adults, and support targets less likely picked than containment targets
+```
 
@@
 Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
-When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*SD(Target Vel)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
-<!-- For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).
--->
-<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
--->
+When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*SD(Target Vel)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$).
+For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).
+For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
 Many of the other features showed weak or even moderate negative correlations with people's choices.
@@
 These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
-<!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
-These networks are trained simultaneously to solve different problems: the world-model attempts to predict the consequences of the agent's actions (either the forward or inverse dynamics), while the self-model attempts to learn to predict the errors of the world-model.
-The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will challenge its world-model. 
--->
+
+Such embodied deep reinforcement learning agents are often composed of two models: a *world model* which attempts to predict the consequences of the agent's actions (i.e., the forward dynamics--physics--of the world), while the *self model* attempts to predict the errors of the world model.
+The predictions of the self model can be used to implement different curiosity policies for choosing actions [e.g., picking actions that are expected to challenge its world model; @Haber2018learning].
 In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people when asked to "drop it like it's hot" [@Snoop].
+Will these agents show choices consistent with potential containment/support relations, or do these human-like preferences require representation and selection of possible goals?
+How might the agents' choices evolve over time, as the world model matures?
+Might the agents' curiosity policies need to change over development in order to match people's choices, or do these goals emerge through the dynamics of learning?
 
 The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 
-We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real-world.
+We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real world.
+
+<!-- Is containment inherently more satisfying, or is there greater interest because it is more achievable? (Less susceptible to small amounts of error)
+Are children less interested in relations that are more difficult to achieve with more motor noise?
+Or are they less aware (or simply less interested in) support?
+Or do children find some other goal relatively more enticing? -->
 
@@
 Our modeling approach is resonant with recent work that has instantiated such intrinsic-motivation mechanisms in robots to help them learn robust ways to predict physical events in the world world [@Oudeyer2007; @Oudeyer2013], although this work typically involves pretraining models on a separate physical prediction task before implementing curiosity-driven learning, and has not yet been directly compared to human behavior in the same prediction tasks.
--->
-<!--
-Is containment inherently more satisfying, or is there greater interest because it is more achievable? (Less susceptible to small amounts of error)
-Are children less interested in relations that are more difficult to achieve with more motor noise?
-Or are they less aware (or simply less interested in) support?
-Or do children find some other goal relatively more enticing?
 -->

### 2021-05-10 paper/paper2021.Rmd
minor edits

@@
     {\large \bf Judith Fan}$^2$, \\
-    $^{\star}$\texttt{kachergis@stanford.edu} \\
-    {\large \bf Daniel Bear}$^{1,3}$, {\large \bf Daniel Yamins}$^{1,3}$, {\large \bf Michael C.~Frank}$^1$ \\ 
+    {\large \bf Daniel Bear}$^{1,3}$, {\large \bf Daniel Yamins}$^{1,3}$, \and {\large \bf Michael C.~Frank}$^1$ \\ 
     $^1$Department of Psychology, Stanford University \\
     $^2$Department of Psychology, University of California at San Diego \\
-    $^3$Department of Computer Science, Stanford University}
+    $^3$Department of Computer Science, Stanford University \\
+    $^{\star}$\texttt{kachergis@stanford.edu}}
 
@@
   tidyboot_mean(chose_target) %>%
-  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
+  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + 
+  geom_bar(stat="identity", position=pos) + 
+  scale_fill_brewer(palette="Dark2") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
@@
   ggplot(aes(x=mean, y=Model_targ_prop, group=relation, color=relation)) + 
+    #scale_color_manual(values=c("#E69F00", "#56B4E9")) +
     geom_point(alpha=.6) + 
@@
 <!--According to these theories, curiosity-driven behavior reflects a gap between the learner's knowledge and the state of the world [@Loewenstein1994], and thus they predict that as a learner gains additional knowledge, their preferences will shift toward more complex stimuli [@Dember1957]
-Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are compared.
+Although these theories have provided important qualitative insights, one of their major limitations is that they do not provide precise ways to characterize a learner's current knowledge state, how physical states of the world are represented in their mind, nor how discrepancies between a learner's knowledge and such states are evaluated.
 Our approach leverages theory and insights from reinforcement learning (RL), including the value of mechanisms that equip RL agents with "intrinsic motivation" — a drive to explore the state space even when rewards are sparse or absent, and favor actions with uncertain outcomes, because they may result in the discovery of new policies with high expected values [@Schmidhuber2010].
@@
 
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://osf.io/37qvb}}} \vspace{1em}
+
 # Acknowledgements
-This work was funded by a Stanford University Human-centered Artificial Intelligence seed grant.
+This work was funded by a Stanford University Human-centered Artificial Intelligence grant.
 

### 2021-05-10 paper/paper2021.Rmd
table number corrections

@@
 Figure 5 shows adults' (Experiment 1) vs.
-children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
+children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 1, but with 95% CIs).
 If adults' and children's judgments corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).

### 2021-05-12 paper/paper2021.Rmd
final edits

@@
 In other words, children seem to actively learn about physical interactions by intervening on the world and observing the consequences of their actions [@needham2000improvements; @Gopnik2009; @gureckis2012self; @allen2020].
-However, relatively little work has examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of exploration or of physics learning.
+However, relatively little work has either examined what types of physical interactions children are most interested in testing, or linked children's actions to formal theories of exploration or of physics learning.
 Instead, most work that has investigated exploratory behavior in children has done so by examining how they play with relatively complex objects -- for example, documenting the number of functions discovered while playing with a novel toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014; @hoicka2016].
@@
 After making their choice on the practice trial, participants were shown a 10-second video recording of 3D-printed plastic toys carrying out their chosen interaction (e.g., if they chose the dumbbell, they would see the torus dropped on the dumbbell).
-This was done to ensure that they understood the consequences of the choice they made.
-After the video of the torus drop, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on.
+This was done to ensure that they understood the consequences of the choice they made, although it was pointed out to them that the video they saw showed only one possible outcome.
+After the example video, participants were given a sequence of 20 more drop trials asking them to choose which toy (X or Y) they would like to drop object Z on.
 Four catch trials were interspersed among the 20 drop trials, which asked them to indicate which object they had just dropped on the previous trial (3-alternative forced choice).
@@
 Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
-Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
-After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
+Participant exclusions were made based on cases where i) the participant did not complete more than half of the trials or ii) the parent did not consent for video recording of the session. 
+After exclusions, results from `r Nch` children were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.
 
@@
 For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).
-For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
+For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$), which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).
 Many of the other features showed weak or even moderate negative correlations with people's choices.
@@
 For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
-These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
+These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curiosity" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
 

### 2021-05-12 paper/paper2021.Rmd
finalized CogSci 2021 revisions

@@
     {\large \bf Judith Fan}$^2$, \\
-    {\large \bf Daniel Bear}$^{1,3}$, {\large \bf Daniel Yamins}$^{1,3}$, \and {\large \bf Michael C.~Frank}$^1$ \\ 
+    {\large \bf Michael Lingelbach}$^{1,3}$, {\large \bf Daniel M. Bear}$^{1,3}$, {\large \bf Daniel L. K. Yamins}$^{1,3}$, \and {\large \bf Michael C.~Frank}$^1$ \\ 
     $^1$Department of Psychology, Stanford University \\

### 2021-06-03 analysis/exp3_analysis.Rmd
exp3 analysis start

---
title: 'Experiment 3: ratings'
author: "George"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
library(png)
library(grid)
library(ggplot2)
library(xtable)
require(here)
require(tidyverse)
require(tidyboot)
library(apa) # for generating APA-style text to report statistical tests
library(ggpubr)
require(gridExtra)
require(papaja)
require(kableExtra)
```

## Load Data

```{r pressure, echo=FALSE}

load(file=here("paper/processed_data.RData"))

int_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Intestingness.csv")) 
lik_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Likelihood.csv"))

```

## Clean data

```{r}
install.packages("qualtRics")
```

### 2021-06-03 analysis/exp3_analysis.Rmd
making summary tables

@@
 require(kableExtra)
+require(qualtRics)
 ```
@@
 ```{r pressure, echo=FALSE}
-
+# Preregistration: https://docs.google.com/document/d/10iQ80L4K9PSa8yINPcjURj7xl10hXxzFHqtsS3DnsII/edit
 load(file=here("paper/processed_data.RData"))
 
-int_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Intestingness.csv")) 
-lik_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Likelihood.csv"))
+int_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Intestingness.csv")) %>% 
+  select(-`c1-14a`, -`c2-21a`, -`c3-22a`, -`c4-28a`, -`Q9`, -`Q8_1`)
+lik_dat <- read_csv(here("analysis/data_exp3/curiodrop V2 data - Likelihood.csv")) %>%
+  select(-`c1-14a`, -`c2-21a`, -`c3-22a`, -`c4-28a`, -`Q9`, -`Q8_1`)
 
+new_col_names = unlist(int_dat[1,])
+new_col_names[1:2] = c("Exclusion","SC0")
+new_col_names[length(new_col_names)] = "subjID"
+names(int_dat) = new_col_names
+names(lik_dat) = new_col_names
+
+int_dat = int_dat[2:nrow(int_dat),]
+lik_dat = lik_dat[2:nrow(lik_dat),]
 ```
@@
 ```{r}
-install.packages("qualtRics")
+# ToDo: count exclusions
+int_dat <- int_dat %>% filter(is.na(Exclusion))
+
+lik_dat <- lik_dat %>% filter(is.na(Exclusion))
 ```
+
+# Pivot
+
+```{r}
+int_long <- int_dat %>% relocate(subjID) %>% # SC0 = score of catch trials
+  pivot_longer(cols=4:ncol(int_dat), names_to="trial", values_to = "rating") %>%
+  separate(col=trial, sep='-', into=c("drop","choice")) %>% select(-Exclusion) %>%
+  rename(catch_trials_correct=`SC0`)
+
+lik_long <- lik_dat %>% relocate(subjID) %>%
+  pivot_longer(cols=4:ncol(int_dat), names_to="trial", values_to = "rating") %>%
+  separate(col=trial, sep='-', into=c("drop","choice")) %>% select(-Exclusion) %>%
+  filter(!is.na(rating))
+```
+
+## Data inspection
+
+```{r}
+table(int_long$subjID)
+table(lik_long$subjID)
+
+sum(is.na(int_long$rating))
+sum(is.na(lik_long$rating))
+```
+
+## Summarize Choice Data
+
+```{r}
+adult_agg <- adult_long %>% group_by(drop, target, relation) %>%
+  summarize(chose_target = mean(chose_target)) # do we want raw counts for chose target vs. foil?
+# for trial 1, 70% chose target (30% chose distractor)
+
+child_agg <- child_long %>% group_by(drop, target, relation) %>%
+  summarize(chose_target = mean(chose_target))
+```
+
+## Summarize Ratings Data
+
+```{r}
+lik_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
+  group_by(drop, choice) %>%
+  summarise(likelihood = mean(rating))
+
+int_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
+  group_by(drop, choice) %>%
+  summarise(interest = mean(rating)) 
+# also want ratings scaled 0-1?
+```

### 2021-06-04 analysis/exp3_analysis.Rmd
exp 3 analysis

@@
 title: 'Experiment 3: ratings'
-author: "George"
+author: "George, Sama, and Mike"
 date: "6/3/2021"
@@
 require(kableExtra)
-require(qualtRics)
+#require(qualtRics)
+require(lmerTest)
+require(ggpubr)
 ```
@@
 sum(is.na(lik_long$rating))
+
 ```
@@
 ```{r}
+#combos = adult_long %>% distinct(drop, choice, target)
+distractors = c("trig prism", "trig prism", "octahedron", "sphere", "octahedron", "pyramid", "pyramid", "sphere", "sphere", "pyramid", "octahedron", "dumbbell", "dumbbell", "sphere", "pentagon", "cone", "octahedron", "dumbbell", "dumbbell", "cone")
+
 adult_agg <- adult_long %>% group_by(drop, target, relation) %>%
-  summarize(chose_target = mean(chose_target)) # do we want raw counts for chose target vs. foil?
+  summarize(chose_target = mean(chose_target))
+
+adult_agg$distractor = distractors
+  # do we want raw counts for chose target vs. foil?
 # for trial 1, 70% chose target (30% chose distractor)
@@
   summarize(chose_target = mean(chose_target))
+
+child_agg$distractor = distractors
 ```
@@
   group_by(drop, choice) %>%
-  summarise(likelihood = mean(rating))
+  summarise(likelihood = mean(rating) - 1) # shift from 1-6 to 0-5
 
-int_agg <- lik_long %>% mutate(rating = as.numeric(rating)) %>%
+int_agg <- int_long %>% mutate(rating = as.numeric(rating)) %>%
   group_by(drop, choice) %>%
-  summarise(interest = mean(rating)) 
+  summarise(interest = mean(rating) - 1) 
 # also want ratings scaled 0-1?
 ```
+
+## Merge ratings with adults' drop choices
+
+```{r}
+adult_agg <- adult_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
+  rename(target_likelihood = likelihood) %>%
+  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
+  rename(distractor_likelihood = likelihood)
+
+adult_agg <- adult_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
+  rename(target_interest = interest) %>%
+  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
+  rename(distractor_interest = interest)
+
+adult_agg <- adult_agg %>% 
+  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
+         prop_target_interest = target_interest / (target_interest + distractor_interest))
+```
+
+## Merge ratings with children's drop choices
+
+```{r}
+child_agg <- child_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
+  rename(target_likelihood = likelihood) %>%
+  left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
+  rename(distractor_likelihood = likelihood)
+
+child_agg <- child_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
+  rename(target_interest = interest) %>%
+  left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
+  rename(distractor_interest = interest)
+
+child_agg <- child_agg %>% 
+  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
+         prop_target_interest = target_interest / (target_interest + distractor_interest))
+```
+
+## Compare adult choice proportions vs. likelihood proportions
+
+Regression:
+
+```{r}
+m_lik <- lm(chose_target ~ relation * prop_target_likelihood, data=adult_agg)
+m_int <- lm(chose_target ~ relation * prop_target_interest, data=adult_agg)
+summary(m_lik) # Rsq = .63
+summary(m_int) # Rsq = .84
+anova(m_lik, m_int)
+
+m3 <- lm(chose_target ~ relation * prop_target_likelihood + relation * prop_target_interest, data=adult_agg)
+summary(m3)
+```
+
+```{r}
+p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
+  xlab("Proportion of Adults Choosing Target") +
+  ylab("Luce choice of Target vs. Distractor Likelihood") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  stat_cor(method = "pearson")
+
+p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
+  xlab("Proportion of Adults Choosing Target") +
+  ylab("Luce choice of Target vs. Distractor Interestingness") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  stat_cor(method = "pearson")
+
+ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
+```

### 2021-06-04 analysis/exp3_analysis.Rmd
added child comparison graphs

@@
 child_agg <- child_long %>% group_by(drop, target, relation) %>%
-  summarize(chose_target = mean(chose_target))
+  summarize(chose_target = mean(chose_target, na.rm=T))
 
@@
 
-## Compare adult choice proportions vs. likelihood proportions
+## Compare adult choices to ratings-derived proportions
 
@@
 ```
+
+## Compare children's choices to ratings-derived proportions
+
+```{r}
+p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
+  xlab("Proportion of Adults Choosing Target") +
+  ylab("Luce choice of Target vs. Distractor Likelihood") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  stat_cor(method = "pearson")
+
+p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
+  xlab("Proportion of Adults Choosing Target") +
+  ylab("Luce choice of Target vs. Distractor Interestingness") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  stat_cor(method = "pearson")
+
+ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
+```

### 2021-06-05 analysis/exp3_analysis.Rmd
overall R^2 on plots

@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  stat_cor(method = "pearson")
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_likelihood, 
+               label = paste(..rr.label.., sep = "~`,`~")))
 
@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  stat_cor(method = "pearson")
+  #stat_cor(method = "pearson")
+  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_interest, 
+               label = paste(..rr.label.., sep = "~`,`~")))
 

### 2021-06-07 analysis/exp3_analysis.Rmd
added ratingscomparison to physics support model

@@
 ```
+
+## Compare Likelihood Ratings to Physics Models
+
+```{r}
+load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
+# load(here("models/support_probability_fit_df.RData"))
+
+#mdat %>% select(drop, target, relation, trial, support_probability) %>%
+#  pivot_wider(id_cols=trial, names_from=trial, values_from=support_probability)
+supp_prob <- mdat %>% select(drop, target, relation, support_probability)
+
+trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
+  left_join(supp_prob, by=c("drop","target","relation")) %>%
+  rename(targ_supp_prob = support_probability) %>%
+  left_join(supp_prob, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
+  rename(dist_supp_prob = support_probability) %>%
+  mutate(prop_target_supp = (targ_supp_prob) / (targ_supp_prob + dist_supp_prob + 1e-5))
+
+adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
+  ggplot(aes(x=prop_target_supp, y=prop_target_likelihood, color=relation)) + geom_point(alpha=.8) +
+  xlab("Proportion Target Support in Model") +
+  ylab("Luce choice of Target vs. Distractor Likelihood") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_target_likelihood, 
+               label = paste(..rr.label.., sep = "~`,`~")))
+```

### 2021-06-07 analysis/exp3_analysis.Rmd
added data tables

--- 2021-06-04 analysis/exp3_analysis.Rmd
@@
 require(ggpubr)
+require(DT)
 ```
@@
 # also want ratings scaled 0-1?
+
+results_table <- lik_agg %>% left_join(int_agg) %>%
+  arrange(desc(likelihood))
+
+datatable(results_table) %>% formatRound(columns=c("likelihood","interest"), digits=3)
 ```
@@
 adult_agg <- adult_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
-  rename(target_likelihood = likelihood) %>%
+  rename(targ_lik = likelihood) %>%
   left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
-  rename(distractor_likelihood = likelihood)
+  rename(dist_lik = likelihood)
 
 adult_agg <- adult_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
-  rename(target_interest = interest) %>%
+  rename(targ_int = interest) %>%
   left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
-  rename(distractor_interest = interest)
+  rename(dist_int = interest)
 
 adult_agg <- adult_agg %>% 
-  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
-         prop_target_interest = target_interest / (target_interest + distractor_interest))
+  mutate(prop_targ_lik = targ_lik / (targ_lik + dist_lik),
+         prop_targ_int = targ_int / (targ_int + dist_int))
 ```
@@
 child_agg <- child_agg %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice")) %>%
-  rename(target_likelihood = likelihood) %>%
+  rename(targ_lik = likelihood) %>%
   left_join(lik_agg, by=c("drop"="drop", "distractor"="choice")) %>%
-  rename(distractor_likelihood = likelihood)
+  rename(dist_lik = likelihood)
 
 child_agg <- child_agg %>% left_join(int_agg, by=c("drop"="drop", "target"="choice")) %>%
-  rename(target_interest = interest) %>%
+  rename(targ_int = interest) %>%
   left_join(int_agg, by=c("drop"="drop", "distractor"="choice")) %>%
-  rename(distractor_interest = interest)
+  rename(dist_int = interest)
 
 child_agg <- child_agg %>% 
-  mutate(prop_target_likelihood = target_likelihood / (target_likelihood + distractor_likelihood),
-         prop_target_interest = target_interest / (target_interest + distractor_interest))
+  mutate(prop_targ_lik = targ_lik / (targ_lik + dist_lik),
+         prop_targ_int = targ_int / (targ_int + dist_int))
+```
+
+## Adult Choices vs. Ratings Table
+
+```{r}
+adult_agg %>% relocate(relation) %>% 
+  relocate(distractor, .after=target) %>% 
+  relocate(prop_targ_lik, .after=dist_lik) %>%
+  DT::datatable() %>% 
+  formatRound(columns=c("chose_target","targ_lik","dist_lik",
+                        "targ_int","dist_int","prop_targ_lik",
+                        "prop_targ_int"), digits=3)
 ```
@@
 ```{r}
-m_lik <- lm(chose_target ~ relation * prop_target_likelihood, data=adult_agg)
-m_int <- lm(chose_target ~ relation * prop_target_interest, data=adult_agg)
+m_lik <- lm(chose_target ~ relation * prop_targ_lik, data=adult_agg)
+m_int <- lm(chose_target ~ relation * prop_targ_int, data=adult_agg)
 summary(m_lik) # Rsq = .63
@@
 
-m3 <- lm(chose_target ~ relation * prop_target_likelihood + relation * prop_target_interest, data=adult_agg)
+m3 <- lm(chose_target ~ relation * prop_targ_lik + relation * prop_targ_int, data=adult_agg)
 summary(m3)
@@
 
-```{r}
-p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
+```{r, fig.width=7.0, fig.height=3.8}
+p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_targ_lik, color=relation)) + geom_point() +
   xlab("Proportion of Adults Choosing Target") +
@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  stat_cor(method = "pearson")
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_lik, 
+               label = paste(..rr.label.., sep = "~`,`~")))
 
-p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
+p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_targ_int, color=relation)) + geom_point() +
   xlab("Proportion of Adults Choosing Target") +
@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  stat_cor(method = "pearson")
+  #stat_cor(method = "pearson")
+  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_int, 
+               label = paste(..rr.label.., sep = "~`,`~")))
 
@@
 
-```{r}
-p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
-  xlab("Proportion of Adults Choosing Target") +
+```{r, fig.width=7.0, fig.height=3.8}
+p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_targ_lik, color=relation)) + geom_point() +
+  xlab("Proportion of Children Choosing Target") +
   ylab("Luce choice of Target vs. Distractor Likelihood") +
@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  stat_cor(method = "pearson")
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_targ_lik, 
+               label = paste(..rr.label.., sep = "~`,`~")))
 
-p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
-  xlab("Proportion of Adults Choosing Target") +
+p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_targ_int, color=relation)) + geom_point() +
+  xlab("Proportion of Children Choosing Target") +
   ylab("Luce choice of Target vs. Distractor Interestingness") +
@@
 ```
+
+## Compare Likelihood Ratings to Physics Models
+
+```{r, fig.width=7.0, fig.height=3.8}
+load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
+# load(here("models/support_probability_fit_df.RData"))
+
+# compare to support probability
+supp_prob <- mdat %>% select(drop, target, relation, support_probability)
+
+trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
+  left_join(supp_prob, by=c("drop","target","relation")) %>%
+  rename(targ_supp_prob = support_probability) %>%
+  left_join(supp_prob, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
+  rename(dist_supp_prob = support_probability) %>%
+  mutate(prop_target_supp = (targ_supp_prob) / (targ_supp_prob + dist_supp_prob + 1e-5))
+
+p1 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
+  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
+  xlab("Proportion Target Support in Model") +
+  ylab("Luce choice of Target vs. Distractor Likelihood") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
+               label = paste(..rr.label.., sep = "~`,`~")))
+
+## compare to support sharpness
+supp_tmp <- mdat %>% select(drop, target, relation, support_std)
+
+trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
+  left_join(supp_tmp, by=c("drop","target","relation")) %>%
+  rename(targ_supp_std = support_std) %>%
+  left_join(supp_tmp, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
+  rename(dist_supp_std = support_std) %>%
+  mutate(prop_target_supp = (targ_supp_std) / (targ_supp_std + dist_supp_std + 1e-5))
+
+p2 <- adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
+  ggplot(aes(x=prop_target_supp, y=prop_targ_lik, color=relation)) + geom_point(alpha=.8) +
+  xlab("Prop. Target Support SD in Model") +
+  ylab("Luce choice of Target vs. Distractor Likelihood") +
+  xlim(0,1) + ylim(0,1) + theme_classic() +
+  geom_abline(slope=1, intercept=0, linetype="dashed") +
+  #stat_cor(method = "pearson") 
+  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
+               label = paste(..rr.label.., sep = "~`,`~")))
+
+ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
+```

### 2021-06-07 analysis/exp3_analysis.Rmd
directly compare model vs. likelihood ratings

@@
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+## Load packages
 
@@
   geom_abline(slope=1, intercept=0, linetype="dashed") +
-  #stat_cor(method = "pearson") 
   stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_targ_lik, 
@@
 ```
+
+## Directly compare ratings to model probs
+
+```{r}
+mdat <- mdat %>% left_join(lik_agg, by=c("drop"="drop", "target"="choice"))
+
+p1 <-mdat %>% ggplot(aes(x=likelihood, y=support_probability, color=relation)) +
+  geom_point(alpha=.7) + theme_classic() + xlab("Adults' Mean Likelihood Rating") +
+  stat_cor(inherit.aes = F, aes(x=likelihood, y=support_probability, 
+               label = paste(..rr.label.., sep = "~`,`~")))
+
+p2 <- mdat %>% ggplot(aes(x=likelihood, y=support_std, color=relation)) +
+  geom_point(alpha=.7) + theme_classic() + xlab("Adults' Mean Likelihood Rating") +
+  stat_cor(inherit.aes = F, aes(x=likelihood, y=support_std, 
+               label = paste(..rr.label.., sep = "~`,`~")))
+
+ggpubr::ggarrange(p1, p2, nrow=1, common.legend = T)
+```
+
+Other feature correlations
+
+```{r}
+with(mdat, cor(likelihood, support_probability)) # r=.75
+with(mdat, cor(likelihood, support_std)) # .77
+with(mdat, cor(likelihood, support_sharpness_accuracy_mean)) # .496
+with(mdat, cor(likelihood, support_response_linearity_r)) # .48
+with(mdat, cor(likelihood, support_response_linearity_pv)) # .53
+```
